### 2016-12-29 doc/ms.tex
back up

%%
%% Beginning of file 'sample61.tex'
%%
%% Modified 2016 September
%%
%% This is a sample manuscript marked up using the
%% AASTeX v6.1 LaTeX 2e macros.
%%
%% AASTeX is now based on Alexey Vikhlinin's emulateapj.cls 
%% (Copyright 2000-2015).  See the classfile for details.

%% AASTeX requires revtex4-1.cls (http://publish.aps.org/revtex4/) and
%% other external packages (latexsym, graphicx, amssymb, longtable, and epsf).
%% All of these external packages should already be present in the modern TeX 
%% distributions.  If not they can also be obtained at www.ctan.org.

%% The first piece of markup in an AASTeX v6.x document is the \documentclass
%% command. LaTeX will ignore any data that comes before this command. The 
%% documentclass can take an optional argument to modify the output style.
%% The command below calls the preprint style  which will produce a tightly 
%% typeset, one-column, single-spaced document.  It is the default and thus
%% does not need to be explicitly stated.
%%
%%
%% using aastex version 6.1
\documentclass[twocolumn]{aastex61}

%% The default is a single spaced, 10 point font, single spaced article.
%% There are 5 other style options available via an optional argument. They
%% can be envoked like this:
%%
%% \documentclass[argument]{aastex61}
%% 
%% where the arguement options are:
%%
%%  twocolumn   : two text columns, 10 point font, single spaced article.
%%                This is the most compact and represent the final published
%%                derived PDF copy of the accepted manuscript from the publisher
%%  manuscript  : one text column, 12 point font, double spaced article.
%%  preprint    : one text column, 12 point font, single spaced article.  
%%  preprint2   : two text columns, 12 point font, single spaced article.
%%  modern      : a stylish, single text column, 12 point font, article with
%% 		  wider left and right margins. This uses the Daniel
%% 		  Foreman-Mackey and David Hogg design.
%%
%% Note that you can submit to the AAS Journals in any of these 6 styles.
%%
%% There are other optional arguments one can envoke to allow other stylistic
%% actions. The available options are:
%%
%%  astrosymb    : Loads Astrosymb font and define \astrocommands. 
%%  tighten      : Makes baselineskip slightly smaller, only works with 
%%                 the twocolumn substyle.
%%  times        : uses times font instead of the default
%%  linenumbers  : turn on lineno package.
%%  trackchanges : required to see the revision mark up and print its output
%%  longauthor   : Do not use the more compressed footnote style (default) for 
%%                 the author/collaboration/affiliations. Instead print all
%%                 affiliation information after each name. Creates a much
%%                 long author list but may be desirable for short author papers
%%
%% these can be used in any combination, e.g.
%%
%% \documentclass[twocolumn,linenumbers,trackchanges]{aastex61}

%% AASTeX v6.* now includes \hyperref support. While we have built in specific
%% defaults into the classfile you can manually override them with the
%% \hypersetup command. For example,
%%
%%\hypersetup{linkcolor=red,citecolor=green,filecolor=cyan,urlcolor=magenta}
%%
%% will change the color of the internal links to red, the links to the
%% bibliography to green, the file links to cyan, and the external links to
%% magenta. Additional information on \hyperref options can be found here:
%% https://www.tug.org/applications/hyperref/manual.html#x1-40003

%% If you want to create your own macros, you can do so
%% using \newcommand. Your macros should appear before
%% the \begin{document} command.
%%
\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}
\newcommand{\sm}{M_\odot}
\newcommand{\sr}{R_\odot}

%% Reintroduced the \received and \accepted commands from AASTeX v5.2
\received{\today}
\revised{\today}
\accepted{\today}
%% Command to document which AAS Journal the manuscript was submitted to.
%% Adds "Submitted to " the arguement.
\submitjournal{ApJ}

%% Mark up commands to limit the number of authors on the front page.
%% Note that in AASTeX v6.1 a \collaboration call (see below) counts as
%% an author in this case.
%
%\AuthorCollaborationLimit=3
%
%% Will only show Schwarz, Muench and "the AAS Journals Data Scientist 
%% collaboration" on the front page of this example manuscript.
%%
%% Note that all of the author will be shown in the published article.
%% This feature is meant to be used prior to acceptance to make the
%% front end of a long author article more manageable. Please do not use
%% this functionality for manuscripts with less than 20 authors. Conversely,
%% please do use this when the number of authors exceeds 40.
%%
%% Use \allauthors at the manuscript end to show the full author list.
%% This command should only be used with \AuthorCollaborationLimit is used.

%% The following command can be used to set the latex table counters.  It
%% is needed in this document because it uses a mix of latex tabular and
%% AASTeX deluxetables.  In general it should not be needed.
%\setcounter{table}{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% The following section outlines numerous optional output that
%% can be displayed in the front matter or as running meta-data.
%%
%% If you wish, you may supply running head information, although
%% this information may be modified by the editorial offices.
\shorttitle{iPTF16abc}
\shortauthors{Cao et al.}
%%
%% You can add a light gray and diagonal water-mark to the first page 
%% with this command:
\watermark{DRAFT}
%% where "text", e.g. DRAFT, is the text to appear.  If the text is 
%% long you can control the water-mark size with:
%  \setwatermarkfontsize{dimension}
%% where dimension is any recognized LaTeX dimension, e.g. pt, in, etc.
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% The following section defines new commands for comments from co-authors
%%
\newcommand{\ycao}[1]{{\color{red} ycao: {#1}}}
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% This is the end of the preamble.  Indicate the beginning of the
%% manuscript itself with \begin{document}.

\begin{document}

\title{iPTF16abc}

%% LaTeX will automatically break titles if they run longer than
%% one line. However, you may use \\ to force a line break if
%% you desire. In v6.1 you can include a footnote in the title.

%% A significant change from earlier AASTEX versions is in the structure for 
%% calling author and affilations. The change was necessary to implement 
%% autoindexing of affilations which prior was a manual process that could 
%% easily be tedious in large author manuscripts.
%%
%% The \author command is the same as before except it now takes an optional
%% arguement which is the 16 digit ORCID. The syntax is:
%% \author[xxxx-xxxx-xxxx-xxxx]{Author Name}
%%
%% This will hyperlink the author name to the author's ORCID page. Note that
%% during compilation, LaTeX will do some limited checking of the format of
%% the ID to make sure it is valid.
%%
%% Use \affiliation for affiliation information. The old \affil is now aliased
%% to \affiliation. AASTeX v6.1 will automatically index these in the header.
%% When a duplicate is found its index will be the same as its previous entry.
%%
%% Note that \altaffilmark and \altaffiltext have been removed and thus 
%% can not be used to document secondary affiliations. If they are used latex
%% will issue a specific error message and quit. Please use multiple 
%% \affiliation calls for to document more than one affiliation.
%%
%% The new \altaffiliation can be used to indicate some secondary information
%% such as fellowships. This command produces a non-numeric footnote that is
%% set away from the numeric \affiliation footnotes.  NOTE that if an
%% \altaffiliation command is used it must come BEFORE the \affiliation call,
%% right after the \author command, in order to place the footnotes in
%% the proper location.
%%
%% Use \email to set provide email addresses. Each \email will appear on its
%% own line so you can put multiple email address in one \email call. A new
%% \correspondingauthor command is available in V6.1 to identify the
%% corresponding author of the manuscript. It is the author's responsibility
%% to make sure this name is also in the author list.
%%
%% While authors can be grouped inside the same \author and \affiliation
%% commands it is better to have a single author for each. This allows for
%% one to exploit all the new benefits and should make book-keeping easier.
%%
%% If done correctly the peer review system will be able to
%% automatically put the author and affiliation information from the manuscript
%% and save the corresponding author the trouble of entering it by hand.

\correspondingauthor{Yi Cao}
\email{ycao16@uw.edu}

\author[0000-0002-8036-8491]{Yi Cao}
\affil{eScience Institute and Astronomy Department, University of Washington,
  Seattle, WA 98195}

\author{Friends}
\affil{the intermediate Palomar Transient Factory}

%% Note that the \and command from previous versions of AASTeX is now
%% depreciated in this version as it is no longer necessary. AASTeX 
%% automatically takes care of all commas and "and"s between authors names.

%% AASTeX 6.1 has the new \collaboration and \nocollaboration commands to
%% provide the collaboration status of a group of authors. These commands 
%% can be used either before or after the list of corresponding authors. The
%% argument for \collaboration is the collaboration identifier. Authors are
%% encouraged to surround collaboration identifiers with ()s. The 
%% \nocollaboration command takes no argument and exists to indicate that
%% the nearby authors are not part of surrounding collaborations.

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}

  In this paper, we present observations of a young normal Type Ia supernova
  iPTF16abc. Our analysis shows that: blabla ...

\end{abstract}

%% Keywords should appear after the \end{abstract} command. 
%% See the online documentation for the full list of available subject
%% keywords and the rules for their use.
\keywords{methods: observational --- supernovae: individual (iPTF16abc)}

%% From the front matter, we move on to the body of the paper.
%% Sections are demarcated by \section and \subsection, respectively.
%% Observe the use of the LaTeX \label
%% command after the \subsection to give a symbolic KEY to the
%% subsection for cross-referencing in a \ref command.
%% You can use LaTeX's \ref and \label commands to keep track of
%% cross-references to sections, equations, tables, and figures.
%% That way, if you change the order of any elements, LaTeX will
%% automatically renumber them.

%% We recommend that authors also use the natbib \citep
%% and \citet commands to identify citations.  The citations are
%% tied to the reference list via symbolic KEYs. The KEY corresponds
%% to the KEY in the \bibitem in the reference list below.

\section{Introduction}
\label{sec:intro}

Although Type Ia supernovae (SNe Ia) have been extensively used as
standardizable candles, their progenitor scenarios and explosion
physics are still in debate (see a recent review by
\citealt{2014ARA&A..52..107M}). Detailed extermely early-phase
observations are one of the most promising avenues to further
constrain this problem.

While the shock breakout of a SN Ia occurs on a sub-second timescale,
the subsequent quasi-adiabatic expanding and cooling of the unbinded
ejecta produces thermal emissions that can be used to infer the
original size of the exploding star
\citep{2010ApJ...708..598P,2011ApJ...728...63R}. Comparing models of
these cooling emissions to the earliest-phase data of SN2011fe,
\citet{2012ApJ...744L..17B} concluded that the radius of the
progenitor star is $\lesssim0.01\sr$ where $\sr$ is the solar
radius. Combining this size constraint and the measured ejecta mass to
derive the mean density of the progenitor star, we confirmed that the
progenitor star is compact and degenerate. Admittedly, due to the
initial small surface area of the progenitor star, the shock cooling
emission of a SN Ia decays drastically as the ejecta expands. Given
typical parameters of a SN Ia, this thermal emission is visible from
events up to $\sim 10\,\textrm{Mpc}$ within one day of their explosions.

Another expectation from the extremely early-phase observations of a
SN Ia is the excess emission from collisions between SN ejecta and a
companion star, a natural consequence from the single-degenerate
progenitor hypothesis \citep{1973ApJ...186.1007W,2010ApJ...708.1025K}.
In a low-velocity SN Ia iPTF14atg, \citet{2015Natur.521..328C} for the
first time detected a strong and declining ultraviolet pulse within a
few days of the SN explosion which is best interpreted as the
SN-companion collision. This signature has been searched in a number
of nearby, early-phase normal SNe Ia, but most of these studies result
in no detection
\citep{2010ApJ...722.1691H,2011ApJ...741...20B,2012ApJ...744...38F,
  2012ApJ...744L..17B,2015Natur.521..332O,
  2013ApJ...778L..15Z,2015ApJ...799..106G,2016ApJ...826..144S,
  2015ApJS..221...22I}. The exception is SN2012cg which
\citet{2016ApJ...820...92M} claimed detection of blue excess in the
earliest-phase light curve and attribute it to SN-companion collision.
However, this statement is recently challenged by
\citet{2016arXiv161007601S}. In fact, it is not surprising that no
SN-companion collision has been observationally confirmed, because
only up to $\sim 10\%$ of events from the single-degenerate channel
have the preferred binary geometry for us to see the collision
signatures.

A transient, designated as iPTF16abc, was discovered by the
intermediate Palomar Transient Factory on 2016 April
$3.36$\footnote{all times in this paper are in UTC.} at
$\textrm{R.A.}=13^h34^m45.49^s$, $\textrm{Dec.}=+13^d51^m14.3^s$
(J2000) with a $g$-band magnitude of $21.31\pm0.27$
\citep{2016PASP..128k4502C,2016ATel.8907....1M}. The transient is
spatially coincident with a tidal tail of the galaxy NGC\,5221 at
100\,Mpc. No activity was detected at the same location down to
$g=22.1$\,mag on April $2.42$. Our spectroscopic follow-up compaign
classified iPTF16abc as a normal SN Ia \citep{2016ATel.8909....1C}.

This paper is organized as follows:

\section{Observations}
\label{sec:obs}

As part of the iPTF transient survey in the 2016 spring quarter, the
field of iPTF16abc was observed in $g$- or $R$-band every night by the
CFH12K camera \citep{2000SPIE.3965...58S} on the 48-inch telescope at
Palomar Observatory (P48). The images were processed by the IPAC image
subtraction and discovery pipeline which subtracts off the background
galaxy light with stacked pre-SN images and performs forced
point-spread-function (PSF) photometry at the location of the SN. The
photometry is then calibrated to the PTF photometric catalog
\citep{2012PASP..124..854O}.

After discovery, we also utilized the rainbow camera of the SED
Machine (\ycao{REF}) mounted on the 60-inch telescope at Palomar
Observatory (P60) to carry out photometric observations in $g$, $r$
and $i$ filters. The image differencing against the archival SDSS
images and forced PSF photometry on the subtracted images were
performed by the Fremling Automated Pipeline
\citep{2016A&A...593A..68F}. The photometry is also calibrated to the
SDSS catalog.

In space, \textit{Swift} observed iPTF16abc for 14 epochs, covering
from the very early phase to the post-peak phase. Aperture photometry
are carried out on the images taken by its Ultraviolet-Optical
Telescope (UVOT) with the usual procedures in the HEASoft and
corrected for the coincident loss and aperture loss. No pre-SN UVOT
image at the SN location is available in the \textit{Swift} archive.
Visual inspection to the UVOT images suggests that the background
galaxy light in the UVOT filters is probably negligible. No X-ray
emission was detected at the location of the SN by the X-ray Telescope
(XRT) in any of these for epochs.

The multi-color light curves of iPTF16abc are illustrated in Figure
\ref{fig:lightcurve}.  For convenience, all magnitudes are in the AB
system with a zero point of $3631$\,Jy in all filters.

\begin{figure*}[htb]
  \centering
  \includegraphics[width=0.95\textwidth]{lightcurve.pdf}
  \caption{Multi-band light curves of iPTF16abc are shown. Filters are
    denoted by different colors and observation instruments by
    different markers. The $t_{max}$ time is the B-band maximum
    determined by SALT2 (Section). The black ticks near the top of the
    figure shows epochs of spectroscopic observations.}
  \label{fig:lightcurve}
\end{figure*}

Spectroscopic observations of iPTF16abc were undertaken with the
Gemini Multi-Object Spectrograph (GMOS; \citealt{2004PASP..116..425H})
on the Gemini North telescope, Low-Resolution Imaging Spectrometer
(LRIS; \citealt{1995PASP..107..375O}) on the Keck-I telescope, DEep
Imaging Multi-Object Spectrograph (DEIMOS;
\citealt{2003SPIE.4841.1657F}) on the Keck-II telescope, The Andalucia
Faint Object Spectrograph and Camera (ALFOSC\footnote{ALFOSC
  instrument webpage:
  \url{http://www.not.iac.es/instruments/alfosc/}}) on the Nordic
Optical Telescope (NOT), and X-shooter \citep{2011A&A...536A.105V} and
Ultraviolet and Visual Echelle Spectrograph (UVES;
\citealt{2000SPIE.4008..534D}) on the Very Large Telescope (VLT). The
observing log is listed in Table \ref{tab:spec_obs_log} and the
low-resolution spectral sequence is shown in Figure
\ref{fig:spec_seq}.

% currently the following table and figure do not include data from LCOGT
\begin{deluxetable*}{cccccc}
  \tablecaption{Spectroscopic observations of iPTF16abc \label{tab:spec_obs_log}}
  \tablehead{
    \colhead{Observation Date} & \colhead{SN phase} & \colhead{Telescope/Instrument} &
    \colhead{Exposure Time (s)} & \colhead{Wavelength Coverage (\AA)} & \colhead{Resolution}
  }
  \startdata
  2016 April $05.88$ & $-15.8$ & Gemini-North/GMOS &     & $3500$ -- $9500$  & $1900$ \\
  2016 April $06.51$ & $-15.1$ & Keck-II/DEIMOS & $1491$ & $5500$ -- $8100$  & $2000$ \\
  2016 April $08.51$ & $-13.1$ & Keck-II/DEIMOS & $900$  & $5500$ -- $8100$  & $2000$ \\
  2016 April $10.38$ & $-11.3$ & Keck-I/LRIS    & $300$  & $3000$ -- $10000$ & $1000$ \\
  2016 April $14.20$ & $-7.5$  & VLT/XSHOOTER   &        & $3000$ -- $25000$ & $10000$ \\
  2016 April $16.??$ & $-5.?$  & VLT/UVES       &        & covers \ion{Ca}{2}\,H$+$K and \ion{Na}{1}\,D lines & $40000$ \\
  2016 April $28.??$ & $6.4$   & NOT/ALFOSC     &        & $3300$ -- $9000$  & $360$ \\
  2016 May   $10.42$ & $18.8$  & Keck-I/LRIS    & $600$  & $3000$ -- $10000$ & $1000$ \\
  2016 May   $12.03$ & $20.4$  & VLT/XSHOOTER   &        & $3000$ -- $25000$ & $10000$ \\
  \enddata
\end{deluxetable*}

\begin{figure*}[htb]
  \centering
  \includegraphics[width=0.9\textwidth]{spec_sequence.pdf}
  \caption{Low-resolution spectra of iPTF16abc are shown in the
    chronical sequence. The phases in units of days are labeled next
    to corresponding spectra. Telluric absorption bands are grayed
    out.}
  \label{fig:spec_seq}
\end{figure*}

\section{Reddening, Classification and Host Galaxy}
\label{sec:usual_staff}

\subsection{Reddening}
\label{sec:reddening}

The foreground Galactic extinctioin along the directionof iPTF16abc ha
$E(B-V)=0.0279\,\textrm{mag}$ \citep{2011ApJ...737..103S}.

The UVES spectrum of iPTF16abc shows narrow double absorption features
from \ion{Ca}{2}\,H$+$K and \ion{Na}{1}\,D lines (Figure
\ref{fig:narrow_features}), indicating two sources of absorption along
the line of sight. Fitting two Gaussian kernels to each of
the \ion{Na}{1} doublet simultaneously leads to redshifts of
$0.02313820\pm0.00000032$ and $0.02322408\pm0.00000033$. The total
equivalent widths of the \ion{Na}{1}\,D1 and D2 lines are
$0.595\pm0.009\,\textrm{\AA}$ and $0.609\pm0.008\,\textrm{\AA}$.
Using the empirical relation in \citet{2012MNRAS.426.1465P}, we derive
a total extinction of $E(B-V)=0.361\pm0.025\textrm{mag}$.

The X-shooter spectra of iPTF16abc also shows absorption features at
\ion{K}{1}\,7665\,\AA and 7699\,\AA. However, the resolution is not
high enough for the spectra to resolve the two components seen in the
profiles of \ion{Ca}{2} and \ion{Na}{1} in the UVES spectrum. The
X-shooter spectra do not show the diffusive interstellar band at
5780\,\AA as well.  Albeit some arguments (e.g.,
\citealt{2013ApJ...779...38P}), the extinction derived from
\ion{Na}{1}\,D absorption provides the best estimate in the case of
iPTF16abc.

\begin{figure}[htb]
  \centering
  \includegraphics[width=0.45\textwidth]{narrow_abs_features.pdf}
  \caption{Narrow absorption lines of iPTF16abc are shown in this
    figure. The zero velocity corresponds to the redshift of the
    apparent host NGC\,5221.}
  \label{fig:narrow_features}
\end{figure}

The \ion{Na}{1}\,D doublet are resolved in multiple spectra spanning
from pre-peak to post-peak phases. Despite the instrumental widening of
different instrument configurations, we do not detect obvious variation
in the profiles of the doublet.

\subsection{Classfication}
\label{sec:classification}

We run Supernova Identification (SNID; \citealt{2007ApJ...666.1024B})
on the low-resolution spectrum of iPTF16abc at $+18.8$ and found best
matches to normal SNe Ia. Separately the characteristic features of a
SN Ia, such as \ion{Si}{2}, \ion{S}{2}, are obviously seen in the
spectra of iPTF16abc.

The optical light curves obtained by P48 and P60, after correction for
extinction, are fitted by the SALT2 template
\citep{2007A&A...466...11G} with the \texttt{sncosmo} Python
module\footnote{The \texttt{sncosmo} module is available at
  \url{https://sncosmo.readthedocs.io/en/v1.4.x/}.}. The fitting
parameters are $t_{max}=57499.65\pm0.02$, $x_0=0.0275\pm0.0002$,
$x_1=1.200\pm0.043$, and $c=-0.3353\pm0.0054$. The best-fit model also
gives an unreddened apparent peak magnitude of
$m^*_{B}=14.4\,\textrm{mag}$ in the SN rest frame.

For convenicne, in the following anlaysis and discussion, we define
$t=MJD - 57499.65\,\textrm{days}$, i.e., the time with respect to the
best-fit $t_{max}$.

\subsection{Host Galaxy}
\label{sec:host}

After establishing iPTF16abc as a normal SN ia, we use the latest
calibration \citep{2014A&A...568A..22B} of the Phillips relation
\citep{1993ApJ...413L.105P} with $m^*_{B}$, $x_1$ and $c$ to derive a
distance modulus $\mu=34.66\pm0.03\,\textrm{mag}$, provided that the
host galaxy of iPTF16abc has a stellar mass less than $10^{10}\sm$.

The location of iPTF16abc is spatially coincident with a tidal tail of
galaxy NGC\,5221. \citet{2007A&A...465...71T} observed this galaxy in
the near-infrared and derived a distance modulus of $35.0\pm0.4\,\textrm{mag}$
from the Tully-Fisher relation. This distance modulus is consistent
with that of iPTF16abc.

Separately, \cite{1998A&AS..130..333T} observed
the 21-cm line in this galaxy and measured a redshift of $0.0233303\pm0.000027$.
The two components in the \ion{Na}{1}\,D have a relative velocity of
$-57.6\pm8.1\,\textrm{km}\,\textrm{s}^{-1}$ and
$-31.8\pm8.1\,\textrm{km}\,\textrm{s}^{-1}$, suggesting that both absorption
resources are probaly located on the tidal tail of NGC\,5221.

\section{First Light And Early Rise}
\label{sec:early_phases}

In this section, we analyze the early light curve and spectra of iPTF16abc.

\subsection{Light Curve Fit}
\label{sec:lc_fit}

In order to estimate the start time of the observed light curve, denoted as $t_0$,
we fit a power-law model
\begin{equation}
  \label{eq:broken_power_law}
  f(t) \left\{
    \begin{array}{ll}
      = 0,\ \textrm{when}\ t<t_0 \\
      \propto (t-t_0)^{\alpha},\ \textrm{when}\ t>t_0
    \end{array}
  \right.
\end{equation}
to the early-phase \textit{g}-band light curve. We experiment the
fitting procedure with different time windows and find that the light
curve between $t=-18\,\textrm{days}$ and $t=-14\,\textrm{days}$
increases approximately linearly. The best fit model of
$\alpha = 0.97$ and $t_0=-18.47$ is shown in the left panel of
Figure \ref{fig:early_lc_fit} and the join probability distribution of
$\alpha$ and $t_0$ is in the right panel of the same figure.  With the
best-fit $t_0$, our first observation was made only
$0.18\,\textrm{day}$ after the rise of the light curve.

\begin{figure*}[htb]
  \centering
  \includegraphics[width=0.45\textwidth]{early_lc.pdf}
  \includegraphics[width=0.45\textwidth]{rise_time_power_law_index.pdf}
  \caption{Broken Power low fitting to the early $g$-band light
    curve. \textit{Left:} the best-fit model of $\alpha=0.94$ and
    $t_0=-18.47\,\textrm{days}$ is illustrated against the
    data. \textit{Right:} the joint distribution of $t_0$ and
    $\alpha$. The cross marker denotes the best-fit parameters. The
    inner and outer contours represent the $68\%$ and $99.7\%$
    confidence levels.}
  \label{fig:early_lc_fit}
\end{figure*}

The \textit{g}-band light curve beyond $t=-14\,\textrm{days}$ rises
significantly faster than the best-fit model above, indicating a
larger value of $\alpha$. In fact, if we fit the light curve between
$t=-14$ and $t=-8$\,days to another power law, we find the best fit at
a power-law index of $1.40$ (Figure \ref{fig:against_sn2012cg}).

Although the early rise behavior of iPTF16abc is distinct from that of
SN2011fe \citep{2011Natur.480..344N} which follows the $t^2$ Arnett
law \citep{1982ApJ...253..785A}, we have seen rise behavior similar to
iPTF16abc (i.e., a steep initial rise followed by a more gradual and
steadier rise) in a few nearby events that were observed at extremely
young phases, such as, SN2013dy \citep{2013ApJ...778L..15Z}, SN2014J
\citep{2014ApJ...783L..24Z}, and ASASSN-14lp
\citep{2016ApJ...826..144S}.

We also note statistical studies on rise
behavior of SNe Ia (e.g., \citealt{2010ApJ...712..350H, 2011MNRAS.416.2607G,
  2012ApJ...745...44G, 2015MNRAS.446.3895F}) which suggest a power-law
index $\gtrapprox2$. However, these studies are not sensitive to SNe Ia
at extremely early phases, so the initial quasi-linear rise of iPTF16abc
is not comparable to their conclusions. On the other hand, the subsequent
$t^{1.40}$ rise of iPTF16abc is roughly consistent with these samples.

\subsection{Expansion Velocity Fit}
\label{sec:early_vel}

As pointed out by \citet{2014ApJ...784...85P}, if a SN light curve is
purely powered by radioactive decay of $^{56}$Ni, the SN may
experience a dark period between the explosion time of the SN
$t_{exp}$ and the rise time of its light curve $t_0$, because it takes
time for radioactive energy to diffuse from where $^{56}$Ni is
deposited in the ejecta and the SN photosphere. Therefore,
\citet{2014ApJ...784...85P} suggests to use the early-phase spectra to
measure line velocities and then estimate $t_{exp}$ by assuming that
$v\propto (t-t_{exp})^{-0.22}$.

We follow the same procedure and
measure the velocities of the \ion{Si}{2}\,6355 line. Because we do
not see signals of multiple velocity components in the
\ion{Si}{2}\,6355 line, and because the \ion{Si}{2}\,6355 line is
partially blended with the \ion{C}{1}\,6580 line, we fit two gaussian
kernels and a linear term simultaneously to spectra between about
6100\,\AA and about 6600\,\AA in the rest frame. Then the velocity is
measured at the minimum of the Gaussian kernel that corresponds to the
\ion{Si}{2} feature.

\begin{figure*}[htb]
  \centering
  \includegraphics[width=0.45\textwidth]{exp_date_chi2.pdf}
  \includegraphics[width=0.45\textwidth]{SiIIVelocity.pdf}
  \caption{Constraints on $t_{exp}$ from fitting the velocity
    evolution of \ion{Si}{2}. \textit{Left panel:} the dashed, solid
    and dash-dotted curves show $\chi^2$ for fitting power laws with
    indices $-0.20$, $-0.22$ and $-0.24$, respectively. The red
    vertical line and the orange region indicate $t_0$ and its
    3-$\sigma$ confidence interval from Section
    \ref{sec:lc_fit}. \textit{Right panel:} Observed \ion{Si}{2}\,6355
    velocities with the best-fit power-law velocity with an index of
    $-0.22$.}
  \label{fig:velocity_t_exp}
\end{figure*}

The expansion velocity fit (Figure \ref{fig:velocity_t_exp}) shows
that the best-fit explosion time $t_{exp}=-17.95\,\textrm{days}$ with
a 3-$\sigma$ confidence interval between $-17.25\,\textrm{days}$ and
$-18.65\,\textrm{days}$.

We further test our assumption $v\propto (t-t_{exp})^{-0.22}$ by
altering the power-law index to $-0.20$ and $-0.24$ (Figure
\ref{fig:velocity_t_exp}).  The best-fit value of $t_0$ varies within
the 3-$\sigma$ confidence interval and the $\chi^2$ value of the
best-fit model varies very little. This test verifies the robustness
of the assumed power-law index of $-0.22$.

Comparing $t_{exp}$ and $t_0$ (Section \ref{sec:lc_fit}), we conclude
that the dark phase of the SN, if exists, is very brief. In the
following analysis, it is reasonable to assume $t_{exp}\simeq t_0$.

\subsection{Light Curve Energy Resources}
\label{sec:lc_energy}

The early portion of a SN light curve may have multiple resources: SN
shockbreakout, SN-companion collision, and radioactive activity. Since
each provides interesting constraints on the progenitor properties, we
explore all the three posibilities.

First, the shock breakout of a SN Ia lasts for a fraction of a second
due to the small size of the exploding star. However, the subsequent
cooling phase may last longer (e.g., \citealt{2010ApJ...708..598P}).
Following the analysis of SN2011fe in \citet{2012ApJ...744L..17B}, we
compare the early-phase \textit{g}-band light curve of iPTF16abc with
two cooling models \citep{2011ApJ...728...63R, 2010ApJ...708..598P}
and reach a not very constraining conclusion that the radius of the
progenitor star of iPTF16abc should be $<1\sr$. In fact, the cooling
emission is negligible at the time of the first detection of iPTF16abc.

Second, if iPTF16abc is born in a single-degenerate channel, with a
chance of $\lesssim10\%$, we expect to see emission produced by SN
ejecta slamming into the companion. In the following we argue from a
statistical \ycao{TBW}

In the case of SN2012cg, \citet{2016ApJ...820...92M} fitted power-law
models to its light curves between $t=-14$ days and $t=-8$ days and
extrapolated backwards to illustrate excess fluxes at $t<-14$
days. The authors further attempted to explain the excess fluxes as
collisional signatures between the SN ejecta and a non-degenerate
companion \citep{2010ApJ...708.1025K}. If we perform the same practice
to the iPTF16abc data, then we find similar excess fluxes at earlier
phases (Figure \ref{fig:against_sn2012cg}). In fact, for any SN whose
light curve can be approximated by a broken-power law, i.e.,
\begin{equation}
  \label{eq:broken-pow}
  f(t) = t^{\alpha}(1 + t^{s(\beta - \alpha)})^{1/s}\ ,
\end{equation}
one can always fit the relative late part of the light curve with a
power law model and find an excess in the early phases.

\begin{figure}[htb]
  \centering
  \includegraphics[width=0.45\textwidth]{another_early_lc.pdf}
  \caption{The early-phase \textit{g}-band light curve of iPTF16abc is
    compared against the best-fit power-law model to the data segment
    between $t=-14$ and $t=-8$ days. Note the ``excess'' between the
    data and the model during $t=-18$ and $t=-15$ days}
  \label{fig:against_sn2012cg}
\end{figure}

As a result of the above analysis, we conclude that the early light
curve of iPTF16abc is probably powered dominantly by radioactive decay
of $^{56}$Ni.  According to calculations in
\citet{2016ApJ...826...96P}, when synthesized $^{56}$Ni is mixed
sufficiently in the ejecta, the dark period is short and the initial
light curve rises quickly. In the opposite situation when $^{56}$Ni is
located deeply inside the ejecta, then the dark period can be as long
as a couple days and the initial light curve rises relatively
slowly. The fast initial rise of iPTF16abc and the negligible length
of the dark period both support that $^{56}$Ni is sufficiently mixed
in the ejecta.

\bibliographystyle{aasjournal}
\bibliography{ref}

\end{document}

### 2016-12-29 data/filters/SEDm/make_eff.py

@@ -1,0 +1,28 @@
+#!/usr/bin/env python
+from astropy.io import ascii
+from astropy.table import Table
+import numpy as np
+from scipy.interpolate import interp1d
+
+qedata = ascii.read('QE.txt')
+qe = interp1d(qedata['wl'],qedata['QE-55C'],kind='cubic')
+
+bands = ['u','g','r','i'] #,'z','zs','y']
+for band in bands :
+    data = ascii.read("%sband.csv"%(band))
+    w = data['Wavelength (nm)']
+    mask = (w>=qedata['wl'].min() )*(w<=qedata['wl'].max())
+    data[band][mask] *= qe(w[mask])
+    data[band][1-mask] *= 0.
+    
+    wmin,wmax = int(w.min())*10,int(w.max())*10
+    ww = np.linspace(wmin,wmax,wmax-wmin)
+    et = interp1d(w*10,data[band],kind='linear')
+    
+    
+    ot = Table([ww,et(ww)],dtype=('f8','f8'))
+    ascii.write(ot,'%sband_eff.dat'%(band),format='basic')
+ 
+ # EOF
+ 
+    

### 2017-01-02 doc/ms.tex
v0.1

@@
 
-\title{iPTF16abc}
+\title{Optifcal Observations of an Extraordinarily Young Type Ia Supernova iPTF16abc}
 
@@
 
-A transient, designated as iPTF16abc, was discovered by the
-intermediate Palomar Transient Factory on 2016 April
-$3.36$\footnote{all times in this paper are in UTC.} at
-$\textrm{R.A.}=13^h34^m45.49^s$, $\textrm{Dec.}=+13^d51^m14.3^s$
-(J2000) with a $g$-band magnitude of $21.31\pm0.27$
-\citep{2016PASP..128k4502C,2016ATel.8907....1M}. The transient is
-spatially coincident with a tidal tail of the galaxy NGC\,5221 at
-100\,Mpc. No activity was detected at the same location down to
-$g=22.1$\,mag on April $2.42$. Our spectroscopic follow-up compaign
-classified iPTF16abc as a normal SN Ia \citep{2016ATel.8909....1C}.
+More commonly, the only observed light curve of a SN Ia is purely
+powered by the radioactive decay of synthesized $^{56}$Ni. Since
+$^{56}$Ni atoms are synthesized, mixed and deposited into different
+layers inside the ejecta, the SN may experience a dark period after
+the SN shock breakout and before the radioactive energy diffuses to
+the photosphere \citep{2014ApJ...784...85P}. In the case of strong
+mixing, $^{56}$Ni energy can reach the photosphere rapidly. As such,
+the dark period is very short and the light curve shows a fast initial
+rise. In the opposite case, it may take up to a couple of days for
+the $^{56}$Ni energy to diffuse to the photosphere. The initial rise
+of the light curve is then moderate \citep{2016ApJ...826...96P}. To
+summarize, the initial rise of the light curve of a SN Ia conveys
+information on distribution of synthesized $^{56}$Ni.
 
-This paper is organized as follows:
+In this paper, we report observations of an extraordinarily young SN
+Ia iPTF16abc, which was discovered by the intermediate Palomar
+Transient Factory on 2016 April $3.36$\footnote{all times in this
+  paper are in UTC.} at $\textrm{R.A.}=13^h34^m45.49^s$,
+$\textrm{Dec.}=+13^d51^m14.3^s$ (J2000) with a $g$-band magnitude of
+$21.31\pm0.27$ \citep{2016PASP..128k4502C,2016ATel.8907....1M}. The
+transient is spatially coincident with a tidal tail of the galaxy
+NGC\,5221 at 100\,Mpc. No activity was detected at the same location
+down to $g=22.1$\,mag on April $2.42$. Our spectroscopic follow-up
+compaign classified iPTF16abc as a normal SN Ia
+\citep{2016ATel.8909....1C}.
+
+This paper is organized as follows: Section \ref{sec:obs} describes
+photometric and spectroscopic observations of iPTF16abc. Section
+\ref{sec:usual_staff} establishes that iPTF16abc is a normal SN Ia
+in NGC\,5221. Section \ref{sec:first_light} analyzes the early
+light curve and spectra.
 
@@
 \label{sec:obs}
+
+\ycao{TODO: include LCOGT data in both text and figures.}
+
+\begin{figure*}[htb]
+  \centering
+  \includegraphics[width=0.95\textwidth]{lightcurve.pdf}
+  \caption{Multi-band light curves of iPTF16abc are shown. Filters are
+    denoted by different colors and observation instruments by
+    different markers. The $t_{max}$ time is the B-band maximum
+    determined by SALT2 (Section). The black ticks near the top of the
+    figure shows epochs of spectroscopic observations.}
+  \label{fig:lightcurve}
+\end{figure*}
 
@@
 
-After discovery, we also utilized the rainbow camera of the SED
+After discovery, we utilized the rainbow camera of the SED
 Machine (\ycao{REF}) mounted on the 60-inch telescope at Palomar
-Observatory (P60) to carry out photometric observations in $g$, $r$
+Observatory (P60) to undertake photometric observations in $g$, $r$
 and $i$ filters. The image differencing against the archival SDSS
@@
 SDSS catalog.
+
+Las Cambres Observatory Global Network (LCOGT) also carry out photometric
+observations in the \textit{BVgri} filters with its 1-m telescope network.
+\ycao{Some info about data reduction}
 
@@
 system with a zero point of $3631$\,Jy in all filters.
-
-\begin{figure*}[htb]
-  \centering
-  \includegraphics[width=0.95\textwidth]{lightcurve.pdf}
-  \caption{Multi-band light curves of iPTF16abc are shown. Filters are
-    denoted by different colors and observation instruments by
-    different markers. The $t_{max}$ time is the B-band maximum
-    determined by SALT2 (Section). The black ticks near the top of the
-    figure shows epochs of spectroscopic observations.}
-  \label{fig:lightcurve}
-\end{figure*}
 
@@
 
-\begin{figure*}[htb]
+\begin{figure*}[!htb]
   \centering
@@
 
-The foreground Galactic extinctioin along the directionof iPTF16abc ha
-$E(B-V)=0.0279\,\textrm{mag}$ \citep{2011ApJ...737..103S}.
+The foreground Galactic extinctioin along the directionof iPTF16abc
+has $E(B-V)=0.0279\,\textrm{mag}$ \citep{2011ApJ...737..103S}.
 
-The UVES spectrum of iPTF16abc shows narrow double absorption features
-from \ion{Ca}{2}\,H$+$K and \ion{Na}{1}\,D lines (Figure
-\ref{fig:narrow_features}), indicating two sources of absorption along
-the line of sight. Fitting two Gaussian kernels to each of
-the \ion{Na}{1} doublet simultaneously leads to redshifts of
-$0.02313820\pm0.00000032$ and $0.02322408\pm0.00000033$. The total
-equivalent widths of the \ion{Na}{1}\,D1 and D2 lines are
-$0.595\pm0.009\,\textrm{\AA}$ and $0.609\pm0.008\,\textrm{\AA}$.
-Using the empirical relation in \citet{2012MNRAS.426.1465P}, we derive
-a total extinction of $E(B-V)=0.361\pm0.025\textrm{mag}$.
+In the highest-resolution spectrum of iPTF16abc by UVES, individual
+components of both \ion{Ca}{2}\,H$+$K and \ion{Na}{1}\,D doublets show
+double-absorption profiles (Figure \ref{fig:narrow_features}),
+indicating two sources of absorption along the line of sight. Fitting
+two Gaussian kernels to each line of the \ion{Na}{1} doublet
+simultaneously leads to redshifts of $0.02313820\pm0.00000032$ and
+$0.02322408\pm0.00000033$. The total equivalent widths of the
+\ion{Na}{1}\,D1 and D2 lines are $0.595\pm0.009\,\textrm{\AA}$ and
+$0.609\pm0.008\,\textrm{\AA}$m, respectively. Using the empirical
+relation between the equivalent width of \ion{Na}{1}\,D lines and
+reddening $E(B-V)$ \citep{2012MNRAS.426.1465P}, we derive
+$E(B-V)=0.361\pm0.025\textrm{mag}$.
 
-The X-shooter spectra of iPTF16abc also shows absorption features at
-\ion{K}{1}\,7665\,\AA and 7699\,\AA. However, the resolution is not
-high enough for the spectra to resolve the two components seen in the
-profiles of \ion{Ca}{2} and \ion{Na}{1} in the UVES spectrum. The
-X-shooter spectra do not show the diffusive interstellar band at
-5780\,\AA as well.  Albeit some arguments (e.g.,
-\citealt{2013ApJ...779...38P}), the extinction derived from
+In the X-shooter spectra of iPTF16abc, we also identify narrow
+absorption features \ion{K}{1}\,7665\,\AA and 7699\,\AA at consistent
+redshifts. However, the resolution of the X-shooter spectra is not
+fine enough to resolve the double-absorption profiles of \ion{Ca}{2}
+and \ion{Na}{1}. The X-shooter spectra do not show the diffusive
+interstellar band at 5780\,\AA as well.  Albeit some debates (e.g.,
+\citealt{2013ApJ...779...38P}), the $E(B-V)$ value derived from
 \ion{Na}{1}\,D absorption provides the best estimate in the case of
@@
 
-The \ion{Na}{1}\,D doublet are resolved in multiple spectra spanning
+The \ion{Na}{1}\,D doublet are seen in multiple spectra spanning
 from pre-peak to post-peak phases. Despite the instrumental widening of
@@
 on the low-resolution spectrum of iPTF16abc at $+18.8$ and found best
-matches to normal SNe Ia. Separately the characteristic features of a
-SN Ia, such as \ion{Si}{2}, \ion{S}{2}, are obviously seen in the
-spectra of iPTF16abc.
+matches to normal SNe Ia. In fact, the characteristic features of a SN
+Ia, such as \ion{Si}{2}, \ion{S}{2}, can be easily identified in the
+spectra of iPTF16abc (Figure \ref{fig:spec_seq}).
 
-The optical light curves obtained by P48 and P60, after correction for
-extinction, are fitted by the SALT2 template
-\citep{2007A&A...466...11G} with the \texttt{sncosmo} Python
-module\footnote{The \texttt{sncosmo} module is available at
-  \url{https://sncosmo.readthedocs.io/en/v1.4.x/}.}. The fitting
-parameters are $t_{max}=57499.65\pm0.02$, $x_0=0.0275\pm0.0002$,
-$x_1=1.200\pm0.043$, and $c=-0.3353\pm0.0054$. The best-fit model also
-gives an unreddened apparent peak magnitude of
-$m^*_{B}=14.4\,\textrm{mag}$ in the SN rest frame.
+Next we standardize the light curve of iPTF16abc by feeding its P48
+and P60 light curves into the \texttt{sncosmo} module\footnote{The
+  \texttt{sncosmo} Python module is available at
+  \url{https://sncosmo.readthedocs.io/en/v1.4.x/}.} and fit a light
+curve model, which composes of the SALT2 template
+\citep{2007A&A...466...11G} modified by the line-of-sight extinction
+curve \citep{1999PASP..111...63F} with $E(B-V)$ values from Section
+\ref{sec:reddening} and $R_V=3.1$. We obtain the rest-frame
+\textit{B}-band peak time $\textrm{MJD}_{max}=57499.65\pm0.02$, the coefficient
+of the zeroth principle component $x_0=0.0275\pm0.0002$, the
+coefficient of the first principle component $x_1=1.200\pm0.043$, and
+the color term $c=-0.3353\pm0.0054$. The best-fit model also gives an
+unreddened apparent peak magnitude of $m^*_{B}=14.4\,\textrm{mag}$ in
+the SN rest frame.
 
-For convenicne, in the following anlaysis and discussion, we define
-$t=MJD - 57499.65\,\textrm{days}$, i.e., the time with respect to the
-best-fit $t_{max}$.
+For convenience, in the following sections, we define the best-fit
+value $\textrm{MJD}_{max}=57499.65$ as phase $t=0$.
 
@@
 calibration \citep{2014A&A...568A..22B} of the Phillips relation
-\citep{1993ApJ...413L.105P} with $m^*_{B}$, $x_1$ and $c$ to derive a
-distance modulus $\mu=34.66\pm0.03\,\textrm{mag}$, provided that the
-host galaxy of iPTF16abc has a stellar mass less than $10^{10}\sm$.
+\citep{1993ApJ...413L.105P} using $m^*_{B}$, $x_1$ and $c$ to derive a
+distance modulus $\mu=34.66\pm0.03\,\textrm{mag}$ to the SN, provided
+that the host galaxy of iPTF16abc has a stellar mass less than
+$10^{10}\sm$.
 
 The location of iPTF16abc is spatially coincident with a tidal tail of
-galaxy NGC\,5221. \citet{2007A&A...465...71T} observed this galaxy in
-the near-infrared and derived a distance modulus of $35.0\pm0.4\,\textrm{mag}$
-from the Tully-Fisher relation. This distance modulus is consistent
-with that of iPTF16abc.
+galaxy NGC\,5221. \citet{2007A&A...465...71T} derived a distance
+modulus of $35.0\pm0.4\,\textrm{mag}$ from the Tully-Fisher
+relation. This distance modulus is consistent with that of iPTF16abc.
 
-Separately, \cite{1998A&AS..130..333T} observed
-the 21-cm line in this galaxy and measured a redshift of $0.0233303\pm0.000027$.
-The two components in the \ion{Na}{1}\,D have a relative velocity of
+Separately, \citet{1998A&AS..130..333T} observed the 21-cm line in
+this galaxy and measured a redshift of $0.0233303\pm0.000027$.  The
+two components in the \ion{Na}{1}\,D have a relative velocity of
 $-57.6\pm8.1\,\textrm{km}\,\textrm{s}^{-1}$ and
-$-31.8\pm8.1\,\textrm{km}\,\textrm{s}^{-1}$, suggesting that both absorption
-resources are probaly located on the tidal tail of NGC\,5221.
+$-31.8\pm8.1\,\textrm{km}\,\textrm{s}^{-1}$, suggesting that both
+absorption resources are probaly located on the tidal tail of
+NGC\,5221.
 
-\section{First Light And Early Rise}
-\label{sec:early_phases}
+\section{First Light And Explosion Time}
+\label{sec:first_light}
 
-In this section, we analyze the early light curve and spectra of iPTF16abc.
+In this section, we estimate the first light and explosion time of
+iPTF16abc.
 
@@
 
-In order to estimate the start time of the observed light curve, denoted as $t_0$,
-we fit a power-law model
+Extrapolation of the earliest-phase light curve with a simple model is
+usually used to estimate the first light time. In theory,
+\citet{1982ApJ...253..785A} derived a quadratic law for an expanding
+fireball with a constant temperature. In order to account for the
+temperature change, here we utilize a power-law model
 \begin{equation}
@@
     \end{array}
-  \right.
+  \right.\ .
 \end{equation}
-to the early-phase \textit{g}-band light curve. We experiment the
-fitting procedure with different time windows and find that the light
-curve between $t=-18\,\textrm{days}$ and $t=-14\,\textrm{days}$
-increases approximately linearly. The best fit model of
-$\alpha = 0.97$ and $t_0=-18.47$ is shown in the left panel of
-Figure \ref{fig:early_lc_fit} and the join probability distribution of
-$\alpha$ and $t_0$ is in the right panel of the same figure.  With the
-best-fit $t_0$, our first observation was made only
-$0.18\,\textrm{day}$ after the rise of the light curve.
+Since the first few detections of the SN were made in the \textit{g}
+band, we perform the fit only to the \textit{g}-band light curve. We
+experiment the fitting procedure with different time windows and find
+that the SN flux between $t=-19\,\textrm{days}$ and
+$t=-15\,\textrm{days}$ rises approximately linearly. The joint
+distribution of $\alpha$ and $t_0$ for this time window is given in
+the left panel of Figure \ref{fig:early_lc_fit} and the best fit model
+with $\alpha = 0.94$ and $t_0=-18.47$ is shown in the right
+panel. With this best-fit value of $t_0$, our first observation was
+made only $0.18\,\textrm{day}$ after the first light of the SN. The
+total rise time to the \textit{B}-band peak is $18.47$ days.
 
@@
   \centering
+  \includegraphics[width=0.45\textwidth]{rise_time_power_law_index.pdf}
   \includegraphics[width=0.45\textwidth]{early_lc.pdf}
-  \includegraphics[width=0.45\textwidth]{rise_time_power_law_index.pdf}
   \caption{Broken Power low fitting to the early $g$-band light
-    curve. \textit{Left:} the best-fit model of $\alpha=0.94$ and
-    $t_0=-18.47\,\textrm{days}$ is illustrated against the
-    data. \textit{Right:} the joint distribution of $t_0$ and
+    curve.
+    \textit{Left:} the joint distribution of $t_0$ and
     $\alpha$. The cross marker denotes the best-fit parameters. The
     inner and outer contours represent the $68\%$ and $99.7\%$
-    confidence levels.}
+    confidence levels.
+    \textit{Right:} the best-fit model of $\alpha=0.94$ and
+    $t_0=-18.47\,\textrm{days}$ is illustrated against the
+    data.
+  }
   \label{fig:early_lc_fit}
@@
 
-The \textit{g}-band light curve beyond $t=-14\,\textrm{days}$ rises
+Since $t=-15\,\textrm{days}$, the \textit{g}-band light curve rises
 significantly faster than the best-fit model above, indicating a
-larger value of $\alpha$. In fact, if we fit the light curve between
-$t=-14$ and $t=-8$\,days to another power law, we find the best fit at
-a power-law index of $1.40$ (Figure \ref{fig:against_sn2012cg}).
+greater value of the power-law index $\alpha$. In fact, the
+light curve between $t=-14$ and $t=-8$\,days can be fitted with a
+power law of index $1.40$.
 
-Although the early rise behavior of iPTF16abc is distinct from that of
-SN2011fe \citep{2011Natur.480..344N} which follows the $t^2$ Arnett
-law \citep{1982ApJ...253..785A}, we have seen rise behavior similar to
-iPTF16abc (i.e., a steep initial rise followed by a more gradual and
-steadier rise) in a few nearby events that were observed at extremely
-young phases, such as, SN2013dy \citep{2013ApJ...778L..15Z}, SN2014J
-\citep{2014ApJ...783L..24Z}, and ASASSN-14lp
-\citep{2016ApJ...826..144S}.
+A more sophisticated broken power-law model has also been used to fit
+SN early-phase light curves (e.g.,
+\citealt{2013ApJ...778L..15Z,2014ApJ...783L..24Z,
+  2016arXiv161202097Z,2016arXiv161202097Z}). Our above result has
+indicates that the \textit{g}-band light curve of iPTF16abc can also
+be fitted by a broken-power law with a power index changing from
+$0.94$ to $1.40$. In fact, many young SNe, including SN2011fe
+\cite{2016arXiv161202097Z} and iPTF16abc, have early light curves that
+follow broken power-laws \citep{2016arXiv161202725Z}). Our above
+result has indicates that the \textit{g}-band light curve of iPTF16abc
+can also be fitted by a broken-power law with a power index changing
+from $0.94$ to $1.40$.
 
-We also note statistical studies on rise
-behavior of SNe Ia (e.g., \citealt{2010ApJ...712..350H, 2011MNRAS.416.2607G,
-  2012ApJ...745...44G, 2015MNRAS.446.3895F}) which suggest a power-law
-index $\gtrapprox2$. However, these studies are not sensitive to SNe Ia
-at extremely early phases, so the initial quasi-linear rise of iPTF16abc
-is not comparable to their conclusions. On the other hand, the subsequent
-$t^{1.40}$ rise of iPTF16abc is roughly consistent with these samples.
+The initial rise of a SN depends on the distribution of $^{56}$Ni
+in the ejecta. Comparing the rapid initial rise of iPTF16abc to
+theoretical calculations in \citet{2016ApJ...826...96P} suggests
+strong mixing of $^{56}$Ni in the iPTF16abc ejecta. The radioactive
+energy from $^{56}$Ni can quickly diffuse to the SN photosphere and
+power its light curve after the SN explosion.
 
@@
 
-As pointed out by \citet{2014ApJ...784...85P}, if a SN light curve is
-purely powered by radioactive decay of $^{56}$Ni, the SN may
-experience a dark period between the explosion time of the SN
-$t_{exp}$ and the rise time of its light curve $t_0$, because it takes
-time for radioactive energy to diffuse from where $^{56}$Ni is
-deposited in the ejecta and the SN photosphere. Therefore,
-\citet{2014ApJ...784...85P} suggests to use the early-phase spectra to
-measure line velocities and then estimate $t_{exp}$ by assuming that
-$v\propto (t-t_{exp})^{-0.22}$.
+The first light of a SN is not necessarily its explotion time
+$t_{exp}$.  Thanks to different deposition of $^{56}$Ni in the SN
+ejecta, as pointed out in \citet{2014ApJ...784...85P}, the SN may
+experience a dark period before the radioactive energy from the
+shallowest $^{56}$Ni layer escapes the ejecta. Therefore, 
+\citet{2014ApJ...784...85P} suggests to examine evolution of absorption
+line velocities, because the velocities do not depend on the $^{56}$Ni
+mixing and are expected to evolve roughly as $v\propto(t-t_{exp})^{-0.22}$.
 
-We follow the same procedure and
-measure the velocities of the \ion{Si}{2}\,6355 line. Because we do
-not see signals of multiple velocity components in the
-\ion{Si}{2}\,6355 line, and because the \ion{Si}{2}\,6355 line is
-partially blended with the \ion{C}{1}\,6580 line, we fit two gaussian
-kernels and a linear term simultaneously to spectra between about
-6100\,\AA and about 6600\,\AA in the rest frame. Then the velocity is
-measured at the minimum of the Gaussian kernel that corresponds to the
-\ion{Si}{2} feature.
+We focus on measuring velocities of the strongest \ion{Si}{2}\,6355
+line, as the second most commonly used \ion{Ca}{2} IR triplet is very
+weak in iPTF16abc. Visual inspection of the early-phase spectra shows
+no sign of any high-velocity component of the \ion{Si}{2} line and
+that the red wing of \ion{Si}{2} overlaps the \ion{C}{2}\,6580
+line. Therefore, we fit simultaneously two gaussian kernels for the
+two lines and a linear term to account for the continuum component.
+Then the velocities are calculated at the minimum of the \ion{Si}{2}
+gaussian kernel.
 
-\begin{figure*}[htb]
+\begin{figure*}[!thb]
   \centering
@@
 
-The expansion velocity fit (Figure \ref{fig:velocity_t_exp}) shows
-that the best-fit explosion time $t_{exp}=-17.95\,\textrm{days}$ with
-a 3-$\sigma$ confidence interval between $-17.25\,\textrm{days}$ and
-$-18.65\,\textrm{days}$.
+Fitting the measured velocities of \ion{Si}{2}\,6355 line to the
+$v\propto(t-t_{exp})^{-0.22}$ model leads to the best-fit explosion
+time $t_{exp}=-17.95\,\textrm{days}$ with a 3-$\sigma$ confidence
+interval between $-17.4\,\textrm{days}$ and $-18.3\,\textrm{days}$
+(Figure \ref{fig:velocity_t_exp}). We further test the robustness of
+a fixed power-law index by altering the index to $-0.20$ and $-0.24$
+and find consistent results within respective 3-$\sigma$ confidence
+intervals.
 
-We further test our assumption $v\propto (t-t_{exp})^{-0.22}$ by
-altering the power-law index to $-0.20$ and $-0.24$ (Figure
-\ref{fig:velocity_t_exp}).  The best-fit value of $t_0$ varies within
-the 3-$\sigma$ confidence interval and the $\chi^2$ value of the
-best-fit model varies very little. This test verifies the robustness
-of the assumed power-law index of $-0.22$.
+The derived $t_{exp}$ is roughly consistent to $t_0$ estimated in
+Section \ref{sec:lc_fit}, confirming that the dark period of iPTF16abc
+is very short. This conclusion is consistent with the inference from the
+rapid initial rise of iPTF16abc in Section \ref{sec:lc_fit}.
 
-Comparing $t_{exp}$ and $t_0$ (Section \ref{sec:lc_fit}), we conclude
-that the dark phase of the SN, if exists, is very brief. In the
-following analysis, it is reasonable to assume $t_{exp}\simeq t_0$.
+Among the several SNe with measurements of $t_{exp}$ and $t_0$
+\citep{2014ApJ...784...85P,2016ApJ...826..144S}, iPTF16abc has the
+shortest dark period and longest rise time ($18.47$ days). In
+comparison, SN2011fe is inferred to have a dark period of $\sim 1$
+day \citep{2014ApJ...784...85P} and a rise time of $17.7$ days
+\citep{2013A&A...554A..27P}; ASASSN-14lp has a dark period of a couple
+of days and a rise time of $16.94$ days. This seems to suggest that
+the time difference between SN explosion and the \textit{B}-band maximum,
+which equals to summation of the dark period and the rise time, is a
+constant for a SN Ia. This is perhaps because the \textit{B}-band maximum
+time only depends on the total amount of $^{56}$Ni.
 
-\subsection{Light Curve Energy Resources}
+\subsection{Strong and Short-Lived Carbon Features}
+\label{sec:carbon}
+
+Interestingly, the first few spectra of iPTF16abc show clear detection
+of \ion{C}{2}\,6580 and \ion{C}{2}\,7234 lines. Their velocity
+evolution is shown in Figure \ref{fig:velocity_t_exp} as well.
+
+The \ion{C}{2} lines only appear in the very early phases. The
+equivalent widths of detected \ion{C}{2}\,6580 and \ion{C}{2}\,7234
+lines are shown in Figure \ref{fig:ew}, and are compared to that of
+the \ion{Si}{2}\,6355 line. Especially in the first spectrum taken at
+$t=-15.8$ days, the \ion{C}{2} equivalent widths are stronger than
+that of \ion{Si}{2}.
+
+\begin{figure}[!htb]
+  \centering
+  \includegraphics[width=0.45\textwidth]{EW.pdf}
+  \caption{Equivalent Width of \ion{Si}{2}\,6355, \ion{C}{2}\,6580 and
+    \ion{C}{2}\,7234 lines}
+  \label{fig:ew}
+\end{figure}
+
+The strong and short-lived \ion{C}{2} features suggest that
+the outermost layers of the ejecta contain a certain amount of
+carbon which is responsible for the \ion{C}{2} absorption. The
+abundance of carbon drops dramatically into the inner layers
+of the ejecta.
+
+Carbon signatures are seen in over $1/4$ of all normal SNe Ia before
+maxima
+\citep{2011ApJ...732...30P,2012MNRAS.425.1917S,2011ApJ...743...27T},
+but the signatures are usually weak. Even in SN2011fe, the \ion{C}{2}
+features are not strong in the first spectra
+\citep{2012ApJ...752L..26P}.  The only normal SN Ia known to have
+strong \ion{C}{2} features at very early phases is SN2013dy
+\citep{2013ApJ...778L..15Z}. Unlike iPTF16abc, the equivalent widths
+of \ion{C}{2} features in SN2013dy are as large as that of
+\ion{Si}{2}\,6355.
+
+\subsection{Discussions and Physical Constraints}
 \label{sec:lc_energy}
 
-The early portion of a SN light curve may have multiple resources: SN
+The early radiation of a SN Ia may have multiple resources: SN
 shockbreakout, SN-companion collision, and radioactive activity. Since
@@
 
-First, the shock breakout of a SN Ia lasts for a fraction of a second
-due to the small size of the exploding star. However, the subsequent
-cooling phase may last longer (e.g., \citealt{2010ApJ...708..598P}).
+\subsubsection{SN Shock Breakout}
+
+The shock breakout of a SN Ia lasts for a fraction of a second due to
+the small size of the exploding star. However, the subsequent cooling
+phase may last longer (e.g., \citealt{2010ApJ...708..598P}).
 Following the analysis of SN2011fe in \citet{2012ApJ...744L..17B}, we
@@
 progenitor star of iPTF16abc should be $<1\sr$. In fact, the cooling
-emission is negligible at the time of the first detection of iPTF16abc.
+emission is negligible at the time of the first detection of
+iPTF16abc.
 
-Second, if iPTF16abc is born in a single-degenerate channel, with a
-chance of $\lesssim10\%$, we expect to see emission produced by SN
-ejecta slamming into the companion. In the following we argue from a
-statistical \ycao{TBW}
+\subsubsection{SN companion}
 
-In the case of SN2012cg, \citet{2016ApJ...820...92M} fitted power-law
-models to its light curves between $t=-14$ days and $t=-8$ days and
-extrapolated backwards to illustrate excess fluxes at $t<-14$
-days. The authors further attempted to explain the excess fluxes as
-collisional signatures between the SN ejecta and a non-degenerate
-companion \citep{2010ApJ...708.1025K}. If we perform the same practice
-to the iPTF16abc data, then we find similar excess fluxes at earlier
-phases (Figure \ref{fig:against_sn2012cg}). In fact, for any SN whose
-light curve can be approximated by a broken-power law, i.e.,
-\begin{equation}
-  \label{eq:broken-pow}
-  f(t) = t^{\alpha}(1 + t^{s(\beta - \alpha)})^{1/s}\ ,
-\end{equation}
-one can always fit the relative late part of the light curve with a
-power law model and find an excess in the early phases.
+If iPTF16abc is born in a single-degenerate channel, with an odd of
+$\lesssim10\%$, we expect to see emission produced by SN ejecta
+slamming into the companion. However, according to calculations by
+\citet{2010ApJ...708.1025K}, collision between SN ejecta and the
+companion star produces thermal emission with a spectrum that peaks
+in the ultraviolet, and the Rayleigh-Jeans tail emission in the \textit{g}
+band is very weak.
 
-\begin{figure}[htb]
+In the case of SN2012cg, in order to illustrate a blue excess in the
+early light curve, \citet{2016ApJ...820...92M} fitted a power-law
+model to its light curves between $t=-14$ days and $t=-8$ days and
+subtracted the extrapolated fluxes at early epochs. Then these authors
+attribute the excess to SN-companion collision. In our iPTF16abc, we
+follow the same procedure and also find a similar excess
+(Figure \ref{fig:against_sn2012cg}).
+
+\begin{figure}[!htb]
   \centering
@@
 
-As a result of the above analysis, we conclude that the early light
-curve of iPTF16abc is probably powered dominantly by radioactive decay
-of $^{56}$Ni.  According to calculations in
-\citet{2016ApJ...826...96P}, when synthesized $^{56}$Ni is mixed
-sufficiently in the ejecta, the dark period is short and the initial
-light curve rises quickly. In the opposite situation when $^{56}$Ni is
-located deeply inside the ejecta, then the dark period can be as long
-as a couple days and the initial light curve rises relatively
-slowly. The fast initial rise of iPTF16abc and the negligible length
-of the dark period both support that $^{56}$Ni is sufficiently mixed
-in the ejecta.
+Actually, for any early light curve that can be approximated by a
+broken power law, as long as the asymptotic power-law index near $t=0$
+is less than that at late time, one can always find such an excess
+near $t=0$. There are not many SNe that were observed at
+extraordinarily early phases. The odd that both SN2012cg and iPTF16abc
+show SN-companion collision signautres is very small.
+
+Separately, our first \textit{Swift} observation of iPTF16abc was made
+about two days after explosion. However, the ultraviolet light curve of
+iPTF16abc does not show any excess.
+
+\subsubsection{Explosion Mechanism}
+
+Our extraordinarily early observations of iPTF16abc put two constraints
+on the mechanism of the SN explosion: first, during the SN explosion,
+synthesized $^{56}$Ni should be strongly mixed in the ejecta; second,
+unburned carbon atoms are accelerated to very high velocities in the ejecta.
+In addition, the commonly seen \ion{Ca}{2} IR triplet is weak in iPTF16abc,
+implying a little amount of calsium in the ejecta.
+
+\section{Conclusion}
+\label{sec:conclusion}
+
+In this paper, we present observations of a normal Type Ia supernova
+iPTF16abc, which is located at one tidal tail of NGC\,5221. Our extraordinarily
+early-phase optical observations of this supernova show that:
+\begin{itemize}
+\item Extrapolation of the early light curve shows that our first observation
+  was made only $0.18$ days after the first light of the SN.
+\item The rapid initial rise and analysis of the line velocity both shows that
+  the dark period of iPTF16abc is very short. Hence, the first light time of
+  the SN is a good approximation to the time of the SN explosion.
+\item Strong and short-lived carbon features in the early spectra of iPTF16abc
+  indicates concentration of unburned carbon in the fastest-moving part of the
+  ejecta.
+\end{itemize}
+
+\acknowledgements
 

### 2017-01-02 data/collect_data.py

@@ -1,0 +1,227 @@
+#! /usr/bin/env python
+# -*- coding: utf-8 -*-
+# vim:fenc=utf-8
+#
+# Copyright © 2016 Yi Cao <ycao16@uw.edu>
+#
+# Distributed under terms of the GNU General Public License 3.0 license.
+
+"""
+This program collects all data for the iPTF16abc paper into a single HDF5
+file.
+"""
+
+
+import numpy as np
+import os
+import tables
+from astropy.io import ascii
+from astropy.time import Time
+
+# global const
+T_MAX = 57499.65
+
+
+# define photometry columns
+class Photometry(tables.IsDescription):
+    time = tables.Float64Col()
+    flux = tables.Float32Col()
+    flux_err = tables.Float32Col()
+    mag = tables.Float32Col()
+    mag_err = tables.Float32Col()
+    telescope = tables.StringCol(16)
+    instrument = tables.StringCol(16)
+    filter_name = tables.StringCol(16)
+
+
+# define transmission curve columns
+class TransmissionCurve(tables.IsDescription):
+    wavelength = tables.Float32Col()
+    transmission = tables.Float32Col()
+
+
+# supernova data set
+class SupernovaData(object):
+    def __init__(self, filename, clobber=False, title=None):
+        if os.path.isfile(filename) and not clobber:
+            msg = ("%s: file exists. Change the filename "
+                   "or set clobber=True") % filename
+            raise FileError(msg)
+        self._filename = filename
+        self._fp = tables.open_file(filename, mode="a", title=title)
+
+        self._phot_group = self._fp.create_group(
+            self._fp.root, "photometry", "Photometric Data")
+        self._lc_table = self._fp.create_table(
+            self._phot_group, "lc", Photometry, "Light Curves")
+        self._lc_table.attrs.FIELD_0_UNIT = "day"
+        self._lc_table.attrs.FIELD_1_UNIT = "Jy"
+        self._lc_table.attrs.FIELD_2_UNIT = "Jy"
+        self._lc_table.attrs.FIELD_3_UNIT = "AB mag"
+        self._lc_table.attrs.FIELD_4_UNIT = "AB mag"
+
+        self._filters_group = self._fp.create_filters(
+            self._phot_group, "filters", "Filter Transmission Curves")
+
+        self._spec_group = self._fp.create_group(
+            self._fp.root, "spectroscopy", "Spectroscopic Data")
+
+    def load_photometry(self, time, filter_name, flux, flux_err,
[…]

### 2017-01-02 data/collect_data.py
create data files

@@ -13,13 +13,9 @@ file.
 
 
 import numpy as np
-import os
 import tables
 from astropy.io import ascii
 from astropy.time import Time
-
-# global const
-T_MAX = 57499.65
 
 
 # define photometry columns
@@ -34,41 +30,31 @@ class Photometry(tables.IsDescription):
     filter_name = tables.StringCol(16)
 
 
-# define transmission curve columns
-class TransmissionCurve(tables.IsDescription):
+class Spectroscopy(tables.IsDescription):
     wavelength = tables.Float32Col()
-    transmission = tables.Float32Col()
+    flux_lambda = tables.Float32Col()
 
 
 # supernova data set
 class SupernovaData(object):
-    def __init__(self, filename, clobber=False, title=None):
-        if os.path.isfile(filename) and not clobber:
-            msg = ("%s: file exists. Change the filename "
-                   "or set clobber=True") % filename
-            raise FileError(msg)
+    def __init__(self, filename):
         self._filename = filename
-        self._fp = tables.open_file(filename, mode="a", title=title)
+        self._fp = tables.open_file(filename, mode="a")
 
-        self._phot_group = self._fp.create_group(
-            self._fp.root, "photometry", "Photometric Data")
-        self._lc_table = self._fp.create_table(
-            self._phot_group, "lc", Photometry, "Light Curves")
-        self._lc_table.attrs.FIELD_0_UNIT = "day"
-        self._lc_table.attrs.FIELD_1_UNIT = "Jy"
-        self._lc_table.attrs.FIELD_2_UNIT = "Jy"
-        self._lc_table.attrs.FIELD_3_UNIT = "AB mag"
-        self._lc_table.attrs.FIELD_4_UNIT = "AB mag"
-
-        self._filters_group = self._fp.create_filters(
-            self._phot_group, "filters", "Filter Transmission Curves")
+        self._phot_table = self._fp.create_table(
+            self._fp.root, "photometry", Photometry, "Photometric Data")
+        self._phot_table.attrs.FIELD_0_UNIT = "day"
+        self._phot_table.attrs.FIELD_1_UNIT = "Jy"
+        self._phot_table.attrs.FIELD_2_UNIT = "Jy"
+        self._phot_table.attrs.FIELD_3_UNIT = "AB mag"
+        self._phot_table.attrs.FIELD_4_UNIT = "AB mag"
 
         self._spec_group = self._fp.create_group(
[…]

### 2017-01-02 data/filter_curves.py

@@ -1,0 +1,87 @@
+#! /usr/bin/env python
+# -*- coding: utf-8 -*-
+# vim:fenc=utf-8
+#
+# Copyright © 2016 Yi Cao <ycao16@uw.edu>
+#
+# Distributed under terms of the GNU General Public License 3.0 license.
+
+"""
+create a hdf5 file that contains filer curves
+"""
+
+
+import numpy as np
+import tables
+
+
+# define transmission curve columns
+class TransmissionCurve(tables.IsDescription):
+    wavelength = tables.Float32Col()
+    transmission = tables.Float32Col()
+
+
+class FilterData(object):
+
+    def __init__(self, filename):
+        self._filename = filename
+        self._fp = tables.open_file(filename, mode="a",
+                                    title="Filter Transmission Curves")
+
+    def add_transmission_curve(self, telescope, instrument, filter_name,
+                               wavelength, transmission, clobber=False):
+        if len(wavelength) != len(transmission):
+            raise InputError("len(wavelength) != len(transmission)")
+        tel_group = self._maybe_create_group(self._fp.root, telescope)
+        inst_group = self._maybe_create_group(tel_group, instrument)
+        if filter_name in inst_group:
+            if clobber:
+                self._fp.remove_node(inst_group._f_get_child(filter_name))
+            else:
+                raise InputError("This filter %s/%s/%s already exists. "
+                                 "Set clobber=True to overwrite it" %
+                                 (telescope, instrument, filter_name))
+        tbl = self._fp.create_table(inst_group, filter_name, TransmissionCurve)
+        tbl.attrs.FIELD_0_UNIT = "Angstrom"
+        tbl.attrs.FIELD_1_UNIT = "Photons per second per Angstrom"
+        row = tbl.row
+        for w, t in zip(wavelength, transmission):
+            row["wavelength"] = w
+            row["transmission"] = t
+            row.append()
+
+    def _maybe_create_group(self, root, child):
+        if child not in root:
+            self._fp.create_group(root, child)
+        return root._f_get_child(child)
+
+
+class InputError(Exception):
+
+    def __init__(self, msg):
+        self.msg = msg
+
+    def __expr__(self):
+        return self.msg
+
+
+def main():
+    file_object = FilterData("filters.h5")
+    # P48
+    for filter_name in ["g", "R"]:
+        curve = np.genfromtxt("filters/P48/P48_%s.dat" % filter_name,
[…]

### 2017-01-20 doc/ms.tex
first completed draft

@@
 \received{\today}
-\revised{\today}
-\accepted{\today}
+\revised{}
+\accepted{}
 %% Command to document which AAS Journal the manuscript was submitted to.
@@
 
-  In this paper, we present observations of a young normal Type Ia supernova
-  iPTF16abc. Our analysis shows that: blabla ...
+  We report discovery of an extraordinarily young Type Ia supernova
+  iPTF16abc by the intermediate Palomar Transient Factory. Our first
+  observation was made only $0.18$ days after the onset of the
+  supernova explosion. Our analysis shows that the early emission of
+  this supernova dominantly comes from the radioactive decay instead
+  of supernova shock breakout or collision between the ejecta and a
+  possible companion star. The fast initial rise of the supernova, the
+  velocity evolution of spectral lines, and the strong and short-lived
+  carbon feature in the earliest spectra together provide strong
+  evidence of strong mixing of synthesized radioactive elements during
+  the supernova explosion.
 
@@
 
-\ycao{TODO: include LCOGT data in both text and figures.}
-
 \begin{figure*}[htb]
@@
     different markers. The $t_{max}$ time is the B-band maximum
-    determined by SALT2 (Section). The black ticks near the top of the
-    figure shows epochs of spectroscopic observations.}
+    determined by SALT2 (Section \ref{sec:classification}). The solid
+    curves are best-fit results from SALT2. The black ticks near the
+    top of the figure shows epochs of spectroscopic observations.}
   \label{fig:lightcurve}
@@
 
-After discovery, we utilized the rainbow camera of the SED
-Machine (\ycao{REF}) mounted on the 60-inch telescope at Palomar
-Observatory (P60) to undertake photometric observations in $g$, $r$
-and $i$ filters. The image differencing against the archival SDSS
-images and forced PSF photometry on the subtracted images were
-performed by the Fremling Automated Pipeline
-\citep{2016A&A...593A..68F}. The photometry is also calibrated to the
-SDSS catalog.
+After discovery, we utilized the rainbow camera of the SED Machine
+(\ycao{REF}) mounted on the 60-inch telescope at Palomar Observatory
+(P60) to undertake photometric observations in $g$, $r$ and $i$
+filters. The image differencing against the archival SDSS images and
+forced PSF photometry on the subtracted images were performed by the
+Fremling Automated Pipeline \citep{2016A&A...593A..68F}. The
+photometry is also calibrated to the SDSS catalog \ycao{which DR?}.
 
-Las Cambres Observatory Global Network (LCOGT) also carry out photometric
-observations in the \textit{BVgri} filters with its 1-m telescope network.
-\ycao{Some info about data reduction}
+Las Cambres Observatory Global Network (LCOGT) also carry out
+photometric observations in the \textit{BVgri} filters with its 1-m
+telescope network.  PSF photometry was measured on these images using
+the \texttt{lcogtsnpipe} pipeline \citep{2016MNRAS.459.3939V}. The
+\textit{BV} magnitudes are calibrated to the Fourth USNO CCD
+Astrograph Catalog \citep{2013AJ....145...44Z}, and the \textit{gri}
+magnitudes are calibrated to SDSS Data Release 6
+\citep{2008ApJS..175..297A}.
 
@@
 Telescope (UVOT) with the usual procedures in the HEASoft and
-corrected for the coincident loss and aperture loss. No pre-SN UVOT
-image at the SN location is available in the \textit{Swift} archive.
-Visual inspection to the UVOT images suggests that the background
-galaxy light in the UVOT filters is probably negligible. No X-ray
-emission was detected at the location of the SN by the X-ray Telescope
-(XRT) in any of these for epochs.
+corrected for the coincident loss and aperture loss. The image counts
+are converted to physical fluxes using the latest calibration
+\citep{2011AIPC.1358..373B}. No pre-SN UVOT image at the SN location
+is available in the \textit{Swift} archive.  Visual inspection to the
+UVOT images suggests that the background galaxy light in the UVOT
+filters is probably negligible. No X-ray emission was detected at the
+location of the SN by the X-ray Telescope (XRT) in any of these
+epochs.
 
 The multi-color light curves of iPTF16abc are illustrated in Figure
-\ref{fig:lightcurve}.  For convenience, all magnitudes are in the AB
-system with a zero point of $3631$\,Jy in all filters.
+\ref{fig:lightcurve}.  For convenience, magnitudes in \textit{all}
+filters are in the AB system with a zero point of $3631$\,Jy.
 
-Spectroscopic observations of iPTF16abc were undertaken with the
-Gemini Multi-Object Spectrograph (GMOS; \citealt{2004PASP..116..425H})
-on the Gemini North telescope, Low-Resolution Imaging Spectrometer
-(LRIS; \citealt{1995PASP..107..375O}) on the Keck-I telescope, DEep
-Imaging Multi-Object Spectrograph (DEIMOS;
-\citealt{2003SPIE.4841.1657F}) on the Keck-II telescope, The Andalucia
-Faint Object Spectrograph and Camera (ALFOSC\footnote{ALFOSC
-  instrument webpage:
-  \url{http://www.not.iac.es/instruments/alfosc/}}) on the Nordic
-Optical Telescope (NOT), and X-shooter \citep{2011A&A...536A.105V} and
-Ultraviolet and Visual Echelle Spectrograph (UVES;
-\citealt{2000SPIE.4008..534D}) on the Very Large Telescope (VLT). The
-observing log is listed in Table \ref{tab:spec_obs_log} and the
-low-resolution spectral sequence is shown in Figure
+Spectroscopic observations of iPTF16abc were undertaken with a variety
+of telescopes and instruments in multiple epochs spanning from a
+couple of days after explosion to two months after its maximum. An
+observing log is listed in Table \ref{tab:spec_obs_log}. Data
+reduction is undertaken with usual routines in IDL/Python. Except for
+the high-resolution spectra obtained by VLT instruments, the optical
+spectral evolution of iPTF16abc is illustrated in Figure
 \ref{fig:spec_seq}.
 
-% currently the following table and figure do not include data from LCOGT
 \begin{deluxetable*}{cccccc}
@@
   \tablehead{
-    \colhead{Observation Date} & \colhead{SN phase} & \colhead{Telescope/Instrument} &
-    \colhead{Exposure Time (s)} & \colhead{Wavelength Coverage (\AA)} & \colhead{Resolution}
+    \colhead{Observation MJD} & \colhead{SN phase} & \colhead{Telescope} &
+    \colhead{Instrument} & \colhead{Wavelength Coverage (\AA)}
   }
   \startdata
-  2016 April $05.88$ & $-15.8$ & Gemini-North/GMOS &     & $3500$ -- $9500$  & $1900$ \\
-  2016 April $06.51$ & $-15.1$ & Keck-II/DEIMOS & $1491$ & $5500$ -- $8100$  & $2000$ \\
-  2016 April $08.51$ & $-13.1$ & Keck-II/DEIMOS & $900$  & $5500$ -- $8100$  & $2000$ \\
-  2016 April $10.38$ & $-11.3$ & Keck-I/LRIS    & $300$  & $3000$ -- $10000$ & $1000$ \\
-  2016 April $14.20$ & $-7.5$  & VLT/XSHOOTER   &        & $3000$ -- $25000$ & $10000$ \\
-  2016 April $16.??$ & $-5.?$  & VLT/UVES       &        & covers \ion{Ca}{2}\,H$+$K and \ion{Na}{1}\,D lines & $40000$ \\
-  2016 April $28.??$ & $6.4$   & NOT/ALFOSC     &        & $3300$ -- $9000$  & $360$ \\
-  2016 May   $10.42$ & $18.8$  & Keck-I/LRIS    & $600$  & $3000$ -- $10000$ & $1000$ \\
-  2016 May   $12.03$ & $20.4$  & VLT/XSHOOTER   &        & $3000$ -- $25000$ & $10000$ \\
+  $57483.26$ & $-16.4$ & DCT & DeVeny\tablenotemark{1} & $3301$--$7499$ \\
+  $57483.88$ & $-15.8$ & Gemini-North & GMOS\tablenotemark{2} & $3800$--$9200$ \\
+  $57484.51$ & $-15.1$ & Keck-II & DEIMOS\tablenotemark{3} & $5500$--$8099$ \\
+  $57486.51$ & $-13.1$ & Keck-II & DEIMOS\tablenotemark{3} & $5500$--$8099$ \\
+  $57488.38$ & $-11.3$ & Keck-I & LRIS\tablenotemark{4} & $3055$--$10411$ \\
+  $57489.51$ & $-10.1$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $3301$--$8999$ \\
+  $57490.40$ & $ -9.3$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $3301$--$9999$ \\
+  $57491.55$ & $ -8.1$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $3300$--$9998$ \\
+  $57492.20$ & $ -7.5$ & VLT & X-shooter\tablenotemark{6} & $3300$--$24550$ \\
+  $57494.00$ & $ -5.7$ & VLT & UVES\tablenotemark{7} & \\
+  $57503.32$ & $ +3.7$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $3300$--$9999$ \\
+  $57506.00$ & $ +6.3$ & NOT & ALFOSC\tablenotemark{8} & $3602$--$8098$ \\
+  $57508.27$ & $ +8.6$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $3301$--$9999$ \\
+  $57518.42$ & $+18.8$ & Keck-I & LRIS\tablenotemark{4} & $3071$--$10208$ \\
+  $57520.03$ & $+20.4$ & VLT & X-shooter\tablenotemark{6} & $3300$--$24789$ \\
+  $57529.40$ & $+29.8$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $4000$--$8998$ \\
+  $57542.41$ & $+42.8$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $4000$--$8998$ \\
+  $57550.40$ & $+50.8$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $4001$--$8999$ \\
+  $57562.38$ & $+62.7$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $4800$--$9300$ \\
   \enddata
+  \tablenotetext{1}{The Deveny Spectrograph \citep{2014SPIE.9147E..2NB}}
+  \tablenotetext{2}{The Gemini Multi-Object Sectrograph \citep{2004PASP..116..425H}}
+  \tablenotetext{3}{DEep Imaging Multi-Object Spectrograph \citep{2003SPIE.4841.1657F}}
+  \tablenotetext{4}{Low-Resolution Imaging Spectrometer \citep{1995PASP..107..375O}}
+  \tablenotetext{5}{FLOYDS \url{https://lco.global/observatory/instruments/floyds}}
+  \tablenotetext{6}{X-shooter \citep{XShooter}}
+  \tablenotetext{7}{Ultraviolet and Visual Echelle Spectrograph \citep{2000SPIE.4008..534D}}
+  \tablenotetext{8}{The Andalucia Faint Object Spectrograph and Camera \url{http://www.not.iac.es/instruments/alfosc}}
 \end{deluxetable*}
@@
   \centering
-  \includegraphics[width=0.9\textwidth]{spec_sequence.pdf}
+  \includegraphics[width=1.0\textwidth]{spectra.pdf}
   \caption{Low-resolution spectra of iPTF16abc are shown in the
-    chronical sequence. The phases in units of days are labeled next
-    to corresponding spectra. Telluric absorption bands are grayed
-    out.}
+    chronical orders. In order for better illustration, each spectrum
+    is normalized by the median flux value between $6,000$ and
+    $7,000\,\textrm{\AA}$ and offset properly.  The phases in units of
+    days are noted next to corresponding spectra. Telluric absorption
+    bands are grayed out. The narrow \ion{Na}{1}\,D absorption is also
+    highlighted in orange.}
   \label{fig:spec_seq}
@@
 reddening $E(B-V)$ \citep{2012MNRAS.426.1465P}, we derive
-$E(B-V)=0.361\pm0.025\textrm{mag}$.
+$E(B-V)=0.361\pm0.025\textrm{mag}$. We caution that the empirical
+relation has a quite large scatter.
 
@@
 in the profiles of the doublet.
+
+We also note in Figure \ref{fig:narrow_features} that the absorption
+profiles of \ion{Ca}{2}\,H$+$K are quite different from those of \ion{Na}{1}\,D
+doublet, implying that the dust compositions in the two absorption sources
+may have some difference.
 
@@
 
-Extrapolation of the earliest-phase light curve with a simple model is
-usually used to estimate the first light time. In theory,
-\citet{1982ApJ...253..785A} derived a quadratic law for an expanding
-fireball with a constant temperature. In order to account for the
-temperature change, here we utilize a power-law model
+Extrapolation of the earliest-phase light curve with a simple
+mathematical model is usually used to estimate the first light time of
+a SN. In theory, \citet{1982ApJ...253..785A} derived a quadratic law
+for an ideal expanding fireball with a constant temperature. In order
+to account for variation of photospheric temperatures during
+expansion, we utilize a power-law curve to model the early light curve.
 \begin{equation}
@@
 Since the first few detections of the SN were made in the \textit{g}
-band, we perform the fit only to the \textit{g}-band light curve. We
-experiment the fitting procedure with different time windows and find
-that the SN flux between $t=-19\,\textrm{days}$ and
-$t=-15\,\textrm{days}$ rises approximately linearly. The joint
-distribution of $\alpha$ and $t_0$ for this time window is given in
-the left panel of Figure \ref{fig:early_lc_fit} and the best fit model
-with $\alpha = 0.94$ and $t_0=-18.47$ is shown in the right
-panel. With this best-fit value of $t_0$, our first observation was
-made only $0.18\,\textrm{day}$ after the first light of the SN. The
-total rise time to the \textit{B}-band peak is $18.47$ days.
+band, our modeling is limited to the early \textit{g}-band light
+curve. We minimize $\chi^2$ in a large search grid of $t_0$, $\alpha$
+and the proportionality constant. We also note that the definition of
+the time window for the early light curve may affect the fitting
+result, so we experiment the fitting procedure with different time
+windows. The modeling results show that the SN flux between
+$t=-19\,\textrm{days}$ and $t=-15\,\textrm{days}$ rises approximately
+linearly. Figure \ref{fig:early_lc_fit} shows the best-fit result and
+the joint marginal distribution of $t_0$ and $\alpha$. With the
+best-fit model of $\alpha=0.92$ and $t_0=-18.47$ days, our first
+observation was made only $0.18\,\textrm{day}$ after the first light
+of the SN. The total rise time to the \textit{B}-band peak is $18.47$
+days.
 
@@
   \centering
-  \includegraphics[width=0.45\textwidth]{rise_time_power_law_index.pdf}
-  \includegraphics[width=0.45\textwidth]{early_lc.pdf}
+  \includegraphics[width=0.95\textwidth]{early_lc.pdf}
   \caption{Broken Power low fitting to the early $g$-band light
-    curve.
-    \textit{Left:} the joint distribution of $t_0$ and
-    $\alpha$. The cross marker denotes the best-fit parameters. The
-    inner and outer contours represent the $68\%$ and $99.7\%$
+    curve. The best-fit model of $\alpha=0.92$ and $t_0=-18.47\,\textrm{days}$
+    and corresponding residues are shown in the top and bottom panels, respectively.
+    The joint distribution of $t_0$ and $\alpha$ is illustrated in the inset of
+    the upper panel. The solid and dashed contours represent the $68\%$ and $99.7\%$
     confidence levels.
-    \textit{Right:} the best-fit model of $\alpha=0.94$ and
-    $t_0=-18.47\,\textrm{days}$ is illustrated against the
-    data.
   }
@@
 
-Since $t=-15\,\textrm{days}$, the \textit{g}-band light curve rises
-significantly faster than the best-fit model above, indicating a
-greater value of the power-law index $\alpha$. In fact, the
-light curve between $t=-14$ and $t=-8$\,days can be fitted with a
-power law of index $1.40$.
+Starting from $t=-15\,\textrm{days}$, the \textit{g}-band light curve
+rises significantly faster than the best-fit model above, indicating a
+greater value of the power-law index $\alpha$. In fact, the light
+curve between $t=-14$ and $t=-8$\,days can be fitted with another
+power law of index $1.40$. In another word, the whole light curve
+before $t=-8$\,days can be approximated by a broken power-law model
+(e.g.,
+\citealt{2013ApJ...778L..15Z,2014ApJ...783L..24Z,2016arXiv161202097Z,
+  2016arXiv161202725Z}).
 
-A more sophisticated broken power-law model has also been used to fit
-SN early-phase light curves (e.g.,
-\citealt{2013ApJ...778L..15Z,2014ApJ...783L..24Z,
-  2016arXiv161202097Z,2016arXiv161202097Z}). Our above result has
-indicates that the \textit{g}-band light curve of iPTF16abc can also
-be fitted by a broken-power law with a power index changing from
-$0.94$ to $1.40$. In fact, many young SNe, including SN2011fe
-\cite{2016arXiv161202097Z} and iPTF16abc, have early light curves that
-follow broken power-laws \citep{2016arXiv161202725Z}). Our above
-result has indicates that the \textit{g}-band light curve of iPTF16abc
-can also be fitted by a broken-power law with a power index changing
-from $0.94$ to $1.40$.
-
-The initial rise of a SN depends on the distribution of $^{56}$Ni
-in the ejecta. Comparing the rapid initial rise of iPTF16abc to
-theoretical calculations in \citet{2016ApJ...826...96P} suggests
-strong mixing of $^{56}$Ni in the iPTF16abc ejecta. The radioactive
-energy from $^{56}$Ni can quickly diffuse to the SN photosphere and
-power its light curve after the SN explosion.
+As discussed in Section \ref{sec:lc_energy}, the initial light curve
+of iPTF16abc is probably purely powered by radioactive decay of
+$^{56}$Ni. Therefore, the initial rise of the light curve depends on
+the depth of the shallowest layer where $^{56}$Ni is deposited
+\citep{2014ApJ...784...85P}. According to theoretical mdels
+\citep{2016ApJ...826...96P}, the linearly rising light curve implies
+strong mixing of $^{56}$Ni in the ejecta. As a result, the time lag
+between the SN explosion and the initial rise of the radioactively
+powered light curve is negligible.
 
@@
 
-The first light of a SN is not necessarily its explotion time
-$t_{exp}$.  Thanks to different deposition of $^{56}$Ni in the SN
-ejecta, as pointed out in \citet{2014ApJ...784...85P}, the SN may
-experience a dark period before the radioactive energy from the
-shallowest $^{56}$Ni layer escapes the ejecta. Therefore, 
-\citet{2014ApJ...784...85P} suggests to examine evolution of absorption
-line velocities, because the velocities do not depend on the $^{56}$Ni
-mixing and are expected to evolve roughly as $v\propto(t-t_{exp})^{-0.22}$.
+In order to constrain the explosion time of the SN independently of
+the SN light curve, \citet{2014ApJ...784...85P} suggested to measure
+the expansion velocities of the photosphere, because the expansion of
+the ejecta starts at the onset of the SN explosion. Assuming a
+constant opacity in the ejecta, the photospheric velocity evolves as
+$v_{ph}\propto(t-t_{exp})^{-0.22}$. While the photospheric velocities
+are not easy to measure, line velocities of \ion{Si}{2} or \ion{Ca}{2}
+are usually used to approximate the photospheric velocities
+\citep{2014ApJ...784...85P,2016ApJ...826..144S}.
 
-We focus on measuring velocities of the strongest \ion{Si}{2}\,6355
-line, as the second most commonly used \ion{Ca}{2} IR triplet is very
-weak in iPTF16abc. Visual inspection of the early-phase spectra shows
-no sign of any high-velocity component of the \ion{Si}{2} line and
-that the red wing of \ion{Si}{2} overlaps the \ion{C}{2}\,6580
-line. Therefore, we fit simultaneously two gaussian kernels for the
-two lines and a linear term to account for the continuum component.
-Then the velocities are calculated at the minimum of the \ion{Si}{2}
-gaussian kernel.
+In the case of iPTF16abc, the \ion{Ca}{2} IR triplet is very weak in
+the spectra probably due to high temperatures in the ejecta. Thus we
+perform our measurements on the \ion{Si}{2}\,6355 line. Visual
+inspection of the spectra shows no sign of multi-velocity components
+of \ion{Si}{2}, and that the \ion{C}{2}\,6580 line overlaps the red
+wing of the \ion{Si}{2} line. Consequently we apply a mathematical
+model of two gaussian kernels superposed on a linear term, which
+accounts for the absorption of \ion{Si}{2} and \ion{C}{2} and the
+continuum component, respectively, to approach the observed spectra
+between $5,900$ and $6,500$\,\AA (rest-frame). The expansion
+velocity of \ion{Si}{2} is calculated at the central wavelength
+of the \ion{Si}{2} Gaussian kernel.
 
@@
   \centering
-  \includegraphics[width=0.45\textwidth]{exp_date_chi2.pdf}
-  \includegraphics[width=0.45\textwidth]{SiIIVelocity.pdf}
+  \includegraphics[width=0.45\textwidth]{Chi2.pdf}
+  \includegraphics[width=0.45\textwidth]{VelocityPlot.pdf}
   \caption{Constraints on $t_{exp}$ from fitting the velocity
-    evolution of \ion{Si}{2}. \textit{Left panel:} the dashed, solid
+    evolution of \ion{Si}{2}.
+    \textit{Left panel:} the dashed, solid
     and dash-dotted curves show $\chi^2$ for fitting power laws with
@@
     3-$\sigma$ confidence interval from Section
-    \ref{sec:lc_fit}. \textit{Right panel:} Observed \ion{Si}{2}\,6355
-    velocities with the best-fit power-law velocity with an index of
+    \ref{sec:lc_fit}.
+    \textit{Right panel:} Observed \ion{Si}{2}\,6355
+    velocities and the best-fit power-law velocity with an index of
     $-0.22$.}
@@
 
-Fitting the measured velocities of \ion{Si}{2}\,6355 line to the
-$v\propto(t-t_{exp})^{-0.22}$ model leads to the best-fit explosion
-time $t_{exp}=-17.95\,\textrm{days}$ with a 3-$\sigma$ confidence
-interval between $-17.4\,\textrm{days}$ and $-18.3\,\textrm{days}$
-(Figure \ref{fig:velocity_t_exp}). We further test the robustness of
-a fixed power-law index by altering the index to $-0.20$ and $-0.24$
-and find consistent results within respective 3-$\sigma$ confidence
+We fit the measured velocities of \ion{Si}{2}\,6355 line to the
+$v\propto(t-t_{exp})^{-0.22}$ model by minimizing the $\chi^2$ value
+and find the best-fit explosion time $t_{exp}=-17.95\,\textrm{days}$
+with a 3-$\sigma$ confidence interval between $-17.4\,\textrm{days}$
+and $-18.3\,\textrm{days}$ (Figure \ref{fig:velocity_t_exp}). We also
+alter the power-law index to $-0.20$ and $-0.24$ to examine how
+sensitively the result depends on the assumed power-law index.  we
+find consistent results within respective 3-$\sigma$ confidence
 intervals.
 
-The derived $t_{exp}$ is roughly consistent to $t_0$ estimated in
-Section \ref{sec:lc_fit}, confirming that the dark period of iPTF16abc
-is very short. This conclusion is consistent with the inference from the
-rapid initial rise of iPTF16abc in Section \ref{sec:lc_fit}.
+Keeping in mind that $t_{exp}$ has a very large uncertainty mostly due
+to the assumption in the $v\propto(t-t_{exp})^{-0.22}$ model, we
+compare the estimated $t_{exp}$ to $t_0$ (left panel of Figure
+\ref{fig:velocity_t_exp}) and find that $t_0\lessapprox t_{exp}$.
+Since physical causality requires $t_{exp}<t_0$, we draw a qualitative
+conclusion that $t_0\simeq t_{exp}$. This conclusion is consistent
+with our inference from the early light curve analysis in Section
+\ref{sec:lc_fit}.
 
-Among the several SNe with measurements of $t_{exp}$ and $t_0$
-\citep{2014ApJ...784...85P,2016ApJ...826..144S}, iPTF16abc has the
-shortest dark period and longest rise time ($18.47$ days). In
-comparison, SN2011fe is inferred to have a dark period of $\sim 1$
-day \citep{2014ApJ...784...85P} and a rise time of $17.7$ days
-\citep{2013A&A...554A..27P}; ASASSN-14lp has a dark period of a couple
-of days and a rise time of $16.94$ days. This seems to suggest that
-the time difference between SN explosion and the \textit{B}-band maximum,
-which equals to summation of the dark period and the rise time, is a
-constant for a SN Ia. This is perhaps because the \textit{B}-band maximum
-time only depends on the total amount of $^{56}$Ni.
+With $t_{exp}$, we estimate the actual rise time of iPTF16abc from the
+SN explosion to its \textit{B}-band maximum to be $17.95$ days.  In
+comparison, SN2011fe has $t_0=-17.7$ days \citep{2013A&A...554A..27P}
+with a preceding dark period of $\sim 1$ day
+\citep{2014ApJ...784...85P}. ASASSN-14lp has $t_0=-16.94$ days with a
+preceding dark period of about acouple of days
+\citep{2016ApJ...826..144S}. This comparison suggests that the actual
+rise time of a SN Ia between the SN explosion and the \textit{B}-band
+maximum is roughly a constant, which largely depends on the total mass
+of synthesized $^{56}$Ni.
 
@@
 
-Interestingly, the first few spectra of iPTF16abc show clear detection
-of \ion{C}{2}\,6580 and \ion{C}{2}\,7234 lines. Their velocity
-evolution is shown in Figure \ref{fig:velocity_t_exp} as well.
+Another intriguing spectral feature of iPTF16abc is strong absorption of
+\ion{C}{2}\,6580 and \ion{C}{2}\,7234 lines. Our analysis on the
+\ion{Si}{2}\,6355 line also allows us to measure the velocities and
+pseudo-equivalent widths (pEWs) of \ion{C}{2}\,6580. We also fit a Gaussian
+kernel superposing on a linear term to the spectral region near
+the \ion{C}{2}\,7234 line to measure its velocity and pseudo-equivalent
+width. The velocity evolution of \ion{C}{2} is shown in the right panel
+of Figure \ref{fig:velocity_t_exp} and the pEW evolution
+in Figure \ref{fig:ew}.
 
-The \ion{C}{2} lines only appear in the very early phases. The
-equivalent widths of detected \ion{C}{2}\,6580 and \ion{C}{2}\,7234
-lines are shown in Figure \ref{fig:ew}, and are compared to that of
-the \ion{Si}{2}\,6355 line. Especially in the first spectrum taken at
-$t=-15.8$ days, the \ion{C}{2} equivalent widths are stronger than
-that of \ion{Si}{2}.
+Our measurements show that the strong \ion{C}{2} absorption
+only appears in the very early phases. In the spectrum taken at
+$t=-15.8$ days, the pEW of \ion{C}{2}\,6580 is comparable to that
+of \ion{Si}{2}\,6355. Then the pEW of \ion{C}{2} decreases
+until they disappear at about $t=-10$ days.
 
@@
   \centering
-  \includegraphics[width=0.45\textwidth]{EW.pdf}
-  \caption{Equivalent Width of \ion{Si}{2}\,6355, \ion{C}{2}\,6580 and
-    \ion{C}{2}\,7234 lines}
+  \includegraphics[width=0.45\textwidth]{pEW.pdf}
+  \caption{Pseudo-equivalent width of \ion{Si}{2}\,6355,
+    \ion{C}{2}\,6580 and \ion{C}{2}\,7234 lines. The uncertainties
+    in these measurements are less than the sizes of these symbols.}
   \label{fig:ew}
@@
 
-The strong and short-lived \ion{C}{2} features suggest that
-the outermost layers of the ejecta contain a certain amount of
-carbon which is responsible for the \ion{C}{2} absorption. The
-abundance of carbon drops dramatically into the inner layers
-of the ejecta.
+Formation of \ion{C}{2} absorption requires existence of both unburned
+carbon and $^{56}$Ni, the latter of which is responsible to ionize the
+carbon atoms. The strong and short-lived \ion{C}{2} features observed
+in the spectra of iPTF16abc show that a certain amount of carbon atoms
+exist in the outer layers of the ejecta and that $^{56}$Ni atoms are also
+strongly mixed in the same layers. This provides a third piece of evidence
+to strong mixing in the iPTF16abc ejecta.
 
@@
 \citep{2012ApJ...752L..26P}.  The only normal SN Ia known to have
-strong \ion{C}{2} features at very early phases is SN2013dy
-\citep{2013ApJ...778L..15Z}. Unlike iPTF16abc, the equivalent widths
-of \ion{C}{2} features in SN2013dy are as large as that of
-\ion{Si}{2}\,6355.
+strong \ion{C}{2} features at early phases is SN2013dy
+\citep{2013ApJ...778L..15Z}. Unlike iPTF16abc, however, the equivalent
+widths of \ion{C}{2} features in SN2013dy are as large as those of
+\ion{Si}{2}\,6355 in the same spectra.
 
-\subsection{Discussions and Physical Constraints}
+\subsection{Discussions}
 \label{sec:lc_energy}
 
-The early radiation of a SN Ia may have multiple resources: SN
-shockbreakout, SN-companion collision, and radioactive activity. Since
-each provides interesting constraints on the progenitor properties, we
-explore all the three posibilities.
+Early radiation of a SN Ia may have multiple energy sources: SN shock
+breakout, SN-companion collision, and radioactive activity. The
+previous analysis is based on the assumption that the light curve of
+iPTF16abc is powered purely by radioactive decay. Here we discuss the
+other two possibilities.
 
@@
 and reach a not very constraining conclusion that the radius of the
-progenitor star of iPTF16abc should be $<1\sr$. In fact, the cooling
-emission is negligible at the time of the first detection of
-iPTF16abc.
+progenitor star of iPTF16abc should be $<1\sr$. In fact, with a
+typical $0.01\sr$ radius of a white dwarf, the cooling emission of a
+SN Ia is negligible at the time of the first detection of iPTF16abc.
 
-\subsubsection{SN companion}
+\subsubsection{SN-Companion collision}
 
-If iPTF16abc is born in a single-degenerate channel, with an odd of
-$\lesssim10\%$, we expect to see emission produced by SN ejecta
-slamming into the companion. However, according to calculations by
+From a SN Ia born in a single-degenerate system, with an odd of
+$\lesssim10\%$ due to the geometry, we expect to see emission produced
+by SN ejecta slamming into the companion. According to calculations by
 \citet{2010ApJ...708.1025K}, collision between SN ejecta and the
-companion star produces thermal emission with a spectrum that peaks
-in the ultraviolet, and the Rayleigh-Jeans tail emission in the \textit{g}
-band is very weak.
+companion star generates thermal emission with a spectrum with
+spectrum that peaks in the ultraviolet. The Rayleigh-Jeans tail
+emission in the \textit{g} band is very weak.
 
-In the case of SN2012cg, in order to illustrate a blue excess in the
-early light curve, \citet{2016ApJ...820...92M} fitted a power-law
-model to its light curves between $t=-14$ days and $t=-8$ days and
-subtracted the extrapolated fluxes at early epochs. Then these authors
-attribute the excess to SN-companion collision. In our iPTF16abc, we
-follow the same procedure and also find a similar excess
-(Figure \ref{fig:against_sn2012cg}).
+In order to examine the possible SN-companion signature in the early
+light curve of iPTF16abc, we employ the \citet{2010ApJ...708.1025K}
+model by assuming an ejecta mass of $1.4\sm$, an expansion velocity of
+$10^{4}\,\textrm{km}\,\textrm{s}^{-1}$, and a constant opacity of
+$0.2\,\textrm{cm}^2\,\textrm{g}^{-1}$. The angular dependence of this
+emission uses the parameterized equation in
+\citet{2012ApJ...749...18B}.  Figure \ref{fig:SN-companion} compares
+the calculated \textit{g}-band apparent magnitudes of SN-companion
+collision for different combinations of binary separation and viewing
+angle against the first detection of iPTF16abc. The figure shows that,
+even with the most favored viewing angle, the binary separation would
+have to exceed $2\times10^{14}\,\textrm{cm}$. Under the model assumption that the
+companion fills its Roche lobe, the companion star would have to have
+a radius of $\sim10^{14}\,\textrm{cm}\simeq10^{4}\sr$. Given that the
+mass of the companion is $\sim1\sr$, such a large radius seems unlikely.
+Therefore, we conclude that the early emission of iPTF16abc is not likely
+to originate from the SN-companion collision.
 
-\begin{figure}[!htb]
+\begin{figure}[!thb]
   \centering
-  \includegraphics[width=0.45\textwidth]{another_early_lc.pdf}
-  \caption{The early-phase \textit{g}-band light curve of iPTF16abc is
-    compared against the best-fit power-law model to the data segment
-    between $t=-14$ and $t=-8$ days. Note the ``excess'' between the
-    data and the model during $t=-18$ and $t=-15$ days}
-  \label{fig:against_sn2012cg}
+  \includegraphics[width=0.45\textwidth]{SNCompanion.pdf}
+  \caption{apparent magnitude of SN-companion collision (gray region)
+    against the first detection of iPTF16abc (black).}
+  \label{fig:SN-companion}
 \end{figure}
-
-Actually, for any early light curve that can be approximated by a
-broken power law, as long as the asymptotic power-law index near $t=0$
-is less than that at late time, one can always find such an excess
-near $t=0$. There are not many SNe that were observed at
-extraordinarily early phases. The odd that both SN2012cg and iPTF16abc
-show SN-companion collision signautres is very small.
-
-Separately, our first \textit{Swift} observation of iPTF16abc was made
-about two days after explosion. However, the ultraviolet light curve of
-iPTF16abc does not show any excess.
-
-\subsubsection{Explosion Mechanism}
-
-Our extraordinarily early observations of iPTF16abc put two constraints
-on the mechanism of the SN explosion: first, during the SN explosion,
-synthesized $^{56}$Ni should be strongly mixed in the ejecta; second,
-unburned carbon atoms are accelerated to very high velocities in the ejecta.
-In addition, the commonly seen \ion{Ca}{2} IR triplet is weak in iPTF16abc,
-implying a little amount of calsium in the ejecta.
 
@@
 
-In this paper, we present observations of a normal Type Ia supernova
-iPTF16abc, which is located at one tidal tail of NGC\,5221. Our extraordinarily
-early-phase optical observations of this supernova show that:
+In this paper, we present observations of an extraordinarily young
+normal Type Ia supernova iPTF16abc at one tidal tail of NGC\,5221. Our
+extraordinarily fast-response follow-up compaign of this supernova
+allows us to draw the following conclusions:
 \begin{itemize}
-\item Extrapolation of the early light curve shows that our first observation
-  was made only $0.18$ days after the first light of the SN.
-\item The rapid initial rise and analysis of the line velocity both shows that
-  the dark period of iPTF16abc is very short. Hence, the first light time of
-  the SN is a good approximation to the time of the SN explosion.
-\item Strong and short-lived carbon features in the early spectra of iPTF16abc
-  indicates concentration of unburned carbon in the fastest-moving part of the
-  ejecta.
+\item By extrapolating the early light curve, we determine that the
+  first light of the SN light curve was only $0.18$ days before our
+  first observation.
+\item Our analysis shows that the observed early-phase light curve is
+  probably powered by radioactive decay of $^{56}$Ni, instead of SN
+  shock breakout or SN-companion collision (provided that iPTF16abc
+  is born in a single-degenerate channel).
+\item Our measurements on the spectral line velocities shows that the
+  actual explosion date of the SN is approximately equal to the time
+  of the first light of the SN light curve, indicating that
+  synthesized $^{56}$Ni atoms are mixed out into the outer layers of
+  the supernova ejecta.
+\item The strong mixing of $^{56}$Ni is also supported by strong and
+  short-lived carbon features in the earliest spectra of iPTF16abc. 
 \end{itemize}
 
+Observations of extraordinarily young supernovae provide a ``smoking
+gun'' to probe the mixing level in the ejecta, which, in turn, results
+directly from the explosion mechanisms. With the ongoing and planned
+time-domain survyes, a large number of extraordinarily young supernovae
+will be collected in the next few years. With such a sample, we will
+be able to make connections between the observed supernovae and proposed
+mechanisms.
+
+It should also be emphasized that much of the analysis presented in
+this paper would not be possible without the fast-response and
+extensive photometric and spectroscopic follow-up compaign. With the
+great potential of discoveries in the surveys, researchers need to
+be prepared and organized for follow-up observations.
+
 \acknowledgements
+
+YC thanks supports from the postdoc fellowship in the eScience
+institute, University of Washington.
 

### 2017-01-20 data/collect_data.py

@@ -73,7 +73,8 @@ class SupernovaData(object):
         table_name = "%s_%i" % (instrument.replace("-", "_"), int(time))
         tbl = self._fp.create_table(self._spec_group,
                                     table_name,
-                                    Spectroscopy)
+                                    Spectroscopy,
+                                    table_name)
         tbl.attrs.FIELD_0_UNIT = "Angstrom"
         tbl.attrs.FIELD_1_UNIT = "Arbitrary Unit"
         tbl.attrs.OBS_DATE = time
@@ -187,6 +188,8 @@ def main():
                 continue
             items = item.split("\t")
             obs_time = Time(items[1], format="iso", scale="utc")
+            if float(items[3]) < 5. * float(items[4]):
+                continue
             file_object.add_photometry(
                 obs_time.mjd,
                 items[8].strip(),
@@ -198,6 +201,15 @@ def main():
                 "UVOT")
 
     # Spectra
+    filename = "spec/16abc_20160405_DCT_v1.ascii"
+    curve = np.genfromtxt(filename,
+                          names=["wavelength", "flux"])
+    idx = np.logical_and(curve["wavelength"] > 3300,
+                         curve["wavelength"] < 7500)
+    curve = curve[idx]
+    file_object.add_spec(57483.26, "DCT", "DeVeny",
+                         curve["wavelength"], curve["flux"])
+
     filename = "spec/16abc_20160405_Gemini_N_v1.ascii"
     curve = np.genfromtxt(filename,
                           names=["wavelength", "flux"])
@@ -207,12 +219,18 @@ def main():
     filename = "spec/16abc_20160406_Keck2_v1.ascii"
     curve = np.genfromtxt(filename,
                           names=["wavelength", "flux"])
+    idx = np.logical_and(curve["wavelength"] > 5500,
+                         curve["wavelength"] < 8100)
+    curve = curve[idx]
     file_object.add_spec(57484.51, "Keck-II", "DEIMOS",
                          curve["wavelength"], curve["flux"])
 
     filename = "spec/16abc_20160408_Keck2_v2.ascii"
     curve = np.genfromtxt(filename,
                           names=["wavelength", "flux"])
+    idx = np.logical_and(curve["wavelength"] > 5500,
+                         curve["wavelength"] < 8100)
+    curve = curve[idx]
     file_object.add_spec(57486.51, "Keck-II", "DEIMOS",
[…]

### 2017-01-20 data/examine_spec.py

@@ -1,0 +1,30 @@
+#! /usr/bin/env python
+# -*- coding: utf-8 -*-
+# vim:fenc=utf-8
+#
+# Copyright © 2017 Yi Cao <ycao16@uw.edu>
+#
+# Distributed under terms of the GNU General Public License 3.0 license.
+
+"""
+Examine spectral data
+"""
+
+import matplotlib.pyplot as plt
+import numpy as np
+import tables
+
+
+def main():
+    fp = tables.open_file("iPTF16abc.h5", mode="r")
+    group = fp.root.spectroscopy
+    for spec in group:
+        plt.figure()
+        w = np.array([row["wavelength"] for row in spec])
+        f = np.array([row["flux_lambda"] for row in spec])
+        plt.plot(w, f)
+        plt.title(spec.attrs.TITLE)
+    plt.show()
+
+if __name__ == "__main__":
+    main()

### 2017-01-30 doc/ms.tex
backup
Include changes to abstract and introduction

@@
 \newcommand{\ycao}[1]{{\color{red} ycao: {#1}}}
+\newcommand{\amiller}[1]{{\color{blue} amiller: {#1}}}
 %%
@@
 
-  We report discovery of an extraordinarily young Type Ia supernova
-  iPTF16abc by the intermediate Palomar Transient Factory. Our first
-  observation was made only $0.18$ days after the onset of the
-  supernova explosion. Our analysis shows that the early emission of
-  this supernova dominantly comes from the radioactive decay instead
-  of supernova shock breakout or collision between the ejecta and a
-  possible companion star. The fast initial rise of the supernova, the
-  velocity evolution of spectral lines, and the strong and short-lived
-  carbon feature in the earliest spectra together provide strong
-  evidence of strong mixing of synthesized radioactive elements during
-  the supernova explosion.
+  We report the discovery of an extraordinarily young Type Ia supernova,
+  iPTF16abc, by the intermediate Palomar Transient Factory. Our first
+  observation was made only $0.18$~d after the onset of the
+  supernova explosion.
+Our analysis shows that the early emission from iPTF16abc is dominated by radioactive decay, and that contributions from supernova shock breakout or the ejecta colliding with a stellar companion are minimal.
+The combination of (i) a fast initial rise, (ii) the
+  early exponential decline in the photospheric velocity, and (iii) the significant presence of ionized carbon in the earliest spectra together provide
+  evidence for the strong mixing of radioactive elements in the supernova ejecta. \amiller{There should be something about dark times/lack of dark time for this SN in the abstract.}
 
@@
 Although Type Ia supernovae (SNe Ia) have been extensively used as
-standardizable candles, their progenitor scenarios and explosion
-physics are still in debate (see a recent review by
-\citealt{2014ARA&A..52..107M}). Detailed extermely early-phase
-observations are one of the most promising avenues to further
+standardizable candles, their progenitors and explosion
+physics are still debated (see a recent review by
+\citealt{2014ARA&A..52..107M}). Extremely detailed
+observations in the hours to days after explosion are one of the most promising avenues to further
 constrain this problem.
@@
 While the shock breakout of a SN Ia occurs on a sub-second timescale,
-the subsequent quasi-adiabatic expanding and cooling of the unbinded
-ejecta produces thermal emissions that can be used to infer the
+the subsequent quasi-adiabatic expanding and cooling of the unbound
+ejecta produces thermal emission that can be used to infer the
 original size of the exploding star
 \citep{2010ApJ...708..598P,2011ApJ...728...63R}. Comparing models of
-these cooling emissions to the earliest-phase data of SN2011fe,
-\citet{2012ApJ...744L..17B} concluded that the radius of the
-progenitor star is $\lesssim0.01\sr$ where $\sr$ is the solar
+this cooling emission to the earliest-phase data of SN~2011fe,
+\citet{2012ApJ...744L..17B} concluded that the radius of the SN~2011fe progenitor is $\lesssim0.01\sr$, where $\sr$ is the solar
 radius. Combining this size constraint and the measured ejecta mass to
 derive the mean density of the progenitor star, we confirmed that the
-progenitor star is compact and degenerate. Admittedly, due to the
+progenitor star is compact and degenerate\ycao{Ref?}. \ycao{a transition is missing here - not sure how the second half of this paragraph relates to the first} Admittedly, due to the
 initial small surface area of the progenitor star, the shock cooling
 emission of a SN Ia decays drastically as the ejecta expands. Given
-typical parameters of a SN Ia, this thermal emission is visible from
+typical parameters for a SN Ia, this thermal emission is visible from
 events up to $\sim 10\,\textrm{Mpc}$ within one day of their explosions.
 
-Another expectation from the extremely early-phase observations of a
-SN Ia is the excess emission from collisions between SN ejecta and a
-companion star, a natural consequence from the single-degenerate
-progenitor hypothesis \citep{1973ApJ...186.1007W,2010ApJ...708.1025K}.
-In a low-velocity SN Ia iPTF14atg, \citet{2015Natur.521..328C} for the
-first time detected a strong and declining ultraviolet pulse within a
-few days of the SN explosion which is best interpreted as the
-SN-companion collision. This signature has been searched in a number
-of nearby, early-phase normal SNe Ia, but most of these studies result
-in no detection
+SN Ia resulting from a white dwarf and non-degenerate companion, referred to as the single-degenerate progenitor, early-phase observations may detect excess emission due to the collision of the SN ejecta and the non-degenerate companion \citep{1973ApJ...186.1007W,2010ApJ...708.1025K}.
+This excess emission was first detected in iPTF14atg,  \citep{2015Natur.521..328C}, a low-velocity SN Ia with a significant and declining ultraviolet pulse detected within a
+few days of the SN explosion. This signature is best interpreted as a
+SN ejecta-companion collision. Many studies have searched for this excess emission, with most resulting in non-detections
 \citep{2010ApJ...722.1691H,2011ApJ...741...20B,2012ApJ...744...38F,
@@
   2013ApJ...778L..15Z,2015ApJ...799..106G,2016ApJ...826..144S,
-  2015ApJS..221...22I}. The exception is SN2012cg which
-\citet{2016ApJ...820...92M} claimed detection of blue excess in the
-earliest-phase light curve and attribute it to SN-companion collision.
-However, this statement is recently challenged by
-\citet{2016arXiv161007601S}. In fact, it is not surprising that no
-SN-companion collision has been observationally confirmed, because
-only up to $\sim 10\%$ of events from the single-degenerate channel
-have the preferred binary geometry for us to see the collision
-signatures.
+  2015ApJS..221...22I}. An exception is SN2012cg, 
+  as a blue excess in its early-phase light curve is attributed to an ejecta-companion collision in \citet{2016ApJ...820...92M} (though see \citealt{2016arXiv161007601S} for an alternative interpretation).
+With only $\sim 10\%$ of single-degenerate progenitors occupying the preferred binary geometry for us to see the collision
+signatures, it is not surprising that there are few confirmed detections in the literature \ycao{ref?}.
 

### 2017-02-01 doc/ms.tex
Full changes to the language in the entire manuscript.

@@
 
-More commonly, the only observed light curve of a SN Ia is purely
-powered by the radioactive decay of synthesized $^{56}$Ni. Since
-$^{56}$Ni atoms are synthesized, mixed and deposited into different
-layers inside the ejecta, the SN may experience a dark period after
-the SN shock breakout and before the radioactive energy diffuses to
-the photosphere \citep{2014ApJ...784...85P}. In the case of strong
-mixing, $^{56}$Ni energy can reach the photosphere rapidly. As such,
-the dark period is very short and the light curve shows a fast initial
-rise. In the opposite case, it may take up to a couple of days for
-the $^{56}$Ni energy to diffuse to the photosphere. The initial rise
-of the light curve is then moderate \citep{2016ApJ...826...96P}. To
-summarize, the initial rise of the light curve of a SN Ia conveys
-information on distribution of synthesized $^{56}$Ni.
+The detection of SN shock breakout or an ejecta-companion collision is exceedingly rare, and the vast majority of SNe Ia are observed to be 
+powered purely by the radioactive decay of $^{56}$Ni. 
+SNe Ia may experience a dark period after
+the SN shock breakout but before radioactive energy diffuses into
+the photosphere depending on how the newly synthesized $^{56}$Ni is mixed and deposited into different layers of the ejecta \citep{2014ApJ...784...85P}. If there is strong
+mixing, photons from $^{56}$Ni decay can reach the photosphere rapidly.
+This leads to a short dark period and a fast initial rise in the observed optical light curve.
+For weak mixing, it may take several days for
+the radioactive energy to diffuse to the photosphere. The initial rise
+of the light curve is then moderate \citep{2016ApJ...826...96P}. Thus, the initial rise of SN Ia light curves conveys
+information on the distribution of synthesized $^{56}$Ni.
 
 In this paper, we report observations of an extraordinarily young SN
-Ia iPTF16abc, which was discovered by the intermediate Palomar
-Transient Factory on 2016 April $3.36$\footnote{all times in this
+Ia, iPTF16abc, which was discovered by the intermediate Palomar
+Transient Factory on 2016 April $3.36$\footnote{All times in this
   paper are in UTC.} at $\textrm{R.A.}=13^h34^m45.49^s$,
@@
 transient is spatially coincident with a tidal tail of the galaxy
-NGC\,5221 at 100\,Mpc. No activity was detected at the same location
-down to $g=22.1$\,mag on April $2.42$. Our spectroscopic follow-up
+NGC\,5221, which lies at a distance of $\sim$100\,Mpc. iPTF16abc is not detected to a limit of $g=22.1$\,mag on April $2.42$, less than 1 d prior to discovery. Our spectroscopic follow-up
 compaign classified iPTF16abc as a normal SN Ia
-\citep{2016ATel.8909....1C}.
+\citep{2016ATel.8909....1C}. Our observations and analysis provide multiple lines of evidence that the $^{56}$Ni produced by iPTF16abc was strongly mixed throughout the ejecta. 
+\ycao{My personal preference is to not include section by section outline, esp for short papers - this info is clear from section titles. But if you want to include this feel free}
 
-This paper is organized as follows: Section \ref{sec:obs} describes
-photometric and spectroscopic observations of iPTF16abc. Section
-\ref{sec:usual_staff} establishes that iPTF16abc is a normal SN Ia
-in NGC\,5221. Section \ref{sec:first_light} analyzes the early
-light curve and spectra.
+% This paper is organized as follows: Section \ref{sec:obs} describes
+% photometric and spectroscopic observations of iPTF16abc. Section
+% \ref{sec:usual_staff} establishes that iPTF16abc is a normal SN Ia
+% in NGC\,5221. Section \ref{sec:first_light} analyzes the early
+% light curve and spectra.
 
@@
   \includegraphics[width=0.95\textwidth]{lightcurve.pdf}
-  \caption{Multi-band light curves of iPTF16abc are shown. Filters are
-    denoted by different colors and observation instruments by
-    different markers. The $t_{max}$ time is the B-band maximum
+  \caption{Multi-band light curves of iPTF16abc. Each filter is
+  represented with a different color, and each instrument with a 
+  different symbol. $t_{max}$ is the time of B-band maximum
     determined by SALT2 (Section \ref{sec:classification}). The solid
     curves are best-fit results from SALT2. The black ticks near the
-    top of the figure shows epochs of spectroscopic observations.}
+    top of the figure show epochs of spectroscopic observations.}
   \label{fig:lightcurve}
@@
 
-As part of the iPTF transient survey in the 2016 spring quarter, the
-field of iPTF16abc was observed in $g$- or $R$-band every night by the
-CFH12K camera \citep{2000SPIE.3965...58S} on the 48-inch telescope at
-Palomar Observatory (P48). The images were processed by the IPAC image
+During the spring of 2016, the iPTF survey observed the field of iPTF16abc every night in either the $g$- or $R$-band.
+Survey observations were conducted with the
+CFH12K camera \citep{2000SPIE.3965...58S} on the Palomar Observatory 48-inch telescope 
+ (P48). Images were processed by the IPAC image
 subtraction and discovery pipeline which subtracts off the background
 galaxy light with stacked pre-SN images and performs forced
-point-spread-function (PSF) photometry at the location of the SN. The
+point-spread-function (PSF) photometry at the location of the SN.\ycao{Add a reference to Frank's PTFIDE paper - http://iopscience.iop.org/article/10.1088/1538-3873/129/971/014002/pdf} The
 photometry is then calibrated to the PTF photometric catalog
@@
 
-After discovery, we utilized the rainbow camera of the SED Machine
-(\ycao{REF}) mounted on the 60-inch telescope at Palomar Observatory
-(P60) to undertake photometric observations in $g$, $r$ and $i$
-filters. The image differencing against the archival SDSS images and
-forced PSF photometry on the subtracted images were performed by the
-Fremling Automated Pipeline \citep{2016A&A...593A..68F}. The
-photometry is also calibrated to the SDSS catalog \ycao{which DR?}.
+After discovery, photometric observations in the $g'$, $r'$ and $i'$
+filters were obtained with the SED Machine 
+(SEDM; \ycao{REF}) mounted on the Palomar Observatory 
+60-inch telescope (P60).
+We utilized the Fremling Automated Pipeline \citep{2016A&A...593A..68F} to subtract galaxy light from the SEDM images using achival Sloan Digital Sky Survey (SDSS) images as reference images.
+This pipeline then performed forced-PSF photometry at the location of iPTF16abc, which is calibrated to the SDSS catalog \ycao{which DR?}.
 
-Las Cambres Observatory Global Network (LCOGT) also carry out
-photometric observations in the \textit{BVgri} filters with its 1-m
+photometric observations in the \textit{BVgri} were conducted by the Las Cambres Observatory Global Network (LCOGT) 1-m
 telescope network.  PSF photometry was measured on these images using
@@
 
-In space, \textit{Swift} observed iPTF16abc for 14 epochs, covering
-from the very early phase to the post-peak phase. Aperture photometry
-are carried out on the images taken by its Ultraviolet-Optical
-Telescope (UVOT) with the usual procedures in the HEASoft and
-corrected for the coincident loss and aperture loss. The image counts
+In space, \textit{Swift} observed iPTF16abc on 14 epochs, beginning $\sim$15 d pre-maximum light through $\sim$5 d post maximum.
+\ycao{check and confirm numbers} The SN flux is measured via aperture photometry on Ultraviolet-Optical
+Telescope (UVOT) images via the usual procedures in the HEASoft, including corrections for the coincident loss and aperture loss. The image counts
 are converted to physical fluxes using the latest calibration
-\citep{2011AIPC.1358..373B}. No pre-SN UVOT image at the SN location
-is available in the \textit{Swift} archive.  Visual inspection to the
-UVOT images suggests that the background galaxy light in the UVOT
-filters is probably negligible. No X-ray emission was detected at the
-location of the SN by the X-ray Telescope (XRT) in any of these
-epochs.
+\citep{2011AIPC.1358..373B}. There are no pre-SN UVOT images at the SN location available in the \textit{Swift} archive.  Visual inspection of the
+UVOT images suggests negligible host-galaxy contamination in our UVOT flux measurements. There is no X-ray emission detected at the 
+SN position by the \textit{Swift} X-ray Telescope (XRT).
 
-The multi-color light curves of iPTF16abc are illustrated in Figure
-\ref{fig:lightcurve}.  For convenience, magnitudes in \textit{all}
+The multi-color light curves of iPTF16abc are illustrated in 
+Figure~\ref{fig:lightcurve}.  For convenience, magnitudes in \textit{all}
 filters are in the AB system with a zero point of $3631$\,Jy.
@@
 of telescopes and instruments in multiple epochs spanning from a
-couple of days after explosion to two months after its maximum. An
-observing log is listed in Table \ref{tab:spec_obs_log}. Data
-reduction is undertaken with usual routines in IDL/Python. Except for
-the high-resolution spectra obtained by VLT instruments, the optical
+couple of days after explosion to two months after $B$-band maximum. An
+observing log is listed in Table \ref{tab:spec_obs_log}. The spectra were reduced using standard routines in \texttt{IDL}/\texttt{Python}. The optical
 spectral evolution of iPTF16abc is illustrated in Figure
-\ref{fig:spec_seq}.
+\ref{fig:spec_seq}, which excludes high-resolution Very Large Telescope (VLT) spectra for clarity.
 
@@
 
-The foreground Galactic extinctioin along the directionof iPTF16abc
-has $E(B-V)=0.0279\,\textrm{mag}$ \citep{2011ApJ...737..103S}.
+The foreground Galactic extinction toward iPTF16abc
+is $E(B-V)=0.0279\,\mathrm{mag}$ \citep{2011ApJ...737..103S}.
 
-In the highest-resolution spectrum of iPTF16abc by UVES, individual
-components of both \ion{Ca}{2}\,H$+$K and \ion{Na}{1}\,D doublets show
-double-absorption profiles (Figure \ref{fig:narrow_features}),
-indicating two sources of absorption along the line of sight. Fitting
+Our highest-resolution spectrum of iPTF16abc, obtained with VLT/UVES, shows multiple absorption components for each of the individual lines in the \ion{Ca}{2}\,H$+$K and \ion{Na}{1}\,D doublets (Figure \ref{fig:narrow_features}).
+This indicates there are two sources of absorption along the line of sight.
+Fitting
 two Gaussian kernels to each line of the \ion{Na}{1} doublet
 simultaneously leads to redshifts of $0.02313820\pm0.00000032$ and
-$0.02322408\pm0.00000033$. The total equivalent widths of the
-\ion{Na}{1}\,D1 and D2 lines are $0.595\pm0.009\,\textrm{\AA}$ and
-$0.609\pm0.008\,\textrm{\AA}$m, respectively. Using the empirical
-relation between the equivalent width of \ion{Na}{1}\,D lines and
+$0.02322408\pm0.00000033$. The total \ion{Na}{1}\,D equivalent width (EW) is $0.595\pm0.009\,\textrm{\AA}$ and
+$0.609\pm0.008\,\textrm{\AA}$, respectively. Using the empirical
+relation between the EW of \ion{Na}{1}\,D lines and
 reddening $E(B-V)$ \citep{2012MNRAS.426.1465P}, we derive
-$E(B-V)=0.361\pm0.025\textrm{mag}$. We caution that the empirical
-relation has a quite large scatter.
+$E(B-V)=0.361\pm0.025\textrm{mag}$. We note that this relation has large scatter.
 
-In the X-shooter spectra of iPTF16abc, we also identify narrow
-absorption features \ion{K}{1}\,7665\,\AA and 7699\,\AA at consistent
-redshifts. However, the resolution of the X-shooter spectra is not
-fine enough to resolve the double-absorption profiles of \ion{Ca}{2}
-and \ion{Na}{1}. The X-shooter spectra do not show the diffusive
-interstellar band at 5780\,\AA as well.  Albeit some debates (e.g.,
-\citealt{2013ApJ...779...38P}), the $E(B-V)$ value derived from
-\ion{Na}{1}\,D absorption provides the best estimate in the case of
-iPTF16abc.
+In the VLT/X-shooter spectra of iPTF16abc, we also identify narrow \ion{K}{1}\,7665\,\AA\ and 7699\,\AA\ absorption at the same
+redshifts. The double-absorption profiles of \ion{Ca}{2}
+and \ion{Na}{1} are not resolved in the VLT/X-shooter spectra. Furthermore, the X-shooter spectra do not show the diffusive
+interstellar band at 5780\,\AA.
+For iPTF16abc, \ion{Na}{1}\,D provides the best estimate of host-galaxy reddening (though see \citealt{2013ApJ...779...38P} for a discussion on why \ion{Na}{1}\,D is a poor tracer of redenning).
 
@@
 
-The \ion{Na}{1}\,D doublet are seen in multiple spectra spanning
-from pre-peak to post-peak phases. Despite the instrumental widening of
-different instrument configurations, we do not detect obvious variation
-in the profiles of the doublet.
+We detect \ion{Na}{1}\,D in multiple spectra both before and after peak.
+After accounting for differing instrumental resolutions, we do not detect any obvious variations in the \ion{Na}{1}\,D profiles.
 
-We also note in Figure \ref{fig:narrow_features} that the absorption
-profiles of \ion{Ca}{2}\,H$+$K are quite different from those of \ion{Na}{1}\,D
-doublet, implying that the dust compositions in the two absorption sources
-may have some difference.
+Finally, we note that the \ion{Ca}{2}\,H$+$K absorption profile is quite different from the \ion{Na}{1}\,D profile. 
+This suggests that the dust composition may differ in the two absorption components.
 
@@
 
-We run Supernova Identification (SNID; \citealt{2007ApJ...666.1024B})
-on the low-resolution spectrum of iPTF16abc at $+18.8$ and found best
-matches to normal SNe Ia. In fact, the characteristic features of a SN
+Using the Supernova Identification (SNID; \citealt{2007ApJ...666.1024B}) package, 
+we find the low-resolution spectrum of iPTF16abc at $+18.8$ d is best matched by normal SNe Ia. Several characteristic features of a SN
 Ia, such as \ion{Si}{2}, \ion{S}{2}, can be easily identified in the
@@
 
-Next we standardize the light curve of iPTF16abc by feeding its P48
-and P60 light curves into the \texttt{sncosmo} module\footnote{The
+To determine the brightness and time of $B$-band maximum for 
+iPTF16abc, we fit the P48 and P60 light curves with the \texttt{sncosmo} software package.\footnote{The
   \texttt{sncosmo} Python module is available at
-  \url{https://sncosmo.readthedocs.io/en/v1.4.x/}.} and fit a light
-curve model, which composes of the SALT2 template
-\citep{2007A&A...466...11G} modified by the line-of-sight extinction
+  \url{https://sncosmo.readthedocs.io/en/v1.4.x/}.} This fit includes a SALT2 template \citep{2007A&A...466...11G} modified by the line-of-sight extinction
 curve \citep{1999PASP..111...63F} with $E(B-V)$ values from Section
-\ref{sec:reddening} and $R_V=3.1$. We obtain the rest-frame
-\textit{B}-band peak time $\textrm{MJD}_{max}=57499.65\pm0.02$, the coefficient
+\ref{sec:reddening} and $R_V=3.1$.
+
+We determine the time of rest-frame \textit{B}-band maximum to be 
+ $\textrm{MJD}_{max}=57499.65\pm0.02$, the coefficient
 of the zeroth principle component $x_0=0.0275\pm0.0002$, the
@@
 the color term $c=-0.3353\pm0.0054$. The best-fit model also gives an
-unreddened apparent peak magnitude of $m^*_{B}=14.4\,\textrm{mag}$ in
+unreddened apparent peak magnitude of $m^*_{B}=14.4\,\textrm{mag}$ \ycao{uncertainties on Bmax?} in
 the SN rest frame.
@@
 
-After establishing iPTF16abc as a normal SN ia, we use the latest
+After establishing iPTF16abc as a normal SN Ia, we use the latest
 calibration \citep{2014A&A...568A..22B} of the Phillips relation
@@
 galaxy NGC\,5221. \citet{2007A&A...465...71T} derived a distance
-modulus of $35.0\pm0.4\,\textrm{mag}$ from the Tully-Fisher
+modulus of $35.0\pm0.4\,\textrm{mag}$ to NGC\,5221 from the Tully-Fisher
 relation. This distance modulus is consistent with that of iPTF16abc.
@@
 absorption resources are probaly located on the tidal tail of
-NGC\,5221.
+NGC\,5221.\ycao{This is confusing - are those velocities relative to host redshift or LSR?}
 
@@
 
-In this section, we estimate the first light and explosion time of
-iPTF16abc.
-
 \subsection{Light Curve Fit}
@@
 
-Extrapolation of the earliest-phase light curve with a simple
-mathematical model is usually used to estimate the first light time of
-a SN. In theory, \citet{1982ApJ...253..785A} derived a quadratic law
-for an ideal expanding fireball with a constant temperature. In order
-to account for variation of photospheric temperatures during
-expansion, we utilize a power-law curve to model the early light curve.
+The time of first light for SNe is usually estimated by 
+extrapolating early-phase light curves to match simple 
+mathematical models. Assuming an ideal exapnding fireball with 
+constant temperature, \citet{1982ApJ...253..785A} derives that $f 
+\propto t^2$, where $f$ is the SN flux and $t$ is the time since 
+explosion. To account for variations of the photospheric 
+temperature during expansion, we model the early light curve as a power law:
 \begin{equation}
@@
     \end{array}
-  \right.\ .
+  \right.\ ,
 \end{equation}
-Since the first few detections of the SN were made in the \textit{g}
-band, our modeling is limited to the early \textit{g}-band light
-curve. We minimize $\chi^2$ in a large search grid of $t_0$, $\alpha$
-and the proportionality constant. We also note that the definition of
+where $t_0$ is the time of first light and $alpha$ is the power-law index.
+We limit our fit to the earliest detections of iPTF16abc, which were exclusively in $g$-band.
+To determine the best fit parameters, we search a large grid over $t_0$, $\alpha$
+and the proportionality constant, and minimize $\chi^2$. 
+We note that the definition of
 the time window for the early light curve may affect the fitting
 result, so we experiment the fitting procedure with different time
-windows. The modeling results show that the SN flux between
-$t=-19\,\textrm{days}$ and $t=-15\,\textrm{days}$ rises approximately
-linearly. Figure \ref{fig:early_lc_fit} shows the best-fit result and
+windows. \ycao{I don't understand what this previous sentence means}
+The modeling results show that the SN flux rises approximately
+linearly between
+$t=-19\,\textrm{d}$ and $t=-15\,\textrm{d}$. Figure \ref{fig:early_lc_fit} shows the best-fit result and
 the joint marginal distribution of $t_0$ and $\alpha$. With the
 best-fit model of $\alpha=0.92$ and $t_0=-18.47$ days, our first
-observation was made only $0.18\,\textrm{day}$ after the first light
-of the SN. The total rise time to the \textit{B}-band peak is $18.47$
+detection of iPTF16abc was made only $\sim{0.2}\,\textrm{d}$ after 
+the SN first light. From the fit, we additionally infer a total rise time to \textit{B}-band peak of $18.47$
 days.
@@
 
-Starting from $t=-15\,\textrm{days}$, the \textit{g}-band light curve
-rises significantly faster than the best-fit model above, indicating a
-greater value of the power-law index $\alpha$. In fact, the light
-curve between $t=-14$ and $t=-8$\,days can be fitted with another
-power law of index $1.40$. In another word, the whole light curve
+Starting around $t=-15\,\textrm{d}$, the $g$-band light curve 
+deviates from the above best-fit model and 
+rises significantly faster, indicating a
+change in the power-law index $\alpha$. In fact, between $t=-14\,\mathrm{d}$ and $t=-8\,\mathrm{d}$ the light curve is well fit by a power law of index $1.40$. In other words, the entire light curve
 before $t=-8$\,days can be approximated by a broken power-law model
@@
 As discussed in Section \ref{sec:lc_energy}, the initial light curve
-of iPTF16abc is probably purely powered by radioactive decay of
-$^{56}$Ni. Therefore, the initial rise of the light curve depends on
+of iPTF16abc is probably purely powered by the radioactive decay of
+$^{56}$Ni. Thus, the initial rise of the light curve depends on
 the depth of the shallowest layer where $^{56}$Ni is deposited
@@
 strong mixing of $^{56}$Ni in the ejecta. As a result, the time lag
-between the SN explosion and the initial rise of the radioactively
-powered light curve is negligible.
+between the time of explosion and SN first light is negligible.
 
@@
 
-In order to constrain the explosion time of the SN independently of
-the SN light curve, \citet{2014ApJ...784...85P} suggested to measure
-the expansion velocities of the photosphere, because the expansion of
-the ejecta starts at the onset of the SN explosion. Assuming a
-constant opacity in the ejecta, the photospheric velocity evolves as
-$v_{ph}\propto(t-t_{exp})^{-0.22}$. While the photospheric velocities
-are not easy to measure, line velocities of \ion{Si}{2} or \ion{Ca}{2}
-are usually used to approximate the photospheric velocities
+Due to the possibility of an early dark phase for SNe Ia, \citet{2014ApJ...784...85P} suggest that photospheric velocity measurements be used to determine the time of explosion, because the ejecta expand from the onset of the SN explosion.
+Assuming a
+constant opacity in the ejecta, \citeauthor{2014ApJ...784...85P} find that the photospheric velocity evolves as
+$v_{ph}\propto(t-t_{exp})^{-0.22}$. While the photospheric velocity
+is not easy to measure, line velocities of \ion{Si}{2} or \ion{Ca}{2}
+can be used as a proxy
 \citep{2014ApJ...784...85P,2016ApJ...826..144S}.
 
-In the case of iPTF16abc, the \ion{Ca}{2} IR triplet is very weak in
-the spectra probably due to high temperatures in the ejecta. Thus we
-perform our measurements on the \ion{Si}{2}\,6355 line. Visual
-inspection of the spectra shows no sign of multi-velocity components
+In the case of iPTF16abc, the \ion{Ca}{2} IR triplet is very weak, 
+probably due to high ejecta temperature. Thus, we
+determine the photospheric velocity from the \ion{Si}{2}\,6355 line. Visual
+inspection shows no sign of multi-velocity components
 of \ion{Si}{2}, and that the \ion{C}{2}\,6580 line overlaps the red
-wing of the \ion{Si}{2} line. Consequently we apply a mathematical
-model of two gaussian kernels superposed on a linear term, which
-accounts for the absorption of \ion{Si}{2} and \ion{C}{2} and the
-continuum component, respectively, to approach the observed spectra
-between $5,900$ and $6,500$\,\AA (rest-frame). The expansion
-velocity of \ion{Si}{2} is calculated at the central wavelength
+wing of the \ion{Si}{2} line. Consequently, we model the observed 
+spectra between $5,900$ and $6,500$\,\AA (rest-frame)
+with two gaussian kernels superposed on a linear baseline, which
+accounts for \ion{Si}{2}, \ion{C}{2} and the
+continuum, respectively. The expansion
+velocity of \ion{Si}{2} is measured by the central wavelength
 of the \ion{Si}{2} Gaussian kernel.
@@
 with a 3-$\sigma$ confidence interval between $-17.4\,\textrm{days}$
-and $-18.3\,\textrm{days}$ (Figure \ref{fig:velocity_t_exp}). We also
-alter the power-law index to $-0.20$ and $-0.24$ to examine how
-sensitively the result depends on the assumed power-law index.  we
-find consistent results within respective 3-$\sigma$ confidence
-intervals.
+and $-18.3\,\textrm{days}$ (Figure \ref{fig:velocity_t_exp}). We additionally
+alter the power-law index to $-0.20$ and $-0.24$ to examine the
+sensitively of the result on the assumed power-law index.  This 
+leads to consistent results within the respective 3-$\sigma$ 
+confidence intervals.
 
-Keeping in mind that $t_{exp}$ has a very large uncertainty mostly due
-to the assumption in the $v\propto(t-t_{exp})^{-0.22}$ model, we
-compare the estimated $t_{exp}$ to $t_0$ (left panel of Figure
-\ref{fig:velocity_t_exp}) and find that $t_0\lessapprox t_{exp}$.
-Since physical causality requires $t_{exp}<t_0$, we draw a qualitative
-conclusion that $t_0\simeq t_{exp}$. This conclusion is consistent
-with our inference from the early light curve analysis in Section
-\ref{sec:lc_fit}.
+Compare the estimated $t_{exp}$ to $t_0$ (left panel of Figure
+\ref{fig:velocity_t_exp}), we find that $t_0\lessapprox t_{exp}$.\footnote{Note that the uncertainties on $t_{exp}$ are large due to assumptions in the $v\propto(t-t_{exp})^{-0.22}$ model.}
+Since physical causality requires $t_{exp}<t_0$, we draw the qualitative
+conclusion that $t_0\simeq t_{exp}$, which is consistent
+with our inference from the early light curve analysis (Section
+\ref{sec:lc_fit}).
 
-With $t_{exp}$, we estimate the actual rise time of iPTF16abc from the
-SN explosion to its \textit{B}-band maximum to be $17.95$ days.  In
-comparison, SN2011fe has $t_0=-17.7$ days \citep{2013A&A...554A..27P}
+From $t_{exp}$, we estimate the actual rise time of iPTF16abc from the
+time of explosion to \textit{B}-band maximum to be $17.95$ d.  In
+comparison, SN2011fe has $t_0=-17.7$ d \citep{2013A&A...554A..27P}
 with a preceding dark period of $\sim 1$ day
@@
 maximum is roughly a constant, which largely depends on the total mass
-of synthesized $^{56}$Ni.
+of synthesized $^{56}$Ni.\ycao{I am not convinced by this last sentence}
 
@@
 
-Another intriguing spectral feature of iPTF16abc is strong absorption of
-\ion{C}{2}\,6580 and \ion{C}{2}\,7234 lines. Our analysis on the
+iPTF16abc exhibits unusually strong absorption of
+\ion{C}{2} $\lambda\lambda$6580, 7234 for SNe Ia. Our analysis of the
 \ion{Si}{2}\,6355 line also allows us to measure the velocities and
 pseudo-equivalent widths (pEWs) of \ion{C}{2}\,6580. We also fit a Gaussian
-kernel superposing on a linear term to the spectral region near
-the \ion{C}{2}\,7234 line to measure its velocity and pseudo-equivalent
-width. The velocity evolution of \ion{C}{2} is shown in the right panel
+kernel with linear baseline to the spectral region near
+the \ion{C}{2}\,7234 line to measure its velocity and pEW. 
+The velocity evolution of \ion{C}{2} is shown in the right panel
 of Figure \ref{fig:velocity_t_exp} and the pEW evolution
@@
 $t=-15.8$ days, the pEW of \ion{C}{2}\,6580 is comparable to that
-of \ion{Si}{2}\,6355. Then the pEW of \ion{C}{2} decreases
-until they disappear at about $t=-10$ days.
+of \ion{Si}{2}\,6355. Subsequent spectra the pEW of \ion{C}{2} 
+decreases until the feature is no longer detectable 
+around $t=-10$ days.
 
@@
 
-Formation of \ion{C}{2} absorption requires existence of both unburned
-carbon and $^{56}$Ni, the latter of which is responsible to ionize the
-carbon atoms. The strong and short-lived \ion{C}{2} features observed
-in the spectra of iPTF16abc show that a certain amount of carbon atoms
-exist in the outer layers of the ejecta and that $^{56}$Ni atoms are also
-strongly mixed in the same layers. This provides a third piece of evidence
-to strong mixing in the iPTF16abc ejecta.
+\ion{C}{2} absorption requires the existence of both unburned
+carbon and $^{56}$Ni, which radioactively decays and ionizes the C 
+atoms. The strong and short-lived \ion{C}{2} features reveal 
+that $^{56}$Ni atoms have been strongly mixed in to the outter 
+layers of the ejecta. This provides a third piece of evidence
+for strong mixing in the iPTF16abc ejecta.
 
-Carbon signatures are seen in over $1/4$ of all normal SNe Ia before
+Carbon signatures are seen in $> 1/4$ of all normal SNe Ia before
 maxima
 \citep{2011ApJ...732...30P,2012MNRAS.425.1917S,2011ApJ...743...27T},
-but the signatures are usually weak. Even in SN2011fe, the \ion{C}{2}
+but the signatures are usually weak. Even in SN2011fe, which was discovered and spectroscopically observed shortly after explosion, the \ion{C}{2}
 features are not strong in the first spectra
@@
 strong \ion{C}{2} features at early phases is SN2013dy
-\citep{2013ApJ...778L..15Z}. Unlike iPTF16abc, however, the equivalent
-widths of \ion{C}{2} features in SN2013dy are as large as those of
-\ion{Si}{2}\,6355 in the same spectra.
+\citep{2013ApJ...778L..15Z}. Unlike iPTF16abc, however, the pEWs 
+of the \ion{C}{2} features in SN2013dy are \ycao{not?} as large as 
+those of \ion{Si}{2}\,6355 in the same spectra.
 
-\subsection{Discussions}
+\subsection{Discussion}
 \label{sec:lc_energy}
 
-Early radiation of a SN Ia may have multiple energy sources: SN shock
-breakout, SN-companion collision, and radioactive activity. The
-previous analysis is based on the assumption that the light curve of
+Multiple energy sources can contribute to the early radiation from a SN Ia: SN shock
+breakout, SN ejecta-companion collision, and radioactive 
+$^{56}$Ni. The previous analysis is based on the assumption that the light curve of
 iPTF16abc is powered purely by radioactive decay. Here we discuss the
@@
 compare the early-phase \textit{g}-band light curve of iPTF16abc with
-two cooling models \citep{2011ApJ...728...63R, 2010ApJ...708..598P}
-and reach a not very constraining conclusion that the radius of the
-progenitor star of iPTF16abc should be $<1\sr$. In fact, with a
-typical $0.01\sr$ radius of a white dwarf, the cooling emission of a
-SN Ia is negligible at the time of the first detection of iPTF16abc.
+two cooling models \citep{2011ApJ...728...63R, 2010ApJ...708..598P}. From this comparison, we limit the radius of 
+the
+progenitor of iPTF16abc to be $<1\sr$, which is a weak constraint compared to SN~2011fe. Assuming a 
+typical white-dwarf radius for the progenitor, $\sim{0.01}\sr$, the cooling emission of a
+SN Ia is negligible at the time of our first iPTF16abc detection. 
+Thus, we conclude that shock cooling does not contribute to the 
+early light from iPTF16abc.
 
@@
 
-From a SN Ia born in a single-degenerate system, with an odd of
-$\lesssim10\%$ due to the geometry, we expect to see emission produced
-by SN ejecta slamming into the companion. According to calculations by
-\citet{2010ApJ...708.1025K}, collision between SN ejecta and the
-companion star generates thermal emission with a spectrum with
-spectrum that peaks in the ultraviolet. The Rayleigh-Jeans tail
-emission in the \textit{g} band is very weak.
+SNe Ia with single-degenerate progenitors can produce detectable 
+radiation following the collision of the SN ejecta with the 
+non-degenerate companion. Geometrically the odds of such a 
+detection are low, however, at $\sim$10\%. According to 
+calculations by
+\citet{2010ApJ...708.1025K}, SN ejecta-companion star collisions 
+generate thermal emission with a spectrum that peaks in the 
+ultraviolet. Thus, any resulting \textit{g}-band emission is very weak.
 
-In order to examine the possible SN-companion signature in the early
+To examine the possibility of a SN-companion signature in the early
 light curve of iPTF16abc, we employ the \citet{2010ApJ...708.1025K}
-model by assuming an ejecta mass of $1.4\sm$, an expansion velocity of
+model and assume an ejecta mass of $1.4\sm$, an expansion velocity of
 $10^{4}\,\textrm{km}\,\textrm{s}^{-1}$, and a constant opacity of
@@
 \citet{2012ApJ...749...18B}.  Figure \ref{fig:SN-companion} compares
-the calculated \textit{g}-band apparent magnitudes of SN-companion
-collision for different combinations of binary separation and viewing
+the expected \textit{g}-band apparent magnitudes of SN-companion
+collisions for different binary separation assuming the optimal viewing
 angle against the first detection of iPTF16abc. The figure shows that,
-even with the most favored viewing angle, the binary separation would
+even with the most favorable viewing angle, the binary separation would
 have to exceed $2\times10^{14}\,\textrm{cm}$. Under the model assumption that the
 companion fills its Roche lobe, the companion star would have to have
-a radius of $\sim10^{14}\,\textrm{cm}\simeq10^{4}\sr$. Given that the
-mass of the companion is $\sim1\sr$, such a large radius seems unlikely.
-Therefore, we conclude that the early emission of iPTF16abc is not likely
-to originate from the SN-companion collision.
+a radius of $\sim10^{14}\,\textrm{cm}\simeq10 \mathrm{AU}$. Given that the
+mass of the companion is $\sim1\sr$, such a large radius is unphysical.
+Therefore, we conclude that the early emission of iPTF16abc is not 
+due to a collision between the eject and a non-degenerate companion.
 
@@
   \includegraphics[width=0.45\textwidth]{SNCompanion.pdf}
-  \caption{apparent magnitude of SN-companion collision (gray region)
+  \caption{Apparent magnitude of a SN-companion collision (gray region)
     against the first detection of iPTF16abc (black).}
@@
 
-In this paper, we present observations of an extraordinarily young
-normal Type Ia supernova iPTF16abc at one tidal tail of NGC\,5221. Our
-extraordinarily fast-response follow-up compaign of this supernova
-allows us to draw the following conclusions:
+We have presented observations of the extraordinarily early discovery of the 
+normal Type Ia supernova iPTF16abc. Our fast-response follow-up 
+compaign allowed us to draw the following conclusions:
 \begin{itemize}
-\item By extrapolating the early light curve, we determine that the
-  first light of the SN light curve was only $0.18$ days before our
-  first observation.
-\item Our analysis shows that the observed early-phase light curve is
-  probably powered by radioactive decay of $^{56}$Ni, instead of SN
-  shock breakout or SN-companion collision (provided that iPTF16abc
+\item By extrapolating the early light curve, we determined that the
+  SN first light occured only $\sim{0.2}$ d before our
+  first detection.
+\item Our analysis showed that the observed early-phase light curve is
+  probably powered by $^{56}$Ni radioactive decay. We find no 
+  evidence for detectable signatures of SN
+  shock breakout or SN ejecta-companion collision (provided that 
+  iPTF16abc
   is born in a single-degenerate channel).
-\item Our measurements on the spectral line velocities shows that the
-  actual explosion date of the SN is approximately equal to the time
-  of the first light of the SN light curve, indicating that
-  synthesized $^{56}$Ni atoms are mixed out into the outer layers of
+\item Our measurements of the spectral line velocities show that the
+  SN explosion date is approximately equal to the time
+  of the first light. This indicates that
+  synthesized $^{56}$Ni atoms are strongly mixed into the 
+  outer layers of
   the supernova ejecta.
-\item The strong mixing of $^{56}$Ni is also supported by strong and
-  short-lived carbon features in the earliest spectra of iPTF16abc. 
+\item The strong and short-lived carbon features seen in the 
+  earliest spectra of iPTF16abc provide additional evidence
+  for strong $^{56}$Ni mixing in the SN ejecta.  
 \end{itemize}
 
-Observations of extraordinarily young supernovae provide a ``smoking
-gun'' to probe the mixing level in the ejecta, which, in turn, results
-directly from the explosion mechanisms. With the ongoing and planned
-time-domain survyes, a large number of extraordinarily young supernovae
-will be collected in the next few years. With such a sample, we will
-be able to make connections between the observed supernovae and proposed
-mechanisms.
+Extremely early observations of young SNe provide a ``smoking
+gun'' to probe the mixing level in the ejecta, which, in turn, is 
+a result of the explosion mechanism. Ongoing and planned
+time-domain surveys will discover a large number of very young supernovae over the next few years. As this sample grows, we will
+be able to make connections between the observed SN properties and 
+proposed explosion mechanisms.
 
-It should also be emphasized that much of the analysis presented in
-this paper would not be possible without the fast-response and
-extensive photometric and spectroscopic follow-up compaign. With the
-great potential of discoveries in the surveys, researchers need to
-be prepared and organized for follow-up observations.
+Finally, we close by emphasizing the importance of fast-response photometric and spectroscopic follow-up campaigns.
+Without the early recognition of the youth of this SN and the associated follow-up, much of the analysis presented herein would not have been possible.
+Moving forward, the ability to trigger such observations is essential to improve our understanding of the physics of SNe Ia.
 

### 2017-05-12 doc/ms.tex
backup

--- 2017-01-20 doc/ms.tex
@@
 Although Type Ia supernovae (SNe Ia) have been extensively used as
-standardizable candles, their progenitor scenarios and explosion
-physics are still in debate (see a recent review by
-\citealt{2014ARA&A..52..107M}). Detailed extermely early-phase
-observations are one of the most promising avenues to further
-constrain this problem.
+standardizable candles, their progenitor systems and explosion
+mechanisms remain unclear (see a recent review by
+\citealt{2014ARA&A..52..107M}). Observations of extremely young
+events are one promising avenue to further
+investigation of this problem.
 
-While the shock breakout of a SN Ia occurs on a sub-second timescale,
-the subsequent quasi-adiabatic expanding and cooling of the unbinded
-ejecta produces thermal emissions that can be used to infer the
-original size of the exploding star
-\citep{2010ApJ...708..598P,2011ApJ...728...63R}. Comparing models of
-these cooling emissions to the earliest-phase data of SN2011fe,
-\citet{2012ApJ...744L..17B} concluded that the radius of the
+While the shock breakout of a SN Ia occurs on a minisecond timescale,
+the subsequent adiabatic cooling of the unbinded ejecta during its free
+expansion produces thermal emission, before the radioactive energy manages
+to heat up the photosphere of the ejecta. The thermal emission during this
+phase therefore be used to infer the original size of the exploding star
+\citep{2010ApJ...708..598P,2011ApJ...728...63R}. For example,
+the earliest observations of SN2011fe allowed
+\citet{2012ApJ...744L..17B} to conclude that the radius of the
 progenitor star is $\lesssim0.01\sr$ where $\sr$ is the solar
-radius. Combining this size constraint and the measured ejecta mass to
-derive the mean density of the progenitor star, we confirmed that the
-progenitor star is compact and degenerate. Admittedly, due to the
-initial small surface area of the progenitor star, the shock cooling
-emission of a SN Ia decays drastically as the ejecta expands. Given
-typical parameters of a SN Ia, this thermal emission is visible from
-events up to $\sim 10\,\textrm{Mpc}$ within one day of their explosions.
+radius and that the progenitor has to be compact and degenerate.
+However, due to the small surface area of the progenitor star,
+the cooling emission at this phase is not luminous and decays rapidly.
+As a result, this method is only applicable to events
+within $\sim 10\,\textrm{Mpc}$.
 
-Another expectation from the extremely early-phase observations of a
-SN Ia is the excess emission from collisions between SN ejecta and a
-companion star, a natural consequence from the single-degenerate
-progenitor hypothesis \citep{1973ApJ...186.1007W,2010ApJ...708.1025K}.
-In a low-velocity SN Ia iPTF14atg, \citet{2015Natur.521..328C} for the
-first time detected a strong and declining ultraviolet pulse within a
-few days of the SN explosion which is best interpreted as the
-SN-companion collision. This signature has been searched in a number
-of nearby, early-phase normal SNe Ia, but most of these studies result
-in no detection
-\citep{2010ApJ...722.1691H,2011ApJ...741...20B,2012ApJ...744...38F,
-  2012ApJ...744L..17B,2015Natur.521..332O,
-  2013ApJ...778L..15Z,2015ApJ...799..106G,2016ApJ...826..144S,
-  2015ApJS..221...22I}. The exception is SN2012cg which
-\citet{2016ApJ...820...92M} claimed detection of blue excess in the
-earliest-phase light curve and attribute it to SN-companion collision.
-However, this statement is recently challenged by
-\citet{2016arXiv161007601S}. In fact, it is not surprising that no
-SN-companion collision has been observationally confirmed, because
-only up to $\sim 10\%$ of events from the single-degenerate channel
-have the preferred binary geometry for us to see the collision
-signatures.
+If a SN Ia is born in the single degenerate (SD) channel
+\citep{1973ApJ...186.1007W}, then the SN ejecta slams into the companion and
+produces a non-thermal X-ray flash. Once the fast-moving ejecta covers the
+collision region, the collision heats up the surrounding material. The
+collisional energy is then released near the direction of the companion (about
+a few to ten percent of the $4\pi$ solid angle) as thermal emission with a
+spectrum that peaks in the UV \citep{2010ApJ...708.1025K}.
+This SN-companion collisional
+signature serves as a ``smoking gun'' for the SD channel, because it is not
+expected in the competing double-degenerate channel \ycao{REF}. This signature
+has been searched in several nearby SNe Ia and a few samples of distant
+SNe Ia \citep{2010ApJ...722.1691H,2011ApJ...741...20B,2012ApJ...744...38F,
+2012ApJ...744L..17B,2015Natur.521..332O,2013ApJ...778L..15Z,
+2015ApJ...799..106G,2016ApJ...826..144S,2015ApJS..221...22I}, only in a
+low-velocity SNe Ia was a strong and declining ultraviolet (UV) pulse seen
+within a few days of the explosion.
 
-More commonly, the only observed light curve of a SN Ia is purely
-powered by the radioactive decay of synthesized $^{56}$Ni. Since
-$^{56}$Ni atoms are synthesized, mixed and deposited into different
-layers inside the ejecta, the SN may experience a dark period after
-the SN shock breakout and before the radioactive energy diffuses to
-the photosphere \citep{2014ApJ...784...85P}. In the case of strong
-mixing, $^{56}$Ni energy can reach the photosphere rapidly. As such,
-the dark period is very short and the light curve shows a fast initial
-rise. In the opposite case, it may take up to a couple of days for
-the $^{56}$Ni energy to diffuse to the photosphere. The initial rise
-of the light curve is then moderate \citep{2016ApJ...826...96P}. To
-summarize, the initial rise of the light curve of a SN Ia conveys
-information on distribution of synthesized $^{56}$Ni.
+More commonly, the observed light curve of a SN Ia is purely
+powered by the radioactive decay of synthesized $^{56}$Ni.
+Depending on the depth of the shallowest layer where $^{56}$Ni is deposited,
+the SN may experience a dark period before the radioactive energy diffuses to
+the photosphere. According to the calculation in \citet{2016ApJ...826...96P},
+strong mixing leads to a short dark period and a fast initial rise, while
+weak mixing results in a long dark period and a moderate initial rise.
+Measuring the initial rise rate of a SN Ia allows us to constrain the mixing
+level of the SN ejecta which is closely related to the explosion mechanism.
 
-In this paper, we report observations of an extraordinarily young SN
-Ia iPTF16abc, which was discovered by the intermediate Palomar
+In this paper, we report observations of a young SN Ia iPTF16abc within a day
+of its explosion. This SN was discovered by the intermediate Palomar
 Transient Factory on 2016 April $3.36$\footnote{all times in this
@@
 down to $g=22.1$\,mag on April $2.42$. Our spectroscopic follow-up
-compaign classified iPTF16abc as a normal SN Ia
-\citep{2016ATel.8909....1C}.
+compaign classified iPTF16abc as a normal SN Ia \citep{2016ATel.8909....1C}.
 

### 2017-06-06 doc/ms.tex
Update the text to reflect new values following an improved fit to the SALTs parameters.

--- 2017-02-01 doc/ms.tex
@@
 To determine the brightness and time of $B$-band maximum for 
-iPTF16abc, we fit the P48 and P60 light curves with the \texttt{sncosmo} software package.\footnote{The
+iPTF16abc, we fit the P60 light curves with the \texttt{sncosmo} software package.\footnote{The
   \texttt{sncosmo} Python module is available at
-  \url{https://sncosmo.readthedocs.io/en/v1.4.x/}.} This fit includes a SALT2 template \citep{2007A&A...466...11G} modified by the line-of-sight extinction
+  \url{https://sncosmo.readthedocs.io/en/v1.5.x/}.} This fit includes a SALT2 template \citep{2007A&A...466...11G} modified by the line-of-sight extinction
 curve \citep{1999PASP..111...63F} with $E(B-V)$ values from Section
@@
 We determine the time of rest-frame \textit{B}-band maximum to be 
- $\textrm{MJD}_{max}=57499.65\pm0.02$, the coefficient
-of the zeroth principle component $x_0=0.0275\pm0.0002$, the
-coefficient of the first principle component $x_1=1.200\pm0.043$, and
-the color term $c=-0.3353\pm0.0054$. The best-fit model also gives an
-unreddened apparent peak magnitude of $m^*_{B}=14.4\,\textrm{mag}$ \ycao{uncertainties on Bmax?} in
+ $\textrm{MJD}_{max}=57499.54\pm0.23$, the coefficient
+of the zeroth principle component $x_0 = XXX \pm XXX$, the
+coefficient of the first principle component $x_1 = 0.9655 \pm 0.0003$, and
+the color term $c = 0.012 \pm 0.029$. The best-fit model also gives an
+unreddened apparent peak magnitude of $m^*_{B}=15.6\,\textrm{mag}$ \ycao{uncertainties on Bmax?} in
 the SN rest frame.
@@
 For convenience, in the following sections, we define the best-fit
-value $\textrm{MJD}_{max}=57499.65$ as phase $t=0$.
+value $\textrm{MJD}_{max}=57499.54$ as phase $t=0$.
 
@@
 \citep{1993ApJ...413L.105P} using $m^*_{B}$, $x_1$ and $c$ to derive a
-distance modulus $\mu=34.66\pm0.03\,\textrm{mag}$ to the SN, provided
+distance modulus $\mu = 34.72 \pm 0.09 \,\textrm{mag}$ to the SN, provided
 that the host galaxy of iPTF16abc has a stellar mass less than
-$10^{10}\sm$.
+$10^{10}\sm$. We note that a more massive host galaxy would result in a larger inferred distance modulus that is nevertheless consistent within the uncertainties.
 

### 2017-06-06 doc/ms.tex

@@
  $\textrm{MJD}_{max}=57499.54\pm0.23$, the coefficient
-of the zeroth principle component $x_0 = XXX \pm XXX$, the
-coefficient of the first principle component $x_1 = 0.9655 \pm 0.0003$, and
+of the zeroth principle component $x_0 = 0.0093 \pm 0.0003$, the
+coefficient of the first principle component $x_1 = 0.97 \pm 0.15$, and
 the color term $c = 0.012 \pm 0.029$. The best-fit model also gives an

### 2017-06-14 doc/ms.tex
Include major rewrite of the paper to reflect new figures and updated analysis of the explanation for the early observations of iPTF 16abc.

--- 2017-06-06 doc/ms.tex
@@
 \newcommand{\sr}{R_\odot}
+\newcommand{\abc}{iPTF\,16abc}
 
@@
 %% this information may be modified by the editorial offices.
-\shorttitle{iPTF16abc}
-\shortauthors{Cao et al.}
+\shorttitle{\abc}
+\shortauthors{Alphabet Friends}
 %%
@@
 
-\title{Optifcal Observations of an Extraordinarily Young Type Ia Supernova iPTF16abc}
+\title{Let There Be Light: \\ Early Observations of the Normal Type Ia Supernova \abc\ \\Show No Evidence for a Dark Period}
 
@@
 
-\author[0000-0002-8036-8491]{Yi Cao}
-\affil{eScience Institute and Astronomy Department, University of Washington,
-  Seattle, WA 98195}
+% \author[0000-0002-8036-8491]{Yi Cao}
+% \affil{eScience Institute and Astronomy Department, University of Washington,
+%   Seattle, WA 98195}
 
-\author{Friends}
+\author{The Alphabet Friends}
 \affil{the intermediate Palomar Transient Factory}
@@
 
-  We report the discovery of an extraordinarily young Type Ia supernova,
-  iPTF16abc, by the intermediate Palomar Transient Factory. Our first
-  observation was made only $0.18$~d after the onset of the
-  supernova explosion.
-Our analysis shows that the early emission from iPTF16abc is dominated by radioactive decay, and that contributions from supernova shock breakout or the ejecta colliding with a stellar companion are minimal.
-The combination of (i) a fast initial rise, (ii) the
-  early exponential decline in the photospheric velocity, and (iii) the significant presence of ionized carbon in the earliest spectra together provide
-  evidence for the strong mixing of radioactive elements in the supernova ejecta. \amiller{There should be something about dark times/lack of dark time for this SN in the abstract.}
+Early observations of type Ia supernovae (SNe) provide a unique probe of their progenitor systems and explosion physics.
+Here, we report the intermediate Palomar Transient Factory (iPTF) discovery of an extraordinarily young Type Ia supernova, \abc.
+The initial detection of the SN was made only $0.18$~d after the time of first light.
+In the $\sim$24 hr after discovery \abc\ rose by $\sim$2 mag in the $g_\mathrm{PTF}$ band, which is very rare for young type Ia SNe.
+Furthermore, by measuring the evolution of the photospheric velocity we determine that the time of explosion for \abc\ is approximately equal to the time of first light.
+Spectra obtained in the week after explosion reveal the presence of strong \ion{C}{2} absorption, which steadily fades over that time period.
+We show that the unusually fast, near-linear rise in flux for \abc\ cannot be explained by either SN shock breakout and the assciated subsequent cooling or the collision of the SN ejecta with a stellar companion.
+Instead, we show that each of the unusual characteristics of \abc: (i) the rapid, near-linear rise, (ii) the lack of a dark period between explosion and first light, and (iii) the strong lines from ionized carbon in the earliest spectra, can all be explained if radioactive $^{56}$Ni is strongly mixed throughout the SN ejecta.
+In the next few years, dozens of very young \textit{normal} SNe Ia will be discovered, and observations similar to those presented here will constrain the white dwarf explosion mechanism.
 
@@
 %% keywords and the rules for their use.
-\keywords{methods: observational --- supernovae: individual (iPTF16abc)}
+\keywords{methods: observational --- supernovae: individual (\abc)}
 
@@
 Although Type Ia supernovae (SNe Ia) have been extensively used as
-standardizable candles, their progenitors and explosion
+standardizable candles, their progenitor systems and explosion
 physics are still debated (see a recent review by
@@
 While the shock breakout of a SN Ia occurs on a sub-second timescale,
-the subsequent quasi-adiabatic expanding and cooling of the unbound
+the subsequent quasi-adiabatic expansion and cooling of the unbound
 ejecta produces thermal emission that can be used to infer the
-original size of the exploding star
+radius of the exploding star
 \citep{2010ApJ...708..598P,2011ApJ...728...63R}. Comparing models of
 this cooling emission to the earliest-phase data of SN~2011fe,
-\citet{2012ApJ...744L..17B} concluded that the radius of the SN~2011fe progenitor is $\lesssim0.01\sr$, where $\sr$ is the solar
-radius. Combining this size constraint and the measured ejecta mass to
-derive the mean density of the progenitor star, we confirmed that the
-progenitor star is compact and degenerate\ycao{Ref?}. \ycao{a transition is missing here - not sure how the second half of this paragraph relates to the first} Admittedly, due to the
-initial small surface area of the progenitor star, the shock cooling
-emission of a SN Ia decays drastically as the ejecta expands. Given
-typical parameters for a SN Ia, this thermal emission is visible from
-events up to $\sim 10\,\textrm{Mpc}$ within one day of their explosions.
+\citet{2012ApJ...744L..17B} concluded that the explosion came from a 
+stars with $R_\ast \lesssim 0.02\sr$, where $\sr$ is the solar
+radius. Combining the radius constraint with the measured ejecta 
+mass \citeauthor{2012ApJ...744L..17B} derive the mean density of the 
+progenitor star, confirming that at least some type Ia SNe come from 
+compact and degenerate stars.
 
-SN Ia resulting from a white dwarf and non-degenerate companion, referred to as the single-degenerate progenitor, early-phase observations may detect excess emission due to the collision of the SN ejecta and the non-degenerate companion \citep{1973ApJ...186.1007W,2010ApJ...708.1025K}.
-This excess emission was first detected in iPTF14atg,  \citep{2015Natur.521..328C}, a low-velocity SN Ia with a significant and declining ultraviolet pulse detected within a
-few days of the SN explosion. This signature is best interpreted as a
-SN ejecta-companion collision. Many studies have searched for this excess emission, with most resulting in non-detections
-\citep{2010ApJ...722.1691H,2011ApJ...741...20B,2012ApJ...744...38F,
+Early phase observations of SNe Ia from a white dwarf (WD)$+$non-degenarate binary
+may detect excess emission, relative to most type Ia SNe, due to the 
+collision of the SN ejecta with the non-degenerate companion 
+\citep{1973ApJ...186.1007W,2010ApJ...708.1025K}. This excess 
+emission was first detected in iPTF\,14atg  \citep{2015Natur.521..328C}, a low-velocity SN Ia with a significant and declining ultraviolet (UV) pulse detected within a
+few days of the SN explosion. This UV pulse is best interpreted as a
+SN ejecta-companion collision. While such emission requires a 
+favorable geometric alignment and is only expected in $\lesssim$ 
+10\% of SNe Ia \citep{2010ApJ...708.1025K}, many studies have 
+searched for signatures of an ejecta-companion interaction, 
+typically resulting in non-detections 
+(e.g., \citealt{2010ApJ...722.1691H,2011ApJ...741...20B,2012ApJ...744...38F,
   2012ApJ...744L..17B,2015Natur.521..332O,
   2013ApJ...778L..15Z,2015ApJ...799..106G,2016ApJ...826..144S,
-  2015ApJS..221...22I}. An exception is SN2012cg, 
-  as a blue excess in its early-phase light curve is attributed to an ejecta-companion collision in \citet{2016ApJ...820...92M} (though see \citealt{2016arXiv161007601S} for an alternative interpretation).
-With only $\sim 10\%$ of single-degenerate progenitors occupying the preferred binary geometry for us to see the collision
-signatures, it is not surprising that there are few confirmed detections in the literature \ycao{ref?}.
+  2015ApJS..221...22I}). A possible exception is SN\,2012cg, 
+which exhibited excess blue emission in its early-phase light curve 
+\citet{2016ApJ...820...92M} (though see 
+\citealt{2016arXiv161007601S} for an interpretation that does not 
+invoke ejecta-companion interaction). 
+% With only $\sim 10\%$ of single-degenerate progenitors occupying the preferred binary geometry for us to see the collision
+% signatures, it is not surprising that there are few confirmed detections in the literature \ycao{ref?}.
 
-The detection of SN shock breakout or an ejecta-companion collision is exceedingly rare, and the vast majority of SNe Ia are observed to be 
-powered purely by the radioactive decay of $^{56}$Ni. 
-SNe Ia may experience a dark period after
-the SN shock breakout but before radioactive energy diffuses into
-the photosphere depending on how the newly synthesized $^{56}$Ni is mixed and deposited into different layers of the ejecta \citep{2014ApJ...784...85P}. If there is strong
-mixing, photons from $^{56}$Ni decay can reach the photosphere rapidly.
-This leads to a short dark period and a fast initial rise in the observed optical light curve.
-For weak mixing, it may take several days for
-the radioactive energy to diffuse to the photosphere. The initial rise
-of the light curve is then moderate \citep{2016ApJ...826...96P}. Thus, the initial rise of SN Ia light curves conveys
-information on the distribution of synthesized $^{56}$Ni.
+The vast majority of SNe Ia are observed 
+to be powered purely by the radioactive decay of $^{56}$Ni. 
+While the detection of SN shock cooling or ejecta-companion interaction is rare, the level of $^{56}$Ni mixing in the SN ejecta can fundamentally alter the appearance of the SN shortly after explosion.
+SNe Ia experience a dark period after
+the SN shock breakout but before radioactive energy  
+diffuses into the photosphere \citep{2014ApJ...784...85P}. The 
+duration of this dark period is set by how the newly synthesized 
+$^{56}$Ni is mixed and deposited into different layers of the ejecta.
+In the case of strong mixing, the dark period is short, or 
+non-existent, as photons from $^{56}$Ni decay can reach the 
+photosphere rapidly. This also leads to blue optical colors and a 
+rapid initial rise in the observed light curve. If the mixing is 
+weak and the $^{56}$Ni is confined to the innermost layers of the 
+ejecta, the dark period can last for several days as the radioactive 
+energy diffuses to the photosphere. The early evolution of such SNe 
+results in redder colors and a more moderate rise in luminosity 
+\citep{2016ApJ...826...96P}.
+Thus, the early light curves of even non-exotic type Ia SNe convey information about their progenitor systems by constraining the distribution of synthesized $^{56}$Ni, which in turn constrains the explosion mechanism.
 
 In this paper, we report observations of an extraordinarily young SN
-Ia, iPTF16abc, which was discovered by the intermediate Palomar
-Transient Factory on 2016 April $3.36$\footnote{All times in this
+Ia, \abc, which was discovered by the intermediate Palomar
+Transient Factory (iPTF) on 2016 April $3.36$\footnote{All times in this
   paper are in UTC.} at $\textrm{R.A.}=13^h34^m45.49^s$,
-$\textrm{Dec.}=+13^d51^m14.3^s$ (J2000) with a $g$-band magnitude of
-$21.31\pm0.27$ \citep{2016PASP..128k4502C,2016ATel.8907....1M}. The
+$\textrm{Dec.}=+13^d51^m14.3^s$ (J2000) with a $g_\mathrm{PTF}$-band magnitude of
+$21.31\pm0.27$ \citep{2016ATel.8907....1M}. The
 transient is spatially coincident with a tidal tail of the galaxy
-NGC\,5221, which lies at a distance of $\sim$100\,Mpc. iPTF16abc is not detected to a limit of $g=22.1$\,mag on April $2.42$, less than 1 d prior to discovery. Our spectroscopic follow-up
-compaign classified iPTF16abc as a normal SN Ia
-\citep{2016ATel.8909....1C}. Our observations and analysis provide multiple lines of evidence that the $^{56}$Ni produced by iPTF16abc was strongly mixed throughout the ejecta. 
-\ycao{My personal preference is to not include section by section outline, esp for short papers - this info is clear from section titles. But if you want to include this feel free}
+NGC\,5221, which lies at a distance of $\sim$100\,Mpc.
+\abc\ is not detected to a limit of $g=22.1$\,mag on April $2.42$, less than 1 d prior to discovery, and rose by $\sim$2 mag in the 24 hr following its initial detection.
+Our spectroscopic follow-up
+compaign classified \abc\ as a normal SN Ia
+\citep{2016ATel.8909....1C}. Our observations and analysis provide multiple lines of evidence that the $^{56}$Ni produced by \abc\ was strongly mixed throughout the ejecta.
 
 % This paper is organized as follows: Section \ref{sec:obs} describes
-% photometric and spectroscopic observations of iPTF16abc. Section
-% \ref{sec:usual_staff} establishes that iPTF16abc is a normal SN Ia
+% photometric and spectroscopic observations of \abc. Section
+% \ref{sec:usual_staff} establishes that \abc\ is a normal SN Ia
 % in NGC\,5221. Section \ref{sec:first_light} analyzes the early
@@
   \centering
-  \includegraphics[width=0.95\textwidth]{lightcurve.pdf}
-  \caption{Multi-band light curves of iPTF16abc. Each filter is
-  represented with a different color, and each instrument with a 
-  different symbol. $t_{max}$ is the time of B-band maximum
-    determined by SALT2 (Section \ref{sec:classification}). The solid
-    curves are best-fit results from SALT2. The black ticks near the
-    top of the figure show epochs of spectroscopic observations.}
+  \includegraphics[width=0.95\textwidth]{logLC_with_colors.pdf}
+  \caption{Photometric evolution of \abc. \textit{Top}: The $g$-band
+  light curve of \abc. Observations from different 
+  telescopes are shown with different symbols. Time is measured in 
+  rest-frame d relative to the time of first light, $t_0$ (see 
+  \S\ref{sec:lc_fit}). Note that the horizonal axis is shown with a linear scale 
+  for $-2 \; \mathrm{d} \le t - t_0 \le 3 \; \mathrm{d}$ and a 
+  $\log$ scale for $t - t_0 > 3 \; \mathrm{d}$. The solid curve 
+  represents the best-fit model from SALT2 
+  (\S\ref{sec:classification}). The black ticks near the
+  bottom of the panel show epochs of spectroscopic observations.
+  \textit{Bottom}: Color curves of \abc. Each color curve is 
+  represented with a different color, with each symbol corresponding 
+  to a different instrument, as detailed in the legend. Magnitude 
+  offsets applied to each color curve are also shown.
+  }
   \label{fig:lightcurve}
@@
 
-During the spring of 2016, the iPTF survey observed the field of iPTF16abc every night in either the $g$- or $R$-band.
+During the spring of 2016, the iPTF survey observed the field of \abc\ every night in either the $g_\mathrm{PTF}$- or 
+$R_\mathrm{PTF}$-band.\footnote{P48 observations of \abc\ is reported in the $g_\mathrm{PTF}$ and $R_\mathrm{PTF}$ filters throughout, which are similar to the SDSS $g'$ and $r'$ filters, respectively (see \citealt{2012PASP..124..854O} for details on PTF calibration).
+The correction from the $g_\mathrm{PTF}$ and $R_\mathrm{PTF}$ filters to SDSS $g'$ and $r'$ requires knowledge of the intrinsic source color (see Eqns.~1 and 2 in \citealt{2012PASP..124..854O}).
+The spectral diversity of SNe Ia in the days after explosion is poorly constrained, and as a result the color terms for \abc\ at these epochs are unknown.
+We proceed by assuming $g_\mathrm{PTF}$ and $R_\mathrm{PTF}$ calibration is on the AB system, which strictly speaking is incorrect, but this does not fundamentally alter any of our conclusions.}
 Survey observations were conducted with the
-CFH12K camera \citep{2000SPIE.3965...58S} on the Palomar Observatory 48-inch telescope 
- (P48). Images were processed by the IPAC image
+CFH12K camera \citep{2000SPIE.3965...58S} on the Palomar Observatory 
+48-inch telescope (P48). Images were processed by the IPAC image
 subtraction and discovery pipeline which subtracts off the background
 galaxy light with stacked pre-SN images and performs forced
-point-spread-function (PSF) photometry at the location of the SN.\ycao{Add a reference to Frank's PTFIDE paper - http://iopscience.iop.org/article/10.1088/1538-3873/129/971/014002/pdf} The
+point-spread-function (PSF) photometry at the location of the SN 
+\citep{2017PASP..129a4002M}. The
 photometry is then calibrated to the PTF photometric catalog
@@
 filters were obtained with the SED Machine 
-(SEDM; \ycao{REF}) mounted on the Palomar Observatory 
+(SEDm; Blagorodnova et al.\ 2017, in prep.) mounted on the Palomar Observatory 
 60-inch telescope (P60).
-We utilized the Fremling Automated Pipeline \citep{2016A&A...593A..68F} to subtract galaxy light from the SEDM images using achival Sloan Digital Sky Survey (SDSS) images as reference images.
-This pipeline then performed forced-PSF photometry at the location of iPTF16abc, which is calibrated to the SDSS catalog \ycao{which DR?}.
+We utilized the Fremling Automated Pipeline \citep{2016A&A...593A..68F} to subtract galaxy light from the SEDm images using achival Sloan Digital Sky Survey (SDSS) images as a reference.
+This pipeline then performed forced-PSF photometry at the location of \abc, which is calibrated to the SDSS catalog \citep{2014ApJS..211...17A}.
 
-photometric observations in the \textit{BVgri} were conducted by the Las Cambres Observatory Global Network (LCOGT) 1-m
+Photometric observations in the \textit{BVg'r'i'} filters were conducted by the Las Cambres Observatory (LCO) 1-m
 telescope network.  PSF photometry was measured on these images using
@@
 \textit{BV} magnitudes are calibrated to the Fourth USNO CCD
-Astrograph Catalog \citep{2013AJ....145...44Z}, and the \textit{gri}
+Astrograph Catalog \citep{2013AJ....145...44Z}, and the \textit{g'r'i'}
 magnitudes are calibrated to SDSS Data Release 6
@@
 
-In space, \textit{Swift} observed iPTF16abc on 14 epochs, beginning $\sim$15 d pre-maximum light through $\sim$5 d post maximum.
-\ycao{check and confirm numbers} The SN flux is measured via aperture photometry on Ultraviolet-Optical
-Telescope (UVOT) images via the usual procedures in the HEASoft, including corrections for the coincident loss and aperture loss. The image counts
+The \textit{Swift} satellite observed \abc\ on 14 epochs, beginning 
+$\sim$15 d pre-maximum light through $\sim$22 d post maximum. The SN 
+flux is measured via aperture photometry on Ultraviolet-Optical
+Telescope (UVOT) images via the usual procedures in 
+\texttt{HEASoft}, including corrections for the coincident loss and 
+aperture loss. The image counts
 are converted to physical fluxes using the latest calibration
-\citep{2011AIPC.1358..373B}. There are no pre-SN UVOT images at the SN location available in the \textit{Swift} archive.  Visual inspection of the
-UVOT images suggests negligible host-galaxy contamination in our UVOT flux measurements. There is no X-ray emission detected at the 
-SN position by the \textit{Swift} X-ray Telescope (XRT).
+\citep{2011AIPC.1358..373B}. There are no pre-SN UVOT images at the 
+SN location in the \textit{Swift} archive.  Visual inspection of the
+UVOT images suggests negligible host-galaxy contamination in our 
+UVOT flux measurements. No X-ray emission is detected from \abc\ by the \textit{Swift} X-ray Telescope (XRT).
 
-The multi-color light curves of iPTF16abc are illustrated in 
-Figure~\ref{fig:lightcurve}.  For convenience, magnitudes in \textit{all}
-filters are in the AB system with a zero point of $3631$\,Jy.
+The $g$-band discovery data and color curves of \abc\ are 
+illustrated in Figure~\ref{fig:lightcurve}.  For convenience, 
+magnitudes in 
+\textit{all} filters are in the AB system with a zero point of 
+$3631$\,Jy. As previously noted the color terms necessary to convert the $g_\mathrm{PTF}$ and $R_\mathrm{PTF}$ to the AB system are unknown and assumed to be zero.
 
-Spectroscopic observations of iPTF16abc were undertaken with a variety
-of telescopes and instruments in multiple epochs spanning from a
-couple of days after explosion to two months after $B$-band maximum. An
-observing log is listed in Table \ref{tab:spec_obs_log}. The spectra were reduced using standard routines in \texttt{IDL}/\texttt{Python}. The optical
-spectral evolution of iPTF16abc is illustrated in Figure
+Spectroscopic observations of \abc\ were taken with a variety
+of telescopes and instruments over multiple epochs spanning from a
+couple of days after explosion to two months after $B$-band maximum. 
+An observing log is listed in Table \ref{tab:spec_obs_log}. The spectra were reduced using standard routines in \texttt{IDL}/\texttt{Python}. The optical
+spectral evolution of \abc\ is illustrated in Figure
 \ref{fig:spec_seq}, which excludes high-resolution Very Large Telescope (VLT) spectra for clarity.
@@
 \begin{deluxetable*}{cccccc}
-  \tablecaption{Spectroscopic observations of iPTF16abc \label{tab:spec_obs_log}}
+  \tablecaption{Spectroscopic observations of \abc\ \label{tab:spec_obs_log}}
   \tablehead{
@@
   \includegraphics[width=1.0\textwidth]{spectra.pdf}
-  \caption{Low-resolution spectra of iPTF16abc are shown in the
-    chronical orders. In order for better illustration, each spectrum
-    is normalized by the median flux value between $6,000$ and
-    $7,000\,\textrm{\AA}$ and offset properly.  The phases in units of
-    days are noted next to corresponding spectra. Telluric absorption
+  \caption{Observed spectral sequence of \abc. For clarity, offsets 
+  have been applied to each 
+  spectrum which are normalized by their median flux between 
+  6,000 and 7,000$\,\textrm{\AA}$. The phase of each spectrum 
+  relative to $T_{B_\mathrm{max}}$ is shown. Telluric absorption
   bands are grayed out. The narrow \ion{Na}{1}\,D absorption is also
@@
 
-The foreground Galactic extinction toward iPTF16abc
-is $E(B-V)=0.0279\,\mathrm{mag}$ \citep{2011ApJ...737..103S}.
-
-Our highest-resolution spectrum of iPTF16abc, obtained with VLT/UVES, shows multiple absorption components for each of the individual lines in the \ion{Ca}{2}\,H$+$K and \ion{Na}{1}\,D doublets (Figure \ref{fig:narrow_features}).
-This indicates there are two sources of absorption along the line of sight.
-Fitting
-two Gaussian kernels to each line of the \ion{Na}{1} doublet
-simultaneously leads to redshifts of $0.02313820\pm0.00000032$ and
-$0.02322408\pm0.00000033$. The total \ion{Na}{1}\,D equivalent width (EW) is $0.595\pm0.009\,\textrm{\AA}$ and
-$0.609\pm0.008\,\textrm{\AA}$, respectively. Using the empirical
-relation between the EW of \ion{Na}{1}\,D lines and
-reddening $E(B-V)$ \citep{2012MNRAS.426.1465P}, we derive
-$E(B-V)=0.361\pm0.025\textrm{mag}$. We note that this relation has large scatter.
-
-In the VLT/X-shooter spectra of iPTF16abc, we also identify narrow \ion{K}{1}\,7665\,\AA\ and 7699\,\AA\ absorption at the same
-redshifts. The double-absorption profiles of \ion{Ca}{2}
-and \ion{Na}{1} are not resolved in the VLT/X-shooter spectra. Furthermore, the X-shooter spectra do not show the diffusive
-interstellar band at 5780\,\AA.
-For iPTF16abc, \ion{Na}{1}\,D provides the best estimate of host-galaxy reddening (though see \citealt{2013ApJ...779...38P} for a discussion on why \ion{Na}{1}\,D is a poor tracer of redenning).
-
-\begin{figure}[htb]
-  \centering
-  \includegraphics[width=0.45\textwidth]{narrow_abs_features.pdf}
-  \caption{Narrow absorption lines of iPTF16abc are shown in this
-    figure. The zero velocity corresponds to the redshift of the
-    apparent host NGC\,5221.}
-  \label{fig:narrow_features}
-\end{figure}
-
-We detect \ion{Na}{1}\,D in multiple spectra both before and after peak.
-After accounting for differing instrumental resolutions, we do not detect any obvious variations in the \ion{Na}{1}\,D profiles.
-
-Finally, we note that the \ion{Ca}{2}\,H$+$K absorption profile is quite different from the \ion{Na}{1}\,D profile. 
-This suggests that the dust composition may differ in the two absorption components.
+A detailed study of the reddening towards \abc\ is presented in a 
+companion paper (Ferretti et al.\ 2017, submitted). Briefly, the 
+foreground Galactic extinction toward \abc\
+is $E(B-V) = 0.0279 \, \mathrm{mag}$ \citep{2011ApJ...737..103S}.
+The high-resolution spectra presented in Ferretti et al.\ (2017) show multiple absorption components for both the \ion{Ca}{2}\,H$+$K and \ion{Na}{1}\,D doublets.
+While the equivalent width (EW) of these lines is quite large, implying a large amount of extinction (e.g., \citealt{2012MNRAS.426.1465P}), Ferretti et al.\ compare the evolution of \abc\ to the well-observed normal type Ia SN\,2011fe and find evidence for only a small amount of extinction.
+The empircal relation between the EW of \ion{Na}{1}\,D and extinction is known to have a large scatter, and thus, we instead adopt $E(B-V) = 0.05 \, \mathrm{mag}$ as the local extinction for \abc\ (Ferretti et al.\ 2017).
+For the remainder of our analysis we therefore adopt a total, Galactic $+$ host galaxy, line-of-sight extinction of $E(B-V) = 0.0779 \, \mathrm{mag}$.
 
@@
 Using the Supernova Identification (SNID; \citealt{2007ApJ...666.1024B}) package, 
-we find the low-resolution spectrum of iPTF16abc at $+18.8$ d is best matched by normal SNe Ia. Several characteristic features of a SN
+we find the low-resolution spectrum of \abc\ at $+18.8$ d is best matched by normal SNe Ia. Several characteristic features of a SN
 Ia, such as \ion{Si}{2}, \ion{S}{2}, can be easily identified in the
-spectra of iPTF16abc (Figure \ref{fig:spec_seq}).
+spectra of \abc\ (Figure \ref{fig:spec_seq}).
 
 To determine the brightness and time of $B$-band maximum for 
-iPTF16abc, we fit the P60 light curves with the \texttt{sncosmo} software package.\footnote{The
+\abc, we fit the P60 light curves with the \texttt{sncosmo} software package.\footnote{The
   \texttt{sncosmo} Python module is available at
   \url{https://sncosmo.readthedocs.io/en/v1.5.x/}.} This fit includes a SALT2 template \citep{2007A&A...466...11G} modified by the line-of-sight extinction
-curve \citep{1999PASP..111...63F} with $E(B-V)$ values from Section
-\ref{sec:reddening} and $R_V=3.1$.
+curve \citep{1999PASP..111...63F} with $E(B-V)$ values from 
+\S\ref{sec:reddening} and $R_V=3.1$.
 
@@
  $\textrm{MJD}_{max}=57499.54\pm0.23$, the coefficient
-of the zeroth principle component $x_0 = XXX \pm XXX$, the
-coefficient of the first principle component $x_1 = 0.9655 \pm 0.0003$, and
-the color term $c = 0.012 \pm 0.029$. The best-fit model also gives an
-unreddened apparent peak magnitude of $m^*_{B}=15.6\,\textrm{mag}$ \ycao{uncertainties on Bmax?} in
-the SN rest frame.
+of the zeroth principle component $x_0 = 0.0086 \pm 0.0003$, the
+coefficient of the first principle component $x_1 = 0.96 \pm 0.15$, 
+and the color term $c = 0.033 \pm 0.029$. The best-fit model also 
+gives an unreddened apparent peak magnitude of $m^*_{B}=15.80 \pm 
+0.04 \,\textrm{mag}$ in the SN rest frame.
 
 For convenience, in the following sections, we define the best-fit
-value $\textrm{MJD}_{max}=57499.54$ as phase $t=0$.
+value $\textrm{MJD}_{max}=57499.54$ as the time of $B$-band maximum, $T_{B_\mathrm{max}}$, which we also adopt as phase $t=0$.
 
@@
 
-After establishing iPTF16abc as a normal SN Ia, we use the latest
+After establishing \abc\ as a normal SN Ia, we use the latest
 calibration \citep{2014A&A...568A..22B} of the Phillips relation
-\citep{1993ApJ...413L.105P} using $m^*_{B}$, $x_1$ and $c$ to derive a
-distance modulus $\mu = 34.72 \pm 0.09 \,\textrm{mag}$ to the SN, provided
-that the host galaxy of iPTF16abc has a stellar mass less than
-$10^{10}\sm$. We note that a more massive host galaxy would result in a larger inferred distance modulus that is nevertheless consistent within the uncertainties.
+\citep{1993ApJ...413L.105P} using $m^*_{B}$, $x_1$ and $c$ to derive 
+a distance modulus $\mu = 34.88 \pm 0.10 \,\textrm{mag}$ to the SN, 
+provided that the host galaxy of \abc\ has a stellar mass less than
+$10^{10}\sm$. We note that a more massive host galaxy would result 
+in a larger inferred distance modulus that is nevertheless 
+consistent within the uncertainties.
 
-The location of iPTF16abc is spatially coincident with a tidal tail of
+The location of \abc\ is spatially coincident with a tidal tail of
 galaxy NGC\,5221. \citet{2007A&A...465...71T} derived a distance
-modulus of $35.0\pm0.4\,\textrm{mag}$ to NGC\,5221 from the Tully-Fisher
-relation. This distance modulus is consistent with that of iPTF16abc.
+modulus of $35.0\pm0.4\,\textrm{mag}$ to NGC\,5221 from the 
+Tully-Fisher relation, which is consistent with that of \abc.
 
-Separately, \citet{1998A&AS..130..333T} observed the 21-cm line in
-this galaxy and measured a redshift of $0.0233303\pm0.000027$.  The
-two components in the \ion{Na}{1}\,D have a relative velocity of
-$-57.6\pm8.1\,\textrm{km}\,\textrm{s}^{-1}$ and
-$-31.8\pm8.1\,\textrm{km}\,\textrm{s}^{-1}$, suggesting that both
-absorption resources are probaly located on the tidal tail of
-NGC\,5221.\ycao{This is confusing - are those velocities relative to host redshift or LSR?}
+Separately, \citet{2015MNRAS.447.1531C} observe the 21-cm line in
+NGC\,5221 and measure a redshift of $0.0234$, which we adopt for the remaining analysis in this paper.
 
@@
 The time of first light for SNe is usually estimated by 
-extrapolating early-phase light curves to match simple 
-mathematical models. Assuming an ideal exapnding fireball with 
+extrapolating early-phase light curves to determine when the 
+SN is equal to 0. Assuming an ideal exapnding fireball with 
 constant temperature, \citet{1982ApJ...253..785A} derives that $f 
 \propto t^2$, where $f$ is the SN flux and $t$ is the time since 
-explosion. To account for variations of the photospheric 
-temperature during expansion, we model the early light curve as a power law:
+explosion. Despite the basic assumption of a constant temperature at 
+early times, multiple studies have found that the early emission 
+from type Ia SNe can be described as a power law in time, with 
+power-law index consistent with 2, i.e. $f \propto t^2$ (e.g., \citep{2006AJ....132.1707C, 2010ApJ...712..350H, 2011MNRAS.416.2607G}).
+
+As our observations include especially early observations of \abc, there are upper limits $\sim$1 d prior to the discovery epoch, we model the early flux from \abc\ as a power law, but allow the power-lax index to vary, as opposed to fixing it at 2, to account for potential variations in the photospheric temperature during expansion:
 \begin{equation}
@@
 \end{equation}
-where $t_0$ is the time of first light and $alpha$ is the power-law index.
-We limit our fit to the earliest detections of iPTF16abc, which were exclusively in $g$-band.
+where $t_0$ is the time of first light and $\alpha$ is the power-law index.
+To determine $t_0$ and $\alpha$ we fit the earliest observations of \abc, which were taken exclusively with P48 in the $g_\mathrm{PTF}$ filter.
 To determine the best fit parameters, we search a large grid over $t_0$, $\alpha$
 and the proportionality constant, and minimize $\chi^2$. 
-We note that the definition of
-the time window for the early light curve may affect the fitting
-result, so we experiment the fitting procedure with different time
-windows. \ycao{I don't understand what this previous sentence means}
 The modeling results show that the SN flux rises approximately
 linearly between
-$t=-19\,\textrm{d}$ and $t=-15\,\textrm{d}$. Figure \ref{fig:early_lc_fit} shows the best-fit result and
+$t=-18\,\textrm{d}$ and $t=-15\,\textrm{d}$. Figure \ref{fig:early_lc_fit} shows the best-fit result and
 the joint marginal distribution of $t_0$ and $\alpha$. With the
-best-fit model of $\alpha=0.92$ and $t_0=-18.47$ days, our first
-detection of iPTF16abc was made only $\sim{0.2}\,\textrm{d}$ after 
-the SN first light. From the fit, we additionally infer a total rise time to \textit{B}-band peak of $18.47$
-days.
+best-fit model of $\alpha=0.96$ and $t_0=-18.4$ days, our first
+detection of \abc\ occurred $\sim{0.2}\,\textrm{d}$ after 
+the SN first light.
 
-\begin{figure*}[htb]
+\begin{figure*}[!htb]
   \centering
@@
 (e.g.,
-\citealt{2013ApJ...778L..15Z,2014ApJ...783L..24Z,2016arXiv161202097Z,
+\citealt{2016arXiv161202097Z,
   2016arXiv161202725Z}).
 
-As discussed in Section \ref{sec:lc_energy}, the initial light curve
-of iPTF16abc is probably purely powered by the radioactive decay of
-$^{56}$Ni. Thus, the initial rise of the light curve depends on
-the depth of the shallowest layer where $^{56}$Ni is deposited
-\citep{2014ApJ...784...85P}. According to theoretical mdels
-\citep{2016ApJ...826...96P}, the linearly rising light curve implies
-strong mixing of $^{56}$Ni in the ejecta. As a result, the time lag
-between the time of explosion and SN first light is negligible.
+As previously noted, the early emission from most SNe Ia can be explained via a $f \propto t^2$ model, including SNe with extremely early observations like \abc, such as SN\,2011fe \citep{2011Natur.480..344N}.
+Thus, the near-linear rise in flux over the first few days after first light for \abc\ is unusual.
+To our knowledge this behavior has only been observed in 2 other SNe (2013dy, 2014J; \citealt{2013ApJ...778L..15Z,2014ApJ...783L..24Z}).
+Any model to explain the observations of \abc\ must be able to account for this unusual behavior in the days after first light.
+
+% \amiller{Revisit this paragraph in context of discussion -- might need to be moved to later section} As discussed in Section \ref{sec:lc_energy}, the initial light curve
+% of \abc\ is probably purely powered by the radioactive decay of
+% $^{56}$Ni. Thus, the initial rise of the light curve depends on
+% the depth of the shallowest layer where $^{56}$Ni is deposited
+% \citep{2014ApJ...784...85P}. According to theoretical models
+% \citep{2016ApJ...826...96P}, the linearly rising light curve implies
+% strong mixing of $^{56}$Ni in the ejecta. As a result, the time lag
+% between the time of explosion and SN first light is negligible.
 
@@
 
-Due to the possibility of an early dark phase for SNe Ia, \citet{2014ApJ...784...85P} suggest that photospheric velocity measurements be used to determine the time of explosion, because the ejecta expand from the onset of the SN explosion.
-Assuming a
-constant opacity in the ejecta, \citeauthor{2014ApJ...784...85P} find that the photospheric velocity evolves as
+As previously noted, $t_0$ does not correspond to the time of 
+explosion, $t_\mathrm{exp}$, for type Ia SNe as the SN may 
+experience a dark phase following shock breakout before radioactive 
+energy can difuse to the photosphere. \citet{2014ApJ...784...85P} 
+instead suggest that measurements of the photospheric velocity be 
+used to determine $t_\mathrm{exp}$ given that the ejecta begin 
+expanding from the moment of explosion.  Assuming a
+constant opacity in the ejecta, \citeauthor{2014ApJ...784...85P} 
+find that the photospheric velocity evolves as
 $v_{ph}\propto(t-t_{exp})^{-0.22}$. While the photospheric velocity
@@
 
-In the case of iPTF16abc, the \ion{Ca}{2} IR triplet is very weak, 
-probably due to high ejecta temperature. Thus, we
-determine the photospheric velocity from the \ion{Si}{2}\,6355 line. Visual
-inspection shows no sign of multi-velocity components
-of \ion{Si}{2}, and that the \ion{C}{2}\,6580 line overlaps the red
-wing of the \ion{Si}{2} line. Consequently, we model the observed 
-spectra between $5,900$ and $6,500$\,\AA (rest-frame)
-with two gaussian kernels superposed on a linear baseline, which
+In the case of \abc, the \ion{Ca}{2} IR triplet is very weak, 
+likely due to high temperatures in the ejecta. Thus, we
+determine the photospheric velocity from the 
+\ion{Si}{2}\,$\lambda$6355 line. Visual inspection shows no 
+sign of multi-velocity components of \ion{Si}{2}, and that 
+\ion{C}{2}\,$\lambda$6580 line overlaps the red
+wing of the \ion{Si}{2} line (see Figures~\ref{fig:spec_seq} and \ref{}). Consequently, we model the observed 
+spectra between 5,900 and 6,500\,\AA (rest-frame) as the combination 
+of two gaussian kernels plus a linear baseline, which
 accounts for \ion{Si}{2}, \ion{C}{2} and the
@@
 
-We fit the measured velocities of \ion{Si}{2}\,6355 line to the
+We fit the measured velocities of \ion{Si}{2}\,$\lambda$6355 to the
 $v\propto(t-t_{exp})^{-0.22}$ model by minimizing the $\chi^2$ value
-and find the best-fit explosion time $t_{exp}=-17.95\,\textrm{days}$
+and find the best-fit explosion time $t_{exp} = -17.95\,\textrm{days}$
 with a 3-$\sigma$ confidence interval between $-17.4\,\textrm{days}$
@@
 leads to consistent results within the respective 3-$\sigma$ 
-confidence intervals.
+confidence intervals. \amiller{This analysis needs to be updated to reflect the new time of maximum}
 
-Compare the estimated $t_{exp}$ to $t_0$ (left panel of Figure
-\ref{fig:velocity_t_exp}), we find that $t_0\lessapprox t_{exp}$.\footnote{Note that the uncertainties on $t_{exp}$ are large due to assumptions in the $v\propto(t-t_{exp})^{-0.22}$ model.}
+Comparing our estimates for $t_{exp}$ and $t_0$ (left panel of 
+Figure \ref{fig:velocity_t_exp}), we find that 
+$t_0\lessapprox t_{exp}$.\footnote{Note that the uncertainties on $t_{exp}$ are large due to assumptions in the $v\propto(t-t_{exp})^{-0.22}$ model.}
 Since physical causality requires $t_{exp}<t_0$, we draw the qualitative
@@
 
-From $t_{exp}$, we estimate the actual rise time of iPTF16abc from the
-time of explosion to \textit{B}-band maximum to be $17.95$ d.  In
-comparison, SN2011fe has $t_0=-17.7$ d \citep{2013A&A...554A..27P}
-with a preceding dark period of $\sim 1$ day
-\citep{2014ApJ...784...85P}. ASASSN-14lp has $t_0=-16.94$ days with a
-preceding dark period of about acouple of days
-\citep{2016ApJ...826..144S}. This comparison suggests that the actual
-rise time of a SN Ia between the SN explosion and the \textit{B}-band
-maximum is roughly a constant, which largely depends on the total mass
-of synthesized $^{56}$Ni.\ycao{I am not convinced by this last sentence}
+% From $t_{exp}$, we estimate the actual rise time of \abc\ from the
+% time of explosion to \textit{B}-band maximum to be $17.95$ d.  In
+% comparison, SN2011fe has $t_0=-17.7$ d \citep{2013A&A...554A..27P}
+% with a preceding dark period of $\sim 1$ day
+% \citep{2014ApJ...784...85P}. ASASSN-14lp has $t_0=-16.94$ days with a
+% preceding dark period of about acouple of days
+% \citep{2016ApJ...826..144S}. This comparison suggests that the actual
+% rise time of a SN Ia between the SN explosion and the \textit{B}-band
+% maximum is roughly a constant, which largely depends on the total mass
+% of synthesized $^{56}$Ni.\ycao{I am not convinced by this last sentence}
 
@@
 
-iPTF16abc exhibits unusually strong absorption of
-\ion{C}{2} $\lambda\lambda$6580, 7234 for SNe Ia. Our analysis of the
-\ion{Si}{2}\,6355 line also allows us to measure the velocities and
-pseudo-equivalent widths (pEWs) of \ion{C}{2}\,6580. We also fit a Gaussian
-kernel with linear baseline to the spectral region near
-the \ion{C}{2}\,7234 line to measure its velocity and pEW. 
-The velocity evolution of \ion{C}{2} is shown in the right panel
-of Figure \ref{fig:velocity_t_exp} and the pEW evolution
-in Figure \ref{fig:ew}.
+The early spectra of \abc\ exhibit unusually strong absorption due 
+to \ion{C}{2} $\lambda\lambda$6580, 7234. We highlight the evolution 
+of these spectral features in Figure~\ref{fig:carbon}. From these 
+spectra we see that \ion{C}{2}\,$\lambda$6580 is as strong as 
+\ion{Si}{2}\,$\lambda$6355 at $t \approx -16 \; \mathrm{d}$. The 
+strength of the \ion{C}{2} lines declines with time to the point 
+where they are no longer detectible more than 1 wk after explosion.
 
-Our measurements show that the strong \ion{C}{2} absorption
-only appears in the very early phases. In the spectrum taken at
-$t=-15.8$ days, the pEW of \ion{C}{2}\,6580 is comparable to that
-of \ion{Si}{2}\,6355. Subsequent spectra the pEW of \ion{C}{2} 
+\begin{figure}[]
+  \centering
+  \includegraphics[width=0.49\textwidth]{CarbonFeature.pdf}
+  \caption{Evolution of the \ion{C}{2} features observed in the 
+  early spectra of \abc. The raw spectra are shown in grey, while 
+  the solid black lines show a smoothed version to highlight the 
+  observed spectral features.}
+  \label{fig:carbon}
+\end{figure}
+
+Similar to our analysis of the \ion{Si}{2}\,$\lambda$6355 line, we 
+can measure velocities and pseudo-equivalent widths (pEWs) of 
+\ion{C}{2}\,$\lambda\lambda$6580, 7234. We compare the velocity 
+evolution of the \ion{C}{2} lines to \ion{Si}{2} in the right panel 
+of Figure \ref{fig:velocity_t_exp} and the pEW evolution is
+shown in Figure \ref{fig:ew}. These measurements confirm the qualitative analysis from Figure~\ref{fig:carbon}: namely, the pEW of \ion{C}{2}\,$\lambda$6580 is comparable to that
+of \ion{Si}{2}\,$\lambda$6355 at $t \approx -16 \; \mathrm{d}$ and 
+the pEW of \ion{C}{2} 
 decreases until the feature is no longer detectable 
@@
 
-\begin{figure}[!htb]
+\begin{figure}[]
   \centering
   \includegraphics[width=0.45\textwidth]{pEW.pdf}
-  \caption{Pseudo-equivalent width of \ion{Si}{2}\,6355,
-    \ion{C}{2}\,6580 and \ion{C}{2}\,7234 lines. The uncertainties
-    in these measurements are less than the sizes of these symbols.}
+  \caption{Evolution of the pseudo-equivalent width of 
+  \ion{Si}{2}\,$\lambda$6355, and \ion{C}{2}\,$\lambda\lambda$6580, 
+  7234 in the week following explosion.}
   \label{fig:ew}
@@
 
-\ion{C}{2} absorption requires the existence of both unburned
-carbon and $^{56}$Ni, which radioactively decays and ionizes the C 
-atoms. The strong and short-lived \ion{C}{2} features reveal 
-that $^{56}$Ni atoms have been strongly mixed in to the outter 
-layers of the ejecta. This provides a third piece of evidence
-for strong mixing in the iPTF16abc ejecta.
+The detection of \ion{C}{2} in SNe Ia spectra is relatively rare
+as it requires both unburned carbon, which is likely only present in the outermost layers of the ejecta, and non-local thermal equilibrium effects in order to excite the ionized carbon (e.g., \citealt{2007ApJ...654L..53T}).
+Spectra obtained around or after $T_{B_\mathrm{max}}$ rarely show \ion{C}{2} as the photosphere has receeded from the outermost ejecta, while pre-max spectra show evidence for \ion{C}{2} in $\sim$1/4 of all normal SNe Ia (e.g., \citealt{2011ApJ...732...30P,2012MNRAS.425.1917S,2011ApJ...743...27T}), but the signatures are typically weak.
+While we caution that the sample of normal SNe Ia with spectra taken within a few days of explosion is small, SN\,2013dy is the only other object known to have strong \ion{C}{2} features like \abc\ \citet{2013ApJ...778L..15Z}.
+As a counterexample, SN\,2011fe only exhibited weak \ion{C}{2} features in its first spectra
+\citep{2012ApJ...752L..26P}. Thus, models of \abc\ must explain the anomously strong \ion{C}{2} absorption observed shortly after explosion.
 
-Carbon signatures are seen in $> 1/4$ of all normal SNe Ia before
-maxima
-\citep{2011ApJ...732...30P,2012MNRAS.425.1917S,2011ApJ...743...27T},
-but the signatures are usually weak. Even in SN2011fe, which was discovered and spectroscopically observed shortly after explosion, the \ion{C}{2}
-features are not strong in the first spectra
-\citep{2012ApJ...752L..26P}.  The only normal SN Ia known to have
-strong \ion{C}{2} features at early phases is SN2013dy
-\citep{2013ApJ...778L..15Z}. Unlike iPTF16abc, however, the pEWs 
-of the \ion{C}{2} features in SN2013dy are \ycao{not?} as large as 
-those of \ion{Si}{2}\,6355 in the same spectra.
-
-\subsection{Discussion}
+\section{Discussion}
 \label{sec:lc_energy}
 
-Multiple energy sources can contribute to the early radiation from a SN Ia: SN shock
-breakout, SN ejecta-companion collision, and radioactive 
-$^{56}$Ni. The previous analysis is based on the assumption that the light curve of
-iPTF16abc is powered purely by radioactive decay. Here we discuss the
-other two possibilities.
+We have identified several unusual properties in the early observations of \abc, including: (i) a near-linear photometric rise in the days after explosion, (ii) the lack of a dark phase typical of most SNe Ia, and (iii) the presence of strong \ion{C}{2} absorption.
+While most SNe Ia are powered purely by radioactive decay, the observed radiation shortly after explosion can also include contributions
+from SN shock cooling or the collision of the SN ejecta with a non-degenerate companion. Here we consider those scenarios as a possible explanation for the early behavior of \abc.
 
-\subsubsection{SN Shock Breakout}
+\subsection{SN Shock Cooling}
 
 The shock breakout of a SN Ia lasts for a fraction of a second due to
-the small size of the exploding star. However, the subsequent cooling
-phase may last longer (e.g., \citealt{2010ApJ...708..598P}).
-Following the analysis of SN2011fe in \citet{2012ApJ...744L..17B}, we
-compare the early-phase \textit{g}-band light curve of iPTF16abc with
-two cooling models \citep{2011ApJ...728...63R, 2010ApJ...708..598P}. From this comparison, we limit the radius of 
-the
-progenitor of iPTF16abc to be $<1\sr$, which is a weak constraint compared to SN~2011fe. Assuming a 
-typical white-dwarf radius for the progenitor, $\sim{0.01}\sr$, the cooling emission of a
-SN Ia is negligible at the time of our first iPTF16abc detection. 
+compact size of the exploding star. Emission from the subsequent 
+cooling phase may last for several days, however (e.g., 
+\citealt{2010ApJ...708..598P}). Following the analysis of \citet{2012ApJ...744L..17B} for SN\,2011fe, we
+compare the early-phase $g_\mathrm{PTF}$ light curve of \abc\ with
+two shock cooling models \citep{2011ApJ...728...63R, 
+2010ApJ...708..598P}. From this analysis, we constrain the \abc\ 
+progenitor radius to be $<1\sr$. Our observations of \abc\ cannot 
+place tight constraints on the size of SNe Ia progenitors. Indeed, 
+for a typical WD radius, such as that inferred for SN\,2011fe 
+($\lesssim 0.02$--$0.04\,\sr$; \citealt{2012ApJ...744L..17B, 
+2014ApJ...784...85P}), the expected emission from shock cooling is 
+$\sim$2 mag fainter than the P48 $g_\mathrm{PTF}$ detection limit. 
 Thus, we conclude that shock cooling does not contribute to the 
-early light from iPTF16abc.
+early emission from \abc.
 
-\subsubsection{SN-Companion collision}
+\subsection{SN-Companion collision}
 
-SNe Ia with single-degenerate progenitors can produce detectable 
-radiation following the collision of the SN ejecta with the 
-non-degenerate companion. Geometrically the odds of such a 
-detection are low, however, at $\sim$10\%. According to 
-calculations by
-\citet{2010ApJ...708.1025K}, SN ejecta-companion star collisions 
-generate thermal emission with a spectrum that peaks in the 
-ultraviolet. Thus, any resulting \textit{g}-band emission is very weak.
+The detection of excess emission due to the collision of SN ejecta 
+with a non-degenerate companion requires a favorable orbital 
+alignment relative to the line of sight. Thus, from geometric 
+considerations alone the probability of detecting ejecta-companion 
+interaction is low, $\sim$10\%. For any single type Ia SN, this 
+probability is further reduced because many explosions come from 
+WD-WD binaries. \citet{2010ApJ...708.1025K} calculates that the 
+collision of SN ejecta with a companion  
+generates thermal emission with a spectrum that peaks in the 
+UV. Thus, any resulting \textit{g}-band emission is very weak.
 
 To examine the possibility of a SN-companion signature in the early
-light curve of iPTF16abc, we employ the \citet{2010ApJ...708.1025K}
-model and assume an ejecta mass of $1.4\sm$, an expansion velocity of
-$10^{4}\,\textrm{km}\,\textrm{s}^{-1}$, and a constant opacity of
-$0.2\,\textrm{cm}^2\,\textrm{g}^{-1}$. The angular dependence of this
-emission uses the parameterized equation in
-\citet{2012ApJ...749...18B}.  Figure \ref{fig:SN-companion} compares
-the expected \textit{g}-band apparent magnitudes of SN-companion
-collisions for different binary separation assuming the optimal viewing
-angle against the first detection of iPTF16abc. The figure shows that,
-even with the most favorable viewing angle, the binary separation would
-have to exceed $2\times10^{14}\,\textrm{cm}$. Under the model assumption that the
-companion fills its Roche lobe, the companion star would have to have
-a radius of $\sim10^{14}\,\textrm{cm}\simeq10 \mathrm{AU}$. Given that the
-mass of the companion is $\sim1\sr$, such a large radius is unphysical.
-Therefore, we conclude that the early emission of iPTF16abc is not 
-due to a collision between the eject and a non-degenerate companion.
+light curve of \abc, we employ the \citet{2010ApJ...708.1025K}
+model and assume canonical ejecta mass of $1.4\sm$, expansion velocity of
+$10^{4}\,\textrm{km}\,\textrm{s}^{-1}$, and constant opacity of
+$0.2\,\textrm{cm}^2\,\textrm{g}^{-1}$. We calculate the expected 
+$g_\mathrm{PTF}$ brightness of an ejecta-companion collision at the 
+distance of \abc\ using the parameterized equations in 
+\citet{2012ApJ...749...18B}. If we assume the binary is aligned with 
+the optimal orientation relative to the line of sight, the binary 
+separation would need to exceed $2\times10^{14}\,\textrm{cm}$ to 
+explain the initial detection of \abc. Assuming the companion fills 
+its Roche lobe, it would need to 
+have a radius of $\sim10^{14}\,\textrm{cm}\simeq10 \,\mathrm{AU}$.
+Such a radius is implausibly large for a WD binary companion, 
+therefore, we conclude that the early emission from \abc\ is not 
+due to a collision between the ejecta and a non-degenerate companion.
+Our early \textit{Swift} observations support this conclusion, as the UV $-$ optical colors are very red, whereas iPTF\,14atg exhibited much bluer UV $-$ optical colors at the same epoch \citep{2015Natur.521..328C}.
 
-\begin{figure}[!thb]
+% \begin{figure}[!thb]
+%   \centering
+%   \includegraphics[width=0.45\textwidth]{SNCompanion.pdf}
+%   \caption{Apparent magnitude of a SN-companion collision (gray region)
+%     against the first detection of \abc\ (black). \amiller{Cut this
+%     figure? Doesn't add a lot of information.}}
+%   \label{fig:SN-companion}
+% \end{figure}
+
+\subsection{Interaction with Diffuse Material}
+
+Here we consider a model that has not, as of yet, been discussed in the context of \abc.
+In the context of SN\,2001fe, \citet{2014MNRAS.441..532D} recently examined pulsational delayed-detonation (PDD) models as an explanation for some SNe Ia.
+Briefly, PDD models differ from ``standard'' delayed detonation (DD) models in that the initial deflagration causes the WD to expand resulting in the release of some unbound material.
+As the bound material contracts, eventually a subsequent detonation occurs.\footnote{\citet{2014MNRAS.441..532D} note that the deflagration and detonation in their PDD models are artificially triggered.} An important consequence of this sequence for PDD models is that they naturally produce material that avoids burning, unlike DD models that typically leave no unburnt material.
+This enables the presence of significantly more carbon in the outer layers of the SN ejecta \citep{2014MNRAS.441..532D}.
+
+While examining observations of SN\,2011fe in the context of DD models, \citet{2014MNRAS.441..532D} find that the models are universally too faint and red at early times, $\sim$24-48 hr after explosion.
+These discrepancies can be somewhat improved if the newly synthesized $^{56}$Ni is artificailly mixed throughout the SN ejecta (see \S\ref{sec:Ni_mixing} for further details on the importance of mixing).
+Instead, \citet{2014MNRAS.441..532D} find that PDD models provide a better match to observations.
+Briefly, the diffuse material surrounding the WD heats the outer layers of the SN ejecta leading to a steeper more luminous rise, with bluer colors in the few days after explosion.
+Importantly, the PDD models are nearly indistinguishable from DD models around and post peak.
+
+Qualitatively, the PDD models provide a better match to the observations of \abc\ than DD models.
+In particular, PDD models provide higher luminosities and faster rise times in the days after explosion, a more rapid evolution towards blue optical colors, and the formation of strong \ion{C}{2} lines that gradually disappear in the $\sim$week after explosion.
+Quantitatively, there are still some short comings of the models presented in \citet{2014MNRAS.441..532D}.
+In particular, the power-law index for the $g$-band rise is $\alpha \approx 3$ for each of the PDD models, which is significantly more steep than $\alpha = 0.96$, which we measure for \abc.
+The optical colors for \abc\ are blue from our first epoch $\sim$1.7 d after explosion and remain approximately constant in the 10 d after explosion, whereas the PDD models in \citet{2014MNRAS.441..532D} either exhibit distinct color evolution (i.e.\ are not constant) or are too red in the first few days after explosion.
+Nevertheless, the PDD models presented in \citet{2014MNRAS.441..532D} provide several attractive explanations for the unusual features in the early behavior of \abc, and it may be possible that small adjustments to the model, e.g., additional mixing of the radioactive products from the explosion, can better match \abc.
+
+\subsection{Strong $^{56}Ni$ Mixing as an Explanation for \abc}
+\label{sec:Ni_mixing}
+
+Having ruled out other possibilities we now consider whether the unusual properties of \abc\ can be explained simply by invoking strong mixing in the SN ejecta.
+As previously mentioned, strong mixing can lead to a short dark phase and \ion{C}{2} absorption.
+Here we additionally examine if strong mixing can explain the rapid, near-linear rise in the light curve.
+
+In Figure~\ref{fig:Ni56LC} we compare model calculations from \citet{2016ApJ...826...96P} to the observed photometry of \abc.
+The \citeauthor{2016ApJ...826...96P} models employ a piston driven explosion to explode a single WD progenitor model.
+As the piston explosion does not result in any nucleosynthesis, the distribution of $^{56}$Ni in the ejecta must be prescribed by hand, which enables their study of the effects of mixing on the resulting SN emission.
+Each model employs a fixed $0.5\,\sm$ of $^{56}$Ni that has been distributed throughout the ejecta via boxcar averaging (see their Figure~1).
+The resulting light curves are synthesized using the SuperNova Explosion Code (\texttt{SNEC}; \citealt{2015ApJ...814...63M}), as shown in Figure~\ref{fig:Ni56LC}.
+Broadly speaking, the results can be summarized as follows: SN with strong mixing exhibit a rapid almost linear rise and quickly develop blue colors, whereas models where the $^{56}$Ni is confined to the innermost layers of the ejecta remain very faint for days after explosion while exhibiting relatively red optical colors during this period.
+The fast rise and blue color of \abc\ are consistent with the strong mixing models from \citet{2016ApJ...826...96P}, as shown in Figure~\ref{fig:Ni56LC}.
+We conclude that the early observations of \abc\ can be explained if the $^{56}$Ni synthesized in the explosion is mixed into the outermost layers of the SN ejecta.
+
+\begin{figure}[]
   \centering
-  \includegraphics[width=0.45\textwidth]{SNCompanion.pdf}
-  \caption{Apparent magnitude of a SN-companion collision (gray region)
-    against the first detection of iPTF16abc (black).}
-  \label{fig:SN-companion}
+  \includegraphics[width=0.48\textwidth]{iPTF16abc_Ni_lc.pdf}
+  \caption{Photometric comparison of \abc\ and the theoretical 
+  models of \citet{2016ApJ...826...96P}. The amount of $^{56}$Ni 
+  mixing in the SN ejecta increases from the short-dash, dark lines 
+  to the long-dash, light lines.
+  \textit{Top}: $M_g$ vs.\ time, where the observed $g$-band 
+  magnitudes  
+  have been corrected to $M_g$ using the distance modulus to \abc\ 
+  (\S\ref{sec:host})
+  and the total line-of-site reddening ($E(B-V) = 0.078 \; 
+  \mathrm{mag}$; Ferretti et al.\ 2017, submitted).
+  \textit{Bottom}: $(g' - r')_0$ vs.\ time. The observed colors have 
+  been corrected for reddening.
+  }
+  \label{fig:Ni56LC}
 \end{figure}
@@
 We have presented observations of the extraordinarily early discovery of the 
-normal Type Ia supernova iPTF16abc. Our fast-response follow-up 
-compaign allowed us to draw the following conclusions:
+normal Type Ia supernova \abc. Our fast-response follow-up 
+campaign allowed us to draw the following conclusions:
+
 \begin{itemize}
-\item By extrapolating the early light curve, we determined that the
-  SN first light occured only $\sim{0.2}$ d before our
-  first detection.
-\item Our analysis showed that the observed early-phase light curve is
-  probably powered by $^{56}$Ni radioactive decay. We find no 
-  evidence for detectable signatures of SN
-  shock breakout or SN ejecta-companion collision (provided that 
-  iPTF16abc
-  is born in a single-degenerate channel).
-\item Our measurements of the spectral line velocities show that the
-  SN explosion date is approximately equal to the time
-  of the first light. This indicates that
-  synthesized $^{56}$Ni atoms are strongly mixed into the 
-  outer layers of
-  the supernova ejecta.
+    \item Extrapolation of the early light curve shows that the initial detection of \abc\ occurred only $\sim$0.2 d after the time of first light.
+
+    \item The early emission from \abc\ is powered solely by radioactive $^{56}$Ni decay.
+We find no evidence for detectable signatures of SN shock cooling or the collision of the SN ejecta with a non-degnerate binary companion.
+
+\item The velocity evolution of the SN ejecta shows that the time of explosion is approximately equal to the time of first light.
+This constitutes the first major piece of evidence that $^{56}$Ni is strongly mixed into the outer layers of the supernova ejecta.
+
 \item The strong and short-lived carbon features seen in the 
-  earliest spectra of iPTF16abc provide additional evidence
-  for strong $^{56}$Ni mixing in the SN ejecta.  
+earliest spectra of \abc\ can only be explained if there is incomplete burning during the explosion and there is a non-thermal 
+radiation source in the outermost layers of the ejecta to excite the ionized carbon.
+$^{56}$Ni decay is the likely source of the nonthermal emission, providing another piece of evidence for strong mixing in the ejecta of \abc.
+
+\textbf{Does anyone know of any theoretical studies that specifically predict incomplete burning and strong Ni mixing?}
+
+\item Finally, we show that the early light curve evolution and colors of \abc\ are well matched by the theoretical models of \citet{2016ApJ...826...96P} that include significant mixing of $^{56}$Ni into the outer layers of the SN ejecta.
+
 \end{itemize}
+%
+Taken together, these observations all indicate that the nucleosynthetic products from the explosion are well mixed throughout the SN ejecta.
+There are elements of the PDD models from \citet{2014MNRAS.441..532D} that are attractive for explaining \abc, in particular, the strong \ion{C}{2} absorption seen at early times.
+In the future, it would be useful to investigate PDD models that incorporate strong $^{56}Ni$ mixing to see if they better replicate the observations of \abc.
 
@@
 gun'' to probe the mixing level in the ejecta, which, in turn, is 
-a result of the explosion mechanism. Ongoing and planned
-time-domain surveys will discover a large number of very young supernovae over the next few years. As this sample grows, we will
-be able to make connections between the observed SN properties and 
-proposed explosion mechanisms.
+a result of the explosion mechanism.
+Wide-field, high-cadence surveys, such as the Zwicky Transient Facility \citep{2016PASP..128h4501B} and ATLAS \citep{2011PASP..123...58T,2013RSPTA.37120269T}, will discover a large number of very young supernovae over the next few years.
+These surveys will generate large observational samples that probe SNe in the hours after explosion.
+While the sample of extremely young SNe Ia will grow by more than an order of magnitude, the detection of shock breakout cooling and ejecta-companion interaction will prove challenging.
+Given the diminutive size of WDs, the thermal emission following shock breakout can only be detected to $\sim 10\,\mathrm{Mpc}$ on 1-m class telescopes.
+Furthermore, only $\sim$10\% of single-degenerate progenitors are expected to give rise to detectable emission following the collision of the SN ejecta with the binary companion \citep{2010ApJ...708.1025K}.
+Despite these limitations, this study of \abc\ shows that the early detection of SNe Ia can constrain the explosion physics by probing the amount of mixing in the SN ejecta.
+Moving forward, a large sample of such objects will enable strict constraints on the proposed explosion mechanisms for type Ia SNe.
 
@@
 Without the early recognition of the youth of this SN and the associated follow-up, much of the analysis presented herein would not have been possible.
-Moving forward, the ability to trigger such observations is essential to improve our understanding of the physics of SNe Ia.
+The ability to trigger such observations is essential to improve our understanding of the physics of SNe Ia.
 
 \acknowledgements
+
+\amiller{Need to thank Rollin for chatting about \ion{C}{2}}
 

### 2017-06-14 doc/ms.tex

@@
 
+% \author{A.~A.~Miller}
+% \affil{Center for Interdisciplinary Exploration and Research in Astrophysics (CIERA) and Department of Physics and Astronomy, Northwestern University, 2145 Sheridan Road, Evanston, IL 60208, USA}
+% \affil{The Adler Planetarium, Chicago, IL 60605, USA}
+%
 % \author[0000-0002-8036-8491]{Yi Cao}
@@
 %   Seattle, WA 98195}
-
+%
+% \author{B.~D.~Bue}
+% \affil{Jet Propulsion Laboratory, California Institute of Technology, Pasadena, CA 91109, USA}
+%
+% \author{M.~M.~Kasliwal}
+% \affil{Division of Physics, Mathematics, and Astronomy, California Institute of Technology, Pasadena, CA 91125, USA}
+%
+% \author{R.~Ferretti}
+% \affil{The Oskar Klein Centre, Department of Physics, AlbaNova, SE-106 91 Stockholm, Sweden}
+%
+% \author{A.~Goobar}
+% \affil{The Oskar Klein Centre, Department of Physics, AlbaNova, SE-106 91 Stockholm, Sweden}
+%
+% \author{R.~R.~Laher}
+% \affil{Infrared Processing and Analysis Center, California Institute of Technology, Pasadena, CA 91125, USA}
+%
+% \author{F.~J.~Masci}
+% \affil{Infrared Processing and Analysis Center, California Institute of Technology, Pasadena, CA 91125, USA}
+%
+% \author{P.~E.~Nugent}
+% \affil{Lawrence Berkeley National Laboratory, Berkeley, California 94720, USA}
+% \affil{University of California -- Berkeley, Berkeley, CA 94720, USA}
+%
+% \author{J.~Sollerman}
+% \affil{The Oskar Klein Centre, Department of Astronomy, AlbaNova, SE-106 91 Stockholm, Sweden}
+%
+% \author{F.~Taddia}
+% \affil{The Oskar Klein Centre, Department of Astronomy, AlbaNova, SE-106 91 Stockholm, Sweden}
+%
+% \author{S. R. Kulkarni}
+% \affil{Division of Physics, Mathematics, and Astronomy, California Institute of Technology, Pasadena, CA 91125, USA}
+%
 \author{The Alphabet Friends}
@@
 \ion{C}{2}\,$\lambda$6580 line overlaps the red
-wing of the \ion{Si}{2} line (see Figures~\ref{fig:spec_seq} and \ref{}). Consequently, we model the observed 
+wing of the \ion{Si}{2} line (see Figures~\ref{fig:spec_seq} and \ref{fig:carbon}). Consequently, we model the observed 
 spectra between 5,900 and 6,500\,\AA (rest-frame) as the combination 
@@
 \amiller{Need to thank Rollin for chatting about \ion{C}{2}}
+\amiller{Need to thank Uli, Rahman for chatting about SALT2}
+
+% Observers: Michael West, Gemini observers, J. Cohen, Plant,J.Torres,Jang,Cunningham,Guhathakurta, Ravi, Cao, Yan, Vedantham, Kulkarni, N. Suzuki, Y. Cao, V. Ravi, Walters, Lunnan, Ho, De
 
@@
 institute, University of Washington.
+
+Part of this research was carried out at the Jet Propulsion Laboratory, California Institute of Technology, under a contract with the NASA.
+
+DAH, CM, and GH are supported by NSF-1313484. Support for IA was provided by NASA through the Einstein Fellowship Program, grant PF6-170148. This work makes use of observations from the LCO network.
 

### 2017-06-15 doc/ms.tex

@@
 
-\correspondingauthor{Yi Cao}
-\email{ycao16@uw.edu}
+\correspondingauthor{A.~A.~Miller}
+\email{amiller@northestern.edu}
 
@@
 The initial detection of the SN was made only $0.18$~d after the time of first light.
-In the $\sim$24 hr after discovery \abc\ rose by $\sim$2 mag in the $g_\mathrm{PTF}$ band, which is very rare for young type Ia SNe.
+In the $\sim$24 hr after discovery, \abc\ rose by $\sim$2 mag in the $g_\mathrm{PTF}$ band, which is very rare for young type Ia SNe.
 Furthermore, by measuring the evolution of the photospheric velocity we determine that the time of explosion for \abc\ is approximately equal to the time of first light.
 Spectra obtained in the week after explosion reveal the presence of strong \ion{C}{2} absorption, which steadily fades over that time period.
-We show that the unusually fast, near-linear rise in flux for \abc\ cannot be explained by either SN shock breakout and the assciated subsequent cooling or the collision of the SN ejecta with a stellar companion.
-Instead, we show that each of the unusual characteristics of \abc: (i) the rapid, near-linear rise, (ii) the lack of a dark period between explosion and first light, and (iii) the strong lines from ionized carbon in the earliest spectra, can all be explained if radioactive $^{56}$Ni is strongly mixed throughout the SN ejecta.
+We show that the unusually fast, near-linear rise in flux for \abc\ cannot be explained by either SN shock breakout and the associated subsequent cooling or the collision of the SN ejecta with a stellar companion.
+Instead, we show each of the unusual characteristics of \abc: (i) the rapid, near-linear rise, (ii) the lack of a dark period between explosion and first light, and (iii) the strong lines from ionized carbon in the earliest spectra, can all be explained if radioactive $^{56}$Ni is strongly mixed throughout the SN ejecta.
 In the next few years, dozens of very young \textit{normal} SNe Ia will be discovered, and observations similar to those presented here will constrain the white dwarf explosion mechanism.
@@
 
-Early phase observations of SNe Ia from a white dwarf (WD)$+$non-degenarate binary
+Early phase observations of SNe Ia from a white dwarf (WD)$+$non-degenerate binary
 may detect excess emission, relative to most type Ia SNe, due to the 
@@
 Our spectroscopic follow-up
-compaign classified \abc\ as a normal SN Ia
+campaign classified \abc\ as a normal SN Ia
 \citep{2016ATel.8909....1C}. Our observations and analysis provide multiple lines of evidence that the $^{56}$Ni produced by \abc\ was strongly mixed throughout the ejecta.
@@
   rest-frame d relative to the time of first light, $t_0$ (see 
-  \S\ref{sec:lc_fit}). Note that the horizonal axis is shown with a linear scale 
+  \S\ref{sec:lc_fit}). Note that the horizontal axis is shown with a linear scale 
   for $-2 \; \mathrm{d} \le t - t_0 \le 3 \; \mathrm{d}$ and a 
@@
 60-inch telescope (P60).
-We utilized the Fremling Automated Pipeline \citep{2016A&A...593A..68F} to subtract galaxy light from the SEDm images using achival Sloan Digital Sky Survey (SDSS) images as a reference.
+We utilized the Fremling Automated Pipeline \citep{2016A&A...593A..68F} to subtract galaxy light from the SEDm images using archival Sloan Digital Sky Survey (SDSS) images as a reference.
 This pipeline then performed forced-PSF photometry at the location of \abc, which is calibrated to the SDSS catalog \citep{2014ApJS..211...17A}.
@@
   \tablenotetext{1}{The Deveny Spectrograph \citep{2014SPIE.9147E..2NB}}
-  \tablenotetext{2}{The Gemini Multi-Object Sectrograph \citep{2004PASP..116..425H}}
+  \tablenotetext{2}{The Gemini Multi-Object Spectrograph \citep{2004PASP..116..425H}}
   \tablenotetext{3}{DEep Imaging Multi-Object Spectrograph \citep{2003SPIE.4841.1657F}}
@@
 While the equivalent width (EW) of these lines is quite large, implying a large amount of extinction (e.g., \citealt{2012MNRAS.426.1465P}), Ferretti et al.\ compare the evolution of \abc\ to the well-observed normal type Ia SN\,2011fe and find evidence for only a small amount of extinction.
-The empircal relation between the EW of \ion{Na}{1}\,D and extinction is known to have a large scatter, and thus, we instead adopt $E(B-V) = 0.05 \, \mathrm{mag}$ as the local extinction for \abc\ (Ferretti et al.\ 2017).
+The empirical relation between the EW of \ion{Na}{1}\,D and extinction is known to have a large scatter, and thus, we instead adopt $E(B-V) = 0.05 \, \mathrm{mag}$ as the local extinction for \abc\ (Ferretti et al.\ 2017).
 For the remainder of our analysis we therefore adopt a total, Galactic $+$ host galaxy, line-of-sight extinction of $E(B-V) = 0.0779 \, \mathrm{mag}$.
 
-\subsection{Classfication}
+\subsection{Classification}
 \label{sec:classification}
@@
 extrapolating early-phase light curves to determine when the 
-SN is equal to 0. Assuming an ideal exapnding fireball with 
+SN is equal to 0. Assuming an ideal expanding fireball with 
 constant temperature, \citet{1982ApJ...253..785A} derives that $f 
@@
 experience a dark phase following shock breakout before radioactive 
-energy can difuse to the photosphere. \citet{2014ApJ...784...85P} 
+energy can diffuse to the photosphere. \citet{2014ApJ...784...85P} 
 instead suggest that measurements of the photospheric velocity be 
@@
 as it requires both unburned carbon, which is likely only present in the outermost layers of the ejecta, and non-local thermal equilibrium effects in order to excite the ionized carbon (e.g., \citealt{2007ApJ...654L..53T}).
-Spectra obtained around or after $T_{B_\mathrm{max}}$ rarely show \ion{C}{2} as the photosphere has receeded from the outermost ejecta, while pre-max spectra show evidence for \ion{C}{2} in $\sim$1/4 of all normal SNe Ia (e.g., \citealt{2011ApJ...732...30P,2012MNRAS.425.1917S,2011ApJ...743...27T}), but the signatures are typically weak.
+Spectra obtained around or after $T_{B_\mathrm{max}}$ rarely show \ion{C}{2} as the photosphere has receded from the outermost ejecta, while pre-max spectra show evidence for \ion{C}{2} in $\sim$1/4 of all normal SNe Ia (e.g., \citealt{2011ApJ...732...30P,2012MNRAS.425.1917S,2011ApJ...743...27T}), but the signatures are typically weak.
 While we caution that the sample of normal SNe Ia with spectra taken within a few days of explosion is small, SN\,2013dy is the only other object known to have strong \ion{C}{2} features like \abc\ \citet{2013ApJ...778L..15Z}.
 As a counterexample, SN\,2011fe only exhibited weak \ion{C}{2} features in its first spectra
-\citep{2012ApJ...752L..26P}. Thus, models of \abc\ must explain the anomously strong \ion{C}{2} absorption observed shortly after explosion.
+\citep{2012ApJ...752L..26P}. Thus, models of \abc\ must explain the anomalously strong \ion{C}{2} absorption observed shortly after explosion.
 
@@
 While examining observations of SN\,2011fe in the context of DD models, \citet{2014MNRAS.441..532D} find that the models are universally too faint and red at early times, $\sim$24-48 hr after explosion.
-These discrepancies can be somewhat improved if the newly synthesized $^{56}$Ni is artificailly mixed throughout the SN ejecta (see \S\ref{sec:Ni_mixing} for further details on the importance of mixing).
+These discrepancies can be somewhat improved if the newly synthesized $^{56}$Ni is artificially mixed throughout the SN ejecta (see \S\ref{sec:Ni_mixing} for further details on the importance of mixing).
 Instead, \citet{2014MNRAS.441..532D} find that PDD models provide a better match to observations.
@@
 radiation source in the outermost layers of the ejecta to excite the ionized carbon.
-$^{56}$Ni decay is the likely source of the nonthermal emission, providing another piece of evidence for strong mixing in the ejecta of \abc.
+$^{56}$Ni decay is the likely source of the non-thermal emission, providing another piece of evidence for strong mixing in the ejecta of \abc.
 

### 2017-06-15 doc/ms.tex
Include updated early light curve figure and new values for the power-law fits in the paper.

@@
 \end{equation}
-where $t_0$ is the time of first light and $\alpha$ is the power-law index.
-To determine $t_0$ and $\alpha$ we fit the earliest observations of \abc, which were taken exclusively with P48 in the $g_\mathrm{PTF}$ filter.
+where $t_0$ is the time of first light, $\alpha$ is the power-law index, and $t$ is measured in the rest-frame of the SN.
+To determine $t_0$ and $\alpha$ we fit the earliest observations of \abc.
+Due to slight variations in the passbands, we fit the model to the relative flux measured in the $g_\mathrm{PTF}$-band, which is the only filter with observations prior to first light, a necessity for constraining $t_0$.
+
 To determine the best fit parameters, we search a large grid over $t_0$, $\alpha$
@@
 linearly between
-$t=-18\,\textrm{d}$ and $t=-15\,\textrm{d}$. Figure \ref{fig:early_lc_fit} shows the best-fit result and
+$t=-18\,\textrm{d}$ and $t=-14\,\textrm{d}$. Figure \ref{fig:early_lc_fit} shows the best-fit result and
 the joint marginal distribution of $t_0$ and $\alpha$. With the
-best-fit model of $\alpha=0.96$ and $t_0=-18.4$ days, our first
+best-fit model of $\alpha=0.98$ and $t_0=-17.94$ d, our first
 detection of \abc\ occurred $\sim{0.2}\,\textrm{d}$ after 
 the SN first light.
+Figure~\ref{fig:early_lc_fit} additionally shows $g'$-bands observations from P60 and LCO, where we have normalized the flux assuming that the $g$ magnitudes from each instrument have the same zero-point.
+This assumption is incorrect (see \S\ref{sec:obs}), and, as expected, the residuals show a systematic offset between the $g_\mathrm{PTF}$-band and the $g'$-band.
+Nevertheless, if we ignore this systematic and fit all of the $g$-band observations simultaneous we obtain marginalized best-fit parameters that are consistent within the uncertainties with the $g_\mathrm{PTF}$-only values above.
+In the analysis that follows, the precise values of the best-fit parameters is not important.
+The critical finding here is that $\alpha \approx 1$ and $t_0 \approx -18 \, \mathrm{d}$.
 
@@
   \includegraphics[width=0.95\textwidth]{early_lc.pdf}
-  \caption{Broken Power low fitting to the early $g$-band light
-    curve. The best-fit model of $\alpha=0.92$ and $t_0=-18.47\,\textrm{days}$
-    and corresponding residues are shown in the top and bottom panels, respectively.
-    The joint distribution of $t_0$ and $\alpha$ is illustrated in the inset of
-    the upper panel. The solid and dashed contours represent the $68\%$ and $99.7\%$
-    confidence levels.
+  \caption{Best-fit power-law model to describe the early flux from 
+  \abc\ in the $g_\mathrm{PTF}$-band. The model flux, adopting 
+  best-fit parameters $\alpha=0.98$ and $t_0=-17.94\,\textrm{d}$, 
+  is shown as a solid black line in the top panel. The lower panel 
+  shows the model residuals, and the symbols are the same as in
+  Figure~\ref{fig:lightcurve}. The model is fit to just the 
+  $g_\mathrm{PTF}$-band observations to avoid systematic difference 
+  between the filters (see the text for further 
+  details). The joint distribution of $t_0$ and $\alpha$ is 
+  illustrated in the inset of the upper panel. The solid and 
+  dashed contours represent the $68\%$ and $99.7\%$ confidence 
+  levels.
   }
@@
 
-Starting around $t=-15\,\textrm{d}$, the $g$-band light curve 
-deviates from the above best-fit model and 
-rises significantly faster, indicating a
-change in the power-law index $\alpha$. In fact, between $t=-14\,\mathrm{d}$ and $t=-8\,\mathrm{d}$ the light curve is well fit by a power law of index $1.40$. In other words, the entire light curve
-before $t=-8$\,days can be approximated by a broken power-law model
-(e.g.,
-\citealt{2016arXiv161202097Z,
-  2016arXiv161202725Z}).
+% Starting around $t=-15\,\textrm{d}$, the $g$-band light curve
+% deviates from the above best-fit model and
+% rises significantly faster, indicating a
+% change in the power-law index $\alpha$. In fact, between $t=-14\,\mathrm{d}$ and $t=-8\,\mathrm{d}$ the light curve is well fit by a power law of index $1.40$. In other words, the entire light curve
+% before $t=-8$\,days can be approximated by a broken power-law model
+% (e.g.,
+% \citealt{2016arXiv161202097Z,
+%   2016arXiv161202725Z}).
 
@@
 Any model to explain the observations of \abc\ must be able to account for this unusual behavior in the days after first light.
-
-% \amiller{Revisit this paragraph in context of discussion -- might need to be moved to later section} As discussed in Section \ref{sec:lc_energy}, the initial light curve
-% of \abc\ is probably purely powered by the radioactive decay of
-% $^{56}$Ni. Thus, the initial rise of the light curve depends on
-% the depth of the shallowest layer where $^{56}$Ni is deposited
-% \citep{2014ApJ...784...85P}. According to theoretical models
-% \citep{2016ApJ...826...96P}, the linearly rising light curve implies
-% strong mixing of $^{56}$Ni in the ejecta. As a result, the time lag
-% between the time of explosion and SN first light is negligible.
 

### 2017-06-18 doc/ms.tex
Include udpated captions for spectroscopy figures.

@@
 %   Seattle, WA 98195}
+% \affil{Google, Mountain View, CA 94043, USA}
 %
@@
 % \affil{Jet Propulsion Laboratory, California Institute of Technology, Pasadena, CA 91109, USA}
-%
-% \author{M.~M.~Kasliwal}
-% \affil{Division of Physics, Mathematics, and Astronomy, California Institute of Technology, Pasadena, CA 91125, USA}
-%
+
 % \author{R.~Ferretti}
@@
 % \affil{The Oskar Klein Centre, Department of Physics, AlbaNova, SE-106 91 Stockholm, Sweden}
+%
+% \author{G.~Hosseinzadeh}
+% \affil{Las Cumbres Observatory, Goleta, CA 93117, USA}
+% \affil{Physics Department, University of California, Santa Barbara, CA 93106, USA}
+%
+% \author{M.~M.~Kasliwal}
+% \affil{Division of Physics, Mathematics, and Astronomy, California Institute of Technology, Pasadena, CA 91125, USA}
 %
@@
 \citet{2012ApJ...744L..17B} concluded that the explosion came from a 
-stars with $R_\ast \lesssim 0.02\sr$, where $\sr$ is the solar
+star with $R_\ast \lesssim 0.02\sr$, where $\sr$ is the solar
 radius. Combining the radius constraint with the measured ejecta 
@@
     and dash-dotted curves show $\chi^2$ for fitting power laws with
-    indices $-0.20$, $-0.22$ and $-0.24$, respectively. The red
-    vertical line and the orange region indicate $t_0$ and its
-    3-$\sigma$ confidence interval from Section
-    \ref{sec:lc_fit}.
-    \textit{Right panel:} Observed \ion{Si}{2}\,6355
-    velocities and the best-fit power-law velocity with an index of
-    $-0.22$.}
+    indices $-0.20$, $-0.22$ and $-0.24$, respectively. The blue
+    vertical line and the orange shaded region indicate $t_0$ and its
+    99.7\% confidence interval from Section
+    \ref{sec:lc_fit}, respectively.
+    \textit{Right panel:} Observed \ion{Si}{2}\,$\lambda$6355
+    velocities (blue circles) and the best-fit power-law model
+     with an index of $-0.22$ (dashed line). Additionally the 
+     measured velocites of \ion{C}{2}\,$\lambda\lambda$6580, 7234 
+     are shown.}
   \label{fig:velocity_t_exp}
@@
   \caption{Evolution of the \ion{C}{2} features observed in the 
-  early spectra of \abc. The raw spectra are shown in grey, while 
-  the solid black lines show a smoothed version to highlight the 
-  observed spectral features.}
+  early spectra of \abc. The raw spectra are shown in orange, while 
+  the solid blue lines show the best-fit models including gaussian 
+  components for each line and a linear component for the continuum 
+  (see text for further details). The dark grey vertical lines show 
+  the measured line centers, indicating the decline in the 
+  photosphere velocity in the $\sim$wk after explosion (note that 
+  \ion{C}{2}\,$\lambda$7234 is not detected in the $-10.9$ d 
+  spectrum). The phase of each spectrum relative to 
+  $T_{B,\mathrm{max}}$ is shown to the right of each spectrum.
+  }
   \label{fig:carbon}
@@
 Quantitatively, there are still some short comings of the models presented in \citet{2014MNRAS.441..532D}.
-In particular, the power-law index for the $g$-band rise is $\alpha \approx 3$ for each of the PDD models, which is significantly more steep than $\alpha = 0.96$, which we measure for \abc.
+In particular, the power-law index for the $g$-band rise is $\alpha \approx 3$ for each of the PDD models, which is significantly more steep than $\alpha = 0.98$, which we measure for \abc.
 The optical colors for \abc\ are blue from our first epoch $\sim$1.7 d after explosion and remain approximately constant in the 10 d after explosion, whereas the PDD models in \citet{2014MNRAS.441..532D} either exhibit distinct color evolution (i.e.\ are not constant) or are too red in the first few days after explosion.
@@
 
-\amiller{Need to thank Rollin for chatting about \ion{C}{2}}
-\amiller{Need to thank Uli, Rahman for chatting about SALT2}
+We are deeply grateful to R.~C.~Thomas for induldging a slew of questions regarding \ion{C}{2} in SNe.
+Similarly, it is our pleasure to buy a beer for R.~Amanullah and U.~Feindt for discussions regarding SALT2.
 
-% Observers: Michael West, Gemini observers, J. Cohen, Plant,J.Torres,Jang,Cunningham,Guhathakurta, Ravi, Cao, Yan, Vedantham, Kulkarni, N. Suzuki, Y. Cao, V. Ravi, Walters, Lunnan, Ho, De
+Much of the analysis presented herein would not have been possible without the help of several observers.
+We thank M.~West for taking the first spectrum of \abc\ as a ToO on the DCT.
+We also thank the Gemini service observers for executing our ToO observations.
+Additionally, J.~Cohen, N.~Suzuki, V.~Ravi, R.~Walters, A.~Ho, and L.~Yan helped obtain data for this paper.
 
-YC thanks supports from the postdoc fellowship in the eScience
-institute, University of Washington.
+% Observers:  Plant,J.Torres,Jang,Cunningham,Guhathakurta, Vedantham, De
 
+AAM is funded by the Large Synoptic Survey Telescope Corporation in support of the Data Science Fellowship Program.
+YC thanks support from a postdoc fellowship in the eScience institute, University of Washington.
+
+DAH, CM, and GH are supported by NSF-1313484. Support for IA was provided by NASA through the Einstein Fellowship Program, grant PF6-170148.
+
+The Intermediate Palomar Transient Factory project is a scientific collaboration among the California Institute of Technology, Los Alamos National Laboratory, the University of Wisconsin, Milwaukee, the Oskar Klein Center, the Weizmann Institute of Science, the TANGO Program of the University System of Taiwan, and the Kavli Institute for the Physics and Mathematics of the Universe.
+This work was supported by the GROWTH project funded by the National Science Foundation under Grant No 1545949.
 Part of this research was carried out at the Jet Propulsion Laboratory, California Institute of Technology, under a contract with the NASA.
-
-DAH, CM, and GH are supported by NSF-1313484. Support for IA was provided by NASA through the Einstein Fellowship Program, grant PF6-170148. This work makes use of observations from the LCO network.
+This work makes use of observations from the LCO network.
 

### 2017-06-19 doc/ms.tex
Add the confidence intervals for alpha and t_0 to the paper.

@@
 $t=-18\,\textrm{d}$ and $t=-14\,\textrm{d}$. Figure \ref{fig:early_lc_fit} shows the best-fit result and
-the joint marginal distribution of $t_0$ and $\alpha$. With the
-best-fit model of $\alpha=0.98$ and $t_0=-17.94$ d, our first
+the joint marginal distribution of $t_0$ and $\alpha$. From the
+best-fit model we obtain $\alpha=0.98 \pm ^{0.06}_{0.10}$ and $t_0=-17.94 \pm ^{0.05}_{0.06}$ d, where the uncertainties represent the marginalized 95\% confidence intervals. Our first
 detection of \abc\ occurred $\sim{0.2}\,\textrm{d}$ after 
@@
 Here we consider a model that has not, as of yet, been discussed in the context of \abc.
-In the context of SN\,2001fe, \citet{2014MNRAS.441..532D} recently examined pulsational delayed-detonation (PDD) models as an explanation for some SNe Ia.
+In the context of SN\,2011fe, \citet{2014MNRAS.441..532D} recently examined pulsational delayed-detonation (PDD) models as an explanation for some SNe Ia.
 Briefly, PDD models differ from ``standard'' delayed detonation (DD) models in that the initial deflagration causes the WD to expand resulting in the release of some unbound material.

### 2017-06-22 doc/ms.tex
Update velocity figs, and provide uncertainties on the best-fit time of explosion.

@@
 We fit the measured velocities of \ion{Si}{2}\,$\lambda$6355 to the
-$v\propto(t-t_{exp})^{-0.22}$ model by minimizing the $\chi^2$ value
-and find the best-fit explosion time $t_{exp} = -17.95\,\textrm{days}$
-with a 3-$\sigma$ confidence interval between $-17.4\,\textrm{days}$
-and $-18.3\,\textrm{days}$ (Figure \ref{fig:velocity_t_exp}). We additionally
-alter the power-law index to $-0.20$ and $-0.24$ to examine the
-sensitively of the result on the assumed power-law index.  This 
-leads to consistent results within the respective 3-$\sigma$ 
-confidence intervals. \amiller{This analysis needs to be updated to reflect the new time of maximum}
+$v\propto(t-t_{exp})^{-0.22}$ model by minimizing the $\chi^2$ value and find the best-fit explosion time relative to $T_{B,\mathrm{max}}$ in the SN rest frame to be $t_{exp} = -17.45 \pm ^{0.14}_{0.16}\;\textrm{d}$, where the uncertainties represent the 95\% confidence interval (Figure \ref{fig:velocity_t_exp}).
+Following the analysis in \citet{2014ApJ...784...85P}, we additionally alter the power-law index to $-0.20$ and $-0.24$ to examine the sensitively of the result on the assumed power-law index.
+We find that this variation in the power-law index result in inferred explosion times that vary by $\approx$1 d (Figure \ref{fig:velocity_t_exp}).
+Given the theorhetical expectation that $v \propto t^{-0.22}$, we adopt $t_{exp} = -17.45 \pm 0.5 \; \mathrm{d}$, where the uncertainty reflects possible variations in the power-lax index (see \citealt{2014ApJ...784...85P}).
 
@@
 Figure \ref{fig:velocity_t_exp}), we find that 
-$t_0\lessapprox t_{exp}$.\footnote{Note that the uncertainties on $t_{exp}$ are large due to assumptions in the $v\propto(t-t_{exp})^{-0.22}$ model.}
+$t_0\lessapprox t_{exp}$.
 Since physical causality requires $t_{exp}<t_0$, we draw the qualitative
-conclusion that $t_0\simeq t_{exp}$, which is consistent
-with our inference from the early light curve analysis (Section
-\ref{sec:lc_fit}).
+conclusion that $t_0\simeq t_{exp}$, which is consistent to within the uncertainties.
 

### 2017-06-25 data/collect_data.py
Add RATIR photometry to data file. Update P48 photometry to properly account for uncertainties.

@@ -16,7 +16,7 @@ import numpy as np
 import tables
 from astropy.io import ascii
 from astropy.time import Time
-
+from makelc.ptfidelc import ptfide_light_curve as plc
 
 # define photometry columns
 class Photometry(tables.IsDescription):
@@ -102,33 +102,28 @@ def main():
     # P48
     data_dict = {"g": "lc/forcepsffitdiff_d100151_f1_c11.out",
                  "R": "lc/forcepsffitdiff_d3381_f2_c10.out"}
-    for filter_name, filename in data_dict.iteritems():
-        data = ascii.read(filename, format="ipac")
-        for item in data:
-            if item["MJD"] < 57470:
+    for filter_name, filename in data_dict.items():
+        hjdDet, magDet, magUncDet, hjdLim, magLim, hjdFlux, flux, fluxUnc = plc(filename, 57470)
+        for hjd, f, f_unc in zip(hjdFlux, flux, fluxUnc):
+            if hjd < 2457470:
                 continue
-            if item["flux"] >= 5. * item["sigflux"]:
+            if hjd in hjdDet:
                 file_object.add_photometry(
-                    item["MJD"],
+                    hjd - 2400000.5,
                     filter_name,
-                    item["flux"] * 10**(-item["zpmag"] / 2.5) * 3631,
-                    abs(item["flux"] * 10**(-item["zpmag"] / 2.5) * 3631) *
-                    ((item["sigflux"] / item["flux"])**2 +
-                     (item["zprms"] / 2.5)**2)**0.5,
-                    -2.5 * np.log10(item["flux"]) + item["zpmag"],
-                    ((2.5 * item["sigflux"] / item["flux"])**2 +
-                     item["zprms"]**2)**0.5,
+                    f,
+                    f_unc,
+                    magDet[hjdDet == hjd],
+                    magUncDet[hjdDet == hjd],
                     "P48",
                     "CFH12K")
-            else:
+            elif hjd in hjdLim:
                 file_object.add_photometry(
-                    item["MJD"],
+                    hjd - 2400000.5,
                     filter_name,
-                    item["flux"] * 10**(-item["zpmag"] / 2.5) * 3631,
-                    abs(item["flux"] * 10**(-item["zpmag"] / 2.5) * 3631) *
-                    ((item["sigflux"] / item["flux"])**2 +
-                     (item["zprms"] / 2.5)**2)**0.5,
-                    -2.5 * np.log10(item["sigflux"] * 5.) + item["zpmag"],
[…]

### 2017-06-25 data/collect_data.py
Correct error in definition of hjd0 for 16abc.

@@ -103,7 +103,7 @@ def main():
     data_dict = {"g": "lc/forcepsffitdiff_d100151_f1_c11.out",
                  "R": "lc/forcepsffitdiff_d3381_f2_c10.out"}
     for filter_name, filename in data_dict.items():
-        hjdDet, magDet, magUncDet, hjdLim, magLim, hjdFlux, flux, fluxUnc = plc(filename, 57470)
+        hjdDet, magDet, magUncDet, hjdLim, magLim, hjdFlux, flux, fluxUnc = plc(filename, 2457470)
         for hjd, f, f_unc in zip(hjdFlux, flux, fluxUnc):
             if hjd < 2457470:
                 continue

### 2017-06-25 data/collect_data.py
Correct typo for P48 upper limit magnitudes. Update comments for RATIR photometry.

@@ -123,7 +123,7 @@ def main():
                     filter_name,
                     f,
                     f_unc,
-                    magLim[hjdDet == hjd],
+                    magLim[hjdLim == hjd],
                     99,
                     "P48",
                     "CFH12K")
@@ -197,7 +197,7 @@ def main():
     # RATIR Data
     with open("lc/16abc_ratir_clean.dat", "r") as fp_txt:
         for item in fp_txt:
-            if item.startswith("t"):
+            if item.startswith("#"):
                 continue
             items = item.split("  ")
             MJD = float(items[0])

### 2017-06-28 data/extinction_cal.py
Include extinction_cal.py in the repository.

@@ -1,0 +1,77 @@
+'''
+Extinction models
+'''
+
+import numpy as np
+from scipy import interpolate
+
+def fm90( wv, c1, c2, c3, c4, x0, gamma ):
+    '''
+    Ref: Fitzpatrick & Massa et al. 1990
+    Input: 
+        wv     - wavelength in Angstrom
+        c1     - intercept
+        c2     - slope
+        c3     - bump strength
+        c4     - FUV curvature
+        x0     - bump position
+        gamma  - bump width
+    Return:
+        E(wv-V)/E(B-V)
+    '''
+
+    def F(x):
+        return ( 0.5392 + 0.05644 * ( x - 5.9 ) ) * ( x - 5.9 ) * ( x - 5.9 ) * ( x > 5.9 )
+
+    x = 1e4 / wv
+
+    return c1 + c2 * x + \
+        c3 * x * x / ( ( x * x - x0 * x0 ) * ( x * x - x0 * x0 ) + x * x * gamma * gamma ) + \
+        c4 * F(x)
+
+
+def ftz( wv, RV ):
+    '''
+    Ref: Fitzpatrick 1999
+    Input: 
+        wv     - wavelength in Angstrom
+        RV     - R_V
+        EBV    - E(B-V)
+    Return:
+        E(wv-V)/E(B-V)
+    '''
+
+    # UV, lambda < 2700
+    c2 = -0.824 + 4.717 / RV
+    c1 = 2.030 - 3.007 * c2
+    x0 = 4.596
+    gamma = 0.99
+    c3 = 3.23
+    c4 = 0.41
+    UVFunc = lambda wv: fm90( wv, c1, c2, c3, c4, x0, gamma )
+
+    # Optical, UV, lambda > 2700
+    ## Anchor points
+    x = np.array ( [ 0.000, 0.377, 0.820, 1.667, 1.828, 2.141, 2.433, 3.704, 3.846 ] )
+    y = np.array ( [ 0.000, 0.265 * RV / 3.1, 0.829 * RV / 3.1,
+                     -0.426 + 1.004 * RV, -0.050 + 1.0016 * RV, 0.701 + 1.0016 * RV,
+                     1.208 + 1.0032 * RV - 0.00033 * RV * RV,
+                     UVFunc( 2700 ) + RV, UVFunc( 2600 ) + RV ] )
+    tck = interpolate.splrep( x, y )
[…]

### 2017-06-29 doc/ms.tex
Included updated measurements for time of first light in the paper.

@@
 the joint marginal distribution of $t_0$ and $\alpha$. From the
-best-fit model we obtain $\alpha=0.98 \pm ^{0.06}_{0.10}$ and $t_0=-17.94 \pm ^{0.05}_{0.06}$ d, where the uncertainties represent the marginalized 95\% confidence intervals. Our first
-detection of \abc\ occurred $\sim{0.2}\,\textrm{d}$ after 
+best-fit model we obtain $\alpha=0.98 \pm ^{0.16}_{0.14}$ and $t_0=-17.91 \pm ^{0.07}_{0.15}$ d, where the uncertainties represent the marginalized 95\% confidence intervals. Our first
+detection of \abc\ occurred $\sim{0.15}\,\textrm{d}$ after 
 the SN first light.
@@
     vertical line and the orange shaded region indicate $t_0$ and its
-    99.7\% confidence interval from Section
+    95\% confidence interval from Section
     \ref{sec:lc_fit}, respectively.

### 2017-06-30 doc/ms.tex
Add more stringent constraints on the companion interaction scenario to the paper.

@@
 
-The detection of excess emission due to the collision of SN ejecta 
+The detection of excess emission due to the collision of the SN ejecta 
 with a non-degenerate companion requires a favorable orbital 
@@
 considerations alone the probability of detecting ejecta-companion 
-interaction is low, $\sim$10\%. For any single type Ia SN, this 
-probability is further reduced because many explosions come from 
-WD-WD binaries. \citet{2010ApJ...708.1025K} calculates that the 
+interaction is low, $\sim$10\%. \citet{2010ApJ...708.1025K} calculates that the 
 collision of SN ejecta with a companion  
 generates thermal emission with a spectrum that peaks in the 
-UV. Thus, any resulting \textit{g}-band emission is very weak.
+UV. The resulting \textit{g}-band emission is expected to be weak.
 
@@
 light curve of \abc, we employ the \citet{2010ApJ...708.1025K}
-model and assume canonical ejecta mass of $1.4\sm$, expansion velocity of
-$10^{4}\,\textrm{km}\,\textrm{s}^{-1}$, and constant opacity of
+model and assume canonical values for the ejecta mass, $1.4\,\sm$, expansion velocity,
+$10^{4}\,\textrm{km}\,\textrm{s}^{-1}$, and a constant opacity, 
 $0.2\,\textrm{cm}^2\,\textrm{g}^{-1}$. We calculate the expected 
 $g_\mathrm{PTF}$ brightness of an ejecta-companion collision at the 
-distance of \abc\ using the parameterized equations in 
-\citet{2012ApJ...749...18B}. If we assume the binary is aligned with 
-the optimal orientation relative to the line of sight, the binary 
-separation would need to exceed $2\times10^{14}\,\textrm{cm}$ to 
-explain the initial detection of \abc. Assuming the companion fills 
-its Roche lobe, it would need to 
-have a radius of $\sim10^{14}\,\textrm{cm}\simeq10 \,\mathrm{AU}$.
-Such a radius is implausibly large for a WD binary companion, 
-therefore, we conclude that the early emission from \abc\ is not 
-due to a collision between the ejecta and a non-degenerate companion.
-Our early \textit{Swift} observations support this conclusion, as the UV $-$ optical colors are very red, whereas iPTF\,14atg exhibited much bluer UV $-$ optical colors at the same epoch \citep{2015Natur.521..328C}.
+distance of \abc\ behind a total redenning of $E(B-V) = 0.0779 \, \mathrm{mag}$ using the parameterized equations in 
+\citet{2012ApJ...749...18B}.
+If we assume the binary is aligned with the optimal orientation relative to the line of sight, a binary separation of $a \approx 2 \times 10^{13}\, \mathrm{cm}$ is needed to explain the initial detection of \abc, as shown in Figure~\ref{fig:SN-companion}.
+This model does not, however, match the $g_\mathrm{PTF}$ evolution for $t > t_0 + 1 \, \mathrm{d}$ (though it is possible that the SN photosphere dominates the companion-interaction signature at this phase).
+Furthermore, this model significantly overpredicts the observed flux in the \textit{Swift}/$UVW1$ filter $\sim$3.1~d after $t_0$.
+As such, we do not favor such a model as the explanation for the early emission from \abc.
 
-% \begin{figure}[!thb]
-%   \centering
-%   \includegraphics[width=0.45\textwidth]{SNCompanion.pdf}
-%   \caption{Apparent magnitude of a SN-companion collision (gray region)
-%     against the first detection of \abc\ (black). \amiller{Cut this
-%     figure? Doesn't add a lot of information.}}
-%   \label{fig:SN-companion}
-% \end{figure}
+Figure~\ref{fig:SN-companion} additionally shows that a companion at $a = 10^{14} \, \mathrm{cm}$ provides a good match to the observations $\sim$1--3~d after $t_0$ if $t_\mathrm{exp} \approx t_0 + 0.3 \; \mathrm{d}$.
+Like the $a = 2 \times 10^{13} \, \mathrm{cm}$ model, this model significantly overpredicts the observed UV flux from \abc.
+Additionally, this model cannot account for the brightness of \abc\ at the epoch of discovery.
+The challenges associated with each of the previous two models lead us to conclude that the early evolution of \abc\ cannot be explained via the interaction of the SN ejecta with a red-giant companion.\footnote{The \citet{2010ApJ...708.1025K} model assumes Roche-lobe overflow, meaning that $a > 10^{13} \, \mathrm{cm}$ implies a companion with $R_\ast \gtrsim 100 \, R_\odot$.} We cannot, however, exclude the presence of a red-giant companion as our calculations have assumed that the binary is aligned with the optimal geometry relative to the line of sight.
+If the geometry is not favorable, then it is possible that signatures from interaction with a companion are not visible.
+
+ % Our early \textit{Swift} observations support this conclusion, as the UV $-$ optical colors are very red, whereas iPTF\,14atg exhibited much bluer UV $-$ optical colors at the same epoch \citep{2015Natur.521..328C}.
+
+\begin{figure}[!thb]
+  \centering
+  \includegraphics[width=0.48\textwidth]{companion_lc.pdf}
+  \caption{Comparison of SN ejecta-companion interaction models 
+  with the early $g_\mathrm{PTF}$ light curve of \abc. 
+  Detections are shown as circles, while 3$\sigma$
+  upper limits are shown as downward facing arrows.
+  expected $g_\mathrm{PTF}$ light curve for the smallest orbital 
+  separation capable of explaining the initial detection of \abc. 
+  This model also requires $t_\mathrm{exp} \approx t_0 - 1 \; 
+  \mathrm{d}$. Assuming $t_\mathrm{exp} = t_0$, interaction with a 
+  companion at $a = 2 \times 10^{13} \; \mathrm{cm}$ matches the 
+  initial detection of \abc\ (solid line). This model 
+  significantly overestimates the UV flux detected from \abc\ 
+  $\sim$3 d after explosion (see text). The $g_\mathrm{PTF}$ 
+  observations $\sim$1--3~d after $t_0$ are well matched to 
+  companion-interaction models for $a = 10^{14} \; \mathrm{cm}$ 
+  if $t_\mathrm{exp} \approx t_0 + 0.3 \; \mathrm{d}$ (dash-dot 
+  line). This model significantly underestimates the flux at the 
+  epoch of discovery, while also overestimating the UV flux. Thus, 
+  none of these possibilities uniquely explain the early flux from 
+  \abc.
+  \amiller{Add Swift light curve and photometry to make it clear that two large companions don't explain the observations? Also -- make labels for this fig bigger}}
+  \label{fig:SN-companion}
+\end{figure}
+
+Finally, we examine the minimum binary separation capable of explaining the observed brightness at the epoch of discovery.
+Figure~\ref{fig:SN-companion} shows that models with $a \approx 8 \times 10^{11} \, \mathrm{cm}$ peak at $\sim$21.5~mag in the $g_\mathrm{PTF}$-band, provided that $t_\mathrm{exp} \approx t_0 - 1 \; \mathrm{d}$.
+To explain just the epoch of discovery, models with larger $a$ would require even earlier explosion times, which is not compatible with our non-detections the night before discovery, while models with smaller $a$ are not bright enough.
+While it is otherwise compatible with the observations, we do not favor the $a \approx 8 \times 10^{11} \, \mathrm{cm}$ model as the explanation for the early flux from \abc\ because it does not explain the 2 mag rise in the $\sim$24 hr after discovery.
+
+Recently, \citet{2017arXiv170608990H} showed that the early light curve of SN\,2017cbv has a clearly resolved bump in the $U$, $B$, and $g'$ bands in the $\sim$5 d after explosion.
+\citeauthor{2017arXiv170608990H} find that the bump can be explained via the combination of ejecta-companion interaction and the normal evolution of a type Ia SN.
+A challenge for this model is that it significantly overpredicts the UV brightness of the SN compared to what is observed.
+It is argued in \citet{2017arXiv170608990H} that the shock resulting from the companion collision may not be a blackbody, which could reconcile the model with the observed UV photometry.
+Qualitatively, \abc\ and SN\,2017cbv exhibit similar characteristics: both feature strong \ion{C}{2} absorption in their early spectra and a bump in their early light curves.
+Below, we argue for circumstellar interaction and strong $^{56}$Ni mixing as a possible explanation for \abc, and indeed \citet{2017arXiv170608990H} consider these possibilities for SN\,2017cbv as well.
+While there are arguments in favor of and against each of these possibilities, we believe that the early behavior of SN\,2017cbv and \abc\ reflect a common physical origin.
+\amiller{should this paragraph be in the conclusions?}
 

### 2017-07-01 data/collect_data.py
Correct indent typo for storing RATIR data in hdf table

@@ -206,15 +206,15 @@ def main():
             mag_err = 2.5/np.log(10)*float(items[3])/float(items[2])
             flux = 10**(-0.4*mag) * 3631 # Jy
             flux_err = flux*float(items[3])/float(items[2])
-        file_object.add_photometry(
-            MJD,
-            filter_name,
-            flux,
-            flux_err,
-            mag,
-            mag_err,
-            "SPM-1.5m",
-            "RATIR")
+            file_object.add_photometry(
+                MJD,
+                filter_name,
+                flux,
+                flux_err,
+                mag,
+                mag_err,
+                "SPM-1.5m",
+                "RATIR")
 
     # Spectra
     filename = "spec/16abc_20160405_DCT_v1.ascii"

### 2017-07-17 doc/ms.tex
Update phases in the spectroscopy table.

@@
   \startdata
-  $57483.26$ & $-16.4$ & DCT & DeVeny\tablenotemark{1} & $3301$--$7499$ \\
-  $57483.88$ & $-15.8$ & Gemini-North & GMOS\tablenotemark{2} & $3800$--$9200$ \\
-  $57484.51$ & $-15.1$ & Keck-II & DEIMOS\tablenotemark{3} & $5500$--$8099$ \\
-  $57486.51$ & $-13.1$ & Keck-II & DEIMOS\tablenotemark{3} & $5500$--$8099$ \\
-  $57488.38$ & $-11.3$ & Keck-I & LRIS\tablenotemark{4} & $3055$--$10411$ \\
-  $57489.51$ & $-10.1$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $3301$--$8999$ \\
-  $57490.40$ & $ -9.3$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $3301$--$9999$ \\
-  $57491.55$ & $ -8.1$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $3300$--$9998$ \\
-  $57492.20$ & $ -7.5$ & VLT & X-shooter\tablenotemark{6} & $3300$--$24550$ \\
-  $57494.00$ & $ -5.7$ & VLT & UVES\tablenotemark{7} & \\
+  $57483.26$ & $-15.9$ & DCT & DeVeny\tablenotemark{1} & $3301$--$7499$ \\
+  $57483.88$ & $-15.3$ & Gemini-North & GMOS\tablenotemark{2} & $3800$--$9200$ \\
+  $57484.51$ & $-14.7$ & Keck-II & DEIMOS\tablenotemark{3} & $5500$--$8099$ \\
+  $57486.51$ & $-12.7$ & Keck-II & DEIMOS\tablenotemark{3} & $5500$--$8099$ \\
+  $57488.38$ & $-10.9$ & Keck-I & LRIS\tablenotemark{4} & $3055$--$10411$ \\
+  $57489.51$ & $ -9.8$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $3301$--$8999$ \\
+  $57490.40$ & $ -8.9$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $3301$--$9999$ \\
+  $57491.55$ & $ -7.8$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $3300$--$9998$ \\
+  $57492.20$ & $ -7.2$ & VLT & X-shooter\tablenotemark{6} & $3300$--$24550$ \\
+  $57494.00$ & $ -5.4$ & VLT & UVES\tablenotemark{7} & \\
   $57503.32$ & $ +3.7$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $3300$--$9999$ \\
   $57506.00$ & $ +6.3$ & NOT & ALFOSC\tablenotemark{8} & $3602$--$8098$ \\
-  $57508.27$ & $ +8.6$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $3301$--$9999$ \\
-  $57518.42$ & $+18.8$ & Keck-I & LRIS\tablenotemark{4} & $3071$--$10208$ \\
-  $57520.03$ & $+20.4$ & VLT & X-shooter\tablenotemark{6} & $3300$--$24789$ \\
-  $57529.40$ & $+29.8$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $4000$--$8998$ \\
-  $57542.41$ & $+42.8$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $4000$--$8998$ \\
-  $57550.40$ & $+50.8$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $4001$--$8999$ \\
-  $57562.38$ & $+62.7$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $4800$--$9300$ \\
+  $57508.27$ & $ +8.5$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $3301$--$9999$ \\
+  $57518.42$ & $+18.5$ & Keck-I & LRIS\tablenotemark{4} & $3071$--$10208$ \\
+  $57520.03$ & $+20.0$ & VLT & X-shooter\tablenotemark{6} & $3300$--$24789$ \\
+  $57529.40$ & $+29.2$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $4000$--$8998$ \\
+  $57542.41$ & $+41.9$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $4000$--$8998$ \\
+  $57550.40$ & $+49.7$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $4001$--$8999$ \\
+  $57562.38$ & $+61.4$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $4800$--$9300$ \\
   \enddata

### 2017-07-18 doc/ms.tex
Update the caption for the companion interaction figure

@@
 
-\begin{deluxetable*}{cccccc}
+\begin{deluxetable}{cccccc}
   \tablecaption{Spectroscopic observations of \abc\ \label{tab:spec_obs_log}}
   \tablehead{
-    \colhead{Observation MJD} & \colhead{SN phase} & \colhead{Telescope} &
-    \colhead{Instrument} & \colhead{Wavelength Coverage (\AA)}
+    \colhead{Observation} & \colhead{SN} & \colhead{} &
+    \colhead{} & \colhead{Range} \\
+    \colhead{MJD} & \colhead{phase} & \colhead{Telescope} &
+    \colhead{Instrument} & \colhead{(\AA)}
   }
@@
   \tablenotetext{8}{The Andalucia Faint Object Spectrograph and Camera \url{http://www.not.iac.es/instruments/alfosc}}
-\end{deluxetable*}
+\end{deluxetable}
 
@@
   \includegraphics[width=1.0\textwidth]{spectra.pdf}
-  \caption{Observed spectral sequence of \abc. For clarity, offsets 
-  have been applied to each 
-  spectrum which are normalized by their median flux between 
-  6,000 and 7,000$\,\textrm{\AA}$. The phase of each spectrum 
+  \caption{Observed spectral sequence of \abc. The spectra are 
+  normalized by their median flux between 6,000 and 
+  7,000$\,\textrm{\AA}$.  The phase of each spectrum 
   relative to $T_{B_\mathrm{max}}$ is shown. Telluric absorption
-  bands are grayed out. The narrow \ion{Na}{1}\,D absorption is also
-  highlighted in orange.}
+  bands are grayed out. Line identifications are provided for 
+  the spectral features discussed in the text. 
+  For clarity, high-resolution spectra obtained with the VLT have been omitted (see Ferretti et al.\ 2017, submitted, for a detailed discussion of these spectra).}
   \label{fig:spec_seq}
@@
   \caption{Comparison of SN ejecta-companion interaction models 
-  with the early $g_\mathrm{PTF}$ light curve of \abc. 
-  Detections are shown as circles, while 3$\sigma$
-  upper limits are shown as downward facing arrows.
-  expected $g_\mathrm{PTF}$ light curve for the smallest orbital 
-  separation capable of explaining the initial detection of \abc. 
-  This model also requires $t_\mathrm{exp} \approx t_0 - 1 \; 
-  \mathrm{d}$. Assuming $t_\mathrm{exp} = t_0$, interaction with a 
-  companion at $a = 2 \times 10^{13} \; \mathrm{cm}$ matches the 
-  initial detection of \abc\ (solid line). This model 
-  significantly overestimates the UV flux detected from \abc\ 
-  $\sim$3 d after explosion (see text). The $g_\mathrm{PTF}$ 
-  observations $\sim$1--3~d after $t_0$ are well matched to 
-  companion-interaction models for $a = 10^{14} \; \mathrm{cm}$ 
-  if $t_\mathrm{exp} \approx t_0 + 0.3 \; \mathrm{d}$ (dash-dot 
-  line). This model significantly underestimates the flux at the 
-  epoch of discovery, while also overestimating the UV flux. Thus, 
-  none of these possibilities uniquely explain the early flux from 
-  \abc.
-  \amiller{Add Swift light curve and photometry to make it clear that two large companions don't explain the observations? Also -- make labels for this fig bigger}}
+  with early observations of \abc. $g_\mathrm{PTF}$ observations 
+  (green) detections and 3$\sigma$ upper limits are shown 
+  as circles and downward arrows, respectively. The initial 
+  \textit{Swift}/$UVW1$ observation (magenta) is shown as a 
+  hexagon.
+  The dashed, solid, and dash-dot lines show the expected flux 
+  for various companion interaction models in 
+  the $g_\mathrm{PTF}$ (green) and $UVW1$ (magenta) filters. The 
+  models have been adjusted to account for the distance and 
+  redenning towards \abc. Each 
+  model features a different companion semi-major axis, $a$, and 
+  time of explosion, $t_\mathrm{exp}$, as labeled in the figure 
+  legend. While models with $a \gtrsim 10^{13} \, \mathrm{cm}$ can 
+  explain the early $g_\mathrm{PTF}$ emission, they greatly 
+  overpredict the flux in the UV. If the time of explosion is 
+  $\sim$1 d prior to $t_0$, then models with $a \approx 10^{12} \, 
+  \mathrm{cm}$ can explain the initial detection \abc, but they 
+  fail to replicate the $\sim$2 mag rise in the $\sim$24 hr after 
+  explosion. Thus, SN ejecta-companion interaction models fail
+  to uniquely explain the early flux from \abc.
+  }
   \label{fig:SN-companion}
@@
 \label{sec:Ni_mixing}
+
+\amiller{need to mention velocities}
 

### 2017-07-18 doc/ms.tex
Update text regarding velocity fits to better reflect more recent numerical work.

@@
 
-\subsection{Light Curve Fit}
+\subsection{Time of First Light from the Early Light Curve}
 \label{sec:lc_fit}
@@
 
-\subsection{Expansion Velocity Fit}
+\subsection{Time of Explosion from the Photospheric Velocity}
 \label{sec:early_vel}
@@
 find that the photospheric velocity evolves as
-$v_{ph}\propto(t-t_{exp})^{-0.22}$. While the photospheric velocity
+$v_{ph}\propto(t-t_\mathrm{exp})^{-0.22}$.
+Numerical experiments by \citet{2016ApJ...826...96P} find that the consatnt-opacity assumption strongly depends on the amount of $^{56}$Ni mixing in the SN ejecta (for a more detailed discussion of $^{56}$Ni mixing see \S\ref{sec:Ni_mixing}).
+As a result, the adoption of a $t^{-0.22}$ power-law model may not be valid for all SNe Ia.
+Nevertheless, we proceed on the assumption that \abc\ experienced strong $^{56}$Ni mixing, corresponding to the models that are best approximated as a $t^{-0.22}$ power law.
+We do this in part to compare with previous studies, though we caution that our derived value for $t_{exp}$ is subject to uncertainties related to ejecta mixing.
+
+While the photospheric velocity
 is not easy to measure, line velocities of \ion{Si}{2} or \ion{Ca}{2}
 can be used as a proxy
-\citep{2014ApJ...784...85P,2016ApJ...826..144S}.
-
-In the case of \abc, the \ion{Ca}{2} IR triplet is very weak, 
+\citep{2014ApJ...784...85P,2016ApJ...826..144S}. In the case of \abc, the \ion{Ca}{2} IR triplet is very weak, 
 likely due to high temperatures in the ejecta. Thus, we
@@
 sign of multi-velocity components of \ion{Si}{2}, and that 
-\ion{C}{2}\,$\lambda$6580 line overlaps the red
+the \ion{C}{2}\,$\lambda$6580 line overlaps the red
 wing of the \ion{Si}{2} line (see Figures~\ref{fig:spec_seq} and \ref{fig:carbon}). Consequently, we model the observed 
-spectra between 5,900 and 6,500\,\AA (rest-frame) as the combination 
+spectra between 5,900 and 6,500\,\AA\ (rest-frame) as the combination 
 of two gaussian kernels plus a linear baseline, which
@@
 $v\propto(t-t_{exp})^{-0.22}$ model by minimizing the $\chi^2$ value and find the best-fit explosion time relative to $T_{B,\mathrm{max}}$ in the SN rest frame to be $t_{exp} = -17.45 \pm ^{0.14}_{0.16}\;\textrm{d}$, where the uncertainties represent the 95\% confidence interval (Figure \ref{fig:velocity_t_exp}).
-Following the analysis in \citet{2014ApJ...784...85P}, we additionally alter the power-law index to $-0.20$ and $-0.24$ to examine the sensitively of the result on the assumed power-law index.
-We find that this variation in the power-law index result in inferred explosion times that vary by $\approx$1 d (Figure \ref{fig:velocity_t_exp}).
-Given the theorhetical expectation that $v \propto t^{-0.22}$, we adopt $t_{exp} = -17.45 \pm 0.5 \; \mathrm{d}$, where the uncertainty reflects possible variations in the power-lax index (see \citealt{2014ApJ...784...85P}).
+Following the analysis in \citet{2014ApJ...784...85P}, we additionally alter the power-law index to $-0.20$ and $-0.24$ to examine the sensitivety of the result on the assumed power-law index.
+We find that this variation in the power-law index results in inferred explosion times that vary by $\approx$1 d (Figure \ref{fig:velocity_t_exp}).
+Given the analytical approximation that $v \propto t^{-0.22}$, we adopt $t_{exp} = -17.5 \pm 0.5 \; \mathrm{d}$, where the uncertainty reflects possible variations in the power-lax index (see \citealt{2014ApJ...784...85P}).
 
@@
 conclusion that $t_0\simeq t_{exp}$, which is consistent to within the uncertainties.
+Again, we caution that this derivation of $t_\mathrm{exp}$ relies on the assumption $v \propto t^{-0.22}$, which may not be valid for all SNe Ia.
 

### 2017-07-24 doc/ms.tex
Include discussion of some of the faillings of the mixing models in the paper.

@@
 decreases until the feature is no longer detectable 
-around $t=-10$ days.
+around $t = -10$ d.
 
@@
 Spectra obtained around or after $T_{B_\mathrm{max}}$ rarely show \ion{C}{2} as the photosphere has receded from the outermost ejecta, while pre-max spectra show evidence for \ion{C}{2} in $\sim$1/4 of all normal SNe Ia (e.g., \citealt{2011ApJ...732...30P,2012MNRAS.425.1917S,2011ApJ...743...27T}), but the signatures are typically weak.
-While we caution that the sample of normal SNe Ia with spectra taken within a few days of explosion is small, SN\,2013dy is the only other object known to have strong \ion{C}{2} features like \abc\ \citet{2013ApJ...778L..15Z}.
+While we caution that the sample of normal SNe Ia with spectra taken within a few days of explosion is small, SN\,2013dy is the only other object known to have strong \ion{C}{2} features like \abc\ \citep{2013ApJ...778L..15Z}.
 As a counterexample, SN\,2011fe only exhibited weak \ion{C}{2} features in its first spectra
@@
 
-We have identified several unusual properties in the early observations of \abc, including: (i) a near-linear photometric rise in the days after explosion, (ii) the lack of a dark phase typical of most SNe Ia, and (iii) the presence of strong \ion{C}{2} absorption.
+Relative to the nearby, normal SN\,2011fe, we have identified several unusual properties in the early observations of \abc, including: (i) a near-linear photometric rise in the days after explosion, (ii) the lack of a dark phase typical of most SNe Ia, and (iii) the presence of strong \ion{C}{2} absorption.
 While most SNe Ia are powered purely by radioactive decay, the observed radiation shortly after explosion can also include contributions
@@
 Here we consider a model that has not, as of yet, been discussed in the context of \abc.
-In the context of SN\,2011fe, \citet{2014MNRAS.441..532D} recently examined pulsational delayed-detonation (PDD) models as an explanation for some SNe Ia.
+To model SN\,2011fe, \citet{2014MNRAS.441..532D} recently examined pulsational delayed-detonation (PDD) models as an explanation for some SNe Ia.
 Briefly, PDD models differ from ``standard'' delayed detonation (DD) models in that the initial deflagration causes the WD to expand resulting in the release of some unbound material.
@@
 
-While examining observations of SN\,2011fe in the context of DD models, \citet{2014MNRAS.441..532D} find that the models are universally too faint and red at early times, $\sim$24-48 hr after explosion.
-These discrepancies can be somewhat improved if the newly synthesized $^{56}$Ni is artificially mixed throughout the SN ejecta (see \S\ref{sec:Ni_mixing} for further details on the importance of mixing).
+When comparing observations of SN\,2011fe to their DD models, \citet{2014MNRAS.441..532D} find that the models are universally too faint and red at early times, $\sim$24-48 hr after explosion.
 Instead, \citet{2014MNRAS.441..532D} find that PDD models provide a better match to observations.
@@
 The optical colors for \abc\ are blue from our first epoch $\sim$1.7 d after explosion and remain approximately constant in the 10 d after explosion, whereas the PDD models in \citet{2014MNRAS.441..532D} either exhibit distinct color evolution (i.e.\ are not constant) or are too red in the first few days after explosion.
-Nevertheless, the PDD models presented in \citet{2014MNRAS.441..532D} provide several attractive explanations for the unusual features in the early behavior of \abc, and it may be possible that small adjustments to the model, e.g., additional mixing of the radioactive products from the explosion, can better match \abc.
+Nevertheless, the PDD models presented in \citet{2014MNRAS.441..532D} provide several attractive explanations for the unusual features in the early behavior of \abc, and it may be possible that small adjustments to the model (e.g., additional mixing of the radioactive material, adjustments in the explosion energy, etc.) can better match \abc.
 
@@
 
-Having ruled out other possibilities we now consider whether the unusual properties of \abc\ can be explained simply by invoking strong mixing in the SN ejecta.
-As previously mentioned, strong mixing can lead to a short dark phase and \ion{C}{2} absorption.
-Here we additionally examine if strong mixing can explain the rapid, near-linear rise in the light curve.
+Having examined other possibilities we now consider whether the unusual properties of \abc\ can be explained simply by invoking strong mixing in the SN ejecta.
+As previously mentioned, strong mixing can lead to a short dark phase.
+Here we additionally examine whether strong mixing can explain the rapid, near-linear rise in the light curve.
 
@@
 The \citeauthor{2016ApJ...826...96P} models employ a piston driven explosion to explode a single WD progenitor model.
-As the piston explosion does not result in any nucleosynthesis, the distribution of $^{56}$Ni in the ejecta must be prescribed by hand, which enables their study of the effects of mixing on the resulting SN emission.
+As the piston explosion does not result in any nucleosynthesis, the distribution of $^{56}$Ni in the ejecta must be prescribed by hand, which enables the study of the effects of mixing on the resulting SN emission.
 Each model employs a fixed $0.5\,\sm$ of $^{56}$Ni that has been distributed throughout the ejecta via boxcar averaging (see their Figure~1).
@@
 Broadly speaking, the results can be summarized as follows: SN with strong mixing exhibit a rapid almost linear rise and quickly develop blue colors, whereas models where the $^{56}$Ni is confined to the innermost layers of the ejecta remain very faint for days after explosion while exhibiting relatively red optical colors during this period.
-The fast rise and blue color of \abc\ are consistent with the strong mixing models from \citet{2016ApJ...826...96P}, as shown in Figure~\ref{fig:Ni56LC}.
+The fast rise and blue color of \abc\ are qualitatively consistent with the strong mixing models from \citet{2016ApJ...826...96P}, as shown in Figure~\ref{fig:Ni56LC}.
+In fact, if we adopt $t_\mathrm{exp} = t_0 - 0.45 \, \mathrm{d}$, we find that the model with the strongest mixing (orange line in Figure~\ref{fig:Ni56LC} provides an excellent match to the $g$-band observations.
+
+While the models from \citet{2016ApJ...826...96P} provide a good match to the optical photometric evolution of \abc, they consistently overpredict the flux in the UV.
+The models shown in Figure~\ref{fig:Ni56LC} also overpredict the photospheric velocity of \abc\ by $\sim$2--3,000$\; \mathrm{km \; s}^{-1}$.
+These discrepancies may be accounted for following an improved treatment of line-blanketing and a reduction in the model explosion energy, respectively.
+Future modeling efforts may improve the match between the simulations and observations for \abc.
+
+Both the PDD models and ejecta-mixing models show discrepancies with some of the early observations of \abc.
+Nevertheless, we conclude that one, or both, of these scenarios, which feature qualitatively similar predictions, is the most likely explanation for \abc.
+
 We conclude that the early observations of \abc\ can be explained if the $^{56}$Ni synthesized in the explosion is mixed into the outermost layers of the SN ejecta.
@@
 
+\subsection{The Emerging Sample of Young SNe Ia}
+
 \section{Conclusion}

### 2017-07-26 doc/ms.tex
Remove sentence describing asserting Ni mixing is only explanation for SN
Include text with a comparison between 16abc and 11fe for the B-V colors.

@@
 
-\section{First Light And Explosion Time}
+\section{Early Observations}
 \label{sec:first_light}
+
+Here we consider our suite of early observations of \abc, and compare our findings with SN\,2011fe, a well-studied, nearby SN that was discovered shortly after explosion \citep{2011Natur.480..344N,2012ApJ...744L..17B,2014ApJ...784...85P}.
 
@@
 \citep{2012ApJ...752L..26P}. Thus, models of \abc\ must explain the anomalously strong \ion{C}{2} absorption observed shortly after explosion.
+
+\subsection{Blue Optical Colors Shortly After Explosion}
+
+Multiband observations of \abc\ began $\sim$1.5 d after discovery, which allows us to trace its color evolution starting $\sim$1.7 d after $t_0$.
+In Figure~\ref{fig:B-Vcolors} we compare the $(B - V)_0$ color evolution of \abc\ and SN\,2011fe, where the observations of SN\,2011fe are taken from \citet{2016ApJ...820...67Z}.
+For both SN the colors have been corrected for the total inferred redenning along the line of sight.
+Interestingly, \abc\ has a nearly flat color evolution up to 10 d before $T_{B,\mathrm{max}}$, while SN\,2011fe exhibits red colors initially before eventually becoming as blue as \abc.
+
+\begin{figure}[]
+  \centering
+  \includegraphics[width=0.45\textwidth]{16abc_11fe_colors.pdf}
+  \caption{$(B - V)_0$ color evolution of \abc\ (shown as squares) 
+    compared to SN\,2011fe (shown as stars). The $B$ and $V$ 
+    photometry are calibrated on the Vega system. The data for 
+    SN\,2011fe are from \citet{2016ApJ...820...67Z}.}
+  \label{fig:B-Vcolors}
+\end{figure}
+
+Roughly 16 d prior to $B$-band maximum, the $(B - V)_0$ color of \abc\ is $\sim$0.5 mag bluer than SN\,2011fe.
+Like \abc, SN\,2012cg \citep{2016ApJ...820...92M} and SN\,2017cbv \citep{2017arXiv170608990H} exhibit $(B - V)_0$ colors that are significantly bluer than SN\,2011fe at very early epochs.
+While there are many factors that contribute to the early optical colors of SNe Ia (see \S\ref{sec:lc_energy} below), early blue colors are often interpreted as a hallmark of interaction between the SN ejecta and a binary companion.
+Nevertheless, it is interesting to note that despite the blue optical colors the UV $-$ optical colors of \abc, SN\,2012cg, and SN\,2017cbv are significantly redder at these early epochs than the UV $-$ optical colors of iPTF\,14atg \citep{2015Natur.521..328C}, the most likely candidate for an ejecta-companion interaction SN.
 
@@
 
-We conclude that the early observations of \abc\ can be explained if the $^{56}$Ni synthesized in the explosion is mixed into the outermost layers of the SN ejecta.
-
 \begin{figure}[]

### 2017-07-27 doc/ms.tex
Remove unnecessary notes to myself or questions for co-authors from the text
Add subsection to text describing different obs of young SNe Ia.

@@
 \subsection{SN-Companion collision}
+\label{sec:companion}
 
@@
 
-Recently, \citet{2017arXiv170608990H} showed that the early light curve of SN\,2017cbv has a clearly resolved bump in the $U$, $B$, and $g'$ bands in the $\sim$5 d after explosion.
-\citeauthor{2017arXiv170608990H} find that the bump can be explained via the combination of ejecta-companion interaction and the normal evolution of a type Ia SN.
-A challenge for this model is that it significantly overpredicts the UV brightness of the SN compared to what is observed.
-It is argued in \citet{2017arXiv170608990H} that the shock resulting from the companion collision may not be a blackbody, which could reconcile the model with the observed UV photometry.
-Qualitatively, \abc\ and SN\,2017cbv exhibit similar characteristics: both feature strong \ion{C}{2} absorption in their early spectra and a bump in their early light curves.
-Below, we argue for circumstellar interaction and strong $^{56}$Ni mixing as a possible explanation for \abc, and indeed \citet{2017arXiv170608990H} consider these possibilities for SN\,2017cbv as well.
-While there are arguments in favor of and against each of these possibilities, we believe that the early behavior of SN\,2017cbv and \abc\ reflect a common physical origin.
-\amiller{should this paragraph be in the conclusions?}
-
 \subsection{Interaction with Diffuse Material}
@@
 \label{sec:Ni_mixing}
-
-\amiller{need to mention velocities}
 
@@
 
+The proliferation of high-cadence, time-domain surveys has led to several SNe Ia being discovered within $\lesssim$2 d of first light in the past $\sim$decade.
+Observations probing the early evolution of these SNe allows us to place unique constraints on their progenitor systems and the corresponding explosion physics.
+This has revealed diversity in the earliest epochs after explosion and that commonly used SNe Ia templates do not match observations (e.g., \citealt{2012ApJ...744...38F}).
+
+In \S\ref{sec:lc_energy} we compared our early observations of \abc\ to SN\,2011fe, which has the most comprehensive observations of the young SNe Ia sample.
+Given its normal spectroscopic and photometric evolution, SN\,2011fe has been adopted as a standard for the early evolution of SNe Ia in many studies.
+While a detailed quantitative analysis is beyond the scope of this study, a qualitative examination of very young SNe Ia that otherwise exhibit normal spectra and evolution at and post-peak\footnote{This definition excludes iPTF\,14atg, which was shown to be subluminous with SN\,2002es-like spectra \citep{2015Natur.521..328C}.} reveals considerable diversity.
+In other words, at early times SN\,2011fe may not be the norm.
+
+For SN\,2011fe the initial rise is well described by a $t^2$ power law, the $(B - V)_0$ colors evolve from the red to the blue, and the \ion{C}{2} present in the initial spectra is weak \citep{2011Natur.480..344N,2016ApJ...820...67Z,2012ApJ...752L..26P}.
+In contrast, \abc\ exhibits a near linear rise in flux, the $(B - V)_0$ colors are blue and roughly constant, and the \ion{C}{2} absorption is strong.
+Examining just these 3 qualitative features, SN\,2009ig is well matched to SN\,2011fe \citep{2012ApJ...744...38F}, while SN\,2013dy \citep{2013ApJ...778L..15Z}, SN\,2017cbv \citep{2017arXiv170608990H}, and \abc\ all bear a striking resemblance.
+SN\,2012cg, on the other hand, appears to be intermediate to these two groups with weak C II and a relatively shallow early rise, like SN\,2011fe, but blue $(B - V)_0$ colors, like \abc\ \citep{2012ApJ...756L...7S,2016ApJ...820...92M}.
+That these early observations cannot be easily separated into two distinct groups suggests that it is unlikely that a single physical mechanism drives the diversity of SNe Ia at early times.
+\amiller{Not sure what to say about 14J - colors are difficult to measure, and ASASSN-14lp no \ion{C}{2} measurement and no discussion of colors}.
+
+In the case of SN\,2012cg and SN\,2017cbv it has been argued that the early blue optical colors are indicative of interaction between the SN ejecta and a binary companion \citep{2016ApJ...820...92M,2017arXiv170608990H}.
+SN\,2017cbv is particularly remarkable in that the observations presented in \citet{2017arXiv170608990H} show a clearly resolved bump in the $U$, $B$, and $g'$ bands in the $\sim$5 d after explosion.
+In \citeauthor{2017arXiv170608990H} it is found that the bump can be explained via the combination of ejecta-companion interaction and the normal evolution of a SN Ia.
+A challenge for this model, similar to \abc\ (see \S\ref{sec:companion}), is that it significantly overpredicts the UV brightness of the SN compared to what is observed.
+Indeed, in the case of SNe\,2012cg, 2017cbv, and \abc\ the UV - optical colors are significantly redder than those observed in iPTF\,14atg.
+It is argued in \citet{2017arXiv170608990H} that several model assumptions, including: (i) ideal blackbody emission, (ii) a constant opacity, (iii) a simple power-law density profile for the ejecta, and (iv) spherical symmetry, may be incorrect, which could reconcile the discrepancy with the UV observations.
+Above, we argued for circumstellar interaction and strong $^{56}$Ni mixing as a possible explanation for \abc, and indeed \citet{2017arXiv170608990H} consider these possibilities for SN\,2017cbv as well.
+Seperately, several arguments against companion interaction for SN\,2012cg are presented in \citet{2016arXiv161007601S}.
+
+Ultimately, there are arguments in favor of and against each of the possibilties to explain the early emission from SNe Ia.
+Moving forward, more detailed models and simulations are needed to properly explain the observed diversity.
+No matter the correct explanation for the early behavior of SNe\,2013dy, 2017cbv, and \abc, the strong similarities between these events suggests they reflect a common physical origin.
+
 \section{Conclusion}
@@
 $^{56}$Ni decay is the likely source of the non-thermal emission, providing another piece of evidence for strong mixing in the ejecta of \abc.
-
-\textbf{Does anyone know of any theoretical studies that specifically predict incomplete burning and strong Ni mixing?}
 

### 2017-07-28 doc/ms.tex
Update to subsection with context on early Ia observations.

@@
 
-For SN\,2011fe the initial rise is well described by a $t^2$ power law, the $(B - V)_0$ colors evolve from the red to the blue, and the \ion{C}{2} present in the initial spectra is weak \citep{2011Natur.480..344N,2016ApJ...820...67Z,2012ApJ...752L..26P}.
+For SN\,2011fe the initial rise is well described by a $t^2$ power law, the $(B - V)_0$ colors evolve from the red to the blue in the $\sim$week after explosion, and the \ion{C}{2} present in the initial spectra is weak \citep{2011Natur.480..344N,2016ApJ...820...67Z,2012ApJ...752L..26P}.
 In contrast, \abc\ exhibits a near linear rise in flux, the $(B - V)_0$ colors are blue and roughly constant, and the \ion{C}{2} absorption is strong.
 Examining just these 3 qualitative features, SN\,2009ig is well matched to SN\,2011fe \citep{2012ApJ...744...38F}, while SN\,2013dy \citep{2013ApJ...778L..15Z}, SN\,2017cbv \citep{2017arXiv170608990H}, and \abc\ all bear a striking resemblance.
-SN\,2012cg, on the other hand, appears to be intermediate to these two groups with weak C II and a relatively shallow early rise, like SN\,2011fe, but blue $(B - V)_0$ colors, like \abc\ \citep{2012ApJ...756L...7S,2016ApJ...820...92M}.
-That these early observations cannot be easily separated into two distinct groups suggests that it is unlikely that a single physical mechanism drives the diversity of SNe Ia at early times.
-\amiller{Not sure what to say about 14J - colors are difficult to measure, and ASASSN-14lp no \ion{C}{2} measurement and no discussion of colors}.
+SN\,2012cg, on the other hand, is intermediate to these two groups with weak C II and a relatively shallow early rise, like SN\,2011fe, but blue $(B - V)_0$ colors, like \abc\ \citep{2012ApJ...756L...7S,2016ApJ...820...92M}.
+SN\,2014J is intermediate in the other direction in that it exhibits a near linear rise \citep{2014ApJ...783L..24Z,2015ApJ...799..106G}, but the color evolution is very similar to SN\,2011fe \citep{2014ApJ...788L..21A}.\footnote{\ion{C}{2} is not detected in the spectra of SN\,2014J \citep{2014ApJ...784L..12G,2014ApJ...783L..24Z}, though the earliest spectra of SN\,2014J were obtained at a much later phase than the other SNe discussed here.
+\citet{2015ApJ...798...39M} find evidence for \ion{C}{1} in the NIR spectra of SN\,2014J, but this detection cannot constrain the relative strength of \ion{C}{2} and \ion{Si}{2} shortly after explosion.} That these early observations cannot be easily separated into two distinct groups suggests that it is unlikely that a single physical mechanism drives the diversity of SNe Ia at early times.
 

### 2017-07-28 doc/ms.tex
Update text in the asbtract of the manuscript to reflect new conclusions.

@@
 
-Early observations of type Ia supernovae (SNe) provide a unique probe of their progenitor systems and explosion physics.
-Here, we report the intermediate Palomar Transient Factory (iPTF) discovery of an extraordinarily young Type Ia supernova, \abc.
-The initial detection of the SN was made only $0.18$~d after the time of first light.
-In the $\sim$24 hr after discovery, \abc\ rose by $\sim$2 mag in the $g_\mathrm{PTF}$ band, which is very rare for young type Ia SNe.
-Furthermore, by measuring the evolution of the photospheric velocity we determine that the time of explosion for \abc\ is approximately equal to the time of first light.
-Spectra obtained in the week after explosion reveal the presence of strong \ion{C}{2} absorption, which steadily fades over that time period.
-We show that the unusually fast, near-linear rise in flux for \abc\ cannot be explained by either SN shock breakout and the associated subsequent cooling or the collision of the SN ejecta with a stellar companion.
-Instead, we show each of the unusual characteristics of \abc: (i) the rapid, near-linear rise, (ii) the lack of a dark period between explosion and first light, and (iii) the strong lines from ionized carbon in the earliest spectra, can all be explained if radioactive $^{56}$Ni is strongly mixed throughout the SN ejecta.
+Early observations of Type Ia supernovae (SNe) provide a unique probe of their progenitor systems and explosion physics.
+Here, we report the intermediate Palomar Transient Factory (iPTF) discovery of an extraordinarily young SN Ia, \abc.
+The initial detection was made only $0.18\pm^{0.07}_{0.15}$~d after SN first light.
+In the $\sim$24 hr after discovery, \abc\ rose by $\sim$2 mag, following a near-linear rise in flux for $\sim$4 d.
+Assuming the photospheric velocity follows a $t^{-0.22}$ power law, the time of explosion for \abc\ is approximately equal to the time of first light.
+Strong \ion{C}{2} absorption is detected in the early spectra of \abc, before disappearing after $\sim$7~d.
+Unlike SN\,2011fe, the $(B-V)_0$ colors of \abc\ are blue and nearly constant in the days after explosion.
+We show that the fast, near-linear rise in flux for \abc\ cannot be explained by either SN shock breakout and the associated, subsequent cooling or the collision of the SN ejecta with a stellar companion.
+Instead, we argue that the early characteristics of \abc, including: (i) the rapid, near-linear rise, (ii) the non-evolving blue colors, and (iii) the strong lines from ionized carbon in the earliest spectra, are the result of either vigorous mixing of radioactive $^{56}$Ni in the SN ejecta, or the interaction of the ejecta with diffuse material, or a combination of the two.
 In the next few years, dozens of very young \textit{normal} SNe Ia will be discovered, and observations similar to those presented here will constrain the white dwarf explosion mechanism.

### 2017-07-31 doc/ms.tex
Update introduction to reflect the new conclusions regarding diffuse interaction

@@
   2013ApJ...778L..15Z,2015ApJ...799..106G,2016ApJ...826..144S,
-  2015ApJS..221...22I}). A possible exception is SN\,2012cg, 
+  2015ApJS..221...22I}). Possible exceptions include SN\,2012cg, 
 which exhibited excess blue emission in its early-phase light curve 
-\citet{2016ApJ...820...92M} (though see 
+(\citealt{2016ApJ...820...92M}; though see 
 \citealt{2016arXiv161007601S} for an interpretation that does not 
-invoke ejecta-companion interaction). 
+invoke ejecta-companion interaction), and SN\,2017cbv, which shows a clearly resolved ``bump'' in the early $UBg$ light curves \citep{2017arXiv170608990H}. 
 % With only $\sim 10\%$ of single-degenerate progenitors occupying the preferred binary geometry for us to see the collision
@@
 
+Interaction is not limited to systems with a non-degenerate companion, however, as WDs enshoruded in diffuse material following a binary merger or expanded due to a pre-explosion pulsation can give rise to ejecta-interaction signatures (see e.g., \citealt{2014MNRAS.441..532D}).
+Models of this scenario naturally produce \ion{C}{2} absorption that is comparable in strength to \ion{Si}{2} in the days after explosion \citep{2014MNRAS.441..532D}, as was observed in SN\;2013dy \citep{2013ApJ...778L..15Z} and SN\;2017cbv \citep{2017arXiv170608990H}.
+
 The vast majority of SNe Ia are observed 
 to be powered purely by the radioactive decay of $^{56}$Ni. 
-While the detection of SN shock cooling or ejecta-companion interaction is rare, the level of $^{56}$Ni mixing in the SN ejecta can fundamentally alter the appearance of the SN shortly after explosion.
+While the detection of SN shock cooling or ejecta interaction is rare, the level of $^{56}$Ni mixing in the SN ejecta can fundamentally alter the appearance of the SN shortly after explosion.
 SNe Ia experience a dark period after
@@
 duration of this dark period is set by how the newly synthesized 
-$^{56}$Ni is mixed and deposited into different layers of the ejecta.
-In the case of strong mixing, the dark period is short, or 
+$^{56}$Ni is mixed and deposited into different layers of the ejecta. In the case of strong mixing, the dark period is short, or 
 non-existent, as photons from $^{56}$Ni decay can reach the 
@@
 weak and the $^{56}$Ni is confined to the innermost layers of the 
-ejecta, the dark period can last for several days as the radioactive 
-energy diffuses to the photosphere. The early evolution of such SNe 
-results in redder colors and a more moderate rise in luminosity 
-\citep{2016ApJ...826...96P}.
+ejecta, the dark period can last for several days as the radioactive energy diffuses to the photosphere.
+The early evolution of such SNe results in redder colors and a more moderate rise in luminosity \citep{2016ApJ...826...96P}.
 Thus, the early light curves of even non-exotic type Ia SNe convey information about their progenitor systems by constraining the distribution of synthesized $^{56}$Ni, which in turn constrains the explosion mechanism.
 
-In this paper, we report observations of an extraordinarily young SN
-Ia, \abc, which was discovered by the intermediate Palomar
-Transient Factory (iPTF) on 2016 April $3.36$\footnote{All times in this
-  paper are in UTC.} at $\textrm{R.A.}=13^h34^m45.49^s$,
-$\textrm{Dec.}=+13^d51^m14.3^s$ (J2000) with a $g_\mathrm{PTF}$-band magnitude of
-$21.31\pm0.27$ \citep{2016ATel.8907....1M}. The
-transient is spatially coincident with a tidal tail of the galaxy
-NGC\,5221, which lies at a distance of $\sim$100\,Mpc.
+In this paper, we report observations of an extraordinarily young SN Ia, \abc, which was discovered by the intermediate Palomar Transient Factory (iPTF) on 2016 April $3.36$\footnote{All times in this paper are in UTC.} at $\textrm{R.A.}=13^h34^m45.49^s$, $\textrm{Dec.}=+13^d51^m14.3^s$ (J2000) with a $g_\mathrm{PTF}$-band magnitude of $21.31\pm0.27$ \citep{2016ATel.8907....1M}.
+The transient is spatially coincident with a tidal tail of the galaxy NGC\,5221, which lies at a distance of $\sim$100\,Mpc.
 \abc\ is not detected to a limit of $g=22.1$\,mag on April $2.42$, less than 1 d prior to discovery, and rose by $\sim$2 mag in the 24 hr following its initial detection.
@@
 campaign classified \abc\ as a normal SN Ia
-\citep{2016ATel.8909....1C}. Our observations and analysis provide multiple lines of evidence that the $^{56}$Ni produced by \abc\ was strongly mixed throughout the ejecta.
+\citep{2016ATel.8909....1C}.
+Our observations and analysis show that the early evolution of \abc\ exhibited several distinct properties relative to SN\,2011fe.
+We interpret those differences as arising from either strong $^{56}$Ni mixing or ejecta interaction with diffuse material, or a combination of the two.
 

### 2017-07-31 doc/ms.tex
Fix broken commas

@@
 Interaction is not limited to systems with a non-degenerate companion, however, as WDs enshoruded in diffuse material following a binary merger or expanded due to a pre-explosion pulsation can give rise to ejecta-interaction signatures (see e.g., \citealt{2014MNRAS.441..532D}).
-Models of this scenario naturally produce \ion{C}{2} absorption that is comparable in strength to \ion{Si}{2} in the days after explosion \citep{2014MNRAS.441..532D}, as was observed in SN\;2013dy \citep{2013ApJ...778L..15Z} and SN\;2017cbv \citep{2017arXiv170608990H}.
+Models of this scenario naturally produce \ion{C}{2} absorption that is comparable in strength to \ion{Si}{2} in the days after explosion \citep{2014MNRAS.441..532D}, as was observed in SN\,2013dy \citep{2013ApJ...778L..15Z} and SN\,2017cbv \citep{2017arXiv170608990H}.
 

### 2017-08-01 doc/ms.tex
Include updated figures in the manuscript
Update paper to include new figures as well as corresponding captions

@@
 
-\begin{figure*}[htb]
+\begin{figure}[htb]
   \centering
-  \includegraphics[width=0.95\textwidth]{logLC_with_colors.pdf}
-  \caption{Photometric evolution of \abc. \textit{Top}: The $g$-band
+  \includegraphics[width=0.48\textwidth]{logLC_with_colors.pdf}
+  \caption{The $g$-band
   light curve of \abc. Observations from different 
@@
   rest-frame d relative to the time of first light, $t_0$ (see 
-  \S\ref{sec:lc_fit}). Note that the horizontal axis is shown with a linear scale 
-  for $-2 \; \mathrm{d} \le t - t_0 \le 3 \; \mathrm{d}$ and a 
-  $\log$ scale for $t - t_0 > 3 \; \mathrm{d}$. The solid curve 
-  represents the best-fit model from SALT2 
-  (\S\ref{sec:classification}). The black ticks near the
+  \S\ref{sec:lc_fit}). Note that the horizontal axis is shown with 
+  a linear scale for $-2 \; \mathrm{d} \le t - t_0 \le 3 \; 
+  \mathrm{d}$ and a $\log$ scale for $t - t_0 > 3 \; \mathrm{d}$. 
+  The black ticks near the
   bottom of the panel show epochs of spectroscopic observations.
-  \textit{Bottom}: Color curves of \abc. Each color curve is 
-  represented with a different color, with each symbol corresponding 
-  to a different instrument, as detailed in the legend. Magnitude 
-  offsets applied to each color curve are also shown.
   }
   \label{fig:lightcurve}
-\end{figure*}
+\end{figure}
 
@@
   \centering
-  \includegraphics[width=1.0\textwidth]{spectra.pdf}
+  \includegraphics[width=0.8\textwidth]{spectra.pdf}
   \caption{Observed spectral sequence of \abc. The spectra are 
@@
 
-\begin{figure*}[!htb]
+\begin{figure}[!htb]
   \centering
-  \includegraphics[width=0.95\textwidth]{early_lc.pdf}
+  \includegraphics[width=0.48\textwidth]{early_lc.pdf}
   \caption{Best-fit power-law model to describe the early flux from 
@@
   \label{fig:early_lc_fit}
-\end{figure*}
+\end{figure}
 
@@
   \centering
-  \includegraphics[width=0.45\textwidth]{Chi2.pdf}
-  \includegraphics[width=0.45\textwidth]{VelocityPlot.pdf}
+  \includegraphics[width=0.48\textwidth]{Chi2.pdf}
+  \includegraphics[width=0.48\textwidth]{VelocityPlot.pdf}
   \caption{Constraints on $t_{exp}$ from fitting the velocity
     evolution of \ion{Si}{2}.
-    \textit{Left panel:} the dashed, solid
-    and dash-dotted curves show $\chi^2$ for fitting power laws with
+    \textit{Left panel:} the dashed, solid and dash-dotted curves 
+    show $\chi^2$ for fitting power laws with
     indices $-0.20$, $-0.22$ and $-0.24$, respectively. The blue
-    vertical line and the orange shaded region indicate $t_0$ and its
-    95\% confidence interval from Section
+    vertical line and the orange shaded region indicate $t_0$ and 
+    its 95\% confidence interval from Section
     \ref{sec:lc_fit}, respectively.
@@
      measured velocites of \ion{C}{2}\,$\lambda\lambda$6580, 7234 
-     are shown.}
+     are shown. \textit{Right inset}: Evolution of the 
+     pseudo-equivalent width of \ion{Si}{2}\,$\lambda$6355, and 
+     \ion{C}{2}\,$\lambda\lambda$6580, 7234 in the week following 
+     explosion.}
   \label{fig:velocity_t_exp}
@@
 evolution of the \ion{C}{2} lines to \ion{Si}{2} in the right panel 
-of Figure \ref{fig:velocity_t_exp} and the pEW evolution is
-shown in Figure \ref{fig:ew}. These measurements confirm the qualitative analysis from Figure~\ref{fig:carbon}: namely, the pEW of \ion{C}{2}\,$\lambda$6580 is comparable to that
+of Figure \ref{fig:velocity_t_exp}, which also shows the pEW evolution of these lines.
+These measurements confirm the qualitative analysis from Figure~\ref{fig:carbon}: namely, the pEW of \ion{C}{2}\,$\lambda$6580 is comparable to that
 of \ion{Si}{2}\,$\lambda$6355 at $t \approx -16 \; \mathrm{d}$ and 
@@
 around $t = -10$ d.
-
-\begin{figure}[]
-  \centering
-  \includegraphics[width=0.45\textwidth]{pEW.pdf}
-  \caption{Evolution of the pseudo-equivalent width of 
-  \ion{Si}{2}\,$\lambda$6355, and \ion{C}{2}\,$\lambda\lambda$6580, 
-  7234 in the week following explosion.}
-  \label{fig:ew}
-\end{figure}
 
@@
   \centering
-  \includegraphics[width=0.45\textwidth]{16abc_11fe_colors.pdf}
+  \includegraphics[width=0.48\textwidth]{16abc_11fe_colors.pdf}
   \caption{$(B - V)_0$ color evolution of \abc\ (shown as squares) 
     compared to SN\,2011fe (shown as stars). The $B$ and $V$ 
-    photometry are calibrated on the Vega system. The data for 
+    photometry are calibrated on the Vega system, and have been 
+    corrected for extinction. The data for 
     SN\,2011fe are from \citet{2016ApJ...820...67Z}.}
@@
   and the total line-of-site reddening ($E(B-V) = 0.078 \; 
-  \mathrm{mag}$; Ferretti et al.\ 2017, submitted).
-  \textit{Bottom}: $(g' - r')_0$ vs.\ time. The observed colors have 
-  been corrected for reddening.
+  \mathrm{mag}$; Ferretti et al.\ 2017, submitted). The orange 
+  solid line shows the model with the most $^{56}$Ni mixing 
+  shifted to an explosion time of $t_0 - 0.4 \; \mathrm{d}$. This 
+  model provides a good match to the data.
+  \textit{Bottom}: $(g' - r')_0$ vs.\ time. The observed colors 
+  have been corrected for reddening.
   }
@@
 
+\appendix
+
+\section{Photometric Light Curves}
+
+The full photometric light curves of \abc\ are shown in Figure~\ref{fig:ugly_LC}.
+
+\begin{figure}[ht]
+  \centering
+  \includegraphics[width=0.48\textwidth]{lightcurve.pdf}
+  \caption{UV, optical, and NIR light curves for \abc. 
+  \textit{Top}: $BVgri$ light curves from the P48, P60, and LCO-1m 
+  telescopes. The solid lines represent the best-fit model from 
+  SALT2 (see \ref{sec:classification}).
+  \textit{Bottom}: UV and NIR light curves from the \textit{Swift} 
+  and SPM-1.5m telescopes, respectively.
+  For both panels each light curve is represented with a different 
+  color, while the different symbols correspond to different 
+  instruments, as detailed in the legends. The legends also list 
+  offsets applied to each light curve. Photometry is shown in the 
+  AB mag system, with the exception of the $BV$ bands, which are 
+  shown in the Vega system. The photometry shown has not been 
+  corrected for line-of-sight extinction.
+  }
+  \label{fig:ugly_LC}
+\end{figure}
+
 \bibliographystyle{aasjournal}

### 2017-08-03 doc/ms.tex
Update the author list for the paper

@@
 
-% \author{A.~A.~Miller}
-% \affil{Center for Interdisciplinary Exploration and Research in Astrophysics (CIERA) and Department of Physics and Astronomy, Northwestern University, 2145 Sheridan Road, Evanston, IL 60208, USA}
-% \affil{The Adler Planetarium, Chicago, IL 60605, USA}
-%
-% \author[0000-0002-8036-8491]{Yi Cao}
-% \affil{eScience Institute and Astronomy Department, University of Washington,
-%   Seattle, WA 98195}
-% \affil{Google, Mountain View, CA 94043, USA}
-%
-% \author{B.~D.~Bue}
-% \affil{Jet Propulsion Laboratory, California Institute of Technology, Pasadena, CA 91109, USA}
-
-% \author{R.~Ferretti}
-% \affil{The Oskar Klein Centre, Department of Physics, AlbaNova, SE-106 91 Stockholm, Sweden}
-%
-% \author{A.~Goobar}
-% \affil{The Oskar Klein Centre, Department of Physics, AlbaNova, SE-106 91 Stockholm, Sweden}
-%
-% \author{G.~Hosseinzadeh}
-% \affil{Las Cumbres Observatory, Goleta, CA 93117, USA}
-% \affil{Physics Department, University of California, Santa Barbara, CA 93106, USA}
-%
-% \author{M.~M.~Kasliwal}
-% \affil{Division of Physics, Mathematics, and Astronomy, California Institute of Technology, Pasadena, CA 91125, USA}
-%
-% \author{R.~R.~Laher}
-% \affil{Infrared Processing and Analysis Center, California Institute of Technology, Pasadena, CA 91125, USA}
-%
-% \author{F.~J.~Masci}
-% \affil{Infrared Processing and Analysis Center, California Institute of Technology, Pasadena, CA 91125, USA}
-%
-% \author{P.~E.~Nugent}
-% \affil{Lawrence Berkeley National Laboratory, Berkeley, California 94720, USA}
-% \affil{University of California -- Berkeley, Berkeley, CA 94720, USA}
-%
-% \author{J.~Sollerman}
-% \affil{The Oskar Klein Centre, Department of Astronomy, AlbaNova, SE-106 91 Stockholm, Sweden}
-%
-% \author{F.~Taddia}
-% \affil{The Oskar Klein Centre, Department of Astronomy, AlbaNova, SE-106 91 Stockholm, Sweden}
-%
-% \author{S. R. Kulkarni}
-% \affil{Division of Physics, Mathematics, and Astronomy, California Institute of Technology, Pasadena, CA 91125, USA}
-%
-\author{The Alphabet Friends}
-\affil{the intermediate Palomar Transient Factory}
+\author[0000-0001-9515-478X]{A.~A.~Miller}
+\affil{Center for Interdisciplinary Exploration and Research in Astrophysics (CIERA) and Department of Physics and Astronomy, Northwestern University, 2145 Sheridan Road, Evanston, IL 60208, USA}
+\affil{The Adler Planetarium, Chicago, IL 60605, USA}
+
+\author[0000-0002-8036-8491]{Y.~Cao}
+\affil{eScience Institute and Astronomy Department, University of Washington,
+  Seattle, WA 98195}
+\affil{Google, Mountain View, CA 94043, USA}
+
+\author[0000-0001-6806-0673]{A.~L.~Piro}
+\affil{The Observatories of the Carnegie Institution for Science, 813 Santa Barbara Street, Pasadena, CA 91101, USA}
+
+\author{B.~D.~Bue}
+\affil{Jet Propulsion Laboratory, California Institute of Technology, Pasadena, CA 91109, USA}
+
+\author[0000-0003-1673-970X]{S.~B.~Cenko}
+\affil{Joint Space-Science Institute, University of Maryland, College Park, MD 20742, USA}
+\affil{NASA Goddard Space Flight Center, Mail Code 661, Greenbelt, MD 20771, USA}
+
+\author{R.~Ferretti}
+\affil{The Oskar Klein Centre, Department of Physics, AlbaNova, SE-106 91 Stockholm, Sweden}
+
+\author[0000-0003-2238-1572]{O.~D.~Fox}
+\affil{Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218, USA}
+
+\author{A.~Goobar}
+\affil{The Oskar Klein Centre, Department of Physics, AlbaNova, SE-106 91 Stockholm, Sweden}
+
+\author{G.~Hosseinzadeh}
+\affil{Las Cumbres Observatory, Goleta, CA 93117, USA}
+\affil{Physics Department, University of California, Santa Barbara, CA 93106, USA}
+\affil{LSSTC Data Science Fellow}
+
+\author{M.~M.~Kasliwal}
+\affil{Division of Physics, Mathematics, and Astronomy, California Institute of Technology, Pasadena, CA 91125, USA}
+
+\author{R.~R.~Laher}
+\affil{Infrared Processing and Analysis Center, California Institute of Technology, Pasadena, CA 91125, USA}
+
+\author{R.~Lunnan}
+\affil{Division of Physics, Mathematics, and Astronomy, California Institute of Technology, Pasadena, CA 91125, USA}
+
+\author{F.~J.~Masci}
+\affil{Infrared Processing and Analysis Center, California Institute of Technology, Pasadena, CA 91125, USA}
+
+\author{P.~E.~Nugent}
+\affil{Lawrence Berkeley National Laboratory, Berkeley, California 94720, USA}
+\affil{University of California -- Berkeley, Berkeley, CA 94720, USA}
+
+\author{J.~Sollerman}
+\affil{The Oskar Klein Centre, Department of Astronomy, AlbaNova, SE-106 91 Stockholm, Sweden}
+
+\author{F.~Taddia}
+\affil{The Oskar Klein Centre, Department of Astronomy, AlbaNova, SE-106 91 Stockholm, Sweden}
+
+\author{S. R. Kulkarni}
+\affil{Division of Physics, Mathematics, and Astronomy, California Institute of Technology, Pasadena, CA 91125, USA}
+
+% \author{The Alphabet Friends}
+% \affil{the intermediate Palomar Transient Factory}
 
@@
 \begin{itemize}
-    \item Extrapolation of the early light curve shows that the initial detection of \abc\ occurred only $\sim$0.2 d after the time of first light.
-
-    \item The early emission from \abc\ is powered solely by radioactive $^{56}$Ni decay.
-We find no evidence for detectable signatures of SN shock cooling or the collision of the SN ejecta with a non-degnerate binary companion.
-
-\item The velocity evolution of the SN ejecta shows that the time of explosion is approximately equal to the time of first light.
-This constitutes the first major piece of evidence that $^{56}$Ni is strongly mixed into the outer layers of the supernova ejecta.
+    \item Extrapolation of the early light curve shows that the initial detection of \abc\ occurred only 0.15 d after the time of first light.
+
+    \item We find no evidence for detectable signatures of SN shock cooling or the collision of the SN ejecta with a non-degnerate binary companion.
+
+    \item Assuming that $v_\mathrm{photosphere} \propto t^{-0.22}$, the time of explosion is approximately equal to the time of first light.
+A short ``dark period,'' as this implies, is likely the result of either strong $^{56}$Ni mixing or interaction of the SN ejecta with diffuse material.
 
     \item The strong and short-lived carbon features seen in the 
-earliest spectra of \abc\ can only be explained if there is incomplete burning during the explosion and there is a non-thermal 
-radiation source in the outermost layers of the ejecta to excite the ionized carbon.
-$^{56}$Ni decay is the likely source of the non-thermal emission, providing another piece of evidence for strong mixing in the ejecta of \abc.
+earliest spectra of \abc\ can only be explained if there is incomplete burning during the explosion.
+The pulsational delayed detonation models presented in \citet{2014MNRAS.441..532D} produce \ion{C}{2} absorption that is as strong as \ion{Si}{2} at very early phases.
+
+    \item In contrast to SN\,2011fe, $(B - V)_0$ is $\sim$0.5 mag bluer for \abc\ $\sim$2 d after first light.
+Furthermore, the $(B - V)_0$ colors of \abc\ show no evolution over our first $\sim$7 d  of observations.
 
@@
 There are elements of the PDD models from \citet{2014MNRAS.441..532D} that are attractive for explaining \abc, in particular, the strong \ion{C}{2} absorption seen at early times.
-In the future, it would be useful to investigate PDD models that incorporate strong $^{56}Ni$ mixing to see if they better replicate the observations of \abc.
+In the future, it would be useful to investigate more detailed PDD models that incorporate strong $^{56}$Ni mixing to see if they better replicate the observations of \abc.\footnote{Both \citet{2014MNRAS.441..532D} and \citet{2016ApJ...826...96P} consider models with strong mixing and interaction with diffuse material, but the simulations presented in those studies do not replicate all of the salient features of \abc.}
 

### 2017-08-03 doc/ms.tex
Update manuscript to reflect comments from Russ

@@
 
-In this paper, we report observations of an extraordinarily young SN Ia, \abc, which was discovered by the intermediate Palomar Transient Factory (iPTF) on 2016 April $3.36$\footnote{All times in this paper are in UTC.} at $\textrm{R.A.}=13^h34^m45.49^s$, $\textrm{Dec.}=+13^d51^m14.3^s$ (J2000) with a $g_\mathrm{PTF}$-band magnitude of $21.31\pm0.27$ \citep{2016ATel.8907....1M}.
+In this paper, we report observations of an extraordinarily young SN Ia, \abc, which was discovered by the intermediate Palomar Transient Factory (iPTF) on 2016 April $3.36$ UTC at $\textrm{R.A.}=13^h34^m45.49^s$, $\textrm{Dec.}=+13^d51^m14.3^s$ (J2000) with a $g_\mathrm{PTF}$-band magnitude of $21.31\pm0.27$ \citep{2016ATel.8907....1M}.
 The transient is spatially coincident with a tidal tail of the galaxy NGC\,5221, which lies at a distance of $\sim$100\,Mpc.
@@
 During the spring of 2016, the iPTF survey observed the field of \abc\ every night in either the $g_\mathrm{PTF}$- or 
-$R_\mathrm{PTF}$-band.\footnote{P48 observations of \abc\ is reported in the $g_\mathrm{PTF}$ and $R_\mathrm{PTF}$ filters throughout, which are similar to the SDSS $g'$ and $r'$ filters, respectively (see \citealt{2012PASP..124..854O} for details on PTF calibration).
+$R_\mathrm{PTF}$-band.\footnote{P48 observations of \abc\ are reported in the $g_\mathrm{PTF}$ and $R_\mathrm{PTF}$ filters throughout, which are similar to the SDSS $g'$ and $r'$ filters, respectively (see \citealt{2012PASP..124..854O} for details on PTF calibration).
 The correction from the $g_\mathrm{PTF}$ and $R_\mathrm{PTF}$ filters to SDSS $g'$ and $r'$ requires knowledge of the intrinsic source color (see Eqns.~1 and 2 in \citealt{2012PASP..124..854O}).
 The spectral diversity of SNe Ia in the days after explosion is poorly constrained, and as a result the color terms for \abc\ at these epochs are unknown.
-We proceed by assuming $g_\mathrm{PTF}$ and $R_\mathrm{PTF}$ calibration is on the AB system, which strictly speaking is incorrect, but this does not fundamentally alter any of our conclusions.}
+We proceed by assuming the $g_\mathrm{PTF}$ and $R_\mathrm{PTF}$ calibration is on the AB system, which strictly speaking is incorrect, but this does not fundamentally alter any of our conclusions.}
 Survey observations were conducted with the
 CFH12K camera \citep{2000SPIE.3965...58S} on the Palomar Observatory 
-48-inch telescope (P48). Images were processed by the IPAC image
+48-inch telescope (P48; \citealt{2009PASP..121.1395L}). Images were processed by the IPAC image
 subtraction and discovery pipeline which subtracts off the background

### 2017-08-03 doc/ms.tex
Update manuscript to reflect Nadia's comments

@@
 
+\author{N.~Blagorodnova}
+\affil{Division of Physics, Mathematics, and Astronomy, California Institute of Technology, Pasadena, CA 91125, USA}
+
 \author{B.~D.~Bue}
@@
 Here, we report the intermediate Palomar Transient Factory (iPTF) discovery of an extraordinarily young SN Ia, \abc.
-The initial detection was made only $0.18\pm^{0.07}_{0.15}$~d after SN first light.
+The initial detection was made only $0.15\pm^{0.07}_{0.15}$~d after SN first light.
 In the $\sim$24 hr after discovery, \abc\ rose by $\sim$2 mag, following a near-linear rise in flux for $\sim$4 d.
@@
 
-Using the Supernova Identification (SNID; \citealt{2007ApJ...666.1024B}) package, 
+Using the Supernova Identification (\texttt{SNID}; \citealt{2007ApJ...666.1024B}) package, 
 we find the low-resolution spectrum of \abc\ at $+18.8$ d is best matched by normal SNe Ia. Several characteristic features of a SN
@@
 \ion{Si}{2}\,$\lambda$6355 at $t \approx -16 \; \mathrm{d}$. The 
-strength of the \ion{C}{2} lines declines with time to the point 
-where they are no longer detectible more than 1 wk after explosion.
+strength of the \ion{C}{2} lines declines with time, and by $t \approx -10 \; \mathrm{d}$ \ion{C}{2} in no longer detectable.
 
@@
   the measured line centers, indicating the decline in the 
-  photosphere velocity in the $\sim$wk after explosion (note that 
+  photosphere velocity in the $\sim$7~d after explosion (note that 
   \ion{C}{2}\,$\lambda$7234 is not detected in the $-10.9$ d 
@@
 \begin{itemize}
-    \item Extrapolation of the early light curve shows that the initial detection of \abc\ occurred only 0.15 d after the time of first light.
+    \item Extrapolation of the early light curve shows that the initial detection of \abc\ occurred only $0.15\pm^{0.07}_{0.15}$~d after the time of first light.
 
@@
 This work makes use of observations from the LCO network.
+
+\facility{DCT, Gemini:Gillett, Hale, Keck:I, Keck:II, LCOGT, PO:1.2\,m, PO:1.5\,m, VLT, Swift, OANSPM:HJT}
+
+\software{\texttt{PTFIDE} \citep{Masci2017PASP}, \texttt{SALT2}, \texttt{SNID}, \texttt{UVOTSOURCE}}.
 

### 2017-08-03 doc/ms.tex
Update manuscript to reflect Ariel's comments

@@
 few days of the SN explosion. This UV pulse is best interpreted as a
-SN ejecta-companion collision. While such emission requires a 
+SN ejecta-companion collision (but see also \citealt{2016MNRAS.459.4428K,2017arXiv170603613N}). While such emission requires a 
 favorable geometric alignment and is only expected in $\lesssim$ 
@@
 
-Interaction is not limited to systems with a non-degenerate companion, however, as WDs enshoruded in diffuse material following a binary merger or expanded due to a pre-explosion pulsation can give rise to ejecta-interaction signatures (see e.g., \citealt{2014MNRAS.441..532D}).
+Interaction is not limited to systems with a non-degenerate companion, however, as WDs enshoruded in diffuse material following a binary merger (e.g., \citealt{2015MNRAS.447.2803L}) or expanded due to a pre-explosion pulsation can give rise to ejecta-interaction signatures (e.g., \citealt{2014MNRAS.441..532D}).
 Models of this scenario naturally produce \ion{C}{2} absorption that is comparable in strength to \ion{Si}{2} in the days after explosion \citep{2014MNRAS.441..532D}, as was observed in SN\,2013dy \citep{2013ApJ...778L..15Z} and SN\,2017cbv \citep{2017arXiv170608990H}.
@@
 While the equivalent width (EW) of these lines is quite large, implying a large amount of extinction (e.g., \citealt{2012MNRAS.426.1465P}), Ferretti et al.\ compare the evolution of \abc\ to the well-observed normal type Ia SN\,2011fe and find evidence for only a small amount of extinction.
-The empirical relation between the EW of \ion{Na}{1}\,D and extinction is known to have a large scatter, and thus, we instead adopt $E(B-V) = 0.05 \, \mathrm{mag}$ as the local extinction for \abc\ (Ferretti et al.\ 2017).
+The empirical relation between the EW of \ion{Na}{1}\,D and extinction is known to have a large scatter, and \citet{2013ApJ...779...38P} have shown that \ion{Na}{1}\,D absorption is a poor tracer of reddening in Type Ia SNe.
+Thus, we instead adopt $E(B-V) = 0.05 \, \mathrm{mag}$ as the local extinction for \abc\ (Ferretti et al.\ 2017).
 For the remainder of our analysis we therefore adopt a total, Galactic $+$ host galaxy, line-of-sight extinction of $E(B-V) = 0.0779 \, \mathrm{mag}$.
@@
   \texttt{sncosmo} Python module is available at
-  \url{https://sncosmo.readthedocs.io/en/v1.5.x/}.} This fit includes a SALT2 template \citep{2007A&A...466...11G} modified by the line-of-sight extinction
-curve \citep{1999PASP..111...63F} with $E(B-V)$ values from 
-\S\ref{sec:reddening} and $R_V=3.1$.
+  \url{https://sncosmo.readthedocs.io/en/v1.5.x/}.} This fit includes a \texttt{SALT2} template \citep{2007A&A...466...11G} that has been corrected for extinction using the \citep{1999PASP..111...63F} reddening law, $R_V=3.1$, and $E(B-V)$ values from \S\ref{sec:reddening}.
 
@@
 from type Ia SNe can be described as a power law in time, with 
-power-law index consistent with 2, i.e. $f \propto t^2$ (e.g., \citep{2006AJ....132.1707C, 2010ApJ...712..350H, 2011MNRAS.416.2607G}).
+power-law index consistent with 2, i.e.
+$f \propto t^2$ (e.g., \citealt{2006AJ....132.1707C, 2010ApJ...712..350H, 2011MNRAS.416.2607G}).\footnote{Many of the studies that find $f \propto t^2$ sample SNe Ia light curves at a phase that is closer to $T_{B,\mathrm{max}}$ than the initial observations of \abc\ discussed here.}
 
@@
 Thus, the near-linear rise in flux over the first few days after first light for \abc\ is unusual.
-To our knowledge this behavior has only been observed in 2 other SNe (2013dy, 2014J; \citealt{2013ApJ...778L..15Z,2014ApJ...783L..24Z}).
+To our knowledge this behavior has only been observed in 2 other SNe (2013dy, 2014J; \citealt{2013ApJ...778L..15Z,2014ApJ...783L..24Z,2015ApJ...799..106G}).
 Any model to explain the observations of \abc\ must be able to account for this unusual behavior in the days after first light.

### 2017-08-04 doc/ms.tex
Update manuscript to reflect RATIR observations

@@
 
-Photometric observations in the \textit{BVg'r'i'} filters were conducted by the Las Cambres Observatory (LCO) 1-m
+Photometric observations in the $BVg'r'i'$ filters were conducted by the Las Cambres Observatory (LCO) 1-m
 telescope network.  PSF photometry was measured on these images using
@@
 \citep{2008ApJS..175..297A}.
+
+The Reionization and Transients InfraRed (RATIR) camera on the autonomous 1.5\,m Harold L.
+Johnson Telescope at the Observatorio Astron\'{o}mico Nacional \citep{2012SPIE.8446E..10B} was used to observe \abc\ in the $r'i'ZYJH$ filters.
+The $r'i'Z$ filters are calibrated to SDSS, while the $JH$ filters are calibrated to the Two Micron All Sky Survey \citep{2006AJ....131.1163S}.
+For the $Y$-band calibration, we used an empirical relation in terms of the $J$ and $H$ magnitudes derived from the United Kingdom Infrared Telescope (UKIRT; \citealt{2007A&A...467..777C}) Wide Field Camera observations \citep{2009MNRAS.394..675H}.
 
@@
 
-The $g$-band discovery data and color curves of \abc\ are 
-illustrated in Figure~\ref{fig:lightcurve}.  For convenience, 
-magnitudes in 
-\textit{all} filters are in the AB system with a zero point of 
-$3631$\,Jy. As previously noted the color terms necessary to convert the $g_\mathrm{PTF}$ and $R_\mathrm{PTF}$ to the AB system are unknown and assumed to be zero.
+The $g$-band discovery and follow-up data of \abc\ are 
+illustrated in Figure~\ref{fig:lightcurve}.  The photometry is shown in the AB system with a zero point of 
+$3631$\,Jy. As previously noted the color terms necessary to convert $g_\mathrm{PTF}$ to the AB system are unknown and assumed to be zero.
 

### 2017-08-04 doc/ms.tex
Update the manuscript to reflect Brad's comments

@@
 
-\title{Let There Be Light: \\ Early Observations of the Normal Type Ia Supernova \abc\ \\Show No Evidence for a Dark Period}
+\title{Early Observations of the Type Ia Supernova \abc:\\
+XXX NEED SOMETHING CLEVER TO SAY HERE XXX}
 
@@
 Here, we report the intermediate Palomar Transient Factory (iPTF) discovery of an extraordinarily young SN Ia, \abc.
-The initial detection was made only $0.15\pm^{0.07}_{0.15}$~d after SN first light.
+The initial detection was made only $0.15\pm^{0.07}_{0.15}$~d after SN first light, the time when radiation from $^{56}$Ni decay has diffused to the SN photosphere.
 In the $\sim$24 hr after discovery, \abc\ rose by $\sim$2 mag, following a near-linear rise in flux for $\sim$4 d.
-Assuming the photospheric velocity follows a $t^{-0.22}$ power law, the time of explosion for \abc\ is approximately equal to the time of first light.
+% Assuming the photospheric velocity follows a $t^{-0.22}$ power law, the time of explosion for \abc\ is approximately equal to the time of first light.
 Strong \ion{C}{2} absorption is detected in the early spectra of \abc, before disappearing after $\sim$7~d.
@@
 %% keywords and the rules for their use.
-\keywords{methods: observational --- supernovae: individual (\abc)}
+\keywords{methods: observational --- supernovae: general --- supernovae: individual (\abc)}
 
@@
 Survey observations were conducted with the
-CFH12K camera \citep{2000SPIE.3965...58S} on the Palomar Observatory 
+CFH12K camera \citep{2008SPIE.7014E..4YR} on the Palomar Observatory 
 48-inch telescope (P48; \citealt{2009PASP..121.1395L}). Images were processed by the IPAC image
@@
 The $g$-band discovery and follow-up data of \abc\ are 
-illustrated in Figure~\ref{fig:lightcurve}.  The photometry is shown in the AB system with a zero point of 
-$3631$\,Jy. As previously noted the color terms necessary to convert $g_\mathrm{PTF}$ to the AB system are unknown and assumed to be zero.
+illustrated in Figure~\ref{fig:lightcurve}.
+The photometry is shown in the AB system.
+As previously noted the color terms necessary to convert $g_\mathrm{PTF}$ to the AB system are unknown and assumed to be zero.
 
@@
 
-\section{Reddening, Classification and Host Galaxy}
+\section{Host Galaxy, Reddening, and Classification}
 \label{sec:usual_staff}
+
+\subsection{Host Galaxy}
+\label{sec:host}
+
+The location of \abc\ is spatially coincident with a tidal tail of
+galaxy NGC\,5221. \citet{2007A&A...465...71T} derived a distance
+modulus of $35.0\pm0.4\,\textrm{mag}$ to NGC\,5221 from the 
+Tully-Fisher relation, which is consistent with what we later derive from the SN light curve (see \S\ref{sec:classification}).
+
+Separately, \citet{2015MNRAS.447.1531C} observe the 21-cm line in
+NGC\,5221 and measure a redshift of $0.0234$, which we adopt for the remaining analysis in this paper.
 
@@
 Thus, we instead adopt $E(B-V) = 0.05 \, \mathrm{mag}$ as the local extinction for \abc\ (Ferretti et al.\ 2017).
-For the remainder of our analysis we therefore adopt a total, Galactic $+$ host galaxy, line-of-sight extinction of $E(B-V) = 0.0779 \, \mathrm{mag}$.
+For the remainder of our analysis we therefore adopt a total, Galactic $+$ host galaxy, line-of-sight extinction of $E(B-V) = 0.08 \, \mathrm{mag}$.
 
@@
 
-Using the Supernova Identification (\texttt{SNID}; \citealt{2007ApJ...666.1024B}) package, 
+Using the SuperNova IDentification (\texttt{SNID}; \citealt{2007ApJ...666.1024B}) package, 
 we find the low-resolution spectrum of \abc\ at $+18.8$ d is best matched by normal SNe Ia. Several characteristic features of a SN
@@
 
-For convenience, in the following sections, we define the best-fit
+In the following sections, we define the best-fit
 value $\textrm{MJD}_{max}=57499.54$ as the time of $B$-band maximum, $T_{B_\mathrm{max}}$, which we also adopt as phase $t=0$.
-
-\subsection{Host Galaxy}
-\label{sec:host}
 
@@
 calibration \citep{2014A&A...568A..22B} of the Phillips relation
-\citep{1993ApJ...413L.105P} using $m^*_{B}$, $x_1$ and $c$ to derive 
-a distance modulus $\mu = 34.88 \pm 0.10 \,\textrm{mag}$ to the SN, 
-provided that the host galaxy of \abc\ has a stellar mass less than
-$10^{10}\sm$. We note that a more massive host galaxy would result 
-in a larger inferred distance modulus that is nevertheless 
-consistent within the uncertainties.
-
-The location of \abc\ is spatially coincident with a tidal tail of
-galaxy NGC\,5221. \citet{2007A&A...465...71T} derived a distance
-modulus of $35.0\pm0.4\,\textrm{mag}$ to NGC\,5221 from the 
-Tully-Fisher relation, which is consistent with that of \abc.
-
-Separately, \citet{2015MNRAS.447.1531C} observe the 21-cm line in
-NGC\,5221 and measure a redshift of $0.0234$, which we adopt for the remaining analysis in this paper.
+\citep{1993ApJ...413L.105P} using $m^*_{B}$, $x_1$ and $c$ to derive a distance modulus $\mu = 34.89 \pm 0.10 \,\textrm{mag}$ to the SN, provided that the host galaxy of \abc\ has a stellar mass less than $10^{10}\sm$.
+We note that a more massive host galaxy would result in a larger inferred distance modulus that is nevertheless consistent within the uncertainties.
+For the following analysis we adopt a distance modulus $\mu = 34.89 \pm 0.10 \,\textrm{mag}$ for \abc.
 
@@
 To determine $t_0$ and $\alpha$ we fit the earliest observations of \abc.
-Due to slight variations in the passbands, we fit the model to the relative flux measured in the $g_\mathrm{PTF}$-band, which is the only filter with observations prior to first light, a necessity for constraining $t_0$.
+Due to slight variations in the passbands, we fit the model only to the relative flux measured in the $g_\mathrm{PTF}$-band, which is the only filter with observations prior to first light, a necessity for constraining $t_0$.
 
@@
 Figure \ref{fig:velocity_t_exp}), we find that 
-$t_0\lessapprox t_{exp}$.
+$t_0\lesssim t_{exp}$.
 Since physical causality requires $t_{exp}<t_0$, we draw the qualitative
@@
 $g_\mathrm{PTF}$ brightness of an ejecta-companion collision at the 
-distance of \abc\ behind a total redenning of $E(B-V) = 0.0779 \, \mathrm{mag}$ using the parameterized equations in 
+distance of \abc\ behind a total redenning of $E(B-V) = 0.08 \, \mathrm{mag}$ using the parameterized equations in 
 \citet{2012ApJ...749...18B}.
@@
 This work makes use of observations from the LCO network.
+These results made use of the Discovery Channel Telescope at Lowell Observatory.
+Lowell is a private, non-profit institution dedicated to astrophysical research and public appreciation of astronomy and operates the DCT in partnership with Boston University, the University of Maryland, the University of Toledo, Northern Arizona University and Yale University.
+The upgrade of the DeVeny optical spectrograph has been funded by a generous grant from John and Ginger Giovale.
 
@@
 
-\software{\texttt{PTFIDE} \citep{Masci2017PASP}, \texttt{SALT2}, \texttt{SNID}, \texttt{UVOTSOURCE}}.
+\software{\texttt{PTFIDE} \citep{Masci2017PASP}, \texttt{SALT2}, \texttt{SNID}, \texttt{lcogtsnpipe}, \texttt{UVOTSOURCE}}.
 

### 2017-08-04 doc/ms.tex
Update acknowledgements for the paper

@@
   \tablecaption{Spectroscopic observations of \abc\ \label{tab:spec_obs_log}}
+  \tabletypesize{\footnotesize}
   \tablehead{
@@
   $57488.38$ & $-10.9$ & Keck-I & LRIS\tablenotemark{4} & $3055$--$10411$ \\
-  $57489.51$ & $ -9.8$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $3301$--$8999$ \\
-  $57490.40$ & $ -8.9$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $3301$--$9999$ \\
-  $57491.55$ & $ -7.8$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $3300$--$9998$ \\
+  $57489.51$ & $ -9.8$ & LCO-2m & FLOYDS\tablenotemark{5} & $3301$--$8999$ \\
+  $57490.40$ & $ -8.9$ & LCO-2m & FLOYDS\tablenotemark{5} & $3301$--$9999$ \\
+  $57491.55$ & $ -7.8$ & LCO-2m & FLOYDS\tablenotemark{5} & $3300$--$9998$ \\
   $57492.20$ & $ -7.2$ & VLT & X-shooter\tablenotemark{6} & $3300$--$24550$ \\
   $57494.00$ & $ -5.4$ & VLT & UVES\tablenotemark{7} & \\
-  $57503.32$ & $ +3.7$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $3300$--$9999$ \\
+  $57503.32$ & $ +3.7$ & LCO-2m & FLOYDS\tablenotemark{5} & $3300$--$9999$ \\
   $57506.00$ & $ +6.3$ & NOT & ALFOSC\tablenotemark{8} & $3602$--$8098$ \\
-  $57508.27$ & $ +8.5$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $3301$--$9999$ \\
+  $57508.27$ & $ +8.5$ & LCO-2m & FLOYDS\tablenotemark{5} & $3301$--$9999$ \\
   $57518.42$ & $+18.5$ & Keck-I & LRIS\tablenotemark{4} & $3071$--$10208$ \\
   $57520.03$ & $+20.0$ & VLT & X-shooter\tablenotemark{6} & $3300$--$24789$ \\
-  $57529.40$ & $+29.2$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $4000$--$8998$ \\
-  $57542.41$ & $+41.9$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $4000$--$8998$ \\
-  $57550.40$ & $+49.7$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $4001$--$8999$ \\
-  $57562.38$ & $+61.4$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $4800$--$9300$ \\
+  $57529.40$ & $+29.2$ & LCO-2m & FLOYDS\tablenotemark{5} & $4000$--$8998$ \\
+  $57542.41$ & $+41.9$ & LCO-2m & FLOYDS\tablenotemark{5} & $4000$--$8998$ \\
+  $57550.40$ & $+49.7$ & LCO-2m & FLOYDS\tablenotemark{5} & $4001$--$8999$ \\
+  $57562.38$ & $+61.4$ & LCO-2m & FLOYDS\tablenotemark{5} & $4800$--$9300$ \\
   \enddata
@@
 
-As our observations include especially early observations of \abc, there are upper limits $\sim$1 d prior to the discovery epoch, we model the early flux from \abc\ as a power law, but allow the power-lax index to vary, as opposed to fixing it at 2, to account for potential variations in the photospheric temperature during expansion:
+As our observations include especially early observations of \abc, there are upper limits $\sim$1 d prior to the discovery epoch, we model the early flux from \abc\ as a power law, but allow the power-law index to vary, as opposed to fixing it at 2, to account for potential variations in the photospheric temperature during expansion:
 \begin{equation}
@@
 Spectra obtained around or after $T_{B_\mathrm{max}}$ rarely show \ion{C}{2} as the photosphere has receded from the outermost ejecta, while pre-max spectra show evidence for \ion{C}{2} in $\sim$1/4 of all normal SNe Ia (e.g., \citealt{2011ApJ...732...30P,2012MNRAS.425.1917S,2011ApJ...743...27T}), but the signatures are typically weak.
-While we caution that the sample of normal SNe Ia with spectra taken within a few days of explosion is small, SN\,2013dy is the only other object known to have strong \ion{C}{2} features like \abc\ \citep{2013ApJ...778L..15Z}.
+While we caution that the sample of SNe Ia with spectra taken within a few days of explosion is small, SNe\,2013dy and 2017cbv are the only other objects known to have strong \ion{C}{2} features like \abc\ \citep{2013ApJ...778L..15Z,2017arXiv170608990H}.
 As a counterexample, SN\,2011fe only exhibited weak \ion{C}{2} features in its first spectra
@@
 Moving forward, more detailed models and simulations are needed to properly explain the observed diversity.
-No matter the correct explanation for the early behavior of SNe\,2013dy, 2017cbv, and \abc, the strong similarities between these events suggests they reflect a common physical origin.
+No matter the correct explanation for the early behavior of SNe\,2013dy, 2017cbv, and \abc, the strong similarities between these events suggests that they may reflect a common physical origin.
 
@@
 We thank M.~West for taking the first spectrum of \abc\ as a ToO on the DCT.
-We also thank the Gemini service observers for executing our ToO observations.
-Additionally, J.~Cohen, N.~Suzuki, V.~Ravi, R.~Walters, A.~Ho, and L.~Yan helped obtain data for this paper.
+We also thank P.~GuhaThakurta, E.~C.~Cunningham, K.~A.~Plant, H.~Jang, and J.~Torres for executing a Keck ToO as part of the UC/Caltech partnership, and also the Gemini service observers for executing our ToO observations.
+Additionally, J.~Cohen, N.~Suzuki, V.~Ravi, R.~Walters, A.~Ho, H.~Vedanthamand, K.~De, and L.~Yan helped obtain data for this paper.
 

### 2017-08-07 doc/ms.tex
Include comments from Jesper in the manuscript

@@
 radius of the exploding star
-\citep{2010ApJ...708..598P,2011ApJ...728...63R}. Comparing models of
-this cooling emission to the earliest-phase data of SN~2011fe,
-\citet{2012ApJ...744L..17B} concluded that the explosion came from a 
-star with $R_\ast \lesssim 0.02\sr$, where $\sr$ is the solar
+\citep{2010ApJ...708..598P,2011ApJ...728...63R}. Comparing models of this cooling emission to the earliest-phase data of SN~2011fe,
+\citet{2012ApJ...744L..17B} concluded that the explosion came from a star with $R_\ast \lesssim 0.02\sr$, where $\sr$ is the solar
 radius. Combining the radius constraint with the measured ejecta 
-mass \citeauthor{2012ApJ...744L..17B} derive the mean density of the 
-progenitor star, confirming that at least some type Ia SNe come from 
-compact and degenerate stars.
+mass, \citeauthor{2012ApJ...744L..17B} derive the mean density of the progenitor star, confirming that at least some Type Ia SNe come from compact and degenerate stars.
 
 Early phase observations of SNe Ia from a white dwarf (WD)$+$non-degenerate binary
-may detect excess emission, relative to most type Ia SNe, due to the 
+may detect excess emission, relative to most Type Ia SNe, due to the 
 collision of the SN ejecta with the non-degenerate companion 
@@
 $^{56}$Ni is mixed and deposited into different layers of the ejecta. In the case of strong mixing, the dark period is short, or 
-non-existent, as photons from $^{56}$Ni decay can reach the 
-photosphere rapidly. This also leads to blue optical colors and a 
-rapid initial rise in the observed light curve. If the mixing is 
-weak and the $^{56}$Ni is confined to the innermost layers of the 
-ejecta, the dark period can last for several days as the radioactive energy diffuses to the photosphere.
+non-existent, as $\gamma$-rays from the $^{56}$Ni decay diffuse to the photosphere rapidly.
+This also leads to blue optical colors and a rapid initial rise in the observed light curve.
+If the mixing is weak and the $^{56}$Ni is confined to the innermost layers of the ejecta, the dark period can last for several days as the radioactive energy diffuses to the photosphere.
 The early evolution of such SNe results in redder colors and a more moderate rise in luminosity \citep{2016ApJ...826...96P}.
-Thus, the early light curves of even non-exotic type Ia SNe convey information about their progenitor systems by constraining the distribution of synthesized $^{56}$Ni, which in turn constrains the explosion mechanism.
-
-In this paper, we report observations of an extraordinarily young SN Ia, \abc, which was discovered by the intermediate Palomar Transient Factory (iPTF) on 2016 April $3.36$ UTC at $\textrm{R.A.}=13^h34^m45.49^s$, $\textrm{Dec.}=+13^d51^m14.3^s$ (J2000) with a $g_\mathrm{PTF}$-band magnitude of $21.31\pm0.27$ \citep{2016ATel.8907....1M}.
+Thus, the early light curves of even non-exotic Type Ia SNe convey information about their progenitor systems by constraining the distribution of synthesized $^{56}$Ni, which in turn constrains the explosion mechanism.\footnote{While examing a sample of Type Ib/c SNe, \citet{2015A&A...574A..60T} found that a significant dark phase is not prevalent for core-collapse SNe.}
+
+\citet{2017arXiv170603613N} recently demonstrated that disambiguating between these different scenarios via optical photometry alone is challenging.
+\citeauthor{2017arXiv170603613N} further show that estimates of the time of explosion, which are critical for comparing models with observations, are often incorrect by as many as $\sim$2 d using common methods in the literature.
+While analytical models suggest that early spectra can be used to infer the time of explosion (e.g., \citealt{2014ApJ...784...85P}), more detailed simulations show that the photospheric evolution is not so simple \citep{2016ApJ...826...96P}.
+Reconciling these issues requires both a larger sample of early SNe Ia observations and more detailed models that produce synthetic light curves and spectra.
+
+In this paper, we report observations of an extraordinarily young SN Ia, \abc, which was discovered by the intermediate Palomar Transient Factory (iPTF) on 2016 April $3.36$ UTC at $\textrm{R.A.}=13^h34^m45.49^s$, $\textrm{Dec.}=+13\degr51\arcmin14\farcs3$ (J2000) with a $g_\mathrm{PTF}$-band magnitude of $21.31\pm0.27$ \citep{2016ATel.8907....1M}.
 The transient is spatially coincident with a tidal tail of the galaxy NGC\,5221, which lies at a distance of $\sim$100\,Mpc.
@@
   telescopes are shown with different symbols. Time is measured in 
-  rest-frame d relative to the time of first light, $t_0$ (see 
+  rest-frame days relative to the time of first light, $t_0$ (see 
   \S\ref{sec:lc_fit}). Note that the horizontal axis is shown with 
@@
 60-inch telescope (P60).
-We utilized the Fremling Automated Pipeline \citep{2016A&A...593A..68F} to subtract galaxy light from the SEDm images using archival Sloan Digital Sky Survey (SDSS) images as a reference.
+We utilized the Fremling Automated Pipeline (\texttt{FPipe}; \citealt{2016A&A...593A..68F}) to subtract galaxy light from the SEDm images using archival Sloan Digital Sky Survey (SDSS) images as a reference.
 This pipeline then performed forced-PSF photometry at the location of \abc, which is calibrated to the SDSS catalog \citep{2014ApJS..211...17A}.
 
-Photometric observations in the $BVg'r'i'$ filters were conducted by the Las Cambres Observatory (LCO) 1-m
+Photometric observations in the $BVg'r'i'$ filters were conducted by the Las Cumbres Observatory (LCO) 1-m
 telescope network.  PSF photometry was measured on these images using
@@
 couple of days after explosion to two months after $B$-band maximum. 
-An observing log is listed in Table \ref{tab:spec_obs_log}. The spectra were reduced using standard routines in \texttt{IDL}/\texttt{Python}. The optical
+An observing log is listed in Table \ref{tab:spec_obs_log}. The spectra were reduced using standard routines in \texttt{IDL}/\texttt{Python}/\texttt{Matlab}. The optical
 spectral evolution of \abc\ is illustrated in Figure
@@
 The high-resolution spectra presented in Ferretti et al.\ (2017) show multiple absorption components for both the \ion{Ca}{2}\,H$+$K and \ion{Na}{1}\,D doublets.
-While the equivalent width (EW) of these lines is quite large, implying a large amount of extinction (e.g., \citealt{2012MNRAS.426.1465P}), Ferretti et al.\ compare the evolution of \abc\ to the well-observed normal type Ia SN\,2011fe and find evidence for only a small amount of extinction.
+While the equivalent width (EW) of these lines is quite large, implying a large amount of extinction (e.g., \citealt{2012MNRAS.426.1465P}), Ferretti et al.\ compare the evolution of \abc\ to the well-observed normal Type Ia SN\,2011fe and find evidence for only a small amount of extinction.
 The empirical relation between the EW of \ion{Na}{1}\,D and extinction is known to have a large scatter, and \citet{2013ApJ...779...38P} have shown that \ion{Na}{1}\,D absorption is a poor tracer of reddening in Type Ia SNe.
@@
   \texttt{sncosmo} Python module is available at
-  \url{https://sncosmo.readthedocs.io/en/v1.5.x/}.} This fit includes a \texttt{SALT2} template \citep{2007A&A...466...11G} that has been corrected for extinction using the \citep{1999PASP..111...63F} reddening law, $R_V=3.1$, and $E(B-V)$ values from \S\ref{sec:reddening}.
+  \url{https://sncosmo.readthedocs.io/en/v1.5.x/}.} This fit includes a \texttt{SALT2} template \citep{2007A&A...466...11G} that has been corrected for extinction using the \citep{1999PASP..111...63F} reddening law, $R_V=3.1$, and $E(B-V) = 0.08 \; \mathrm{mag}$.
 
@@
 extrapolating early-phase light curves to determine when the 
-SN is equal to 0. Assuming an ideal expanding fireball with 
+SN flux is equal to 0. Assuming an ideal expanding fireball with 
 constant temperature, \citet{1982ApJ...253..785A} derives that $f 
@@
 early times, multiple studies have found that the early emission 
-from type Ia SNe can be described as a power law in time, with 
+from Type Ia SNe can be described as a power law in time, with 
 power-law index consistent with 2, i.e.
@@
     \begin{array}{ll}
-      = 0,\ \textrm{when}\ t<t_0 \\
+      = 0,\ \textrm{when}\ t \le t_0 \\
       \propto (t-t_0)^{\alpha},\ \textrm{when}\ t>t_0
@@
 best-fit model we obtain $\alpha=0.98 \pm ^{0.16}_{0.14}$ and $t_0=-17.91 \pm ^{0.07}_{0.15}$ d, where the uncertainties represent the marginalized 95\% confidence intervals. Our first
-detection of \abc\ occurred $\sim{0.15}\,\textrm{d}$ after 
+detection of \abc\ occurred $\sim$${0.15}\,\textrm{d}$ after 
 the SN first light. 
-Figure~\ref{fig:early_lc_fit} additionally shows $g'$-bands observations from P60 and LCO, where we have normalized the flux assuming that the $g$ magnitudes from each instrument have the same zero-point.
+% Figure~\ref{fig:early_lc_fit} additionally shows $g'$-bands observations from P60 and LCO, where we have normalized the flux assuming that the $g$ magnitudes from each instrument have the same zero-point.
 This assumption is incorrect (see \S\ref{sec:obs}), and, as expected, the residuals show a systematic offset between the $g_\mathrm{PTF}$-band and the $g'$-band.
-Nevertheless, if we ignore this systematic and fit all of the $g$-band observations simultaneous we obtain marginalized best-fit parameters that are consistent within the uncertainties with the $g_\mathrm{PTF}$-only values above.
-In the analysis that follows, the precise values of the best-fit parameters is not important.
-The critical finding here is that $\alpha \approx 1$ and $t_0 \approx -18 \, \mathrm{d}$.
+Nevertheless, if we ignore this systematic and fit all of the $g$-band observations simultaneously we obtain marginalized best-fit parameters that are consistent within the uncertainties with the $g_\mathrm{PTF}$-only values above.
+In the analysis that follows, the precise values of the best-fit parameters are not important. The critical finding here is that $\alpha \approx 1$ and $t_0 \approx -18 \, \mathrm{d}$.
+
+As previously noted, a precise determination of the rise time, $t_\mathrm{rise}$, of SNe Ia is challenging as there may be a ``dark phase'' following explosion \citep{2014ApJ...784...85P}.
+Nevertheless, to be consistent with previous studies (e.g., \citealt{2011MNRAS.416.2607G}), here we find $t_rise = 17.91\pm _{0.07}^{0.15}$ d based on our fit for $t_0$.
+We caution that this measurement may be underestimated due to the uncertain time of explosion.
 
@@
   dashed contours represent the $68\%$ and $99.7\%$ confidence 
-  levels.
+  levels. \amiller{Update figure to remove other photometry}
   }
@@
 
-% Starting around $t=-15\,\textrm{d}$, the $g$-band light curve
-% deviates from the above best-fit model and
-% rises significantly faster, indicating a
-% change in the power-law index $\alpha$. In fact, between $t=-14\,\mathrm{d}$ and $t=-8\,\mathrm{d}$ the light curve is well fit by a power law of index $1.40$. In other words, the entire light curve
-% before $t=-8$\,days can be approximated by a broken power-law model
-% (e.g.,
-% \citealt{2016arXiv161202097Z,
-%   2016arXiv161202725Z}).
-
-As previously noted, the early emission from most SNe Ia can be explained via a $f \propto t^2$ model, including SNe with extremely early observations like \abc, such as SN\,2011fe \citep{2011Natur.480..344N}.
-Thus, the near-linear rise in flux over the first few days after first light for \abc\ is unusual.
+Simulations presented in \citet{2017arXiv170603613N} show that the flux from SNe Ia explosion models does not evolve as a power law in time.
+Despite this non-power-law evolution, \citet{2017arXiv170603613N} show that $f \propto t^\alpha$ models produce good formal fits to simulated observations.
+The $f \propto t^\alpha$ fits to the \citeauthor{2017arXiv170603613N} models result in glaring errors to the estimated explosion times.
+Despite the caution advised in \citet{2017arXiv170603613N}, we proceed with the power-law fits from above for several reasons.
+(1) Our primary aim with the fit is to characterize $\alpha$ for \abc\ compared to SN\,2011fe (see below).
+(2) The errors in the estimated explosion times from \citeauthor{2017arXiv170603613N} increase the later the first observation of the SN is obtained.
+\citeauthor{2017arXiv170603613N} only present fits to observations that start $>$2~d after explosion, whereas the discovery epoch for \abc\ is likely much earlier than that (see \S\ref{sec:early_vel}).
+(3) We do not use the fits to estimate the time of explosion, $t_0$ instead is an estimate of the time of first light.
+(4) Pre-discovery upper limits, which are not included in \citeauthor{2017arXiv170603613N}, provide additional strong constraints on the time of first light.
+Finally, (5) \citet{2017arXiv170603613N} find that models with strong $^{56}$Ni mixing do follow a power-law evolution, and we explore, and argue in favor of, this possibility for \abc\ (see \S\ref{sec:Ni_mixing}).
+
+As previously noted, the early emission from SN\,2011fe is well fit by a $f \propto t^2$ model \citep{2011Natur.480..344N}.
+Thus, the near-linear rise in flux over the first few days after first light for \abc\ is distinct compared to SN\,2011fe.
 To our knowledge this behavior has only been observed in 2 other SNe (2013dy, 2014J; \citealt{2013ApJ...778L..15Z,2014ApJ...783L..24Z,2015ApJ...799..106G}).
-Any model to explain the observations of \abc\ must be able to account for this unusual behavior in the days after first light.
+Any model to explain the observations of \abc\ must account for this near-linear rise in the days after first light.
 
@@
 
-As previously noted, $t_0$ does not correspond to the time of 
-explosion, $t_\mathrm{exp}$, for type Ia SNe as the SN may 
+As previously noted, $t_0$ may not correspond to the time of 
+explosion, $t_\mathrm{exp}$, for Type Ia SNe as the SN may 
 experience a dark phase following shock breakout before radioactive 
@@
 spectra between 5,900 and 6,500\,\AA\ (rest-frame) as the combination 
-of two gaussian kernels plus a linear baseline, which
+of two Gaussian kernels plus a linear baseline, which
 accounts for \ion{Si}{2}, \ion{C}{2} and the
@@
     velocities (blue circles) and the best-fit power-law model
-     with an index of $-0.22$ (dashed line). Additionally the 
+     with an index of $-0.22$ (dashed line). Additionally, the 
      measured velocites of \ion{C}{2}\,$\lambda\lambda$6580, 7234 
-     are shown. \textit{Right inset}: Evolution of the 
+     are shown. Typical uncertainties are smaller than the size of 
+     the points. \textit{Right inset}: Evolution of the 
      pseudo-equivalent width of \ion{Si}{2}\,$\lambda$6355, and 
@@
   early spectra of \abc. The raw spectra are shown in orange, while 
-  the solid blue lines show the best-fit models including gaussian 
+  the solid blue lines show the best-fit models including Gaussian 
   components for each line and a linear component for the continuum 
@@
 
-The detection of \ion{C}{2} in SNe Ia spectra is relatively rare
+The detection of \ion{C}{2} in SN Ia spectra is relatively rare
 as it requires both unburned carbon, which is likely only present in the outermost layers of the ejecta, and non-local thermal equilibrium effects in order to excite the ionized carbon (e.g., \citealt{2007ApJ...654L..53T}).
@@
 2010ApJ...708..598P}. From this analysis, we constrain the \abc\ 
-progenitor radius to be $<1\sr$. Our observations of \abc\ cannot 
-place tight constraints on the size of SNe Ia progenitors. Indeed, 
+progenitor radius to be $<1\,\sr$. Our observations of \abc\ cannot 
+place tight constraints on the size of SN Ia progenitors. Indeed, 
 for a typical WD radius, such as that inferred for SN\,2011fe 
@@
 2014ApJ...784...85P}), the expected emission from shock cooling is 
-$\sim$2 mag fainter than the P48 $g_\mathrm{PTF}$ detection limit. 
+$\sim$2 mag fainter than the P48 $g_\mathrm{PTF}$ detection limit at this distance. 
 Thus, we conclude that shock cooling does not contribute to the 
@@
 
-Here we consider a model that has not, as of yet, been discussed in the context of \abc.
 To model SN\,2011fe, \citet{2014MNRAS.441..532D} recently examined pulsational delayed-detonation (PDD) models as an explanation for some SNe Ia.
@@
 Nevertheless, we conclude that one, or both, of these scenarios, which feature qualitatively similar predictions, is the most likely explanation for \abc.
+Indeed, it may be the case that the typical sequence of photometric and spectroscopic observations of young SNe Ia can never distinguish between these two possibilities \citep{2017arXiv170603613N}.
 
@@
   (\S\ref{sec:host})
-  and the total line-of-site reddening ($E(B-V) = 0.078 \; 
+  and the total line-of-sight reddening ($E(B-V) = 0.08 \; 
   \mathrm{mag}$; Ferretti et al.\ 2017, submitted). The orange 
@@
 
-In \S\ref{sec:lc_energy} we compared our early observations of \abc\ to SN\,2011fe, which has the most comprehensive observations of the young SNe Ia sample.
+In \S\ref{sec:first_light} we compared our early observations of \abc\ to SN\,2011fe, which has the most comprehensive observations of the young SNe Ia sample.
 Given its normal spectroscopic and photometric evolution, SN\,2011fe has been adopted as a standard for the early evolution of SNe Ia in many studies.
@@
 There are elements of the PDD models from \citet{2014MNRAS.441..532D} that are attractive for explaining \abc, in particular, the strong \ion{C}{2} absorption seen at early times.
-In the future, it would be useful to investigate more detailed PDD models that incorporate strong $^{56}$Ni mixing to see if they better replicate the observations of \abc.\footnote{Both \citet{2014MNRAS.441..532D} and \citet{2016ApJ...826...96P} consider models with strong mixing and interaction with diffuse material, but the simulations presented in those studies do not replicate all of the salient features of \abc.}
+In the future, it would be useful to investigate more detailed PDD models that incorporate strong $^{56}$Ni mixing to see if they better replicate the observations of \abc\ as it is otherwise difficult to distinguish between these two scenarios \citep{2017arXiv170603613N}.\footnote{Both \citet{2014MNRAS.441..532D} and \citet{2016ApJ...826...96P} consider models with strong mixing and interaction with diffuse material, but the simulations presented in those studies do not replicate all of the salient features of \abc.}
 
@@
 Despite these limitations, this study of \abc\ shows that the early detection of SNe Ia can constrain the explosion physics by probing the amount of mixing in the SN ejecta.
-Moving forward, a large sample of such objects will enable strict constraints on the proposed explosion mechanisms for type Ia SNe.
+Moving forward, a large sample of such objects will enable strict constraints on the proposed explosion mechanisms for Type Ia SNe.
 
@@
 
-\software{\texttt{PTFIDE} \citep{Masci2017PASP}, \texttt{SALT2}, \texttt{SNID}, \texttt{lcogtsnpipe}, \texttt{UVOTSOURCE}}.
+\software{\texttt{PTFIDE} \citep{Masci2017PASP}, \texttt{FPipe}, \texttt{SALT2}, \texttt{SNID}, \texttt{lcogtsnpipe}, \texttt{UVOTSOURCE}}.
 

### 2017-08-07 doc/ms.tex
Include Ori's changes for the RATIR text.

@@
 The Reionization and Transients InfraRed (RATIR) camera on the autonomous 1.5\,m Harold L.
-Johnson Telescope at the Observatorio Astron\'{o}mico Nacional \citep{2012SPIE.8446E..10B} was used to observe \abc\ in the $r'i'ZYJH$ filters.
-The $r'i'Z$ filters are calibrated to SDSS, while the $JH$ filters are calibrated to the Two Micron All Sky Survey \citep{2006AJ....131.1163S}.
+Johnson Telescope at the Observatorio Astron\'{o}mico Nacional \citep{2012SPIE.8446E..10B,2012SPIE.8444E..5LW} was used to observe \abc\ in the $r'i'ZYJH$ filters.
+Given the lack of a cold shutter in RATIR’s design, IR dark frames are not available.
+Laboratory testing, however, confirms that the dark current is negligible in both IR detectors \citep{2012SPIE.8453E..1OF}.
+
+The RATIR data were reduced, coadded, and analysed using standard CCD and IR processing techniques in \texttt{IDL}, \texttt{Python}, \texttt{SExtractor} \citep{1996A&AS..117..393B}, and \texttt{SWarp}.
+Aperture photometry is obtained following the methods described in \citet{2014AJ....148....2L}.
+The $r'i'Z$ filters are calibrated to SDSS \citep{2012ApJS..203...21A}, while the $JH$ filters are calibrated to the Two Micron All Sky Survey \citep{2006AJ....131.1163S}.
 For the $Y$-band calibration, we used an empirical relation in terms of the $J$ and $H$ magnitudes derived from the United Kingdom Infrared Telescope (UKIRT; \citealt{2007A&A...467..777C}) Wide Field Camera observations \citep{2009MNRAS.394..675H}.
@@
 
-\software{\texttt{PTFIDE} \citep{Masci2017PASP}, \texttt{FPipe}, \texttt{SALT2}, \texttt{SNID}, \texttt{lcogtsnpipe}, \texttt{UVOTSOURCE}}.
+\software{\texttt{PTFIDE} \citep{2017PASP..129a4002M}, \texttt{FPipe}, \texttt{SALT2}, \texttt{SNID}, \texttt{lcogtsnpipe}, \texttt{UVOTSOURCE}}.
 

### 2017-08-07 doc/ms.tex
Include bolometric calculation from Suhail in the paper.

@@
 \affil{NASA Goddard Space Flight Center, Mail Code 661, Greenbelt, MD 20771, USA}
+
+\author{S.~Dhawan}
+\affil{European Southern Observatory, Karl-Schwarzschild-Strasse 2, D-85748 Garching bei München, Germany}
+\affil{Excellence Cluster Universe, Technische Universität München, Boltzmannstrasse 2, D-85748, Garching, Germany}
+\affil{Physik Department, Technische Universität München, James-Franck-Strasse 1, D-85748 Garching bei München, Germany}
+\affil{The Oskar Klein Centre, Department of Physics, AlbaNova, SE-106 91 Stockholm, Sweden}
 
@@
 
+We measure the (pseudo)bolometric luminosity of \abc\ at peak via trapezoidal integration of the reddening-corrected flux from the UV, optical, and NIR (UVOIR) filters.
+The light curves in the individual filters are interpolated so that $L_\mathrm{bol}$ is evaluated at common epochs in each filter.
+From this integration, we determine that the maximum UVOIR luminosity of \abc\ is $L_\mathrm{max} = 1.2 \pm 0.1 \times 10^{43} \; \mathrm{erg \; s}^{-1}$.
+This value is consistent with the sample of normal SNe Ia studied in  \citet{2016A&A...588A..84D}, a sample which excludes low-luminosity SNe.
+
 After establishing \abc\ as a normal SN Ia, we use the latest

### 2017-08-08 doc/ms.tex
Final proof read edits to make sure new draft flows from beginning to end.

--- 2017-08-07 doc/ms.tex
@@
 
+\author{S.~Dhawan}
+\affil{European Southern Observatory, Karl-Schwarzschild-Strasse 2, D-85748 Garching bei München, Germany}
+\affil{Excellence Cluster Universe, Technische Universität München, Boltzmannstrasse 2, D-85748, Garching, Germany}
+\affil{Physik Department, Technische Universität München, James-Franck-Strasse 1, D-85748 Garching bei München, Germany}
+\affil{The Oskar Klein Centre, Department of Physics, AlbaNova, SE-106 91 Stockholm, Sweden}
+
 \author{R.~Ferretti}
@@
 Here, we report the intermediate Palomar Transient Factory (iPTF) discovery of an extraordinarily young SN Ia, \abc.
-The initial detection was made only $0.15\pm^{0.07}_{0.15}$~d after SN first light, the time when radiation from $^{56}$Ni decay has diffused to the SN photosphere.
+By fitting a power law to our early light curve, we infer that first light for the SN, that is when appreciable heating from $^{56}$Ni decay has first diffused to the photosphere, only occurred $0.15\pm_{0.07}^{0.15}$~d before our first detection.
 In the $\sim$24 hr after discovery, \abc\ rose by $\sim$2 mag, following a near-linear rise in flux for $\sim$4 d.
@@
 Unlike SN\,2011fe, the $(B-V)_0$ colors of \abc\ are blue and nearly constant in the days after explosion.
-We show that the fast, near-linear rise in flux for \abc\ cannot be explained by either SN shock breakout and the associated, subsequent cooling or the collision of the SN ejecta with a stellar companion.
-Instead, we argue that the early characteristics of \abc, including: (i) the rapid, near-linear rise, (ii) the non-evolving blue colors, and (iii) the strong lines from ionized carbon in the earliest spectra, are the result of either vigorous mixing of radioactive $^{56}$Ni in the SN ejecta, or the interaction of the ejecta with diffuse material, or a combination of the two.
+We show that our early observations of \abc\ cannot be explained by either SN shock breakout and the associated, subsequent cooling, or the SN ejecta colliding with a stellar companion.
+Instead, we argue that the early characteristics of \abc, including: (i) the rapid, near-linear rise, (ii) the non-evolving blue colors, and (iii) the strong absorption from ionized carbon, are the result of either vigorous mixing of radioactive $^{56}$Ni in the SN ejecta, or ejecta interaction with diffuse material, or a combination of the two.
 In the next few years, dozens of very young \textit{normal} SNe Ia will be discovered, and observations similar to those presented here will constrain the white dwarf explosion mechanism.
@@
 \citealt{2014ARA&A..52..107M}). Extremely detailed
-observations in the hours to days after explosion are one of the most promising avenues to further
-constrain this problem.
+observations in the hours to days after explosion provide a promising avenue to further constrain this problem.
 
@@
 \citep{2010ApJ...708..598P,2011ApJ...728...63R}. Comparing models of this cooling emission to the earliest-phase data of SN~2011fe,
-\citet{2012ApJ...744L..17B} concluded that the explosion came from a star with $R_\ast \lesssim 0.02\sr$, where $\sr$ is the solar
+\citet{2012ApJ...744L..17B} concluded that the explosion came from a star with $R_\ast \lesssim 0.02\;\sr$, where $\sr$ is the solar
 radius. Combining the radius constraint with the measured ejecta 
@@
 emission was first detected in iPTF\,14atg  \citep{2015Natur.521..328C}, a low-velocity SN Ia with a significant and declining ultraviolet (UV) pulse detected within a
-few days of the SN explosion. This UV pulse is best interpreted as a
-SN ejecta-companion collision (but see also \citealt{2016MNRAS.459.4428K,2017arXiv170603613N}). While such emission requires a 
-favorable geometric alignment and is only expected in $\lesssim$ 
-10\% of SNe Ia \citep{2010ApJ...708.1025K}, many studies have 
+few days of the SN explosion. This UV pulse is best interpreted as a SN ejecta-companion collision (but see also \citealt{2016MNRAS.459.4428K,2017arXiv170603613N}). While such emission requires a 
+favorable geometric alignment and is only expected in $\lesssim$10\% of SNe Ia \citep{2010ApJ...708.1025K}, many studies have 
 searched for signatures of an ejecta-companion interaction, 
@@
 While the detection of SN shock cooling or ejecta interaction is rare, the level of $^{56}$Ni mixing in the SN ejecta can fundamentally alter the appearance of the SN shortly after explosion.
-SNe Ia experience a dark period after
+SNe Ia experience a dark phase after
 the SN shock breakout but before radioactive energy  
 diffuses into the photosphere \citep{2014ApJ...784...85P}. The 
-duration of this dark period is set by how the newly synthesized 
-$^{56}$Ni is mixed and deposited into different layers of the ejecta. In the case of strong mixing, the dark period is short, or 
-non-existent, as $\gamma$-rays from the $^{56}$Ni decay diffuse to the photosphere rapidly.
+duration of this dark phase is set by how the newly synthesized 
+$^{56}$Ni is mixed and deposited into different layers of the ejecta. In the case of strong mixing, the dark phase is short, or 
+non-existent, as $\gamma$-rays from the radioactive $^{56}$Ni diffuse to the photosphere rapidly.
 This also leads to blue optical colors and a rapid initial rise in the observed light curve.
-If the mixing is weak and the $^{56}$Ni is confined to the innermost layers of the ejecta, the dark period can last for several days as the radioactive energy diffuses to the photosphere.
+If the mixing is weak and the $^{56}$Ni is confined to the innermost layers of the ejecta, the dark phase can last for several days as the radioactive energy diffuses to the photosphere.
 The early evolution of such SNe results in redder colors and a more moderate rise in luminosity \citep{2016ApJ...826...96P}.
-Thus, the early light curves of even non-exotic Type Ia SNe convey information about their progenitor systems by constraining the distribution of synthesized $^{56}$Ni, which in turn constrains the explosion mechanism.\footnote{While examing a sample of Type Ib/c SNe, \citet{2015A&A...574A..60T} found that a significant dark phase is not prevalent for core-collapse SNe.}
+Thus, the early light curves of even non-exotic Type Ia SNe convey information about their progenitor systems by constraining the distribution of synthesized $^{56}$Ni, which in turn constrains the explosion mechanism.\footnote{\citet{2015A&A...574A..60T} found that a significant dark phase is not prevalent for a sample of Type Ib/c SNe.}
 
@@
 
-During the spring of 2016, the iPTF survey observed the field of \abc\ every night in either the $g_\mathrm{PTF}$- or 
-$R_\mathrm{PTF}$-band.\footnote{P48 observations of \abc\ are reported in the $g_\mathrm{PTF}$ and $R_\mathrm{PTF}$ filters throughout, which are similar to the SDSS $g'$ and $r'$ filters, respectively (see \citealt{2012PASP..124..854O} for details on PTF calibration).
+During the spring of 2016, the iPTF survey observed the field of \abc\ every night during dark time in either the $g_\mathrm{PTF}$ or 
+$R_\mathrm{PTF}$ band.\footnote{P48 observations of \abc\ are reported in the $g_\mathrm{PTF}$ and $R_\mathrm{PTF}$ filters throughout, which are similar to the SDSS $g'$ and Mould-$R$ filters, respectively (see \citealt{2012PASP..124..854O} for details on PTF calibration).
 The correction from the $g_\mathrm{PTF}$ and $R_\mathrm{PTF}$ filters to SDSS $g'$ and $r'$ requires knowledge of the intrinsic source color (see Eqns.~1 and 2 in \citealt{2012PASP..124..854O}).
@@
 Johnson Telescope at the Observatorio Astron\'{o}mico Nacional \citep{2012SPIE.8446E..10B,2012SPIE.8444E..5LW} was used to observe \abc\ in the $r'i'ZYJH$ filters.
-Given the lack of a cold shutter in RATIR’s design, IR dark frames are not available.
+By design, RATIR lacks a cold shutter, which means IR dark frames are not available.
 Laboratory testing, however, confirms that the dark current is negligible in both IR detectors \citep{2012SPIE.8453E..1OF}.
 
-The RATIR data were reduced, coadded, and analysed using standard CCD and IR processing techniques in \texttt{IDL}, \texttt{Python}, \texttt{SExtractor} \citep{1996A&AS..117..393B}, and \texttt{SWarp}.
+The RATIR data were reduced, coadded, and analyzed using standard CCD and IR processing techniques in \texttt{IDL}, \texttt{Python}, \texttt{SExtractor} \citep{1996A&AS..117..393B}, and \texttt{SWarp}.
 Aperture photometry is obtained following the methods described in \citet{2014AJ....148....2L}.
-The $r'i'Z$ filters are calibrated to SDSS \citep{2012ApJS..203...21A}, while the $JH$ filters are calibrated to the Two Micron All Sky Survey \citep{2006AJ....131.1163S}.
+The $r'i'Z$ filters are calibrated to SDSS \citep{2014ApJS..211...17A}, while the $JH$ filters are calibrated to the Two Micron All Sky Survey \citep{2006AJ....131.1163S}.
 For the $Y$-band calibration, we used an empirical relation in terms of the $J$ and $H$ magnitudes derived from the United Kingdom Infrared Telescope (UKIRT; \citealt{2007A&A...467..777C}) Wide Field Camera observations \citep{2009MNRAS.394..675H}.
@@
 Telescope (UVOT) images via the usual procedures in 
-\texttt{HEASoft}, including corrections for the coincident loss and 
+\texttt{HEASoft}, including corrections for coincidence loss and 
 aperture loss. The image counts
@@
 of telescopes and instruments over multiple epochs spanning from a
-couple of days after explosion to two months after $B$-band maximum. 
+couple of days after discovery to two months after $B$-band maximum. 
 An observing log is listed in Table \ref{tab:spec_obs_log}. The spectra were reduced using standard routines in \texttt{IDL}/\texttt{Python}/\texttt{Matlab}. The optical
@@
   \centering
-  \includegraphics[width=0.8\textwidth]{spectra.pdf}
+  \includegraphics[width=0.78\textwidth]{spectra.pdf}
   \caption{Observed spectral sequence of \abc. The spectra are 
@@
 Thus, we instead adopt $E(B-V) = 0.05 \, \mathrm{mag}$ as the local extinction for \abc\ (Ferretti et al.\ 2017).
-For the remainder of our analysis we therefore adopt a total, Galactic $+$ host galaxy, line-of-sight extinction of $E(B-V) = 0.08 \, \mathrm{mag}$.
+Thus, we assume a total, Galactic $+$ host galaxy, line-of-sight extinction of $E(B-V) = 0.08 \, \mathrm{mag}$ for the remainder of our analysis.
 
@@
 To determine the brightness and time of $B$-band maximum for 
-\abc, we fit the P60 light curves with the \texttt{sncosmo} software package.\footnote{The
-  \texttt{sncosmo} Python module is available at
-  \url{https://sncosmo.readthedocs.io/en/v1.5.x/}.} This fit includes a \texttt{SALT2} template \citep{2007A&A...466...11G} that has been corrected for extinction using the \citep{1999PASP..111...63F} reddening law, $R_V=3.1$, and $E(B-V) = 0.08 \; \mathrm{mag}$.
+\abc, we fit the P60 light curves with the \texttt{sncosmo} software package.\footnote{\texttt{sncosmo} is available at
+  \url{https://sncosmo.readthedocs.io}.} This fit includes a \texttt{SALT2} template \citep{2007A&A...466...11G} that has been corrected for extinction using the \citep{1999PASP..111...63F} reddening law, $R_V=3.1$, and $E(B-V) = 0.08 \; \mathrm{mag}$.
 
 We determine the time of rest-frame \textit{B}-band maximum to be 
- $\textrm{MJD}_{max}=57499.54\pm0.23$, the coefficient
+ $\textrm{MJD}_\mathrm{max}=57499.54\pm0.23$, the coefficient
 of the zeroth principle component $x_0 = 0.0086 \pm 0.0003$, the
@@
 0.04 \,\textrm{mag}$ in the SN rest frame.
-
-In the following sections, we define the best-fit
-value $\textrm{MJD}_{max}=57499.54$ as the time of $B$-band maximum, $T_{B_\mathrm{max}}$, which we also adopt as phase $t=0$.
+In the following sections, we define the best-fit value $\textrm{MJD}_\mathrm{max}=57499.54$ as the time of $B$-band maximum, $T_{B_\mathrm{max}}$, which we also define as phase $t=0$.
+
+We measure the (pseudo)bolometric luminosity, $L_{UVOIR}$, of \abc\ at peak via trapezoidal integration of the reddening-corrected flux from the UV, optical, and NIR (UVOIR) filters.
+The light curves in the individual filters are interpolated so that $L_{UVOIR}$ is evaluated at common epochs in each filter.
+From this integration, we determine that \abc\ reaches a maximum luminosity $L_\mathrm{max} = 1.2 \pm 0.1 \times 10^{43} \; \mathrm{erg \; s}^{-1}$.
+This value is consistent with the normal SNe Ia studied in  \citet{2016A&A...588A..84D}, a sample which excludes low-luminosity SNe.
 
@@
 calibration \citep{2014A&A...568A..22B} of the Phillips relation
-\citep{1993ApJ...413L.105P} using $m^*_{B}$, $x_1$ and $c$ to derive a distance modulus $\mu = 34.89 \pm 0.10 \,\textrm{mag}$ to the SN, provided that the host galaxy of \abc\ has a stellar mass less than $10^{10}\sm$.
-We note that a more massive host galaxy would result in a larger inferred distance modulus that is nevertheless consistent within the uncertainties.
+\citep{1993ApJ...413L.105P} using $m^*_{B}$, $x_1$ and $c$ to derive a distance modulus $\mu = 34.89 \pm 0.10 \,\textrm{mag}$ to the SN, provided that the host galaxy of \abc\ has a stellar mass $< 10^{10}\sm$.
+A more massive host galaxy would result in a larger inferred distance modulus that is nevertheless consistent within the uncertainties.
 For the following analysis we adopt a distance modulus $\mu = 34.89 \pm 0.10 \,\textrm{mag}$ for \abc.
@@
 
-The time of first light for SNe is usually estimated by 
+The time of first light, defined as the moment when appreciable heating from $^{56}$Ni decay has first diffused to the photosphere, for SNe is usually estimated by 
 extrapolating early-phase light curves to determine when the 
-SN flux is equal to 0. Assuming an ideal expanding fireball with 
+SN flux is equal to 0. Assuming an ideal, expanding fireball with 
 constant temperature, \citet{1982ApJ...253..785A} derives that $f 
@@
 \end{equation}
-where $t_0$ is the time of first light, $\alpha$ is the power-law index, and $t$ is measured in the rest-frame of the SN.
+where $t_0$ is the time of first light, $\alpha$ is the power-law index, and $t$ is measured in the SN rest-frame.
 To determine $t_0$ and $\alpha$ we fit the earliest observations of \abc.
@@
 
-To determine the best fit parameters, we search a large grid over $t_0$, $\alpha$
+To determine the best fit parameters, we search a large grid over $t_0$, $\alpha$,
 and the proportionality constant, and minimize $\chi^2$. 
@@
 linearly between
-$t=-18\,\textrm{d}$ and $t=-14\,\textrm{d}$. Figure \ref{fig:early_lc_fit} shows the best-fit result and
+$t=-18\,\textrm{d}$ and $t=-15\,\textrm{d}$. Figure \ref{fig:early_lc_fit} shows the best-fit result and
 the joint marginal distribution of $t_0$ and $\alpha$. From the
@@
 As previously noted, a precise determination of the rise time, $t_\mathrm{rise}$, of SNe Ia is challenging as there may be a ``dark phase'' following explosion \citep{2014ApJ...784...85P}.
-Nevertheless, to be consistent with previous studies (e.g., \citealt{2011MNRAS.416.2607G}), here we find $t_rise = 17.91\pm _{0.07}^{0.15}$ d based on our fit for $t_0$.
+Nevertheless, to be consistent with previous studies (e.g., \citealt{2011MNRAS.416.2607G}), here we find $t_\mathrm{rise} = 17.91\pm _{0.07}^{0.15}$ d based on our fit for $t_0$.
 We caution that this measurement may be underestimated due to the uncertain time of explosion.
@@
   \caption{Best-fit power-law model to describe the early flux from 
-  \abc\ in the $g_\mathrm{PTF}$-band. The model flux, adopting 
+  \abc\ in the $g_\mathrm{PTF}$ band. The model flux, adopting 
   best-fit parameters $\alpha=0.98$ and $t_0=-17.94\,\textrm{d}$, 
@@
 
-As previously noted, the early emission from SN\,2011fe is well fit by a $f \propto t^2$ model \citep{2011Natur.480..344N}.
+Unlike \abc, the early emission from SN\,2011fe is well fit by a $f \propto t^2$ model \citep{2011Natur.480..344N}.
 Thus, the near-linear rise in flux over the first few days after first light for \abc\ is distinct compared to SN\,2011fe.
@@
 
-As previously noted, $t_0$ may not correspond to the time of 
-explosion, $t_\mathrm{exp}$, for Type Ia SNe as the SN may 
-experience a dark phase following shock breakout before radioactive 
-energy can diffuse to the photosphere. \citet{2014ApJ...784...85P} 
-instead suggest that measurements of the photospheric velocity be 
-used to determine $t_\mathrm{exp}$ given that the ejecta begin 
-expanding from the moment of explosion.  Assuming a
-constant opacity in the ejecta, \citeauthor{2014ApJ...784...85P} 
+The potential dark phase following shock breakout, where SNe Ia are not luminous because the energy deposition from radioactive decay has not had sufficient time to diffuse to the photosphere, means that the explosion time $t_\mathrm{exp} \ne t_0$ in some cases.
+\citet{2014ApJ...784...85P} suggest that measurements of the photospheric velocity be used to determine $t_\mathrm{exp}$ given that the ejecta begin expanding from the moment of explosion.
+Assuming a constant opacity in the ejecta, \citeauthor{2014ApJ...784...85P}
 find that the photospheric velocity evolves as
@@
 Nevertheless, we proceed on the assumption that \abc\ experienced strong $^{56}$Ni mixing, corresponding to the models that are best approximated as a $t^{-0.22}$ power law.
-We do this in part to compare with previous studies, though we caution that our derived value for $t_{exp}$ is subject to uncertainties related to ejecta mixing.
+We do this in part to compare with previous studies, though we caution that the inferred value of $t_{exp}$ is subject to uncertainties related to ejecta mixing.
 
@@
      pseudo-equivalent width of \ion{Si}{2}\,$\lambda$6355, and 
-     \ion{C}{2}\,$\lambda\lambda$6580, 7234 in the week following 
-     explosion.}
+     \ion{C}{2}\,$\lambda\lambda$6580, 7234 in the $\sim$7~d    
+     following explosion.}
   \label{fig:velocity_t_exp}
@@
 We fit the measured velocities of \ion{Si}{2}\,$\lambda$6355 to the
-$v\propto(t-t_{exp})^{-0.22}$ model by minimizing the $\chi^2$ value and find the best-fit explosion time relative to $T_{B,\mathrm{max}}$ in the SN rest frame to be $t_{exp} = -17.45 \pm ^{0.14}_{0.16}\;\textrm{d}$, where the uncertainties represent the 95\% confidence interval (Figure \ref{fig:velocity_t_exp}).
+$v\propto(t-t_{exp})^{-0.22}$ model by minimizing the $\chi^2$ value and find the best-fit explosion time relative to $T_{B,\mathrm{max}}$ in the SN rest frame to be $t_{exp} = -17.45 \pm ^{0.14}_{0.16}\,\textrm{d}$, where the uncertainties represent the 95\% confidence interval (Figure \ref{fig:velocity_t_exp}).
 Following the analysis in \citet{2014ApJ...784...85P}, we additionally alter the power-law index to $-0.20$ and $-0.24$ to examine the sensitivety of the result on the assumed power-law index.
@@
 $t_0\lesssim t_{exp}$.
-Since physical causality requires $t_{exp}<t_0$, we draw the qualitative
+Since physical causality requires $t_{exp} \le t_0$, we draw the qualitative
 conclusion that $t_0\simeq t_{exp}$, which is consistent to within the uncertainties.
@@
 % comparison, SN2011fe has $t_0=-17.7$ d \citep{2013A&A...554A..27P}
-% with a preceding dark period of $\sim 1$ day
+% with a preceding dark phase of $\sim 1$ day
 % \citep{2014ApJ...784...85P}. ASASSN-14lp has $t_0=-16.94$ days with a
-% preceding dark period of about acouple of days
+% preceding dark phase of about acouple of days
 % \citep{2016ApJ...826..144S}. This comparison suggests that the actual
@@
 spectra we see that \ion{C}{2}\,$\lambda$6580 is as strong as 
-\ion{Si}{2}\,$\lambda$6355 at $t \approx -16 \; \mathrm{d}$. The 
-strength of the \ion{C}{2} lines declines with time, and by $t \approx -10 \; \mathrm{d}$ \ion{C}{2} in no longer detectable.
+\ion{Si}{2}\,$\lambda$6355 at $t \approx -15 \; \mathrm{d}$. The 
+strength of the \ion{C}{2} lines declines with time, and by $t \approx -10 \; \mathrm{d}$ \ion{C}{2} is no longer detectable.
 
@@
   spectrum). The phase of each spectrum relative to 
-  $T_{B,\mathrm{max}}$ is shown to the right of each spectrum.
+  $T_{B,\mathrm{max}}$ is labeled.
   }
@@
 As a counterexample, SN\,2011fe only exhibited weak \ion{C}{2} features in its first spectra
-\citep{2012ApJ...752L..26P}. Thus, models of \abc\ must explain the anomalously strong \ion{C}{2} absorption observed shortly after explosion.
+\citep{2012ApJ...752L..26P}. Thus, models of \abc\ must explain the strong \ion{C}{2} absorption observed shortly after explosion.
 
@@
 In Figure~\ref{fig:B-Vcolors} we compare the $(B - V)_0$ color evolution of \abc\ and SN\,2011fe, where the observations of SN\,2011fe are taken from \citet{2016ApJ...820...67Z}.
-For both SN the colors have been corrected for the total inferred redenning along the line of sight.
-Interestingly, \abc\ has a nearly flat color evolution up to 10 d before $T_{B,\mathrm{max}}$, while SN\,2011fe exhibits red colors initially before eventually becoming as blue as \abc.
+For both SNe the colors have been corrected for the total inferred reddening along the line of sight.
+Interestingly, \abc\ has a nearly flat color evolution up to 10 d before $T_{B,\mathrm{max}}$, while SN\,2011fe exhibits red colors initially before evolving to the blue.
 
@@
 While there are many factors that contribute to the early optical colors of SNe Ia (see \S\ref{sec:lc_energy} below), early blue colors are often interpreted as a hallmark of interaction between the SN ejecta and a binary companion.
-Nevertheless, it is interesting to note that despite the blue optical colors the UV $-$ optical colors of \abc, SN\,2012cg, and SN\,2017cbv are significantly redder at these early epochs than the UV $-$ optical colors of iPTF\,14atg \citep{2015Natur.521..328C}, the most likely candidate for an ejecta-companion interaction SN.
+Nevertheless, it is interesting to note that despite the blue optical colors, the $\mathrm{UV} - \mathrm{optical}$ colors of \abc, SN\,2012cg, and SN\,2017cbv are significantly redder at these early epochs than the $\mathrm{UV} - \mathrm{optical}$ colors of iPTF\,14atg \citep{2015Natur.521..328C}, the most likely candidate for SN ejecta-companion interaction.
 
@@
 
-Relative to the nearby, normal SN\,2011fe, we have identified several unusual properties in the early observations of \abc, including: (i) a near-linear photometric rise in the days after explosion, (ii) the lack of a dark phase typical of most SNe Ia, and (iii) the presence of strong \ion{C}{2} absorption.
+Relative to the nearby, normal SN\,2011fe, we have identified several distinct characteristics of the early evolution of \abc, including: (i) a near-linear photometric rise, (ii) a qualitatively short dark phase, assuming $v_\mathrm{ph} \propto t^{-0.22}$, (iii) the presence of strong \ion{C}{2} absorption, and (iv) blue and non-evolving $(B - V)_0$ color in the week after explosion.
 While most SNe Ia are powered purely by radioactive decay, the observed radiation shortly after explosion can also include contributions
-from SN shock cooling or the collision of the SN ejecta with a non-degenerate companion. Here we consider those scenarios as a possible explanation for the early behavior of \abc.
+from SN shock cooling or the collision of the SN ejecta with a non-degenerate companion or diffuse material. Here we consider those scenarios as a possible explanation for the early behavior of \abc.
 
@@
 $g_\mathrm{PTF}$ brightness of an ejecta-companion collision at the 
-distance of \abc\ behind a total redenning of $E(B-V) = 0.08 \, \mathrm{mag}$ using the parameterized equations in 
+distance of \abc\ behind a total reddening of $E(B-V) = 0.08 \, \mathrm{mag}$ using the parameterized equations in 
 \citet{2012ApJ...749...18B}.
@@
   models have been adjusted to account for the distance and 
-  redenning towards \abc. Each 
+  reddening towards \abc. Each 
   model features a different companion semi-major axis, $a$, and 
-  time of explosion, $t_\mathrm{exp}$, as labeled in the figure 
+  time of explosion, $t_\mathrm{exp}$, as labeled in the 
   legend. While models with $a \gtrsim 10^{13} \, \mathrm{cm}$ can 
@@
   fail to replicate the $\sim$2 mag rise in the $\sim$24 hr after 
-  explosion. Thus, SN ejecta-companion interaction models fail
-  to uniquely explain the early flux from \abc.
+  explosion.
   }
@@
 Briefly, PDD models differ from ``standard'' delayed detonation (DD) models in that the initial deflagration causes the WD to expand resulting in the release of some unbound material.
-As the bound material contracts, eventually a subsequent detonation occurs.\footnote{\citet{2014MNRAS.441..532D} note that the deflagration and detonation in their PDD models are artificially triggered.} An important consequence of this sequence for PDD models is that they naturally produce material that avoids burning, unlike DD models that typically leave no unburnt material.
-This enables the presence of significantly more carbon in the outer layers of the SN ejecta \citep{2014MNRAS.441..532D}.
+As the bound material contracts, eventually a subsequent detonation occurs.\footnote{\citet{2014MNRAS.441..532D} note that the deflagration and detonation in their PDD models are artificially triggered.} An important consequence of this progression for PDD models is that they naturally produce material that avoids burning, unlike DD models that typically leave no unburnt material.
+This results in significantly more carbon in the outer layers of the SN ejecta \citep{2014MNRAS.441..532D}.
 
@@
 
-\subsection{Strong $^{56}Ni$ Mixing as an Explanation for \abc}
+\subsection{Strong $^{56}Ni$ Mixing in the SN Ejecta}
 \label{sec:Ni_mixing}
@@
 Having examined other possibilities we now consider whether the unusual properties of \abc\ can be explained simply by invoking strong mixing in the SN ejecta.
-As previously mentioned, strong mixing can lead to a short dark phase.
+Strong mixing can lead to a short dark phase.
 Here we additionally examine whether strong mixing can explain the rapid, near-linear rise in the light curve.
@@
 The \citeauthor{2016ApJ...826...96P} models employ a piston driven explosion to explode a single WD progenitor model.
-As the piston explosion does not result in any nucleosynthesis, the distribution of $^{56}$Ni in the ejecta must be prescribed by hand, which enables the study of the effects of mixing on the resulting SN emission.
+As the piston explosion does not result in any nucleosynthesis, the distribution of $^{56}$Ni in the ejecta must be prescribed by hand, which enables a study of the effects of mixing on the resulting SN emission.
 Each model employs a fixed $0.5\,\sm$ of $^{56}$Ni that has been distributed throughout the ejecta via boxcar averaging (see their Figure~1).
@@
 The fast rise and blue color of \abc\ are qualitatively consistent with the strong mixing models from \citet{2016ApJ...826...96P}, as shown in Figure~\ref{fig:Ni56LC}.
-In fact, if we adopt $t_\mathrm{exp} = t_0 - 0.45 \, \mathrm{d}$, we find that the model with the strongest mixing (orange line in Figure~\ref{fig:Ni56LC} provides an excellent match to the $g$-band observations.
+In fact, if we adopt $t_\mathrm{exp} = t_0 - 0.4 \, \mathrm{d}$, we find that the model with the strongest mixing (orange line in Figure~\ref{fig:Ni56LC}) provides an excellent match to the $g$-band observations.
 
@@
 
-Both the PDD models and ejecta-mixing models show discrepancies with some of the early observations of \abc.
+Both the PDD models and ejecta-mixing models show discrepancies with some early observations of \abc.
 Nevertheless, we conclude that one, or both, of these scenarios, which feature qualitatively similar predictions, is the most likely explanation for \abc.
@@
 A challenge for this model, similar to \abc\ (see \S\ref{sec:companion}), is that it significantly overpredicts the UV brightness of the SN compared to what is observed.
-Indeed, in the case of SNe\,2012cg, 2017cbv, and \abc\ the UV - optical colors are significantly redder than those observed in iPTF\,14atg.
+Indeed, in the case of SNe\,2012cg, 2017cbv, and \abc\ the $\mathrm{UV} - \mathrm{optical}$ colors are significantly redder than those observed in iPTF\,14atg.
 It is argued in \citet{2017arXiv170608990H} that several model assumptions, including: (i) ideal blackbody emission, (ii) a constant opacity, (iii) a simple power-law density profile for the ejecta, and (iv) spherical symmetry, may be incorrect, which could reconcile the discrepancy with the UV observations.
@@
 \begin{itemize}
-    \item Extrapolation of the early light curve shows that the initial detection of \abc\ occurred only $0.15\pm^{0.07}_{0.15}$~d after the time of first light.
+    \item Extrapolation of the early light curve shows that the initial detection of \abc\ occurred only $0.15\pm_{0.07}^{0.15}$~d after the time of first light, $t_0$.
 
@@
 
-    \item Assuming that $v_\mathrm{photosphere} \propto t^{-0.22}$, the time of explosion is approximately equal to the time of first light.
-A short ``dark period,'' as this implies, is likely the result of either strong $^{56}$Ni mixing or interaction of the SN ejecta with diffuse material.
+    \item Assuming that $v_\mathrm{ph} \propto t^{-0.22}$, then $t_\mathrm{exp} \approx t_0$.
+A short dark phase, as this implies, is likely the result of either strong $^{56}$Ni mixing or interaction of the SN ejecta with diffuse material.
 
     \item The strong and short-lived carbon features seen in the 
-earliest spectra of \abc\ can only be explained if there is incomplete burning during the explosion.
+earliest spectra of \abc\ can only be explained if there is incomplete burning.
 The pulsational delayed detonation models presented in \citet{2014MNRAS.441..532D} produce \ion{C}{2} absorption that is as strong as \ion{Si}{2} at very early phases.
 
-    \item In contrast to SN\,2011fe, $(B - V)_0$ is $\sim$0.5 mag bluer for \abc\ $\sim$2 d after first light.
-Furthermore, the $(B - V)_0$ colors of \abc\ show no evolution over our first $\sim$7 d  of observations.
+    \item In contrast to SN\,2011fe, $(B - V)_0$ is $\sim$0.5 mag bluer for \abc\ $\sim$2 d after $t_0$.
+Furthermore, the $(B - V)_0$ colors of \abc\ show no evolution over the first $\sim$7 d  of observations.
 
@@
 There are elements of the PDD models from \citet{2014MNRAS.441..532D} that are attractive for explaining \abc, in particular, the strong \ion{C}{2} absorption seen at early times.
-In the future, it would be useful to investigate more detailed PDD models that incorporate strong $^{56}$Ni mixing to see if they better replicate the observations of \abc\ as it is otherwise difficult to distinguish between these two scenarios \citep{2017arXiv170603613N}.\footnote{Both \citet{2014MNRAS.441..532D} and \citet{2016ApJ...826...96P} consider models with strong mixing and interaction with diffuse material, but the simulations presented in those studies do not replicate all of the salient features of \abc.}
+In the future, it would be useful to investigate more detailed PDD models that incorporate strong $^{56}$Ni mixing to see if they better replicate the observations of \abc\ as it is otherwise difficult to distinguish between these two scenarios \citep{2017arXiv170603613N}.\footnote{Both \citet{2014MNRAS.441..532D} and \citet{2016ApJ...826...96P} consider models with strong mixing \textit{and} interaction, but those studies do not replicate each of the salient features of \abc.}
 
@@
 a result of the explosion mechanism.
-Wide-field, high-cadence surveys, such as the Zwicky Transient Facility \citep{2016PASP..128h4501B} and ATLAS \citep{2011PASP..123...58T,2013RSPTA.37120269T}, will discover a large number of very young supernovae over the next few years.
-These surveys will generate large observational samples that probe SNe in the hours after explosion.
+Wide-field, high-cadence surveys, such as the Zwicky Transient Facility \citep{2016PASP..128h4501B} and ATLAS \citep{2011PASP..123...58T,2013RSPTA.37120269T}, will discover a large number of very young SNe over the next few years, allowing us to extend our studies beyond single objects.
 While the sample of extremely young SNe Ia will grow by more than an order of magnitude, the detection of shock breakout cooling and ejecta-companion interaction will prove challenging.
@@
 Furthermore, only $\sim$10\% of single-degenerate progenitors are expected to give rise to detectable emission following the collision of the SN ejecta with the binary companion \citep{2010ApJ...708.1025K}.
-Despite these limitations, this study of \abc\ shows that the early detection of SNe Ia can constrain the explosion physics by probing the amount of mixing in the SN ejecta.
+Despite these limitations, this study of \abc\ shows that the early detection of SNe Ia can probe explosion physics by measuring the amount of mixing in the SN ejecta.
 Moving forward, a large sample of such objects will enable strict constraints on the proposed explosion mechanisms for Type Ia SNe.
@@
 Finally, we close by emphasizing the importance of fast-response photometric and spectroscopic follow-up campaigns.
-Without the early recognition of the youth of this SN and the associated follow-up, much of the analysis presented herein would not have been possible.
+Without the early recognition of the youth of this SN, and the associated follow-up, much of the analysis presented herein would not have been possible.
 The ability to trigger such observations is essential to improve our understanding of the physics of SNe Ia.

### 2017-08-08 doc/ms.tex
Update title and author affiliations

@@
 \shorttitle{\abc}
-\shortauthors{Alphabet Friends}
+\shortauthors{Miller et al.}
 %%
@@
 \title{Early Observations of the Type Ia Supernova \abc:\\
-XXX NEED SOMETHING CLEVER TO SAY HERE XXX}
+Evidence for Strong Ejecta Mixing and/or Interaction with Diffuse Material}
 
@@
   Seattle, WA 98195}
-\affil{Google, Mountain View, CA 94043, USA}
 
@@
 \author{S.~Dhawan}
-\affil{European Southern Observatory, Karl-Schwarzschild-Strasse 2, D-85748 Garching bei München, Germany}
-\affil{Excellence Cluster Universe, Technische Universität München, Boltzmannstrasse 2, D-85748, Garching, Germany}
-\affil{Physik Department, Technische Universität München, James-Franck-Strasse 1, D-85748 Garching bei München, Germany}
 \affil{The Oskar Klein Centre, Department of Physics, AlbaNova, SE-106 91 Stockholm, Sweden}

### 2017-08-15 doc/ms.tex
Update author and acknowledgements
Add sentence about the Branch classification of this NS.

@@
 \author[0000-0003-1673-970X]{S.~B.~Cenko}
+\affil{NASA Goddard Space Flight Center, Mail Code 661, Greenbelt, MD 20771, USA}
 \affil{Joint Space-Science Institute, University of Maryland, College Park, MD 20742, USA}
-\affil{NASA Goddard Space Flight Center, Mail Code 661, Greenbelt, MD 20771, USA}
 
@@
 
+\author{C.~Fremling}
+\affil{The Oskar Klein Centre, Department of Astronomy, AlbaNova, SE-106 91 Stockholm, Sweden}
+
 \author{A.~Goobar}
@@
 
-\author{G.~Hosseinzadeh}
+\author[0000-0003-4253-656X]{D.~A.~Howell}
+\affil{Las Cumbres Observatory, Goleta, CA 93117, USA}
+\affil{Physics Department, University of California, Santa Barbara, CA 93106, USA}
+
+\author[0000-0002-0832-2974]{G.~Hosseinzadeh}
 \affil{Las Cumbres Observatory, Goleta, CA 93117, USA}
@@
 
-\author{P.~E.~Nugent}
+% \author[0000-0001-5807-7893]{C.~McCully}
+% \affil{Las Cumbres Observatory, Goleta, CA 93117, USA}
+% \affil{Physics Department, University of California, Santa Barbara, CA 93106, USA}
+
+\author[0000-0002-3389-0586]{P.~E.~Nugent}
 \affil{Lawrence Berkeley National Laboratory, Berkeley, California 94720, USA}
@@
 we find the low-resolution spectrum of \abc\ at $+18.8$ d is best matched by normal SNe Ia. Several characteristic features of a SN
-Ia, such as \ion{Si}{2}, \ion{S}{2}, can be easily identified in the
-spectra of \abc\ (Figure \ref{fig:spec_seq}).
+Ia, such as \ion{Si}{2}, \ion{S}{2}, can be easily identified in the spectra of \abc\ (Figure \ref{fig:spec_seq}).
+From the $+3.7 \, \mathrm{d}$ LCO spectrum, we measure the pseudo-equivalent widths (pEWs) of the absorption features near 5750 and 6100 \AA, which are respectively attributed to \ion{Si}{2}\,$\lambda\lambda$6580, 7234, to be $-12 \pm 2$ \AA\ and $-55 \pm 5$ \AA, respectively.
+From these measurements, \abc\ is a shallow silicon SN, similar to the SN\,1999aa-likes, according to the classification scheme presented in \citet{2009PASP..121..238B}.
 
@@
 Similar to our analysis of the \ion{Si}{2}\,$\lambda$6355 line, we 
-can measure velocities and pseudo-equivalent widths (pEWs) of 
+can measure velocities and pEWs of 
 \ion{C}{2}\,$\lambda\lambda$6580, 7234. We compare the velocity 
@@
 
+This paper utilizes the LCO infrastructure for rapid and regular monitoring of SNe, and we thank S.~Valenti and I.~Arcavi for their development efforts.
+
 Much of the analysis presented herein would not have been possible without the help of several observers.
@@
 
-% Observers:  Plant,J.Torres,Jang,Cunningham,Guhathakurta, Vedantham, De
-
 AAM is funded by the Large Synoptic Survey Telescope Corporation in support of the Data Science Fellowship Program.
@@
 
-DAH, CM, and GH are supported by NSF-1313484. Support for IA was provided by NASA through the Einstein Fellowship Program, grant PF6-170148.
+DAH, CM, and GH are supported by NSF-1313484.
 

### 2017-08-16 doc/ms.tex
Update the manuscript to reflect the comments from Suhail

@@
 \affil{Physics Department, University of California, Santa Barbara, CA 93106, USA}
-\affil{LSSTC Data Science Fellow}
 
@@
 By fitting a power law to our early light curve, we infer that first light for the SN, that is when appreciable heating from $^{56}$Ni decay has first diffused to the photosphere, only occurred $0.15\pm_{0.07}^{0.15}$~d before our first detection.
-In the $\sim$24 hr after discovery, \abc\ rose by $\sim$2 mag, following a near-linear rise in flux for $\sim$4 d.
-% Assuming the photospheric velocity follows a $t^{-0.22}$ power law, the time of explosion for \abc\ is approximately equal to the time of first light.
+In the $\sim$24 hr after discovery, \abc\ rose by $\sim$2 mag, following a near-linear rise in flux for $\gtrsim$3 d.
 Strong \ion{C}{2} absorption is detected in the early spectra of \abc, before disappearing after $\sim$7~d.
-Unlike SN\,2011fe, the $(B-V)_0$ colors of \abc\ are blue and nearly constant in the days after explosion.
+Unlike the extensively-observed Type Ia SN\,2011fe, the $(B-V)_0$ colors of \abc\ are blue and nearly constant in the days after explosion.
 We show that our early observations of \abc\ cannot be explained by either SN shock breakout and the associated, subsequent cooling, or the SN ejecta colliding with a stellar companion.
@@
 A more massive host galaxy would result in a larger inferred distance modulus that is nevertheless consistent within the uncertainties.
-For the following analysis we adopt a distance modulus $\mu = 34.89 \pm 0.10 \,\textrm{mag}$ for \abc.
+For the following analysis we adopt a distance modulus $\mu = 34.89 \pm 0.10 \,\textrm{mag}$ for \abc.\footnote{This $\mu$ is consistent with the $z_\mathrm{SN}$, $H_0 = 73 \, \mathrm{km \, s^{-1} \, Mpc}^{-1}$, and Virgo-infall-corrected distance \citep{2000ApJ...529..786M}.}
 
@@
 find that the photospheric velocity evolves as
-$v_{ph}\propto(t-t_\mathrm{exp})^{-0.22}$.
+$v_\mathrm{ph}\propto(t-t_\mathrm{exp})^{-0.22}$.
 Numerical experiments by \citet{2016ApJ...826...96P} find that the consatnt-opacity assumption strongly depends on the amount of $^{56}$Ni mixing in the SN ejecta (for a more detailed discussion of $^{56}$Ni mixing see \S\ref{sec:Ni_mixing}).
@@
 To model SN\,2011fe, \citet{2014MNRAS.441..532D} recently examined pulsational delayed-detonation (PDD) models as an explanation for some SNe Ia.
-Briefly, PDD models differ from ``standard'' delayed detonation (DD) models in that the initial deflagration causes the WD to expand resulting in the release of some unbound material.
-As the bound material contracts, eventually a subsequent detonation occurs.\footnote{\citet{2014MNRAS.441..532D} note that the deflagration and detonation in their PDD models are artificially triggered.} An important consequence of this progression for PDD models is that they naturally produce material that avoids burning, unlike DD models that typically leave no unburnt material.
+Briefly, PDD models differ from ``standard'' delayed detonation (DD) models in that the expansion of the WD during the initial deflagration phase leads to the release of unbound material.
+Following this pulsation, the bound material contracts eventually triggering a subsequent detonation.\footnote{\citet{2014MNRAS.441..532D} note that the deflagration and detonation in their PDD models are artificially triggered.} An important consequence of this progression for PDD models is that the unbound material expands and avoids burning, unlike DD models that typically leave no unburnt material.
 This results in significantly more carbon in the outer layers of the SN ejecta \citep{2014MNRAS.441..532D}.

### 2017-08-17 doc/ms.tex
Update caption for the early LC fig to describe t^2 power law

@@
   \includegraphics[width=0.48\textwidth]{early_lc.pdf}
-  \caption{Best-fit power-law model to describe the early flux from 
-  \abc\ in the $g_\mathrm{PTF}$ band. The model flux, adopting 
-  best-fit parameters $\alpha=0.98$ and $t_0=-17.94\,\textrm{d}$, 
-  is shown as a solid black line in the top panel. The lower panel 
-  shows the model residuals, and the symbols are the same as in
-  Figure~\ref{fig:lightcurve}. The model is fit to just the 
-  $g_\mathrm{PTF}$-band observations to avoid systematic difference 
-  between the filters (see the text for further 
-  details). The joint distribution of $t_0$ and $\alpha$ is 
-  illustrated in the inset of the upper panel. The solid and 
-  dashed contours represent the $68\%$ and $99.7\%$ confidence 
-  levels. \amiller{Update figure to remove other photometry}
+  \caption{Best-fit power-law model to describe the early flux 
+  from \abc\ in the $g_\mathrm{PTF}$ band. The relative flux, 
+  $f_{g_\mathrm{PTF}}$, shown as green circles, is measured via 
+  forced-PSF photometry at the SN location. The model flux, 
+  adopting best-fit parameters $\alpha=0.98$ and 
+  $t_0=-17.94\,\textrm{d}$, is shown as a dashed black line in the 
+  top panel. Also shown is the best-fit model after fixing 
+  $\alpha=2$ (thin, dash-dot line). 
+  The lower panel shows the observations and models following 
+  subtraction of the best-fit power-law model, $f_{\alpha = 0.98}$.
+  The $t^{0.98}$ model provides a much better fit to the 
+  observations than the $t^2$ model.  
+  The joint distribution of $t_0$ and $\alpha$ for the best-fit 
+  power-law model is illustrated in the inset of the upper panel. 
+  The solid contours represent the $68\%$ and $99.7\%$ confidence 
+  levels. 
   }

### 2017-08-17 doc/ms.tex
Update text to describe the t^2 fit to the early obs

@@
 
-As previously noted, a precise determination of the rise time, $t_\mathrm{rise}$, of SNe Ia is challenging as there may be a ``dark phase'' following explosion \citep{2014ApJ...784...85P}.
+Figure \ref{fig:early_lc_fit} also shows the best-fit model while fixing $\alpha = 2$.
+The $f \propto t^2$ model does not match the observations.
+Formally, for the $\alpha = 2$ model $\chi^2 = 63.7$ with $\nu = 15$ degrees of freedom (dof), while $\chi^2 = 10.2$ with $\nu = 14$ dof for the $\alpha = 0.98$ model.
+
+As previously noted, a precise determination of the rise time, $t_\mathrm{rise}$, of SNe Ia is challenging as there may be a dark phase following explosion \citep{2014ApJ...784...85P}.
 Nevertheless, to be consistent with previous studies (e.g., \citealt{2011MNRAS.416.2607G}), here we find $t_\mathrm{rise} = 17.91\pm _{0.07}^{0.15}$ d based on our fit for $t_0$.

### 2017-08-17 doc/ms.tex
Update caption for the companion-interaction figure

@@
   (green) detections and 3$\sigma$ upper limits are shown 
-  as circles and downward arrows, respectively. The initial 
-  \textit{Swift}/$UVW1$ observation (magenta) is shown as a 
-  hexagon.
+  as circles and downward arrows, respectively. 
+  \textit{Swift}/$UVW1$ observations (magenta) are shown as hexagons.
   The dashed, solid, and dash-dot lines show the expected flux 
-  for various companion interaction models in 
-  the $g_\mathrm{PTF}$ (green) and $UVW1$ (magenta) filters. The 
-  models have been adjusted to account for the distance and 
-  reddening towards \abc. Each 
+  for companion interaction models in the $g_\mathrm{PTF}$ (green) 
+  and $UVW1$ (magenta) filters. The models have been adjusted to 
+  account for the distance and reddening towards \abc. Each 
   model features a different companion semi-major axis, $a$, and 
   time of explosion, $t_\mathrm{exp}$, as labeled in the 
-  legend. While models with $a \gtrsim 10^{13} \, \mathrm{cm}$ can 
-  explain the early $g_\mathrm{PTF}$ emission, they greatly 
-  overpredict the flux in the UV. If the time of explosion is 
-  $\sim$1 d prior to $t_0$, then models with $a \approx 10^{12} \, 
+  legend. While models with $a \gtrsim 10^{12} \, \mathrm{cm}$ can 
+  explain the early rise in $g_\mathrm{PTF}$, they greatly 
+  overpredict the flux in the UV. Models with $a \approx 10^{11} \, 
   \mathrm{cm}$ can explain the initial detection \abc, but they 

### 2017-08-17 doc/ms.tex
Update text to describe new companion-interaction fig

@@
 
-The detection of excess emission due to the collision of the SN ejecta 
+The detection of emission from the collision of the SN ejecta 
 with a non-degenerate companion requires a favorable orbital 
@@
 considerations alone the probability of detecting ejecta-companion 
-interaction is low, $\sim$10\%. \citet{2010ApJ...708.1025K} calculates that the 
-collision of SN ejecta with a companion  
+interaction is low, $\sim$10\%. \citet{2010ApJ...708.1025K} 
+calculates that the collision of SN ejecta with a companion  
 generates thermal emission with a spectrum that peaks in the 
 UV. The resulting \textit{g}-band emission is expected to be weak.
-
-To examine the possibility of a SN-companion signature in the early
-light curve of \abc, we employ the \citet{2010ApJ...708.1025K}
-model and assume canonical values for the ejecta mass, $1.4\,\sm$, expansion velocity,
-$10^{4}\,\textrm{km}\,\textrm{s}^{-1}$, and a constant opacity, 
-$0.2\,\textrm{cm}^2\,\textrm{g}^{-1}$. We calculate the expected 
-$g_\mathrm{PTF}$ brightness of an ejecta-companion collision at the 
-distance of \abc\ behind a total reddening of $E(B-V) = 0.08 \, \mathrm{mag}$ using the parameterized equations in 
-\citet{2012ApJ...749...18B}.
-If we assume the binary is aligned with the optimal orientation relative to the line of sight, a binary separation of $a \approx 2 \times 10^{13}\, \mathrm{cm}$ is needed to explain the initial detection of \abc, as shown in Figure~\ref{fig:SN-companion}.
-This model does not, however, match the $g_\mathrm{PTF}$ evolution for $t > t_0 + 1 \, \mathrm{d}$ (though it is possible that the SN photosphere dominates the companion-interaction signature at this phase).
-Furthermore, this model significantly overpredicts the observed flux in the \textit{Swift}/$UVW1$ filter $\sim$3.1~d after $t_0$.
-As such, we do not favor such a model as the explanation for the early emission from \abc.
-
-Figure~\ref{fig:SN-companion} additionally shows that a companion at $a = 10^{14} \, \mathrm{cm}$ provides a good match to the observations $\sim$1--3~d after $t_0$ if $t_\mathrm{exp} \approx t_0 + 0.3 \; \mathrm{d}$.
-Like the $a = 2 \times 10^{13} \, \mathrm{cm}$ model, this model significantly overpredicts the observed UV flux from \abc.
-Additionally, this model cannot account for the brightness of \abc\ at the epoch of discovery.
-The challenges associated with each of the previous two models lead us to conclude that the early evolution of \abc\ cannot be explained via the interaction of the SN ejecta with a red-giant companion.\footnote{The \citet{2010ApJ...708.1025K} model assumes Roche-lobe overflow, meaning that $a > 10^{13} \, \mathrm{cm}$ implies a companion with $R_\ast \gtrsim 100 \, R_\odot$.} We cannot, however, exclude the presence of a red-giant companion as our calculations have assumed that the binary is aligned with the optimal geometry relative to the line of sight.
-If the geometry is not favorable, then it is possible that signatures from interaction with a companion are not visible.
-
- % Our early \textit{Swift} observations support this conclusion, as the UV $-$ optical colors are very red, whereas iPTF\,14atg exhibited much bluer UV $-$ optical colors at the same epoch \citep{2015Natur.521..328C}.
 
@@
 
-Finally, we examine the minimum binary separation capable of explaining the observed brightness at the epoch of discovery.
-Figure~\ref{fig:SN-companion} shows that models with $a \approx 8 \times 10^{11} \, \mathrm{cm}$ peak at $\sim$21.5~mag in the $g_\mathrm{PTF}$-band, provided that $t_\mathrm{exp} \approx t_0 - 1 \; \mathrm{d}$.
-To explain just the epoch of discovery, models with larger $a$ would require even earlier explosion times, which is not compatible with our non-detections the night before discovery, while models with smaller $a$ are not bright enough.
-While it is otherwise compatible with the observations, we do not favor the $a \approx 8 \times 10^{11} \, \mathrm{cm}$ model as the explanation for the early flux from \abc\ because it does not explain the 2 mag rise in the $\sim$24 hr after discovery.
+To examine the possibility of a SN-companion signature in the early
+light curve of \abc, we employ the \citet{2010ApJ...708.1025K}
+model and assume canonical values for the ejecta mass, $1.4\,\sm$, expansion velocity, $10^{4}\,\textrm{km}\,\textrm{s}^{-1}$, and a constant opacity, $0.2\,\textrm{cm}^2\,\textrm{g}^{-1}$.
+We calculate the expected $g_\mathrm{PTF}$ brightness of an ejecta-companion collision at the distance of \abc\ behind a total reddening of $E(B-V) = 0.08 \, \mathrm{mag}$ using the parameterized equations in \citet{2012ApJ...749...18B}.
+If we assume the binary is aligned with the optimal orientation relative to the line of sight, a binary separation of $a \approx 3 \times 10^{11}\, \mathrm{cm}$ is needed to explain the initial detection of \abc, as shown in Figure~\ref{fig:SN-companion}.
+The minimum binary separation capable of explaining the observed brightness at the epoch of discovery is $a \approx 10^{11} \, \mathrm{cm}$.
+Figure~\ref{fig:SN-companion} shows that such models peak at $g_\mathrm{PTF} \approx 21.5 \, \mathrm{mag}$, provided that $t_\mathrm{exp} \approx t_0 - 0.3 \; \mathrm{d}$.
+These models do not, however, match the $g_\mathrm{PTF}$ evolution for $t > t_0 + 0.5 \, \mathrm{d}$ (though it is possible that the SN photosphere dominates the companion-interaction signature at this phase).
+While they are otherwise compatible with the observations, we do not favor the above models as the explanation for the early flux from \abc\ because they do not explain the 2 mag rise in the $\sim$24 hr after discovery.
+
+Figure~\ref{fig:SN-companion} additionally shows that a companion at $a \approx 18 \times 10^{11} \, \mathrm{cm}$ provides a good match to the initial $g_\mathrm{PTF}$ rise, if $t_\mathrm{exp} \approx t_0 + 0.1 \; \mathrm{d}$.
+Models with $a \gtrsim 10^{12} \, \mathrm{cm}$, which can explain the initial $g_\mathrm{PTF}$ rise, signiticantly overpredict the observed UV flux, however.
+There is no choice of $a$ capable of replicating the early rise of \abc\ without also significantly overpredicting the observed UV flux.
+
+The challenges associated with each of the previously considered models lead us to conclude that the early evolution of \abc\ cannot be explained via the interaction of the SN ejecta with a companion.
+We cannot, however, exclude the presence of a red-giant, or other non-degenerate, companion as our calculations have assumed that the binary is aligned with the optimal geometry relative to the line of sight.
+If the geometry is not favorable, then it is possible that signatures from interaction with a companion are not visible.
 

### 2017-08-17 doc/ms.tex
Minor grammatical clean up for companion section

@@
 
-\begin{figure}[!thb]
-  \centering
-  \includegraphics[width=0.48\textwidth]{companion_lc.pdf}
-  \caption{Comparison of SN ejecta-companion interaction models 
-  with early observations of \abc. $g_\mathrm{PTF}$ observations 
-  (green) detections and 3$\sigma$ upper limits are shown 
-  as circles and downward arrows, respectively. 
-  \textit{Swift}/$UVW1$ observations (magenta) are shown as hexagons.
-  The dashed, solid, and dash-dot lines show the expected flux 
-  for companion interaction models in the $g_\mathrm{PTF}$ (green) 
-  and $UVW1$ (magenta) filters. The models have been adjusted to 
-  account for the distance and reddening towards \abc. Each 
-  model features a different companion semi-major axis, $a$, and 
-  time of explosion, $t_\mathrm{exp}$, as labeled in the 
-  legend. While models with $a \gtrsim 10^{12} \, \mathrm{cm}$ can 
-  explain the early rise in $g_\mathrm{PTF}$, they greatly 
-  overpredict the flux in the UV. Models with $a \approx 10^{11} \, 
-  \mathrm{cm}$ can explain the initial detection \abc, but they 
-  fail to replicate the $\sim$2 mag rise in the $\sim$24 hr after 
-  explosion.
-  }
-  \label{fig:SN-companion}
-\end{figure}
-
 To examine the possibility of a SN-companion signature in the early
@@
 
-Figure~\ref{fig:SN-companion} additionally shows that a companion at $a \approx 18 \times 10^{11} \, \mathrm{cm}$ provides a good match to the initial $g_\mathrm{PTF}$ rise, if $t_\mathrm{exp} \approx t_0 + 0.1 \; \mathrm{d}$.
+\begin{figure}[!thb]
+  \centering
+  \includegraphics[width=0.48\textwidth]{companion_lc.pdf}
+  \caption{Comparison of SN ejecta-companion interaction models 
+  with early observations of \abc. $g_\mathrm{PTF}$ 
+  detections and 3$\sigma$ upper limits are shown 
+  as green circles and downward arrows, respectively. 
+  \textit{Swift}/$UVW1$ observations are shown as magenta hexagons.
+  The dashed, solid, and dash-dot lines show the expected flux 
+  for companion-interaction models in the $g_\mathrm{PTF}$ (green) 
+  and $UVW1$ (magenta) filters. The models have been adjusted to 
+  account for the distance and reddening towards \abc. Each 
+  model features a different companion semi-major axis, $a$, and 
+  time of explosion, $t_\mathrm{exp}$, as labeled in the 
+  legend. While models with $a \gtrsim 10^{12} \, \mathrm{cm}$ can 
+  explain the early optical rise, they greatly 
+  overpredict the UV flux. Models with $a \approx 10^{11} \, 
+  \mathrm{cm}$ can explain the initial detection \abc, but they 
+  fail to replicate the $\sim$2 mag rise in the $\sim$24 hr after 
+  explosion.
+  }
+  \label{fig:SN-companion}
+\end{figure}
+
+Figure~\ref{fig:SN-companion} additionally shows that a companion at $a \approx 18 \times 10^{11} \, \mathrm{cm}$ provides a good match to the initial optical rise, if $t_\mathrm{exp} \approx t_0 + 0.1 \; \mathrm{d}$.
 Models with $a \gtrsim 10^{12} \, \mathrm{cm}$, which can explain the initial $g_\mathrm{PTF}$ rise, signiticantly overpredict the observed UV flux, however.
-There is no choice of $a$ capable of replicating the early rise of \abc\ without also significantly overpredicting the observed UV flux.
+There is no choice of $a$ capable of replicating the early rise of \abc\ without also overpredicting the observed UV flux.
 

### 2017-08-19 doc/ms.tex
Include new sub-section on sub-chandra double det

@@
 
+\subsection{Sub-Chandrasekhar Double Detonation}
+
+The detonation of a WD with $M < 1.4 M_\odot$, which can occur if triggered by a detonation in a He surface layer that was accreted from a binary companion (known as the sub-Chandrasekhar double detonation), can produce a rapid rise and early blue optical colors (e.g., \citealt{2017arXiv170603613N}).
+While this qualitative behavior matches \abc, the $U-V$ colors predicted in \citet{2017arXiv170603613N} do not match our observations.
+In particular, the sub-Chandrasekhar double detonation model $U - V$ colors rapidly evolve from $\sim$$-0.6\,\mathrm{mag}$ $\sim$1\,d after explosion to $\sim$0.5\,mag $\sim$3\,d after explosion.
+We observe a steady $U - V$ color evolution from the red to the blue for \abc, however, with $U - V \approx 0.6 \, \mathrm{mag}$ $\sim$2\,d after $t_0$ and $U - V \approx 0 \, \mathrm{mag}$ $\sim$8\,d after $t_0$.
+As such we conclude that \abc\ is not the result of a sub-Chandrasekhar double detonation.
+\citet{2017arXiv170603613N} do note that their one-dimensional models may not capture the predicted asphericity for sub-Chandrasekhar double detonations, though moving away from the preferred viewing angle results in redder colors and a more gradual rise, which is not observed for \abc.
+
 \subsection{Interaction with Diffuse Material}

### 2017-08-21 doc/ms.tex
Update author list

@@
 \author{S.~Dhawan}
-\affil{The Oskar Klein Centre, Department of Physics, AlbaNova, SE-106 91 Stockholm, Sweden}
+\affil{The Oskar Klein Centre, Department of Physics, Stockholm University, AlbaNova, SE-106 91 Stockholm, Sweden}
 
 \author{R.~Ferretti}
-\affil{The Oskar Klein Centre, Department of Physics, AlbaNova, SE-106 91 Stockholm, Sweden}
+\affil{The Oskar Klein Centre, Department of Physics, Stockholm University, AlbaNova, SE-106 91 Stockholm, Sweden}
 
@@
 \author{C.~Fremling}
-\affil{The Oskar Klein Centre, Department of Astronomy, AlbaNova, SE-106 91 Stockholm, Sweden}
+\affil{The Oskar Klein Centre, Department of Astronomy, Stockholm University, AlbaNova, SE-106 91 Stockholm, Sweden}
 
 \author{A.~Goobar}
-\affil{The Oskar Klein Centre, Department of Physics, AlbaNova, SE-106 91 Stockholm, Sweden}
+\affil{The Oskar Klein Centre, Department of Physics, Stockholm University, AlbaNova, SE-106 91 Stockholm, Sweden}
 
@@
 
-% \author[0000-0001-5807-7893]{C.~McCully}
-% \affil{Las Cumbres Observatory, Goleta, CA 93117, USA}
-% \affil{Physics Department, University of California, Santa Barbara, CA 93106, USA}
+\author[0000-0001-5807-7893]{C.~McCully}
+\affil{Las Cumbres Observatory, Goleta, CA 93117, USA}
+\affil{Physics Department, University of California, Santa Barbara, CA 93106, USA}
 
@@
 \author{J.~Sollerman}
-\affil{The Oskar Klein Centre, Department of Astronomy, AlbaNova, SE-106 91 Stockholm, Sweden}
+\affil{The Oskar Klein Centre, Department of Astronomy, Stockholm University, AlbaNova, SE-106 91 Stockholm, Sweden}
 
 \author{F.~Taddia}
-\affil{The Oskar Klein Centre, Department of Astronomy, AlbaNova, SE-106 91 Stockholm, Sweden}
+\affil{The Oskar Klein Centre, Department of Astronomy, Stockholm University, AlbaNova, SE-106 91 Stockholm, Sweden}
 

### 2017-08-21 doc/ms.tex
Update text following Jesper's last comments and spell check

@@
 
-Interaction is not limited to systems with a non-degenerate companion, however, as WDs enshoruded in diffuse material following a binary merger (e.g., \citealt{2015MNRAS.447.2803L}) or expanded due to a pre-explosion pulsation can give rise to ejecta-interaction signatures (e.g., \citealt{2014MNRAS.441..532D}).
+Interaction is not limited to systems with a non-degenerate companion, however, as WDs enshrouded in diffuse material following a binary merger (e.g., \citealt{2015MNRAS.447.2803L}) or expanded due to a pre-explosion pulsation can give rise to ejecta-interaction signatures (e.g., \citealt{2014MNRAS.441..532D}).
 Models of this scenario naturally produce \ion{C}{2} absorption that is comparable in strength to \ion{Si}{2} in the days after explosion \citep{2014MNRAS.441..532D}, as was observed in SN\,2013dy \citep{2013ApJ...778L..15Z} and SN\,2017cbv \citep{2017arXiv170608990H}.
@@
 
-The time of first light, defined as the moment when appreciable heating from $^{56}$Ni decay has first diffused to the photosphere, for SNe is usually estimated by 
+The time of first light, interpreted in this study as the moment when appreciable heating from $^{56}$Ni decay has first diffused to the photosphere, for SNe is usually estimated by 
 extrapolating early-phase light curves to determine when the 
@@
 $v_\mathrm{ph}\propto(t-t_\mathrm{exp})^{-0.22}$.
-Numerical experiments by \citet{2016ApJ...826...96P} find that the consatnt-opacity assumption strongly depends on the amount of $^{56}$Ni mixing in the SN ejecta (for a more detailed discussion of $^{56}$Ni mixing see \S\ref{sec:Ni_mixing}).
+Numerical experiments by \citet{2016ApJ...826...96P} find that the constant-opacity assumption strongly depends on the amount of $^{56}$Ni mixing in the SN ejecta (for a more detailed discussion of $^{56}$Ni mixing see \S\ref{sec:Ni_mixing}).
 As a result, the adoption of a $t^{-0.22}$ power-law model may not be valid for all SNe Ia.
@@
      with an index of $-0.22$ (dashed line). Additionally, the 
-     measured velocites of \ion{C}{2}\,$\lambda\lambda$6580, 7234 
+     measured velocities of \ion{C}{2}\,$\lambda\lambda$6580, 7234 
      are shown. Typical uncertainties are smaller than the size of 
@@
 $v\propto(t-t_{exp})^{-0.22}$ model by minimizing the $\chi^2$ value and find the best-fit explosion time relative to $T_{B,\mathrm{max}}$ in the SN rest frame to be $t_{exp} = -17.45 \pm ^{0.14}_{0.16}\,\textrm{d}$, where the uncertainties represent the 95\% confidence interval (Figure \ref{fig:velocity_t_exp}).
-Following the analysis in \citet{2014ApJ...784...85P}, we additionally alter the power-law index to $-0.20$ and $-0.24$ to examine the sensitivety of the result on the assumed power-law index.
-We find that this variation in the power-law index results in inferred explosion times that vary by $\approx$1 d (Figure \ref{fig:velocity_t_exp}).
+Following the analysis in \citet{2014ApJ...784...85P}, we additionally alter the power-law index to $-0.20$ and $-0.24$ to examine the sensitivity of the result on the assumed power-law index.
+We find that this variation in the power-law index results in a change of $t_\mathrm{exp}$ of $\approx\pm$0.5\,d (Figure \ref{fig:velocity_t_exp}).
 Given the analytical approximation that $v \propto t^{-0.22}$, we adopt $t_{exp} = -17.5 \pm 0.5 \; \mathrm{d}$, where the uncertainty reflects possible variations in the power-lax index (see \citealt{2014ApJ...784...85P}).
@@
 
-Relative to the nearby, normal SN\,2011fe, we have identified several distinct characteristics of the early evolution of \abc, including: (i) a near-linear photometric rise, (ii) a qualitatively short dark phase, assuming $v_\mathrm{ph} \propto t^{-0.22}$, (iii) the presence of strong \ion{C}{2} absorption, and (iv) blue and non-evolving $(B - V)_0$ color in the week after explosion.
+Relative to the nearby, normal SN\,2011fe, we have identified several distinct characteristics of the early evolution of \abc, including: (i) a near-linear photometric rise, (ii) a qualitatively short, or possibly absent, dark phase, assuming $v_\mathrm{ph} \propto t^{-0.22}$, (iii) the presence of strong \ion{C}{2} absorption, and (iv) blue and non-evolving $(B - V)_0$ color in the week after explosion.
 While most SNe Ia are powered purely by radioactive decay, the observed radiation shortly after explosion can also include contributions
@@
 Figure~\ref{fig:SN-companion} additionally shows that a companion at $a \approx 18 \times 10^{11} \, \mathrm{cm}$ provides a good match to the initial optical rise, if $t_\mathrm{exp} \approx t_0 + 0.1 \; \mathrm{d}$.
-Models with $a \gtrsim 10^{12} \, \mathrm{cm}$, which can explain the initial $g_\mathrm{PTF}$ rise, signiticantly overpredict the observed UV flux, however.
+Models with $a \gtrsim 10^{12} \, \mathrm{cm}$, which can explain the initial $g_\mathrm{PTF}$ rise, significantly overpredict the observed UV flux, however.
 There is no choice of $a$ capable of replicating the early rise of \abc\ without also overpredicting the observed UV flux.
@@
 Having examined other possibilities we now consider whether the unusual properties of \abc\ can be explained simply by invoking strong mixing in the SN ejecta.
-Strong mixing can lead to a short dark phase.
+Strong mixing leads to a shorter dark phase than would otherwise be observed.
 Here we additionally examine whether strong mixing can explain the rapid, near-linear rise in the light curve.
@@
 
-In \S\ref{sec:first_light} we compared our early observations of \abc\ to SN\,2011fe, which has the most comprehensive observations of the young SNe Ia sample.
+In \S\ref{sec:first_light} we compared our early observations of \abc\ to SN\,2011fe, which has the most comprehensive observations of the young SN Ia sample.
 Given its normal spectroscopic and photometric evolution, SN\,2011fe has been adopted as a standard for the early evolution of SNe Ia in many studies.
@@
 Above, we argued for circumstellar interaction and strong $^{56}$Ni mixing as a possible explanation for \abc, and indeed \citet{2017arXiv170608990H} consider these possibilities for SN\,2017cbv as well.
-Seperately, several arguments against companion interaction for SN\,2012cg are presented in \citet{2016arXiv161007601S}.
-
-Ultimately, there are arguments in favor of and against each of the possibilties to explain the early emission from SNe Ia.
+Separately, several arguments against companion interaction for SN\,2012cg are presented in \citet{2016arXiv161007601S}.
+
+Ultimately, there are arguments in favor of and against each of the possibilities to explain the early emission from SNe Ia.
 Moving forward, more detailed models and simulations are needed to properly explain the observed diversity.
@@
 
-We are deeply grateful to R.~C.~Thomas for induldging a slew of questions regarding \ion{C}{2} in SNe.
+We are deeply grateful to R.~C.~Thomas for indulging a slew of questions regarding \ion{C}{2} in SNe.
 Similarly, it is our pleasure to buy a beer for R.~Amanullah and U.~Feindt for discussions regarding SALT2.
@@
 The upgrade of the DeVeny optical spectrograph has been funded by a generous grant from John and Ginger Giovale.
+Based on observations made with the Nordic Optical Telescope, operated by the Nordic Optical Telescope Scientific Association at the Observatorio del Roque de los Muchachos, La Palma, Spain, of the Instituto de Astrofisica de Canarias.
 

### 2017-08-22 doc/ms.tex
Add author info for Shri and Mansi
Final spelling and grammar check for the paper

@@
 \title{Early Observations of the Type Ia Supernova \abc:\\
-Evidence for Strong Ejecta Mixing and/or Interaction with Diffuse Material}
+Evidence for Strong Ejecta Mixing or Interaction with Diffuse Material}
 
@@
 
-\author{M.~M.~Kasliwal}
+\author[0000-0002-5619-4938]{M.~M.~Kasliwal}
 \affil{Division of Physics, Mathematics, and Astronomy, California Institute of Technology, Pasadena, CA 91125, USA}
@@
 
-\author{S. R. Kulkarni}
+\author[0000-0001-5390-8563]{S. R. Kulkarni}
 \affil{Division of Physics, Mathematics, and Astronomy, California Institute of Technology, Pasadena, CA 91125, USA}
@@
 Here, we report the intermediate Palomar Transient Factory (iPTF) discovery of an extraordinarily young SN Ia, \abc.
-By fitting a power law to our early light curve, we infer that first light for the SN, that is when appreciable heating from $^{56}$Ni decay has first diffused to the photosphere, only occurred $0.15\pm_{0.07}^{0.15}$~d before our first detection.
-In the $\sim$24 hr after discovery, \abc\ rose by $\sim$2 mag, following a near-linear rise in flux for $\gtrsim$3 d.
-Strong \ion{C}{2} absorption is detected in the early spectra of \abc, before disappearing after $\sim$7~d.
+By fitting a power law to our early light curve, we infer that first light for the SN, that is when appreciable heating from $^{56}$Ni decay has first diffused to the photosphere, only occurred $0.15\pm_{0.07}^{0.15}$\,d before our first detection.
+In the $\sim$24\,hr after discovery, \abc\ rose by $\sim$2\,mag, following a near-linear rise in flux for $\gtrsim$3\,d.
+Strong \ion{C}{2} absorption is detected in the early spectra of \abc, before disappearing after $\sim$7\,d.
 Unlike the extensively-observed Type Ia SN\,2011fe, the $(B-V)_0$ colors of \abc\ are blue and nearly constant in the days after explosion.
@@
 %% keywords and the rules for their use.
-\keywords{methods: observational --- supernovae: general --- supernovae: individual (\abc)}
+\keywords{methods: observational --- surveys --- supernovae: general --- supernovae: individual (\abc)}
 
@@
 This also leads to blue optical colors and a rapid initial rise in the observed light curve.
-If the mixing is weak and the $^{56}$Ni is confined to the innermost layers of the ejecta, the dark phase can last for several days as the radioactive energy diffuses to the photosphere.
+If the mixing is weak and the $^{56}$Ni is confined to the innermost layers of the ejecta, the dark phase can last for several days.
 The early evolution of such SNe results in redder colors and a more moderate rise in luminosity \citep{2016ApJ...826...96P}.
@@
 
-\citet{2017arXiv170603613N} recently demonstrated that disambiguating between these different scenarios via optical photometry alone is challenging.
-\citeauthor{2017arXiv170603613N} further show that estimates of the time of explosion, which are critical for comparing models with observations, are often incorrect by as many as $\sim$2 d using common methods in the literature.
+\citet{2017arXiv170603613N} demonstrate that disambiguating between these different scenarios via optical photometry alone is challenging.
+\citeauthor{2017arXiv170603613N} further show that estimates of the time of explosion, which are critical for comparing models with observations, are often incorrect by as many as $\sim$2\,d using common methods in the literature.
 While analytical models suggest that early spectra can be used to infer the time of explosion (e.g., \citealt{2014ApJ...784...85P}), more detailed simulations show that the photospheric evolution is not so simple \citep{2016ApJ...826...96P}.
@@
 The transient is spatially coincident with a tidal tail of the galaxy NGC\,5221, which lies at a distance of $\sim$100\,Mpc.
-\abc\ is not detected to a limit of $g=22.1$\,mag on April $2.42$, less than 1 d prior to discovery, and rose by $\sim$2 mag in the 24 hr following its initial detection.
+\abc\ is not detected to a limit of $g=22.1$\,mag on April $2.42$, less than 1\,d prior to discovery, and rose by $\sim$2 mag in the 24 hr following its initial detection.
 Our spectroscopic follow-up
@@
 We interpret those differences as arising from either strong $^{56}$Ni mixing or ejecta interaction with diffuse material, or a combination of the two.
+Alongside this paper, we have released our open source analysis and all of the data utilized in this study.
+These are available online at \texttt{GitHub} \url{https://github.com/adamamiller/iPTF16abc}.
 
@@
 \label{sec:obs}
+
+During the spring of 2016, the iPTF survey observed the field of \abc\ every night during dark time in either the $g_\mathrm{PTF}$ or 
+$R_\mathrm{PTF}$ band.\footnote{P48 observations of \abc\ are reported in the $g_\mathrm{PTF}$ and $R_\mathrm{PTF}$ filters throughout, which are similar to the SDSS $g'$ and Mould-$R$ filters, respectively (see \citealt{2012PASP..124..854O} for details on PTF calibration).
+The correction from the $g_\mathrm{PTF}$ and $R_\mathrm{PTF}$ filters to SDSS $g'$ and $r'$ requires knowledge of the intrinsic source color (see Eqns.~1 and 2 in \citealt{2012PASP..124..854O}).
+The spectral diversity of SNe Ia in the days after explosion is poorly constrained, and as a result the color terms for \abc\ at these epochs are unknown.
+We proceed by assuming the $g_\mathrm{PTF}$ and $R_\mathrm{PTF}$ calibration is on the AB system, which strictly speaking is incorrect, but this does not fundamentally alter any of our conclusions.}
+Survey observations were conducted with the
+CFH12K camera \citep{2008SPIE.7014E..4YR} on the Palomar Observatory 
+48-inch telescope (P48; \citealt{2009PASP..121.1395L}). Images were processed by the IPAC image
+subtraction and discovery pipeline which subtracts off the background
+galaxy light with stacked pre-SN images and performs forced
+point-spread-function (PSF) photometry at the location of the SN 
+\citep{2017PASP..129a4002M}. The
+photometry is then calibrated to the PTF photometric catalog
+\citep{2012PASP..124..854O}.
 
@@
 
-During the spring of 2016, the iPTF survey observed the field of \abc\ every night during dark time in either the $g_\mathrm{PTF}$ or 
-$R_\mathrm{PTF}$ band.\footnote{P48 observations of \abc\ are reported in the $g_\mathrm{PTF}$ and $R_\mathrm{PTF}$ filters throughout, which are similar to the SDSS $g'$ and Mould-$R$ filters, respectively (see \citealt{2012PASP..124..854O} for details on PTF calibration).
-The correction from the $g_\mathrm{PTF}$ and $R_\mathrm{PTF}$ filters to SDSS $g'$ and $r'$ requires knowledge of the intrinsic source color (see Eqns.~1 and 2 in \citealt{2012PASP..124..854O}).
-The spectral diversity of SNe Ia in the days after explosion is poorly constrained, and as a result the color terms for \abc\ at these epochs are unknown.
-We proceed by assuming the $g_\mathrm{PTF}$ and $R_\mathrm{PTF}$ calibration is on the AB system, which strictly speaking is incorrect, but this does not fundamentally alter any of our conclusions.}
-Survey observations were conducted with the
-CFH12K camera \citep{2008SPIE.7014E..4YR} on the Palomar Observatory 
-48-inch telescope (P48; \citealt{2009PASP..121.1395L}). Images were processed by the IPAC image
-subtraction and discovery pipeline which subtracts off the background
-galaxy light with stacked pre-SN images and performs forced
-point-spread-function (PSF) photometry at the location of the SN 
-\citep{2017PASP..129a4002M}. The
-photometry is then calibrated to the PTF photometric catalog
-\citep{2012PASP..124..854O}.
-
 After discovery, photometric observations in the $g'$, $r'$ and $i'$
@@
 The \textit{Swift} satellite observed \abc\ on 14 epochs, beginning 
-$\sim$15 d pre-maximum light through $\sim$22 d post maximum. The SN 
+$\sim$15\,d pre-maximum light through $\sim$22\,d post maximum. The SN 
 flux is measured via aperture photometry on Ultraviolet-Optical
@@
   \centering
-  \includegraphics[width=0.78\textwidth]{spectra.pdf}
+  \includegraphics[width=0.69\textwidth]{spectra.pdf}
   \caption{Observed spectral sequence of \abc. The spectra are 
@@
 The high-resolution spectra presented in Ferretti et al.\ (2017) show multiple absorption components for both the \ion{Ca}{2}\,H$+$K and \ion{Na}{1}\,D doublets.
-While the equivalent width (EW) of these lines is quite large, implying a large amount of extinction (e.g., \citealt{2012MNRAS.426.1465P}), Ferretti et al.\ compare the evolution of \abc\ to the well-observed normal Type Ia SN\,2011fe and find evidence for only a small amount of extinction.
+While the equivalent width (EW) of these lines is quite large, implying significant extinction (e.g., \citealt{2012MNRAS.426.1465P}), Ferretti et al.\ compare the evolution of \abc\ to the well-observed normal Type Ia SN\,2011fe and only find evidence for a small amount of extinction.
 The empirical relation between the EW of \ion{Na}{1}\,D and extinction is known to have a large scatter, and \citet{2013ApJ...779...38P} have shown that \ion{Na}{1}\,D absorption is a poor tracer of reddening in Type Ia SNe.
-Thus, we instead adopt $E(B-V) = 0.05 \, \mathrm{mag}$ as the local extinction for \abc\ (Ferretti et al.\ 2017).
-Thus, we assume a total, Galactic $+$ host galaxy, line-of-sight extinction of $E(B-V) = 0.08 \, \mathrm{mag}$ for the remainder of our analysis.
+Thus, we adopt $E(B-V) = 0.05 \, \mathrm{mag}$ as the local extinction for \abc\ (Ferretti et al.\ 2017).
+For the remainder of our analysis we assume a total, Galactic $+$ host galaxy, line-of-sight extinction of $E(B-V) = 0.08 \, \mathrm{mag}$.
 
@@
 Using the SuperNova IDentification (\texttt{SNID}; \citealt{2007ApJ...666.1024B}) package, 
-we find the low-resolution spectrum of \abc\ at $+18.8$ d is best matched by normal SNe Ia. Several characteristic features of a SN
+we find the low-resolution spectrum of \abc\ at $+18.8$\,d is best matched by normal SNe Ia. Several characteristic features of a SN
 Ia, such as \ion{Si}{2}, \ion{S}{2}, can be easily identified in the spectra of \abc\ (Figure \ref{fig:spec_seq}).
-From the $+3.7 \, \mathrm{d}$ LCO spectrum, we measure the pseudo-equivalent widths (pEWs) of the absorption features near 5750 and 6100 \AA, which are respectively attributed to \ion{Si}{2}\,$\lambda\lambda$6580, 7234, to be $-12 \pm 2$ \AA\ and $-55 \pm 5$ \AA, respectively.
-From these measurements, \abc\ is a shallow silicon SN, similar to the SN\,1999aa-likes, according to the classification scheme presented in \citet{2009PASP..121..238B}.
+From the $+3.7 \, \mathrm{d}$ LCO spectrum, we measure the pseudo-equivalent widths (pEWs) of the absorption features near 5750 and 6100 \AA, which are respectively attributed to \ion{Si}{2}\,$\lambda\lambda$6580, 7234, to be $-12 \pm 2$\,\AA\ and $-55 \pm 5$\,\AA, respectively.
+According to the classification scheme presented in \citet{2009PASP..121..238B}, these pEW measurements indicate that \abc\ is a shallow silicon SN, similar to the SN\,1999aa-likes.
 
@@
 
-As our observations include especially early observations of \abc, there are upper limits $\sim$1 d prior to the discovery epoch, we model the early flux from \abc\ as a power law, but allow the power-law index to vary, as opposed to fixing it at 2, to account for potential variations in the photospheric temperature during expansion:
+As our observations include especially early observations of \abc, there are upper limits $\sim$1\,d prior to the discovery epoch, we model the early flux from \abc\ as a power law, but allow the power-law index to vary, as opposed to fixing it at 2, to account for potential variations in the photospheric temperature during expansion:
 \begin{equation}
@@
 
-As previously noted, a precise determination of the rise time, $t_\mathrm{rise}$, of SNe Ia is challenging as there may be a dark phase following explosion \citep{2014ApJ...784...85P}.
-Nevertheless, to be consistent with previous studies (e.g., \citealt{2011MNRAS.416.2607G}), here we find $t_\mathrm{rise} = 17.91\pm _{0.07}^{0.15}$ d based on our fit for $t_0$.
-We caution that this measurement may be underestimated due to the uncertain time of explosion.
-
 \begin{figure}[!htb]
@@
   \caption{Best-fit power-law model to describe the early flux 
-  from \abc\ in the $g_\mathrm{PTF}$ band. The relative flux, 
+  from \abc\ in the $g_\mathrm{PTF}$ band. \textit{Top}: The 
+  relative flux, 
   $f_{g_\mathrm{PTF}}$, shown as green circles, is measured via 
@@
   adopting best-fit parameters $\alpha=0.98$ and 
-  $t_0=-17.94\,\textrm{d}$, is shown as a dashed black line in the 
-  top panel. Also shown is the best-fit model after fixing 
+  $t_0=-17.94\,\textrm{d}$, is shown as a dashed black line. Also 
+  shown is the best-fit model after fixing 
   $\alpha=2$ (thin, dash-dot line). 
-  The lower panel shows the observations and models following 
+  The joint distribution of $t_0$ and $\alpha$ for the best-fit 
+  power-law model is illustrated in the inset. 
+  The solid contours represent the $68\%$ and $99.7\%$ confidence 
+  levels.
+  \textit{Bottom}: 
+  The observations and models following 
   subtraction of the best-fit power-law model, $f_{\alpha = 0.98}$.
@@
   observations than the $t^2$ model. 
-  The joint distribution of $t_0$ and $\alpha$ for the best-fit 
-  power-law model is illustrated in the inset of the upper panel. 
-  The solid contours represent the $68\%$ and $99.7\%$ confidence 
-  levels. 
   }
@@
 \end{figure}
+
+As previously noted, a precise determination of the rise time, $t_\mathrm{rise}$, of SNe Ia is challenging as there may be a dark phase following explosion \citep{2014ApJ...784...85P}.
+Nevertheless, to be consistent with previous studies (e.g., \citealt{2011MNRAS.416.2607G}), here we find $t_\mathrm{rise} = 17.91\pm _{0.07}^{0.15}$\,d based on our fit for $t_0$.
+We caution that this measurement may be underestimated due to the uncertain time of explosion.
 
@@
 wing of the \ion{Si}{2} line (see Figures~\ref{fig:spec_seq} and \ref{fig:carbon}). Consequently, we model the observed 
-spectra between 5,900 and 6,500\,\AA\ (rest-frame) as the combination 
-of two Gaussian kernels plus a linear baseline, which
+spectra between 5900 and 6500\,\AA\ (rest-frame) as the 
+combination of two Gaussian kernels plus a linear baseline, which
 accounts for \ion{Si}{2}, \ion{C}{2} and the
@@
   \includegraphics[width=0.48\textwidth]{VelocityPlot.pdf}
-  \caption{Constraints on $t_{exp}$ from fitting the velocity
+  \caption{Constraints on $t_\mathrm{exp}$ from fitting the velocity
     evolution of \ion{Si}{2}.
@@
 We fit the measured velocities of \ion{Si}{2}\,$\lambda$6355 to the
-$v\propto(t-t_{exp})^{-0.22}$ model by minimizing the $\chi^2$ value and find the best-fit explosion time relative to $T_{B,\mathrm{max}}$ in the SN rest frame to be $t_{exp} = -17.45 \pm ^{0.14}_{0.16}\,\textrm{d}$, where the uncertainties represent the 95\% confidence interval (Figure \ref{fig:velocity_t_exp}).
+$v\propto(t-t_\mathrm{exp})^{-0.22}$ model by minimizing the $\chi^2$ value and find the best-fit explosion time relative to $T_{B,\mathrm{max}}$ in the SN rest frame to be $t_\mathrm{exp} = -17.45 \pm ^{0.14}_{0.16}\,\textrm{d}$, where the uncertainties represent the 95\% confidence interval (Figure \ref{fig:velocity_t_exp}).
 Following the analysis in \citet{2014ApJ...784...85P}, we additionally alter the power-law index to $-0.20$ and $-0.24$ to examine the sensitivity of the result on the assumed power-law index.
 We find that this variation in the power-law index results in a change of $t_\mathrm{exp}$ of $\approx\pm$0.5\,d (Figure \ref{fig:velocity_t_exp}).
-Given the analytical approximation that $v \propto t^{-0.22}$, we adopt $t_{exp} = -17.5 \pm 0.5 \; \mathrm{d}$, where the uncertainty reflects possible variations in the power-lax index (see \citealt{2014ApJ...784...85P}).
-
-Comparing our estimates for $t_{exp}$ and $t_0$ (left panel of 
+Given the analytical approximation that $v \propto t^{-0.22}$, we adopt $t_\mathrm{exp} = -17.5 \pm 0.5 \; \mathrm{d}$, where the uncertainty reflects possible variations in the power-lax index (see \citealt{2014ApJ...784...85P}).
+
+Comparing our estimates for $t_\mathrm{exp}$ and $t_0$ (left panel of 
 Figure \ref{fig:velocity_t_exp}), we find that 
-$t_0\lesssim t_{exp}$.
-Since physical causality requires $t_{exp} \le t_0$, we draw the qualitative
-conclusion that $t_0\simeq t_{exp}$, which is consistent to within the uncertainties.
+$t_0\lesssim t_\mathrm{exp}$.
+Since physical causality requires $t_\mathrm{exp} \le t_0$, we draw the qualitative
+conclusion that $t_0\simeq t_\mathrm{exp}$, which is consistent to within the uncertainties.
 Again, we caution that this derivation of $t_\mathrm{exp}$ relies on the assumption $v \propto t^{-0.22}$, which may not be valid for all SNe Ia.
@@
 % time of explosion to \textit{B}-band maximum to be $17.95$ d.  In
-% comparison, SN2011fe has $t_0=-17.7$ d \citep{2013A&A...554A..27P}
+% comparison, SN2011fe has $t_0=-17.7$\,d \citep{2013A&A...554A..27P}
 % with a preceding dark phase of $\sim 1$ day
@@
   photosphere velocity in the $\sim$7~d after explosion (note that 
-  \ion{C}{2}\,$\lambda$7234 is not detected in the $-10.9$ d 
+  \ion{C}{2}\,$\lambda$7234 is not detected in the $-10.9$\,d 
   spectrum). The phase of each spectrum relative to 
@@
 
-Multiband observations of \abc\ began $\sim$1.5 d after discovery, which allows us to trace its color evolution starting $\sim$1.7 d after $t_0$.
+Multiband observations of \abc\ began $\sim$1.5\,d after discovery, which allows us to trace its color evolution starting $\sim$1.7\,d after $t_0$.
 In Figure~\ref{fig:B-Vcolors} we compare the $(B - V)_0$ color evolution of \abc\ and SN\,2011fe, where the observations of SN\,2011fe are taken from \citet{2016ApJ...820...67Z}.
 For both SNe the colors have been corrected for the total inferred reddening along the line of sight.
-Interestingly, \abc\ has a nearly flat color evolution up to 10 d before $T_{B,\mathrm{max}}$, while SN\,2011fe exhibits red colors initially before evolving to the blue.
+Interestingly, \abc\ has a nearly flat color evolution up to 10\,d before $T_{B,\mathrm{max}}$, while SN\,2011fe exhibits red colors initially before evolving to the blue.
 
@@
 
-Roughly 16 d prior to $B$-band maximum, the $(B - V)_0$ color of \abc\ is $\sim$0.5 mag bluer than SN\,2011fe.
+Roughly 16\,d prior to $B$-band maximum, the $(B - V)_0$ color of \abc\ is $\sim$0.5 mag bluer than SN\,2011fe.
 Like \abc, SN\,2012cg \citep{2016ApJ...820...92M} and SN\,2017cbv \citep{2017arXiv170608990H} exhibit $(B - V)_0$ colors that are significantly bluer than SN\,2011fe at very early epochs.
@@
 The minimum binary separation capable of explaining the observed brightness at the epoch of discovery is $a \approx 10^{11} \, \mathrm{cm}$.
-Figure~\ref{fig:SN-companion} shows that such models peak at $g_\mathrm{PTF} \approx 21.5 \, \mathrm{mag}$, provided that $t_\mathrm{exp} \approx t_0 - 0.3 \; \mathrm{d}$.
+Figure~\ref{fig:SN-companion} shows that such models peak at $g_\mathrm{PTF} \approx 21.5 \, \mathrm{mag}$, provided that $t_\mathrm{exp} \approx t_0 - 0.3 \, \mathrm{d}$.
 These models do not, however, match the $g_\mathrm{PTF}$ evolution for $t > t_0 + 0.5 \, \mathrm{d}$ (though it is possible that the SN photosphere dominates the companion-interaction signature at this phase).
@@
   \mathrm{cm}$ can explain the initial detection \abc, but they 
-  fail to replicate the $\sim$2 mag rise in the $\sim$24 hr after 
-  explosion.
+  fail to replicate the $\sim$2\,mag rise in the $\sim$24\,hr 
+  after explosion.
   }
@@
 
-The detonation of a WD with $M < 1.4 M_\odot$, which can occur if triggered by a detonation in a He surface layer that was accreted from a binary companion (known as the sub-Chandrasekhar double detonation), can produce a rapid rise and early blue optical colors (e.g., \citealt{2017arXiv170603613N}).
+The detonation of a WD with $M < 1.4 \, M_\odot$, which can occur if triggered by a He-surface-layer detonation (known as the sub-Chandrasekhar double detonation), can produce a rapid rise and early blue optical colors (e.g., \citealt{2017arXiv170603613N}).
 While this qualitative behavior matches \abc, the $U-V$ colors predicted in \citet{2017arXiv170603613N} do not match our observations.
@@
 As such we conclude that \abc\ is not the result of a sub-Chandrasekhar double detonation.
-\citet{2017arXiv170603613N} do note that their one-dimensional models may not capture the predicted asphericity for sub-Chandrasekhar double detonations, though moving away from the preferred viewing angle results in redder colors and a more gradual rise, which is not observed for \abc.
+\citet{2017arXiv170603613N} note that their one-dimensional models may not capture the predicted asphericity for sub-Chandrasekhar double detonations, though moving away from the preferred viewing angle results in redder colors and a more gradual rise, which is not observed for \abc.
 
@@
 
-When comparing observations of SN\,2011fe to their DD models, \citet{2014MNRAS.441..532D} find that the models are universally too faint and red at early times, $\sim$24-48 hr after explosion.
+When comparing observations of SN\,2011fe to their DD models, \citet{2014MNRAS.441..532D} find that the models are universally too faint and red at early times, $\sim$24--48\,hr after explosion.
 Instead, \citet{2014MNRAS.441..532D} find that PDD models provide a better match to observations.
-Briefly, the diffuse material surrounding the WD heats the outer layers of the SN ejecta leading to a steeper more luminous rise, with bluer colors in the few days after explosion.
+Briefly, the diffuse material surrounding the WD heats the outer layers of the SN ejecta leading to a steeper more luminous rise, with bluer colors.
 Importantly, the PDD models are nearly indistinguishable from DD models around and post peak.
@@
 In particular, the power-law index for the $g$-band rise is $\alpha \approx 3$ for each of the PDD models, which is significantly more steep than $\alpha = 0.98$, which we measure for \abc.
-The optical colors for \abc\ are blue from our first epoch $\sim$1.7 d after explosion and remain approximately constant in the 10 d after explosion, whereas the PDD models in \citet{2014MNRAS.441..532D} either exhibit distinct color evolution (i.e.\ are not constant) or are too red in the first few days after explosion.
+The optical colors for \abc\ are blue from our first epoch $\sim$1.7\,d after explosion and remain approximately constant in the 10\,d after explosion, whereas the PDD models in \citet{2014MNRAS.441..532D} either exhibit distinct color evolution (i.e.\ are not constant) or are too red in the first few days after explosion.
 Nevertheless, the PDD models presented in \citet{2014MNRAS.441..532D} provide several attractive explanations for the unusual features in the early behavior of \abc, and it may be possible that small adjustments to the model (e.g., additional mixing of the radioactive material, adjustments in the explosion energy, etc.) can better match \abc.
@@
 
-The proliferation of high-cadence, time-domain surveys has led to several SNe Ia being discovered within $\lesssim$2 d of first light in the past $\sim$decade.
+The proliferation of high-cadence, time-domain surveys has led to several SNe Ia being discovered within $\lesssim$2\,d of first light in the past $\sim$decade.
 Observations probing the early evolution of these SNe allows us to place unique constraints on their progenitor systems and the corresponding explosion physics.
@@
 In the case of SN\,2012cg and SN\,2017cbv it has been argued that the early blue optical colors are indicative of interaction between the SN ejecta and a binary companion \citep{2016ApJ...820...92M,2017arXiv170608990H}.
-SN\,2017cbv is particularly remarkable in that the observations presented in \citet{2017arXiv170608990H} show a clearly resolved bump in the $U$, $B$, and $g'$ bands in the $\sim$5 d after explosion.
+SN\,2017cbv is particularly remarkable in that the observations presented in \citet{2017arXiv170608990H} show a clearly resolved bump in the $U$, $B$, and $g'$ bands in the $\sim$5\,d after explosion.
 In \citeauthor{2017arXiv170608990H} it is found that the bump can be explained via the combination of ejecta-companion interaction and the normal evolution of a SN Ia.
@@
 
-    \item In contrast to SN\,2011fe, $(B - V)_0$ is $\sim$0.5 mag bluer for \abc\ $\sim$2 d after $t_0$.
-Furthermore, the $(B - V)_0$ colors of \abc\ show no evolution over the first $\sim$7 d  of observations.
+    \item In contrast to SN\,2011fe, $(B - V)_0$ is $\sim$0.5 mag bluer for \abc\ $\sim$2\,d after $t_0$.
+Furthermore, the $(B - V)_0$ colors of \abc\ show no evolution over the first $\sim$7\,d  of observations.
 

### 2017-10-26 doc/ms.tex
Reword abstract and include estimate of M_Ni from L_max

--- 2017-08-21 doc/ms.tex
@@
 
-\title{Early Observations of the Type Ia Supernova \abc:\\
-Evidence for Strong Ejecta Mixing and/or Interaction with Diffuse Material}
+\title{Early Observations of \abc:\\
+\textbf{a Type Ia Supernova Featuring Either} Strong Ejecta Mixing and/or Interaction with Diffuse Material}
 
@@
 
-Early observations of Type Ia supernovae (SNe) provide a unique probe of their progenitor systems and explosion physics.
-Here, we report the intermediate Palomar Transient Factory (iPTF) discovery of an extraordinarily young SN Ia, \abc.
-By fitting a power law to our early light curve, we infer that first light for the SN, that is when appreciable heating from $^{56}$Ni decay has first diffused to the photosphere, only occurred $0.15\pm_{0.07}^{0.15}$~d before our first detection.
-In the $\sim$24 hr after discovery, \abc\ rose by $\sim$2 mag, following a near-linear rise in flux for $\gtrsim$3 d.
-Strong \ion{C}{2} absorption is detected in the early spectra of \abc, before disappearing after $\sim$7~d.
-Unlike the extensively-observed Type Ia SN\,2011fe, the $(B-V)_0$ colors of \abc\ are blue and nearly constant in the days after explosion.
-We show that our early observations of \abc\ cannot be explained by either SN shock breakout and the associated, subsequent cooling, or the SN ejecta colliding with a stellar companion.
-Instead, we argue that the early characteristics of \abc, including: (i) the rapid, near-linear rise, (ii) the non-evolving blue colors, and (iii) the strong absorption from ionized carbon, are the result of either vigorous mixing of radioactive $^{56}$Ni in the SN ejecta, or ejecta interaction with diffuse material, or a combination of the two.
-In the next few years, dozens of very young \textit{normal} SNe Ia will be discovered, and observations similar to those presented here will constrain the white dwarf explosion mechanism.
+Early observations of Type Ia supernovae (SNe) provide a unique probe of their
+progenitor systems and explosion physics. Here, we report the intermediate
+Palomar Transient Factory (iPTF) discovery of an extraordinarily young SN Ia,
+\abc. By fitting a power law to our early light curve, we infer that first
+light for the SN, \textbf{that is when the SN produces appreciable optical
+radiation following shock breakout}, \textbf{occurred only}
+$0.15\pm_{0.07}^{0.15}$\,d before our first detection. In the $\sim$24\,hr
+after discovery, \abc\ rose by $\sim$2\,mag, \textbf{featuring} a near-linear
+rise in flux for $\gtrsim$3 d. \textbf{Early spectra show strong \ion{C}{2}
+absorption, which disappears after $\sim$7\,d.} Unlike the
+extensively-observed Type Ia SN\,2011fe, the $(B-V)_0$ colors of \abc\ are
+blue and nearly constant in the days after explosion. We show that our early
+observations of \abc\ cannot be explained by either SN shock breakout and the
+associated, subsequent cooling, or the SN ejecta colliding with a stellar
+companion. Instead, we argue that the early characteristics of \abc,
+including: (i) the rapid, near-linear rise, (ii) the non-evolving blue colors,
+and (iii) the strong absorption from ionized carbon, are the result of either
+vigorous mixing of radioactive $^{56}$Ni in the SN ejecta, or ejecta
+interaction with diffuse material, or a combination of the two. In the next
+few years, dozens of very young \textit{normal} SNe Ia will be discovered, and
+observations similar to those presented here will constrain the white dwarf
+explosion mechanism.
 
@@
   7,000$\,\textrm{\AA}$.  The phase of each spectrum 
-  relative to $T_{B_\mathrm{max}}$ is shown. Telluric absorption
+  relative to \textbf{the time of $B$-band maximum} is shown. Telluric absorption
   bands are grayed out. Line identifications are provided for 
@@
 \abc, we fit the P60 light curves with the \texttt{sncosmo} software package.\footnote{\texttt{sncosmo} is available at
-  \url{https://sncosmo.readthedocs.io}.} This fit includes a \texttt{SALT2} template \citep{2007A&A...466...11G} that has been corrected for extinction using the \citep{1999PASP..111...63F} reddening law, $R_V=3.1$, and $E(B-V) = 0.08 \; \mathrm{mag}$.
+  \url{https://sncosmo.readthedocs.io}.} This fit includes a \texttt{SALT2} template \citep{2007A&A...466...11G} that has been corrected for extinction using the \citet{1999PASP..111...63F} reddening law, $R_V=3.1$, and $E(B-V) = 0.08 \; \mathrm{mag}$.
 
 We determine the time of rest-frame \textit{B}-band maximum to be
- $\textrm{MJD}_\mathrm{max}=57499.54\pm0.23$, the coefficient
-of the zeroth principle component $x_0 = 0.0086 \pm 0.0003$, the
-coefficient of the first principle component $x_1 = 0.96 \pm 0.15$, 
-and the color term $c = 0.033 \pm 0.029$. The best-fit model also 
-gives an unreddened apparent peak magnitude of $m^*_{B}=15.80 \pm 
-0.04 \,\textrm{mag}$ in the SN rest frame.
-In the following sections, we define the best-fit value $\textrm{MJD}_\mathrm{max}=57499.54$ as the time of $B$-band maximum, $T_{B_\mathrm{max}}$, which we also define as phase $t=0$.
+$\textrm{MJD}_\mathrm{max}=57499.54\pm0.23$, the coefficient of the zeroth
+principle component $x_0 = 0.0086 \pm 0.0003$, the coefficient of the first
+principle component $x_1 = 0.96 \pm 0.15$, and the color term $c = 0.033 \pm
+0.029$. The best-fit model also gives an unreddened apparent peak magnitude of
+$m^*_{B}=15.80 \pm 0.04 \,\textrm{mag}$ in the SN rest frame. In the following
+sections, we define the best-fit value $\textrm{MJD}_\mathrm{max}=57499.54$ as
+the time of $B$-band maximum, $T_{B_\mathrm{max}}$, which we also define as
+phase $t=0$.
 
@@
 This value is consistent with the normal SNe Ia studied in  \citet{2016A&A...588A..84D}, a sample which excludes low-luminosity SNe.
+\textbf{Following Arnett's rule \citet{1982ApJ...253..785A, 1985Natur.314..337A}, it is possible to derive the mass of $^{56}$Ni synthesized in the explosion from $L_\mathrm{max}$.
+Assuming a rise time of $19 \pm 3$\,d (see \citealt{2006A&A...450..241S}) we find $M_\mathrm{Ni} = 0.6 \pm 0.1 M_\odot$.\footnote{Assuming a rise time of 17.9\,d, see \S\ref{sec:lc_fit} results in a consistent estimate of $M_\mathrm{Ni}$.}}
 
@@
 For both SNe the colors have been corrected for the total inferred reddening along the line of sight.
-Interestingly, \abc\ has a nearly flat color evolution up to 10 d before $T_{B,\mathrm{max}}$, while SN\,2011fe exhibits red colors initially before evolving to the blue.
+Interestingly, \abc\ has a nearly flat color evolution up to 10\,d before $T_{B,\mathrm{max}}$, while SN\,2011fe exhibits red colors initially before evolving to the blue.
 

### 2017-10-26 doc/ms.tex
Update text regarding power-law fit to observations

@@
 
-We measure the (pseudo)bolometric luminosity, $L_{UVOIR}$, of \abc\ at peak via trapezoidal integration of the reddening-corrected flux from the UV, optical, and NIR (UVOIR) filters.
-The light curves in the individual filters are interpolated so that $L_{UVOIR}$ is evaluated at common epochs in each filter.
-From this integration, we determine that \abc\ reaches a maximum luminosity $L_\mathrm{max} = 1.2 \pm 0.1 \times 10^{43} \; \mathrm{erg \; s}^{-1}$.
-This value is consistent with the normal SNe Ia studied in  \citet{2016A&A...588A..84D}, a sample which excludes low-luminosity SNe.
-\textbf{Following Arnett's rule \citet{1982ApJ...253..785A, 1985Natur.314..337A}, it is possible to derive the mass of $^{56}$Ni synthesized in the explosion from $L_\mathrm{max}$.
-Assuming a rise time of $19 \pm 3$\,d (see \citealt{2006A&A...450..241S}) we find $M_\mathrm{Ni} = 0.6 \pm 0.1 M_\odot$.\footnote{Assuming a rise time of 17.9\,d, see \S\ref{sec:lc_fit} results in a consistent estimate of $M_\mathrm{Ni}$.}}
-
-After establishing \abc\ as a normal SN Ia, we use the latest
-calibration \citep{2014A&A...568A..22B} of the Phillips relation
-\citep{1993ApJ...413L.105P} using $m^*_{B}$, $x_1$ and $c$ to derive a distance modulus $\mu = 34.89 \pm 0.10 \,\textrm{mag}$ to the SN, provided that the host galaxy of \abc\ has a stellar mass $< 10^{10}\sm$.
-A more massive host galaxy would result in a larger inferred distance modulus that is nevertheless consistent within the uncertainties.
-For the following analysis we adopt a distance modulus $\mu = 34.89 \pm 0.10 \,\textrm{mag}$ for \abc.\footnote{This $\mu$ is consistent with the $z_\mathrm{SN}$, $H_0 = 73 \, \mathrm{km \, s^{-1} \, Mpc}^{-1}$, and Virgo-infall-corrected distance \citep{2000ApJ...529..786M}.}
+We measure the (pseudo)bolometric luminosity, $L_{UVOIR}$, of \abc\ at peak
+via trapezoidal integration of the reddening-corrected flux from the UV,
+optical, and NIR (UVOIR) filters. The light curves in the individual filters
+are interpolated so that $L_{UVOIR}$ is evaluated at common epochs in each
+filter. From this integration, we determine that \abc\ reaches a maximum
+luminosity $L_\mathrm{max} = 1.2 \pm 0.1 \times 10^{43} \; \mathrm{erg \;
+s}^{-1}$. This value is consistent with the normal SNe Ia studied in
+\citet{2016A&A...588A..84D}, a sample which excludes low-luminosity SNe.
+\textbf{Following Arnett's rule \citet{1982ApJ...253..785A,
+1985Natur.314..337A}, it is possible to derive the mass of $^{56}$Ni
+synthesized in the explosion from $L_\mathrm{max}$. Assuming a rise time of
+$19 \pm 3$\,d (see \citealt{2006A&A...450..241S}) we find $M_\mathrm{Ni} = 0.6
+\pm 0.1 M_\odot$.\footnote{Assuming a rise time of 17.9\,d, see
+\S\ref{sec:lc_fit} results in a consistent estimate of $M_\mathrm{Ni}$.}}
+
+After establishing \abc\ as a normal SN Ia, we use the latest calibration
+\citep{2014A&A...568A..22B} of the Phillips relation
+\citep{1993ApJ...413L.105P} using $m^*_{B}$, $x_1$ and $c$ to derive a
+distance modulus $\mu = 34.89 \pm 0.10 \,\textrm{mag}$ to the SN, provided
+that the host galaxy of \abc\ has a stellar mass $< 10^{10}\sm$. A more
+massive host galaxy would result in a larger inferred distance modulus that is
+nevertheless consistent within the uncertainties. For the following analysis
+we adopt a distance modulus $\mu = 34.89 \pm 0.10 \,\textrm{mag}$ for
+\abc.\footnote{This $\mu$ is consistent with the $z_\mathrm{SN}$, $H_0 = 73 \,
+\mathrm{km \, s^{-1} \, Mpc}^{-1}$, and Virgo-infall-corrected distance
+\citep{2000ApJ...529..786M}.}
 
@@
 
-Here we consider our suite of early observations of \abc, and compare our findings with SN\,2011fe, a well-studied, nearby SN that was discovered shortly after explosion \citep{2011Natur.480..344N,2012ApJ...744L..17B,2014ApJ...784...85P}.
+Here we consider our suite of early observations of \abc, and compare our
+findings with SN\,2011fe, a well-studied, nearby SN that was discovered
+shortly after explosion
+\citep{2011Natur.480..344N,2012ApJ...744L..17B,2014ApJ...784...85P}.
 
@@
 
-The time of first light, interpreted in this study as the moment when appreciable heating from $^{56}$Ni decay has first diffused to the photosphere, for SNe is usually estimated by 
-extrapolating early-phase light curves to determine when the 
-SN flux is equal to 0. Assuming an ideal, expanding fireball with 
-constant temperature, \citet{1982ApJ...253..785A} derives that $f 
-\propto t^2$, where $f$ is the SN flux and $t$ is the time since 
-explosion. Despite the basic assumption of a constant temperature at 
-early times, multiple studies have found that the early emission 
-from Type Ia SNe can be described as a power law in time, with 
-power-law index consistent with 2, i.e.
-$f \propto t^2$ (e.g., \citealt{2006AJ....132.1707C, 2010ApJ...712..350H, 2011MNRAS.416.2607G}).\footnote{Many of the studies that find $f \propto t^2$ sample SNe Ia light curves at a phase that is closer to $T_{B,\mathrm{max}}$ than the initial observations of \abc\ discussed here.}
-
-As our observations include especially early observations of \abc, there are upper limits $\sim$1 d prior to the discovery epoch, we model the early flux from \abc\ as a power law, but allow the power-law index to vary, as opposed to fixing it at 2, to account for potential variations in the photospheric temperature during expansion:
+The time of first light for SNe is usually estimated by extrapolating
+early-phase light curves to determine when the SN flux is equal to 0.
+Assuming an ideal, expanding fireball with constant temperature,
+\citet{1982ApJ...253..785A} derives that $f \propto t^2$, where $f$ is the SN
+flux and $t$ is the time since explosion. Despite the basic assumption of a
+constant temperature at early times, multiple studies have found that the
+early emission from Type Ia SNe can be described as a power law in time, with
+power-law index consistent with 2, i.e. $f \propto t^2$ (e.g.,
+\citealt{2006AJ....132.1707C, 2010ApJ...712..350H,
+2011MNRAS.416.2607G}).\footnote{Many of the studies that find $f \propto t^2$
+sample SNe Ia light curves at a phase that is closer to $T_{B,\mathrm{max}}$
+than the initial observations of \abc\ discussed here.}
+
+As our observations include especially early observations of \abc, there are
+upper limits $\sim$1 d prior to the discovery epoch, we model the early flux
+from \abc\ as a power law, but allow the power-law index to vary:
 \begin{equation}
@@
 \end{equation}
-where $t_0$ is the time of first light, $\alpha$ is the power-law index, and $t$ is measured in the SN rest-frame.
-To determine $t_0$ and $\alpha$ we fit the earliest observations of \abc.
-Due to slight variations in the passbands, we fit the model only to the relative flux measured in the $g_\mathrm{PTF}$-band, which is the only filter with observations prior to first light, a necessity for constraining $t_0$.
-
-To determine the best fit parameters, we search a large grid over $t_0$, $\alpha$,
-and the proportionality constant, and minimize $\chi^2$. 
-The modeling results show that the SN flux rises approximately
-linearly between
-$t=-18\,\textrm{d}$ and $t=-15\,\textrm{d}$. Figure \ref{fig:early_lc_fit} shows the best-fit result and
-the joint marginal distribution of $t_0$ and $\alpha$. From the
-best-fit model we obtain $\alpha=0.98 \pm ^{0.16}_{0.14}$ and $t_0=-17.91 \pm ^{0.07}_{0.15}$ d, where the uncertainties represent the marginalized 95\% confidence intervals. Our first
-detection of \abc\ occurred $\sim$${0.15}\,\textrm{d}$ after 
-the SN first light. 
-% Figure~\ref{fig:early_lc_fit} additionally shows $g'$-bands observations from P60 and LCO, where we have normalized the flux assuming that the $g$ magnitudes from each instrument have the same zero-point.
-This assumption is incorrect (see \S\ref{sec:obs}), and, as expected, the residuals show a systematic offset between the $g_\mathrm{PTF}$-band and the $g'$-band.
-Nevertheless, if we ignore this systematic and fit all of the $g$-band observations simultaneously we obtain marginalized best-fit parameters that are consistent within the uncertainties with the $g_\mathrm{PTF}$-only values above.
-In the analysis that follows, the precise values of the best-fit parameters are not important. The critical finding here is that $\alpha \approx 1$ and $t_0 \approx -18 \, \mathrm{d}$.
-
-Figure \ref{fig:early_lc_fit} also shows the best-fit model while fixing $\alpha = 2$.
-The $f \propto t^2$ model does not match the observations.
-Formally, for the $\alpha = 2$ model $\chi^2 = 63.7$ with $\nu = 15$ degrees of freedom (dof), while $\chi^2 = 10.2$ with $\nu = 14$ dof for the $\alpha = 0.98$ model.
-
-As previously noted, a precise determination of the rise time, $t_\mathrm{rise}$, of SNe Ia is challenging as there may be a dark phase following explosion \citep{2014ApJ...784...85P}.
-Nevertheless, to be consistent with previous studies (e.g., \citealt{2011MNRAS.416.2607G}), here we find $t_\mathrm{rise} = 17.91\pm _{0.07}^{0.15}$ d based on our fit for $t_0$.
-We caution that this measurement may be underestimated due to the uncertain time of explosion.
+where $t_0$ is the time of first light, $\alpha$ is the power-law index, and
+$t$ is measured in the SN rest-frame. \textbf{We allow $\alpha$ to vary to
+find the best match to the data, and later show that models with $\alpha = 2$
+do not explain the data.} To determine $t_0$ and $\alpha$ we fit the earliest
+observations of \abc. Due to slight variations in the passbands, we fit the
+model only to the relative flux measured in the $g_\mathrm{PTF}$-band, which
+is the only filter with observations prior to first light, a necessity for
+constraining $t_0$.
+
+To determine the best fit parameters, we search a large grid over $t_0$,
+$\alpha$, and the proportionality constant, and minimize $\chi^2$. The
+modeling results show that the SN flux rises approximately linearly between
+$t=-18\,\textrm{d}$ and $t=-15\,\textrm{d}$. Figure \ref{fig:early_lc_fit}
+shows the best-fit result and the joint marginal distribution of $t_0$ and
+$\alpha$. From the best-fit model we obtain $\alpha=0.98 \pm ^{0.16}_{0.14}$
+and $t_0=-17.91 \pm ^{0.07}_{0.15}$ d, where the uncertainties represent the
+marginalized 95\% confidence intervals. Our first detection of \abc\ occurred
+$\sim$${0.15}\,\textrm{d}$ after the SN first light. In the analysis that
+follows, the precise values of the best-fit parameters are not important. The
+critical finding here is that $\alpha \approx 1$ and $t_0 \approx -18 \,
+\mathrm{d}$.
+
+Figure \ref{fig:early_lc_fit} also shows the best-fit model while fixing
+$\alpha = 2$. The $f \propto t^2$ model does not match the observations.
+Formally, for the $\alpha = 2$ model $\chi^2 = 63.7$ with $\nu = 15$ degrees
+of freedom (dof), while $\chi^2 = 10.2$ with $\nu = 14$ dof for the $\alpha =
+0.98$ model.
+
+As previously noted, a precise determination of the rise time,
+$t_\mathrm{rise}$, of SNe Ia is challenging as there may be a dark phase
+following explosion \citep{2014ApJ...784...85P}. Nevertheless, to be
+consistent with previous studies (e.g., \citealt{2011MNRAS.416.2607G}), here
+we find $t_\mathrm{rise} = 17.91\pm _{0.07}^{0.15}$ d based on our fit for
+$t_0$. We caution that this measurement may be underestimated due to the
+uncertain time of explosion.
 
@@
 
-Simulations presented in \citet{2017arXiv170603613N} show that the flux from SNe Ia explosion models does not evolve as a power law in time.
-Despite this non-power-law evolution, \citet{2017arXiv170603613N} show that $f \propto t^\alpha$ models produce good formal fits to simulated observations.
-The $f \propto t^\alpha$ fits to the \citeauthor{2017arXiv170603613N} models result in glaring errors to the estimated explosion times.
-Despite the caution advised in \citet{2017arXiv170603613N}, we proceed with the power-law fits from above for several reasons.
-(1) Our primary aim with the fit is to characterize $\alpha$ for \abc\ compared to SN\,2011fe (see below).
-(2) The errors in the estimated explosion times from \citeauthor{2017arXiv170603613N} increase the later the first observation of the SN is obtained.
-\citeauthor{2017arXiv170603613N} only present fits to observations that start $>$2~d after explosion, whereas the discovery epoch for \abc\ is likely much earlier than that (see \S\ref{sec:early_vel}).
-(3) We do not use the fits to estimate the time of explosion, $t_0$ instead is an estimate of the time of first light.
-(4) Pre-discovery upper limits, which are not included in \citeauthor{2017arXiv170603613N}, provide additional strong constraints on the time of first light.
-Finally, (5) \citet{2017arXiv170603613N} find that models with strong $^{56}$Ni mixing do follow a power-law evolution, and we explore, and argue in favor of, this possibility for \abc\ (see \S\ref{sec:Ni_mixing}).
-
-Unlike \abc, the early emission from SN\,2011fe is well fit by a $f \propto t^2$ model \citep{2011Natur.480..344N}.
-Thus, the near-linear rise in flux over the first few days after first light for \abc\ is distinct compared to SN\,2011fe.
-To our knowledge this behavior has only been observed in 2 other SNe (2013dy, 2014J; \citealt{2013ApJ...778L..15Z,2014ApJ...783L..24Z,2015ApJ...799..106G}).
-Any model to explain the observations of \abc\ must account for this near-linear rise in the days after first light.
+Simulations presented in \citet{2017arXiv170603613N} show that the flux from
+SNe Ia explosion models does not evolve as a power law in time. Despite this
+non-power-law evolution, \citet{2017arXiv170603613N} show that $f \propto
+t^\alpha$ models produce good formal fits to simulated observations. The $f
+\propto t^\alpha$ fits to the \citeauthor{2017arXiv170603613N}\ models result
+in glaring errors to the estimated explosion times. Despite the caution
+advised in \citet{2017arXiv170603613N}, we proceed with the power-law fits
+from above for several reasons. (1) Our primary aim with the fit is to
+characterize $\alpha$ for \abc\ compared to SN\,2011fe (see below). (2) The
+errors in the estimated explosion times from \citeauthor{2017arXiv170603613N}
+increase the later the first observation of the SN is obtained.
+\citeauthor{2017arXiv170603613N} only present fits to observations that start
+$>$2\,d after explosion, whereas the discovery epoch for \abc\ is likely much
+earlier than that (see \S\ref{sec:early_vel}). (3) We do not use the fits to
+estimate the time of explosion, $t_0$ instead is an estimate of the time of
+first light. \textbf{Finally,} (4) Pre-discovery upper limits, which are not
+included in \citeauthor{2017arXiv170603613N}, provide additional strong
+constraints on the time of first light.
+
+Unlike \abc, the early emission from SN\,2011fe is well fit by a $f \propto
+t^2$ model \citep{2011Natur.480..344N}. Thus, the near-linear rise in flux
+over the first few days after first light for \abc\ is distinct compared to
+SN\,2011fe. To our knowledge this behavior has only been observed in 2 other
+SNe (2013dy, 2014J;
+\citealt{2013ApJ...778L..15Z,2014ApJ...783L..24Z,2015ApJ...799..106G}). Any
+model to explain the observations of \abc\ must account for this near-linear
+rise in the days after first light.
 

### 2017-10-26 doc/ms.tex
Remove a few sentences following (reasonable) objections from the referee

@@
 and $t_0=-17.91 \pm ^{0.07}_{0.15}$ d, where the uncertainties represent the
-marginalized 95\% confidence intervals. Our first detection of \abc\ occurred
+marginalized 95\% confidence intervals \textit{THIS IS NOT THE CORRECT MARGINALIZED UNCERTAINTY}. Our first detection of \abc\ occurred
 $\sim$${0.15}\,\textrm{d}$ after the SN first light. In the analysis that
@@
 While most SNe Ia are powered purely by radioactive decay, the observed radiation shortly after explosion can also include contributions
-from SN shock cooling or the collision of the SN ejecta with a non-degenerate companion or diffuse material. Here we consider those scenarios as a possible explanation for the early behavior of \abc.
+from SN shock cooling or the collision of the SN ejecta with a non-degenerate companion or \textbf{nearby, unbound} material.
+Here we consider those scenarios as a possible explanation for the early behavior of \abc.
 
@@
 
-\subsection{Interaction with Diffuse Material}
+\subsection{Interaction with \textbf{Nearby, Unbound} Material}
 
@@
 
-Having examined other possibilities we now consider whether the unusual properties of \abc\ can be explained simply by invoking strong mixing in the SN ejecta.
-Strong mixing leads to a shorter dark phase than would otherwise be observed.
-Here we additionally examine whether strong mixing can explain the rapid, near-linear rise in the light curve.
-
-In Figure~\ref{fig:Ni56LC} we compare model calculations from \citet{2016ApJ...826...96P} to the observed photometry of \abc.
-The \citeauthor{2016ApJ...826...96P} models employ a piston driven explosion to explode a single WD progenitor model.
-As the piston explosion does not result in any nucleosynthesis, the distribution of $^{56}$Ni in the ejecta must be prescribed by hand, which enables a study of the effects of mixing on the resulting SN emission.
-Each model employs a fixed $0.5\,\sm$ of $^{56}$Ni that has been distributed throughout the ejecta via boxcar averaging (see their Figure~1).
-The resulting light curves are synthesized using the SuperNova Explosion Code (\texttt{SNEC}; \citealt{2015ApJ...814...63M}), as shown in Figure~\ref{fig:Ni56LC}.
-Broadly speaking, the results can be summarized as follows: SN with strong mixing exhibit a rapid almost linear rise and quickly develop blue colors, whereas models where the $^{56}$Ni is confined to the innermost layers of the ejecta remain very faint for days after explosion while exhibiting relatively red optical colors during this period.
-The fast rise and blue color of \abc\ are qualitatively consistent with the strong mixing models from \citet{2016ApJ...826...96P}, as shown in Figure~\ref{fig:Ni56LC}.
-In fact, if we adopt $t_\mathrm{exp} = t_0 - 0.4 \, \mathrm{d}$, we find that the model with the strongest mixing (orange line in Figure~\ref{fig:Ni56LC}) provides an excellent match to the $g$-band observations.
-
-While the models from \citet{2016ApJ...826...96P} provide a good match to the optical photometric evolution of \abc, they consistently overpredict the flux in the UV.
-The models shown in Figure~\ref{fig:Ni56LC} also overpredict the photospheric velocity of \abc\ by $\sim$2--3,000$\; \mathrm{km \; s}^{-1}$.
-These discrepancies may be accounted for following an improved treatment of line-blanketing and a reduction in the model explosion energy, respectively.
-Future modeling efforts may improve the match between the simulations and observations for \abc.
-
-Both the PDD models and ejecta-mixing models show discrepancies with some early observations of \abc.
-Nevertheless, we conclude that one, or both, of these scenarios, which feature qualitatively similar predictions, is the most likely explanation for \abc.
-Indeed, it may be the case that the typical sequence of photometric and spectroscopic observations of young SNe Ia can never distinguish between these two possibilities \citep{2017arXiv170603613N}.
+Having examined other possibilities we now consider whether the unusual
+properties of \abc\ can be explained simply by invoking strong mixing in the
+SN ejecta. Strong mixing leads to a shorter dark phase than would otherwise
+be observed. \textbf{We also consider} whether strong mixing can explain the
+rapid, near-linear rise in the light curve.
 
@@
 
+In Figure~\ref{fig:Ni56LC} we compare model calculations from
+\citet{2016ApJ...826...96P} to the observed photometry of \abc. The
+\citeauthor{2016ApJ...826...96P} models employ a piston driven explosion to
+explode a single WD progenitor model. As the piston explosion does not result
+in any nucleosynthesis, the distribution of $^{56}$Ni in the ejecta must be
+prescribed by hand, which enables a study of the effects of mixing on the
+resulting SN emission. Each model employs a fixed $0.5\,\sm$ of $^{56}$Ni
+that has been distributed throughout the ejecta via boxcar averaging (see
+their Figure~1). The resulting light curves are synthesized using the
+SuperNova Explosion Code (\texttt{SNEC}; \citealt{2015ApJ...814...63M}), as
+shown in Figure~\ref{fig:Ni56LC}. Broadly speaking, the results can be
+summarized as follows: SN with strong mixing exhibit a rapid almost linear
+rise and quickly develop blue colors, whereas models where the $^{56}$Ni is
+confined to the innermost layers of the ejecta remain very faint for days
+after explosion while exhibiting relatively red optical colors during this
+period. The fast rise and blue color of \abc\ are qualitatively consistent
+with the strong mixing models from \citet{2016ApJ...826...96P}, as shown in
+Figure~\ref{fig:Ni56LC}. In fact, if we adopt $t_\mathrm{exp} = t_0 - 0.4 \,
+\mathrm{d}$, we find that the model with the strongest mixing (orange line in
+Figure~\ref{fig:Ni56LC}) provides an excellent match to the $g$-band
+observations.
+
+While the models from \citet{2016ApJ...826...96P} provide a good match to the
+optical photometric evolution of \abc, they consistently overpredict the flux
+in the UV. The models shown in Figure~\ref{fig:Ni56LC} also overpredict the
+photospheric velocity of \abc\ by $\sim$2--3,000$\; \mathrm{km \; s}^{-1}$.
+Future modeling efforts may improve the match between the simulations and
+observations for \abc.
+
+Both the PDD models and ejecta-mixing models show discrepancies with some
+early observations of \abc. Nevertheless, we conclude that one, or both, of
+these scenarios, which feature qualitatively similar predictions, is the most
+likely explanation for \abc. Indeed, it may be the case that the typical
+sequence of photometric and spectroscopic observations of young SNe Ia can
+never distinguish between these two possibilities \citep{2017arXiv170603613N}.
+
 \subsection{The Emerging Sample of Young SNe Ia}

### 2017-10-30 doc/ms.tex

@@
 from \abc\ as a power law, but allow the power-law index to vary:
+
 \begin{equation}

### 2017-10-30 doc/ms.tex
add text to describe velocity evolution relative to Branch SNe sample

@@
 
-Using the SuperNova IDentification (\texttt{SNID}; \citealt{2007ApJ...666.1024B}) package, 
-we find the low-resolution spectrum of \abc\ at $+18.8$\,d is best matched by normal SNe Ia. Several characteristic features of a SN
-Ia, such as \ion{Si}{2}, \ion{S}{2}, can be easily identified in the spectra of \abc\ (Figure \ref{fig:spec_seq}).
-From the $+3.7 \, \mathrm{d}$ LCO spectrum, we measure the pseudo-equivalent widths (pEWs) of the absorption features near 5750 and 6100 \AA, which are respectively attributed to \ion{Si}{2}\,$\lambda\lambda$6580, 7234, to be $-12 \pm 2$\,\AA\ and $-55 \pm 5$\,\AA, respectively.
-According to the classification scheme presented in \citet{2009PASP..121..238B}, these pEW measurements indicate that \abc\ is a shallow silicon SN, similar to the SN\,1999aa-likes.
+Using the SuperNova IDentification (\texttt{SNID};
+\citealt{2007ApJ...666.1024B}) package, we find the low-resolution spectrum of
+\abc\ at $+18.8$\,d is best matched by normal SNe Ia. Several characteristic
+features of a SN Ia, such as \ion{Si}{2}, \ion{S}{2}, can be easily identified
+in the spectra of \abc\ (Figure \ref{fig:spec_seq}). From the $+3.7 \,
+\mathrm{d}$ LCO spectrum, we measure the pseudo-equivalent widths (pEWs) of
+the absorption features near 5750 and 6100 \AA, which are respectively
+attributed to \ion{Si}{2}\,$\lambda\lambda$6580, 7234, to be $-12 \pm 2$\,\AA\
+and $-55 \pm 5$\,\AA, respectively. According to the classification scheme
+presented in \citet{2006PASP..118..560B}, these pEW measurements indicate that
+\abc\ is a shallow silicon SN, similar to the SN\,1999aa-likes
+\citep{2009PASP..121..238B}. \textbf{In Figure~\ref{fig:branch_vel}, the
+velocity evolution of \ion{Si}{2}$\,\lambda6355$ in \abc\ is compared to the
+median evolution of the four spectroscopic subclasses defined in
+\citet{2006PASP..118..560B}. The median evolution is defined using the sample
+of SNe Ia in \citet{2012AJ....143..126B}. For each SN, we interpolate the
+\ion{Si}{2} velocity, $v_{\ion{Si}{2}\,\lambda6355}$, to a fixed grid at 1\,d
+intervals. We then take the median $v_{\ion{Si}{2}\,\lambda6355}$ for each
+point on the grid, and only retain those points with at least 3 SNe (to
+prevent the early and late evolution to be defined by a single SN). The
+evolution of \ion{Si}{2} is most reminicent of the shallow-silicon subclass
+defined in \citet{2006PASP..118..560B}.}
+
+\begin{figure}[htb]
+  \centering
+  \includegraphics[width=0.48\textwidth]{Branch_vel_evol.pdf}
+  \caption{\textbf{Velocity evolution of \ion{Si}{2},   
+           $v_{\ion{Si}{2}\,\lambda6355}$, for \abc\ compared to the median 
+           evolution of the four spectroscopic subclasses defined in 
+           \citet{2006PASP..118..560B}, using data from 
+           \citet{2012AJ....143..126B}. Typical uncertainties for \abc\ are 
+           $\sim$1000\,km\,s$^{-1}$ before $T_{B,\mathrm{max}}$, when the 
+           \ion{Si}{2}$\,\lambda6355}$ profile is shallow and the minimum of 
+           absorption is difficult to determine, and $\sim$300\,km\,s$^{-1}$ 
+           after $T_{B,\mathrm{max}}$. For the median curves, the typical 
+           scatter, determined via the interquartile range of the sample, is 
+           XXX $\sim$200\,km\,s$^{-1}$ XXX, around $T_{B,\mathrm{max}}$.
+           At early times, core-normal and broad-line SNe have significantly 
+           faster \ion{Si}{2} than \abc, while the declining trend of cool SNe 
+           does not match \abc.}
+  }
+  \label{fig:branch_vel}
+\end{figure}
 

### 2017-10-30 doc/ms.tex
fix typo in latex math mode

@@
 of SNe Ia in \citet{2012AJ....143..126B}. For each SN, we interpolate the
-\ion{Si}{2} velocity, $v_{\ion{Si}{2}\,\lambda6355}$, to a fixed grid at 1\,d
-intervals. We then take the median $v_{\ion{Si}{2}\,\lambda6355}$ for each
-point on the grid, and only retain those points with at least 3 SNe (to
+\ion{Si}{2} velocity, $v_{\mathrm{Si\,II}\,\lambda6355}$, to a fixed grid at
+1\,d intervals. We then take the median $v_{\mathrm{Si\,II}\,\lambda6355}$ for
+each point on the grid, and only retain those points with at least 3 SNe (to
 prevent the early and late evolution to be defined by a single SN). The
 evolution of \ion{Si}{2} is most reminicent of the shallow-silicon subclass
-defined in \citet{2006PASP..118..560B}.}
+defined in \citet{2006PASP..118..560B}. }
 
@@
   \caption{\textbf{Velocity evolution of \ion{Si}{2},   
-           $v_{\ion{Si}{2}\,\lambda6355}$, for \abc\ compared to the median 
+           $v_{\mathrm{Is\,II}\,\lambda6355}$, for \abc\ compared to the median
            evolution of the four spectroscopic subclasses defined in
@@
            $\sim$1000\,km\,s$^{-1}$ before $T_{B,\mathrm{max}}$, when the
-           \ion{Si}{2}$\,\lambda6355}$ profile is shallow and the minimum of 
+           \ion{Si}{2}$\,\lambda6355$ profile is shallow and the minimum of
            absorption is difficult to determine, and $\sim$300\,km\,s$^{-1}$
@@
            At early times, core-normal and broad-line SNe have significantly
-           faster \ion{Si}{2} than \abc, while the declining trend of cool SNe 
+           faster \ion{Si}{2} than \abc, while the declining trend of coolSNe
            does not match \abc.}

### 2017-10-30 doc/ms.tex
Update uncertainty estimates on median light curves

@@
            scatter, determined via the interquartile range of the sample, is
-           XXX $\sim$200\,km\,s$^{-1}$ XXX, around $T_{B,\mathrm{max}}$.
+           $\sim$700\,km\,s$^{-1}$, around $T_{B,\mathrm{max}}$.
            At early times, core-normal and broad-line SNe have significantly
@@
 and $t_0=-17.91 \pm ^{0.07}_{0.15}$ d, where the uncertainties represent the
-marginalized 95\% confidence intervals \textit{THIS IS NOT THE CORRECT MARGINALIZED UNCERTAINTY}. Our first detection of \abc\ occurred
+marginalized 95\% confidence intervals. Our first detection of \abc\ occurred
 $\sim$${0.15}\,\textrm{d}$ after the SN first light. In the analysis that

### 2017-11-15 doc/ms.tex
update text about dessart PDD models and add Dessart figure to manuscript

@@
 
-To model SN\,2011fe, \citet{2014MNRAS.441..532D} recently examined pulsational delayed-detonation (PDD) models as an explanation for some SNe Ia.
-Briefly, PDD models differ from ``standard'' delayed detonation (DD) models in that the expansion of the WD during the initial deflagration phase leads to the release of unbound material.
-Following this pulsation, the bound material contracts eventually triggering a subsequent detonation.\footnote{\citet{2014MNRAS.441..532D} note that the deflagration and detonation in their PDD models are artificially triggered.} An important consequence of this progression for PDD models is that the unbound material expands and avoids burning, unlike DD models that typically leave no unburnt material.
-This results in significantly more carbon in the outer layers of the SN ejecta \citep{2014MNRAS.441..532D}.
-
-When comparing observations of SN\,2011fe to their DD models, \citet{2014MNRAS.441..532D} find that the models are universally too faint and red at early times, $\sim$24--48\,hr after explosion.
-Instead, \citet{2014MNRAS.441..532D} find that PDD models provide a better match to observations.
-Briefly, the diffuse material surrounding the WD heats the outer layers of the SN ejecta leading to a steeper more luminous rise, with bluer colors.
-Importantly, the PDD models are nearly indistinguishable from DD models around and post peak.
+To model SN\,2011fe, \citet{2014MNRAS.441..532D} recently examined
+pulsational delayed-detonation (PDD) models as an explanation for some SNe
+Ia. Briefly, PDD models differ from ``standard'' delayed detonation (DD)
+models in that the expansion of the WD during the initial deflagration
+phase leads to the release of unbound material. Following this pulsation,
+the bound material contracts eventually triggering a subsequent
+detonation.\footnote{\citet{2014MNRAS.441..532D} note that the deflagration
+and detonation in their PDD models are artificially triggered.} An
+important consequence of this progression for PDD models is that the
+unbound material expands and avoids burning, unlike DD models that
+typically leave no unburnt material. This results in significantly more
+carbon in the outer layers of the SN ejecta \citep{2014MNRAS.441..532D}.
+
+\textbf{\citet{2014MNRAS.441..532D} find that DD models are universally faint and red at early times, $\sim$24--48\,hr after explosion, while the PDD models exhibit a faster rise and bluer colors.
+Briefly, this occurs in the PDD scenario because the collision with the unbound material surrounding the WD heats the outer layers of the SN ejecta.
+Importantly, the PDD models are nearly indistinguishable from DD models around and post peak.}
+
+\begin{figure}[]
+  \centering
+  \includegraphics[width=0.48\textwidth]{compare_Dessart.pdf}
+  \caption{
+  }
+  \label{fig:dessart}
+\end{figure}
+
+\textbf{In Figure~\ref{fig:dessart} we compare photometric observations of \abc\ to the DD and PDD models presented in \citet{2014MNRAS.441..532D}.}
 

### 2017-11-15 doc/ms.tex
udpate discussion of Dessart models in text

@@
 
-\textbf{In Figure~\ref{fig:dessart} we compare photometric observations of \abc\ to the DD and PDD models presented in \citet{2014MNRAS.441..532D}.}
-
-Qualitatively, the PDD models provide a better match to the observations of \abc\ than DD models.
-In particular, PDD models provide higher luminosities and faster rise times in the days after explosion, a more rapid evolution towards blue optical colors, and the formation of strong \ion{C}{2} lines that gradually disappear in the $\sim$week after explosion.
-Quantitatively, there are still some short comings of the models presented in \citet{2014MNRAS.441..532D}.
-In particular, the power-law index for the $g$-band rise is $\alpha \approx 3$ for each of the PDD models, which is significantly more steep than $\alpha = 0.98$, which we measure for \abc.
-The optical colors for \abc\ are blue from our first epoch $\sim$1.7\,d after explosion and remain approximately constant in the 10\,d after explosion, whereas the PDD models in \citet{2014MNRAS.441..532D} either exhibit distinct color evolution (i.e.\ are not constant) or are too red in the first few days after explosion.
-Nevertheless, the PDD models presented in \citet{2014MNRAS.441..532D} provide several attractive explanations for the unusual features in the early behavior of \abc, and it may be possible that small adjustments to the model (e.g., additional mixing of the radioactive material, adjustments in the explosion energy, etc.) can better match \abc.
+\textbf{In Figure~\ref{fig:dessart} we compare photometric
+observations of \abc\ to the large-$^{56}$Ni yield DD and PDD
+models presented in \citet{2014MNRAS.441..532D}. DD and PDD models
+with $M_\mathrm{Ni}/M_\odot \la 0.7$ and 0.5, respectively, fail to
+match the early luminosity and blue colors of \abc. The PDD models
+provide a better match to the observations than the DD models. The
+PDD models evolve more rapidly towards blue colors and provide a
+better match to the $g$-band flux in the days after explosion.
+Furthermore, unlike the DD models, the PDD models exhibit strong
+\ion{C}{2} lines that gradually disappear in the $\sim$week after
+explosion \citet{2014MNRAS.441..532D}. In detail, the early wiggles
+in the \abc\ light curve are not matched by the PDD models, which
+exhibit more smooth variations. Nevertheless, the PDD models
+presented in \citet{2014MNRAS.441..532D} provide several attractive
+explanations for the unusual features in the early behavior of
+\abc, and small adjustments to the model (e.g., additional mixing
+of the radioactive material, which \citeauthor{2014MNRAS.441..532D}
+only explore for the DD model) may better match \abc. }
 

### 2017-11-15 doc/ms.tex
Add caption for the dessart figure

@@
   \includegraphics[width=0.48\textwidth]{compare_Dessart.pdf}
-  \caption{
+  \caption{ \textbf{Comparison of the DD and PDD models of
+  \citet{2014MNRAS.441..532D} to the \abc\ $g$-band light curve
+  (top) and the $(B-V)_0$ color curve. We have translated each
+  light curve to match the LCO observations $\sim$1.7\,d after
+  $t_0$ given the uncertain time of explosion. Translational
+  offsets are listed in the bottom panel legend, which shows the
+  models in order of decreasing $M_\mathrm{Ni}$ from top to bottom.
+  DD models (labeled as DDC to match the nomenclature of
+  \citealt{2014MNRAS.441..532D}) are shown as dash-dot lines, while
+  PDD models (labeled as PDDEL) are shown as dashed lines. The PDD
+  models provide a better match to the observations.}
   }
@@
 in the \abc\ light curve are not matched by the PDD models, which
-exhibit more smooth variations. Nevertheless, the PDD models
-presented in \citet{2014MNRAS.441..532D} provide several attractive
-explanations for the unusual features in the early behavior of
-\abc, and small adjustments to the model (e.g., additional mixing
-of the radioactive material, which \citeauthor{2014MNRAS.441..532D}
-only explore for the DD model) may better match \abc. }
+exhibit more smooth variations. Furthermore, while the focus of
+this study is the early evolution of \abc, the PDD models evolve
+more rapidly to the red post-peak than the observations.
+Nevertheless, the PDD models presented in
+\citet{2014MNRAS.441..532D} provide several attractive explanations
+for the unusual features in the early behavior of \abc, and small
+adjustments to the model (e.g., additional mixing of the
+radioactive material, which \citeauthor{2014MNRAS.441..532D} only
+explore for the DD model) may better match \abc. }
 

### 2017-11-15 doc/ms.tex
include new caption for the Piro figure

--- 2017-11-15 doc/ms.tex
@@
   \caption{
-  }
-  \label{fig:dessart}
+  \textbf{Comparison of the DD and PDD models of \citet{2014MNRAS.441..532D}
+  to the \abc\ $g$-band light curve (\textit{top}) and the $(B-V)_0$ color curve (\textit{bottom}). The
+  light curve has been corrected for the distance modulus to \abc\
+  (\S\ref{sec:host}), while both the light curve and color curve have been
+  corrected for reddening. Each light curve is translated to match the LCO
+  observations $\sim$1.7\,d after $t_0$ given the uncertain time of explosion.
+  Translational offsets are listed in the bottom panel legend, which shows the
+  models in order of decreasing $M_\mathrm{Ni}$ from top to bottom. DD models
+  (labeled as DDC to match the nomenclature of \citealt{2014MNRAS.441..532D})
+  are shown as dash-dot lines, while PDD models (labeled as PDDEL) are shown
+  as dashed lines. The inset in the top panel shows the residuals relative to
+  the PDDEL7n model. The PDD models provide a better match to the
+  observations.} 
+  } \label{fig:dessart} 
 \end{figure}
 
-\textbf{In Figure~\ref{fig:dessart} we compare photometric
-observations of \abc\ to the large-$^{56}$Ni yield DD and PDD
-models presented in \citet{2014MNRAS.441..532D}. DD and PDD models
-with $M_\mathrm{Ni}/M_\odot \la 0.7$ and 0.5, respectively, fail to
-match the early luminosity and blue colors of \abc. The PDD models
-provide a better match to the observations than the DD models. The
-PDD models evolve more rapidly towards blue colors and provide a
-better match to the $g$-band flux in the days after explosion.
-Furthermore, unlike the DD models, the PDD models exhibit strong
-\ion{C}{2} lines that gradually disappear in the $\sim$week after
-explosion \citet{2014MNRAS.441..532D}. In detail, the early wiggles
-in the \abc\ light curve are not matched by the PDD models, which
-exhibit more smooth variations. Nevertheless, the PDD models
-presented in \citet{2014MNRAS.441..532D} provide several attractive
-explanations for the unusual features in the early behavior of
-\abc, and small adjustments to the model (e.g., additional mixing
-of the radioactive material, which \citeauthor{2014MNRAS.441..532D}
-only explore for the DD model) may better match \abc. }
+\textbf{In Figure~\ref{fig:dessart} we compare photometric observations of
+\abc\ to the large-$^{56}$Ni yield DD and PDD models presented in
+\citet{2014MNRAS.441..532D}. DD and PDD models with $M_\mathrm{Ni}/M_\odot \la
+0.7$ and 0.5, respectively, fail to match the early luminosity and blue colors
+of \abc. The PDD models provide a better match to the observations than the DD
+models. The PDD models evolve more rapidly towards blue colors and provide a
+better match to the $g$-band flux in the days after explosion. Furthermore,
+unlike the DD models, the PDD models exhibit strong \ion{C}{2} lines that
+gradually disappear in the $\sim$week after explosion
+\citet{2014MNRAS.441..532D}. In detail, the early wiggles in the \abc\ light
+curve are not matched by the PDD models, which exhibit more smooth variations.
+Furthermore, while the focus of this study is the early evolution of \abc, the
+PDD models evolve more rapidly to the red post-peak than the observations.
+Nevertheless, the PDD models presented in \citet{2014MNRAS.441..532D} provide
+several attractive explanations for the unusual features in the early behavior
+of \abc, and small adjustments to the model (e.g., additional mixing of the
+radioactive material, which \citeauthor{2014MNRAS.441..532D} only explore for
+the DD model) may better match \abc.}
 
@@
   \centering
-  \includegraphics[width=0.48\textwidth]{iPTF16abc_Ni_lc.pdf}
-  \caption{Photometric comparison of \abc\ and the theoretical 
-  models of \citet{2016ApJ...826...96P}. The amount of $^{56}$Ni 
-  mixing in the SN ejecta increases from the short-dash, dark lines 
-  to the long-dash, light lines.
-  \textit{Top}: $M_g$ vs.\ time, where the observed $g$-band 
-  magnitudes  
-  have been corrected to $M_g$ using the distance modulus to \abc\ 
-  (\S\ref{sec:host})
-  and the total line-of-sight reddening ($E(B-V) = 0.08 \; 
-  \mathrm{mag}$; Ferretti et al.\ 2017, submitted). The orange 
-  solid line shows the model with the most $^{56}$Ni mixing 
-  shifted to an explosion time of $t_0 - 0.4 \; \mathrm{d}$. This 
-  model provides a good match to the data.
-  \textit{Bottom}: $(g' - r')_0$ vs.\ time. The observed colors 
-  have been corrected for reddening.
+  \includegraphics[width=0.48\textwidth]{compare_Piro.pdf}
+  \caption{  
+  \textbf{Same as Figure~\ref{fig:dessart}, featuring models from
+  \citet{2016ApJ...826...96P}. The amount of $^{56}$Ni mixing in the SN ejecta
+  increases from the short-dash, light lines to the long-dash, dark lines.
+  Unlike Figure~\ref{fig:dessart}, each model features the same
+  $M_\mathrm{Ni}$, while the model names reflect the boxcar widths used to
+  approximate the effects of mixing in the ejecta (see
+  \citealt{2016ApJ...826...96P}). The top panel inset shows the
+  residuals relative to the $0.25\,M_\odot$ model. The observations are best
+  matched by the $0.25\,M_\odot$ model, i.e. the model with the most
+  significant mixing.}
   }
-  \label{fig:Ni56LC}
+  \label{fig:piro}
 \end{figure}
 
-In Figure~\ref{fig:Ni56LC} we compare model calculations from
+In Figure~\ref{fig:piro} we compare model calculations from
 \citet{2016ApJ...826...96P} to the observed photometry of \abc. The
@@
 SuperNova Explosion Code (\texttt{SNEC}; \citealt{2015ApJ...814...63M}), as
-shown in Figure~\ref{fig:Ni56LC}. Broadly speaking, the results can be
+shown in Figure~\ref{fig:piro}. Broadly speaking, the results can be
 summarized as follows: SN with strong mixing exhibit a rapid almost linear
@@
 with the strong mixing models from \citet{2016ApJ...826...96P}, as shown in
-Figure~\ref{fig:Ni56LC}. In fact, if we adopt $t_\mathrm{exp} = t_0 - 0.4 \,
+Figure~\ref{fig:piro}. In fact, if we adopt $t_\mathrm{exp} = t_0 - 0.4 \,
 \mathrm{d}$, we find that the model with the strongest mixing (orange line in
-Figure~\ref{fig:Ni56LC}) provides an excellent match to the $g$-band
+Figure~\ref{fig:piro}) provides an excellent match to the $g$-band
 observations.
@@
 optical photometric evolution of \abc, they consistently overpredict the flux
-in the UV. The models shown in Figure~\ref{fig:Ni56LC} also overpredict the
+in the UV. The models shown in Figure~\ref{fig:piro} also overpredict the
 photospheric velocity of \abc\ by $\sim$2--3,000$\; \mathrm{km \; s}^{-1}$.

### 2017-11-15 doc/ms.tex
udpate text regarding the mixing models from Piro

@@
 
-Having examined other possibilities we now consider whether the unusual
-properties of \abc\ can be explained simply by invoking strong mixing in the 
-SN ejecta. Strong mixing leads to a shorter dark phase than would otherwise
-be observed. \textbf{We also consider} whether strong mixing can explain the
-rapid, near-linear rise in the light curve.
+Having examined other possibilities we now consider whether the \textbf{early evolution} of \abc\ can be explained simply by invoking strong mixing in the 
+SN ejecta. Strong mixing leads to \textbf{a faster initial rise as well as a more rapid evolution towards blue colors}.
 
@@
 
-In Figure~\ref{fig:piro} we compare model calculations from
-\citet{2016ApJ...826...96P} to the observed photometry of \abc. The
-\citeauthor{2016ApJ...826...96P} models employ a piston driven explosion to
-explode a single WD progenitor model. As the piston explosion does not result
-in any nucleosynthesis, the distribution of $^{56}$Ni in the ejecta must be
-prescribed by hand, which enables a study of the effects of mixing on the
-resulting SN emission. Each model employs a fixed $0.5\,\sm$ of $^{56}$Ni
-that has been distributed throughout the ejecta via boxcar averaging (see
-their Figure~1). The resulting light curves are synthesized using the
+Figure~\ref{fig:piro} compares the models from \citet{2016ApJ...826...96P} to
+\abc. The \citeauthor{2016ApJ...826...96P} models employ a piston driven
+explosion to explode a single WD progenitor model. As the piston explosion
+does not result in any nucleosynthesis, the distribution of $^{56}$Ni in the
+ejecta must be prescribed by hand, which enables a study of the effects of
+mixing on the resulting SN emission. Each model employs a fixed $0.5\,\sm$ of
+$^{56}$Ni that has been distributed throughout the ejecta via boxcar averaging
+(see their Figure~1). The resulting light curves are synthesized using the
 SuperNova Explosion Code (\texttt{SNEC}; \citealt{2015ApJ...814...63M}), as
 shown in Figure~\ref{fig:piro}. Broadly speaking, the results can be
-summarized as follows: SN with strong mixing exhibit a rapid almost linear
-rise and quickly develop blue colors, whereas models where the $^{56}$Ni is
-confined to the innermost layers of the ejecta remain very faint for days
-after explosion while exhibiting relatively red optical colors during this
-period. The fast rise and blue color of \abc\ are qualitatively consistent
-with the strong mixing models from \citet{2016ApJ...826...96P}, as shown in
-Figure~\ref{fig:piro}. In fact, if we adopt $t_\mathrm{exp} = t_0 - 0.4 \,
-\mathrm{d}$, we find that the model with the strongest mixing (orange line in
-Figure~\ref{fig:piro}) provides an excellent match to the $g$-band
-observations.
+summarized as follows: SNe with strong mixing exhibit a rapid rise and quickly
+develop blue colors, whereas models where the $^{56}$Ni is confined to the
+innermost layers of the ejecta remain faint for days after explosion and
+\textbf{feature a gradual color evolution from the red to the blue. The model
+with the strongest mixing (dark, long-dashed line in Figure~\ref{fig:piro})
+best matches the observations of \abc. This is the only model we have found
+that exhibits a flat $(B-V)_0$ color evolution in the days after explosion,
+however, in detail this model is too red relative to the observations of \abc.
+}
 
@@
 optical photometric evolution of \abc, they consistently overpredict the flux
-in the UV. The models shown in Figure~\ref{fig:piro} also overpredict the
+in the UV. \textbf{They} also overpredict the
 photospheric velocity of \abc\ by $\sim$2--3,000$\; \mathrm{km \; s}^{-1}$.
@@
 
-\subsection{The Emerging Sample of Young SNe Ia}
+\section{\textbf{Discussion: The Emerging Sample of Young SNe Ia}}
 

### 2017-11-15 doc/ms.tex
include Noebauer figure in paper and add description of individual models

@@
 \newcommand{\abc}{iPTF\,16abc}
+\newcommand{\sneia}{SNe Ia}
 
@@
 emission was first detected in iPTF\,14atg  \citep{2015Natur.521..328C}, a low-velocity SN Ia with a significant and declining ultraviolet (UV) pulse detected within a
-few days of the SN explosion. This UV pulse is best interpreted as a SN ejecta-companion collision (but see also \citealt{2016MNRAS.459.4428K,2017arXiv170603613N}). While such emission requires a 
+few days of the SN explosion. This UV pulse is best interpreted as a SN ejecta-companion collision (but see also \citealt{2016MNRAS.459.4428K,2017MNRAS.472.2787N}). While such emission requires a 
 favorable geometric alignment and is only expected in $\lesssim$10\% of SNe Ia \citep{2010ApJ...708.1025K}, many studies have 
@@
 \citealt{2016arXiv161007601S} for an interpretation that does not 
-invoke ejecta-companion interaction), and SN\,2017cbv, which shows a clearly resolved ``bump'' in the early $UBg$ light curves \citep{2017arXiv170608990H}. 
+invoke ejecta-companion interaction), and SN\,2017cbv, which shows a clearly resolved ``bump'' in the early $UBg$ light curves \citep{2017ApJ...845L..11H}. 
 % With only $\sim 10\%$ of single-degenerate progenitors occupying the preferred binary geometry for us to see the collision
@@
 Interaction is not limited to systems with a non-degenerate companion, however, as WDs enshrouded in diffuse material following a binary merger (e.g., \citealt{2015MNRAS.447.2803L}) or expanded due to a pre-explosion pulsation can give rise to ejecta-interaction signatures (e.g., \citealt{2014MNRAS.441..532D}).
-Models of this scenario naturally produce \ion{C}{2} absorption that is comparable in strength to \ion{Si}{2} in the days after explosion \citep{2014MNRAS.441..532D}, as was observed in SN\,2013dy \citep{2013ApJ...778L..15Z} and SN\,2017cbv \citep{2017arXiv170608990H}.
+Models of this scenario naturally produce \ion{C}{2} absorption that is comparable in strength to \ion{Si}{2} in the days after explosion \citep{2014MNRAS.441..532D}, as was observed in SN\,2013dy \citep{2013ApJ...778L..15Z} and SN\,2017cbv \citep{2017ApJ...845L..11H}.
 
@@
 
-\citet{2017arXiv170603613N} demonstrate that disambiguating between these different scenarios via optical photometry alone is challenging.
-\citeauthor{2017arXiv170603613N} further show that estimates of the time of explosion, which are critical for comparing models with observations, are often incorrect by as many as $\sim$2\,d using common methods in the literature.
+\citet{2017MNRAS.472.2787N} demonstrate that disambiguating between these different scenarios via optical photometry alone is challenging.
+\citeauthor{2017MNRAS.472.2787N} further show that estimates of the time of explosion, which are critical for comparing models with observations, are often incorrect by as many as $\sim$2\,d using common methods in the literature.
 While analytical models suggest that early spectra can be used to infer the time of explosion (e.g., \citealt{2014ApJ...784...85P}), more detailed simulations show that the photospheric evolution is not so simple \citep{2016ApJ...826...96P}.
@@
 
-Simulations presented in \citet{2017arXiv170603613N} show that the flux from
+Simulations presented in \citet{2017MNRAS.472.2787N} show that the flux from
 SNe Ia explosion models does not evolve as a power law in time. Despite this
-non-power-law evolution, \citet{2017arXiv170603613N} show that $f \propto
+non-power-law evolution, \citet{2017MNRAS.472.2787N} show that $f \propto
 t^\alpha$ models produce good formal fits to simulated observations. The $f
-\propto t^\alpha$ fits to the \citeauthor{2017arXiv170603613N}\ models result
+\propto t^\alpha$ fits to the \citeauthor{2017MNRAS.472.2787N}\ models result
 in glaring errors to the estimated explosion times. Despite the caution
-advised in \citet{2017arXiv170603613N}, we proceed with the power-law fits
+advised in \citet{2017MNRAS.472.2787N}, we proceed with the power-law fits
 from above for several reasons. (1) Our primary aim with the fit is to
 characterize $\alpha$ for \abc\ compared to SN\,2011fe (see below). (2) The
-errors in the estimated explosion times from \citeauthor{2017arXiv170603613N}
+errors in the estimated explosion times from \citeauthor{2017MNRAS.472.2787N}
 increase the later the first observation of the SN is obtained.
-\citeauthor{2017arXiv170603613N} only present fits to observations that start
+\citeauthor{2017MNRAS.472.2787N} only present fits to observations that start
 $>$2\,d after explosion, whereas the discovery epoch for \abc\ is likely much
@@
 first light. \textbf{Finally,} (4) Pre-discovery upper limits, which are not
-included in \citeauthor{2017arXiv170603613N}, provide additional strong
+included in \citeauthor{2017MNRAS.472.2787N}, provide additional strong
 constraints on the time of first light.
@@
 Spectra obtained around or after $T_{B_\mathrm{max}}$ rarely show \ion{C}{2} as the photosphere has receded from the outermost ejecta, while pre-max spectra show evidence for \ion{C}{2} in $\sim$1/4 of all normal SNe Ia (e.g., \citealt{2011ApJ...732...30P,2012MNRAS.425.1917S,2011ApJ...743...27T}), but the signatures are typically weak.
-While we caution that the sample of SNe Ia with spectra taken within a few days of explosion is small, SNe\,2013dy and 2017cbv are the only other objects known to have strong \ion{C}{2} features like \abc\ \citep{2013ApJ...778L..15Z,2017arXiv170608990H}.
+While we caution that the sample of SNe Ia with spectra taken within a few days of explosion is small, SNe\,2013dy and 2017cbv are the only other objects known to have strong \ion{C}{2} features like \abc\ \citep{2013ApJ...778L..15Z,2017ApJ...845L..11H}.
 As a counterexample, SN\,2011fe only exhibited weak \ion{C}{2} features in its first spectra
@@
 Roughly 16\,d prior to $B$-band maximum, the $(B - V)_0$ color of \abc\ is $\sim$0.5 mag bluer than SN\,2011fe.
-Like \abc, SN\,2012cg \citep{2016ApJ...820...92M} and SN\,2017cbv \citep{2017arXiv170608990H} exhibit $(B - V)_0$ colors that are significantly bluer than SN\,2011fe at very early epochs.
+Like \abc, SN\,2012cg \citep{2016ApJ...820...92M} and SN\,2017cbv \citep{2017ApJ...845L..11H} exhibit $(B - V)_0$ colors that are significantly bluer than SN\,2011fe at very early epochs.
 While there are many factors that contribute to the early optical colors of SNe Ia (see \S\ref{sec:lc_energy} below), early blue colors are often interpreted as a hallmark of interaction between the SN ejecta and a binary companion.
@@
 
-\section{Discussion}
+\section{Discussion: \textbf{Modeling the Early Evolution of \abc}}
 \label{sec:lc_energy}
@@
 
-\subsection{Sub-Chandrasekhar Double Detonation}
-
-The detonation of a WD with $M < 1.4 \, M_\odot$, which can occur if triggered by a He-surface-layer detonation (known as the sub-Chandrasekhar double detonation), can produce a rapid rise and early blue optical colors (e.g., \citealt{2017arXiv170603613N}).
-While this qualitative behavior matches \abc, the $U-V$ colors predicted in \citet{2017arXiv170603613N} do not match our observations.
+\subsection{\textbf{Sub-Chandrasekhar Detonations and Pure Deflagrations}}
+
+\textbf{In \citet{2017MNRAS.472.2787N} the early photometric evolution of Type Ia SNe is explored via a variety of explosion models and detailed radiative-transfer calculations.
+Specifically, \citet{2017MNRAS.472.2787N} examine 2 Chandrasekhar-mass ($M_\mathrm{Ch}$) explosions and compare their evolution to sub-Chandrasekhar explosions and pure deflagrations.
+The 2 $M_\mathrm{Ch}$ explosions include the ``W7'' carbon-deflagration model of \citet{1984ApJ...286..644N} and the ``N100'' delayed-detonation model from \citet{2013MNRAS.429.1156S}.
+The sub-Chandrasekhar models include: a violent WD-WD merger, which triggers a carbon detonation in the more massive WD, a centrally ignited detonation, and a sub-Chandrasehkar double detonation explosion, in which a He-surface-layer detonation triggers a carbon detonation in the WD core.
+\citet{2017MNRAS.472.2787N} note that, of these last two sub-Chandrasehkar models, the later provides the more realistic scenario.
+Finally, \citet{2017MNRAS.472.2787N} also examine the ``N5def'' and ``N1600Cdef'' pure deflagrations from \citet{2014MNRAS.438.1762F}.}
+
+\begin{figure}[]
+  \centering
+  \includegraphics[width=0.48\textwidth]{compare_Noebauer.pdf}
+  \caption{
+  \textbf{Comparison of the models from \citet{2017MNRAS.472.2787N}
+  to the \abc\ $g$-band light curve (\textit{top}) and the $(B-V)_0$ color curve (\textit{bottom}). The
+  light curve has been corrected for the distance modulus to \abc\
+  (\S\ref{sec:host}), while both the light curve and color curve have been
+  corrected for reddening. Each light curve is translated to match the LCO
+  observations $\sim$1.7\,d after $t_0$ given the uncertain time of explosion.
+  Translational offsets are listed in the bottom panel legend, which shows the
+  models in order of decreasing $M_\mathrm{Ni}$ from top to bottom. DD models
+  (labeled as DDC to match the nomenclature of \citealt{2014MNRAS.441..532D})
+  are shown as dash-dot lines, while PDD models (labeled as PDDEL) are shown
+  as dashed lines. The inset in the top panel shows the residuals relative to
+  the PDDEL7n model. The PDD models provide a better match to the
+  observations.} 
+  } \label{fig:noebauer} 
+\end{figure}
+
+\textbf{In Figure~\ref{fig:noebauer} we compare photometric observations of
+\abc\ to the large-$^{56}$Ni yield DD and PDD models presented in
+\citet{2014MNRAS.441..532D}.
+}
+
+The detonation of a WD with $M < 1.4 \, M_\odot$, which can occur if triggered by a He-surface-layer detonation (known as the sub-Chandrasekhar double detonation), can produce a rapid rise and early blue optical colors (e.g., \citealt{2017MNRAS.472.2787N}).
+While this qualitative behavior matches \abc, the $U-V$ colors predicted in \citet{2017MNRAS.472.2787N} do not match our observations.
 In particular, the sub-Chandrasekhar double detonation model $U - V$ colors rapidly evolve from $\sim$$-0.6\,\mathrm{mag}$ $\sim$1\,d after explosion to $\sim$0.5\,mag $\sim$3\,d after explosion.
@@
 As such we conclude that \abc\ is not the result of a sub-Chandrasekhar double detonation.
-\citet{2017arXiv170603613N} note that their one-dimensional models may not capture the predicted asphericity for sub-Chandrasekhar double detonations, though moving away from the preferred viewing angle results in redder colors and a more gradual rise, which is not observed for \abc.
+\citet{2017MNRAS.472.2787N} note that their one-dimensional models may not capture the predicted asphericity for sub-Chandrasekhar double detonations, though moving away from the preferred viewing angle results in redder colors and a more gradual rise, which is not observed for \abc.
 
@@
 sequence of photometric and spectroscopic observations of young SNe Ia can
-never distinguish between these two possibilities \citep{2017arXiv170603613N}.
-
-\section{\textbf{Discussion: The Emerging Sample of Young SNe Ia}}
+never distinguish between these two possibilities \citep{2017MNRAS.472.2787N}.
+
+\section{\textbf{Discussion: The Emerging Sample of Young \sneia}}
 
@@
 In contrast, \abc\ exhibits a near linear rise in flux, the $(B - V)_0$ colors are blue and roughly constant, and the \ion{C}{2} absorption is strong.
-Examining just these 3 qualitative features, SN\,2009ig is well matched to SN\,2011fe \citep{2012ApJ...744...38F}, while SN\,2013dy \citep{2013ApJ...778L..15Z}, SN\,2017cbv \citep{2017arXiv170608990H}, and \abc\ all bear a striking resemblance.
+Examining just these 3 qualitative features, SN\,2009ig is well matched to SN\,2011fe \citep{2012ApJ...744...38F}, while SN\,2013dy \citep{2013ApJ...778L..15Z}, SN\,2017cbv \citep{2017ApJ...845L..11H}, and \abc\ all bear a striking resemblance.
 SN\,2012cg, on the other hand, is intermediate to these two groups with weak C II and a relatively shallow early rise, like SN\,2011fe, but blue $(B - V)_0$ colors, like \abc\ \citep{2012ApJ...756L...7S,2016ApJ...820...92M}.
@@
 
-In the case of SN\,2012cg and SN\,2017cbv it has been argued that the early blue optical colors are indicative of interaction between the SN ejecta and a binary companion \citep{2016ApJ...820...92M,2017arXiv170608990H}.
-SN\,2017cbv is particularly remarkable in that the observations presented in \citet{2017arXiv170608990H} show a clearly resolved bump in the $U$, $B$, and $g'$ bands in the $\sim$5\,d after explosion.
-In \citeauthor{2017arXiv170608990H} it is found that the bump can be explained via the combination of ejecta-companion interaction and the normal evolution of a SN Ia.
+In the case of SN\,2012cg and SN\,2017cbv it has been argued that the early blue optical colors are indicative of interaction between the SN ejecta and a binary companion \citep{2016ApJ...820...92M,2017ApJ...845L..11H}.
+SN\,2017cbv is particularly remarkable in that the observations presented in \citet{2017ApJ...845L..11H} show a clearly resolved bump in the $U$, $B$, and $g'$ bands in the $\sim$5\,d after explosion.
+In \citeauthor{2017ApJ...845L..11H} it is found that the bump can be explained via the combination of ejecta-companion interaction and the normal evolution of a SN Ia.
 A challenge for this model, similar to \abc\ (see \S\ref{sec:companion}), is that it significantly overpredicts the UV brightness of the SN compared to what is observed.
 Indeed, in the case of SNe\,2012cg, 2017cbv, and \abc\ the $\mathrm{UV} - \mathrm{optical}$ colors are significantly redder than those observed in iPTF\,14atg.
-It is argued in \citet{2017arXiv170608990H} that several model assumptions, including: (i) ideal blackbody emission, (ii) a constant opacity, (iii) a simple power-law density profile for the ejecta, and (iv) spherical symmetry, may be incorrect, which could reconcile the discrepancy with the UV observations.
-Above, we argued for circumstellar interaction and strong $^{56}$Ni mixing as a possible explanation for \abc, and indeed \citet{2017arXiv170608990H} consider these possibilities for SN\,2017cbv as well.
+It is argued in \citet{2017ApJ...845L..11H} that several model assumptions, including: (i) ideal blackbody emission, (ii) a constant opacity, (iii) a simple power-law density profile for the ejecta, and (iv) spherical symmetry, may be incorrect, which could reconcile the discrepancy with the UV observations.
+Above, we argued for circumstellar interaction and strong $^{56}$Ni mixing as a possible explanation for \abc, and indeed \citet{2017ApJ...845L..11H} consider these possibilities for SN\,2017cbv as well.
 Separately, several arguments against companion interaction for SN\,2012cg are presented in \citet{2016arXiv161007601S}.
@@
 There are elements of the PDD models from \citet{2014MNRAS.441..532D} that are attractive for explaining \abc, in particular, the strong \ion{C}{2} absorption seen at early times.
-In the future, it would be useful to investigate more detailed PDD models that incorporate strong $^{56}$Ni mixing to see if they better replicate the observations of \abc\ as it is otherwise difficult to distinguish between these two scenarios \citep{2017arXiv170603613N}.\footnote{Both \citet{2014MNRAS.441..532D} and \citet{2016ApJ...826...96P} consider models with strong mixing \textit{and} interaction, but those studies do not replicate each of the salient features of \abc.}
+In the future, it would be useful to investigate more detailed PDD models that incorporate strong $^{56}$Ni mixing to see if they better replicate the observations of \abc\ as it is otherwise difficult to distinguish between these two scenarios \citep{2017MNRAS.472.2787N}.\footnote{Both \citet{2014MNRAS.441..532D} and \citet{2016ApJ...826...96P} consider models with strong mixing \textit{and} interaction, but those studies do not replicate each of the salient features of \abc.}
 

### 2017-11-15 doc/ms.tex
include description of the Noebauer models

@@
 
-\textbf{In \citet{2017MNRAS.472.2787N} the early photometric evolution of Type Ia SNe is explored via a variety of explosion models and detailed radiative-transfer calculations.
-Specifically, \citet{2017MNRAS.472.2787N} examine 2 Chandrasekhar-mass ($M_\mathrm{Ch}$) explosions and compare their evolution to sub-Chandrasekhar explosions and pure deflagrations.
-The 2 $M_\mathrm{Ch}$ explosions include the ``W7'' carbon-deflagration model of \citet{1984ApJ...286..644N} and the ``N100'' delayed-detonation model from \citet{2013MNRAS.429.1156S}.
-The sub-Chandrasekhar models include: a violent WD-WD merger, which triggers a carbon detonation in the more massive WD, a centrally ignited detonation, and a sub-Chandrasehkar double detonation explosion, in which a He-surface-layer detonation triggers a carbon detonation in the WD core.
-\citet{2017MNRAS.472.2787N} note that, of these last two sub-Chandrasehkar models, the later provides the more realistic scenario.
-Finally, \citet{2017MNRAS.472.2787N} also examine the ``N5def'' and ``N1600Cdef'' pure deflagrations from \citet{2014MNRAS.438.1762F}.}
+\textbf{In \citet{2017MNRAS.472.2787N} the early photometric evolution of Type
+Ia SNe is explored via a variety of explosion models and detailed
+radiative-transfer calculations. Specifically, \citet{2017MNRAS.472.2787N}
+examine two Chandrasekhar-mass ($M_\mathrm{Ch}$) explosions and compare their
+evolution to sub-Chandrasekhar explosions and pure deflagrations. The
+$M_\mathrm{Ch}$ explosions include the ``W7'' carbon-deflagration model of
+\citet{1984ApJ...286..644N} and the ``N100'' delayed-detonation model from
+\citet{2013MNRAS.429.1156S}. The sub-Chandrasekhar models include: a violent
+WD-WD merger, which triggers a carbon detonation in the more massive WD, a
+centrally ignited sub-Chandrasehkar detonation, and a sub-Chandrasehkar double
+detonation explosion, in which a He-surface-layer detonation triggers a carbon
+detonation in the core. \citet{2017MNRAS.472.2787N} note that, of these
+last two sub-Chandrasehkar models, the later provides the more realistic
+scenario. Finally, \citet{2017MNRAS.472.2787N} also examine the ``N5def'' and
+``N1600Cdef'' pure deflagration explosions from \citet{2014MNRAS.438.1762F}.}
 
@@
   \caption{
-  \textbf{Comparison of the models from \citet{2017MNRAS.472.2787N}
-  to the \abc\ $g$-band light curve (\textit{top}) and the $(B-V)_0$ color curve (\textit{bottom}). The
-  light curve has been corrected for the distance modulus to \abc\
-  (\S\ref{sec:host}), while both the light curve and color curve have been
-  corrected for reddening. Each light curve is translated to match the LCO
-  observations $\sim$1.7\,d after $t_0$ given the uncertain time of explosion.
-  Translational offsets are listed in the bottom panel legend, which shows the
-  models in order of decreasing $M_\mathrm{Ni}$ from top to bottom. DD models
-  (labeled as DDC to match the nomenclature of \citealt{2014MNRAS.441..532D})
-  are shown as dash-dot lines, while PDD models (labeled as PDDEL) are shown
-  as dashed lines. The inset in the top panel shows the residuals relative to
-  the PDDEL7n model. The PDD models provide a better match to the
-  observations.} 
-  } \label{fig:noebauer} 
+%
+  \textbf{Comparison of the models from \citet{2017MNRAS.472.2787N} to the
+  \abc\ $V$-band light curve (\textit{top}) and the $(B-V)_0$ color curve
+  (\textit{bottom}). The light curve has been corrected for the distance
+  modulus to \abc\ (\S\ref{sec:host}), while both the light curve and color
+  curve have been corrected for reddening. To guide the eye early
+  $g_\mathrm{PTF}$ observations are shown as open circles, though we caution
+  that \abc\ may exhibit significant color evolution at this phase in which
+  case $g_\mathrm{PTF}$ would be a poor proxy for $V$. Each model light curve
+  is translated to match the LCO observations $\sim$1.7\,d after $t_0$ given
+  the uncertain time of explosion. Translational offsets are listed in the
+  bottom panel legend, which shows the models in order of decreasing
+  $^{56}$Ni from top to bottom, then left to right. The inset in
+  the top panel shows the residuals relative to the W7 model.} }
+  \label{fig:noebauer} 
 \end{figure}
@@
 \textbf{In Figure~\ref{fig:noebauer} we compare photometric observations of
-\abc\ to the large-$^{56}$Ni yield DD and PDD models presented in
-\citet{2014MNRAS.441..532D}.
+\abc\ to the models presented in
+\citet{2017MNRAS.472.2787N}.
+Interestingly, the sub-Chandrasekhar double detonation model (subChDoubleDet) replicates the early wiggle in the $V$-band light curve.
+However, this match requires an explosion \textit{after} our initial detection of \abc, \textit{and} extreme color evolution.
+Thus, the subChDoubleDet model is incompatible with the observations.
+The sub-Chandrasekhar detonation (subChDet) provides a better match to the observations, though this model is not favored as a particularly realistic scenario (see above).
+Of the sub-Chandrasekhar models the violent merger model (Merger) provides the best match to the observations including the early rise and color evolution.
+In detail, however, this model does not match the early wiggles in the light curve, has consistently redder colors than \abc, and requires $t_\mathrm{exp} \approx 2.3$\,d prior to $t_0$.
+As such, we postulate that \abc\ is not the result of a violent WD-WD merger.}
+
+\textbf{For clarity, of the two pure deflagration models only N5def is shown, however, the evolution of N1600Cdef is very similar.
+While the pure deflagration models produce the bluest colors at early times, they are underluminous at times $> t_0 + 4\,\mathrm{d}$ and already rapidly evolving towards the red at $\sim$$t_0 + 7$ (\abc\ exhibits a nearly constant $(B-V)_0$ color for $\sim$19\,d after $t_0$).
+Thus, we conclude that \abc\ is not compatible with pure deflagrations.}
+
+\textbf{Of the $M_\textrm{Ch}$ models, the W7 model better matches the observations as the N100 model features a faster rise and higher luminosity than what is observed.
+We explore delayed detonation models in further detail below.
 }
-
-The detonation of a WD with $M < 1.4 \, M_\odot$, which can occur if triggered by a He-surface-layer detonation (known as the sub-Chandrasekhar double detonation), can produce a rapid rise and early blue optical colors (e.g., \citealt{2017MNRAS.472.2787N}).
-While this qualitative behavior matches \abc, the $U-V$ colors predicted in \citet{2017MNRAS.472.2787N} do not match our observations.
-In particular, the sub-Chandrasekhar double detonation model $U - V$ colors rapidly evolve from $\sim$$-0.6\,\mathrm{mag}$ $\sim$1\,d after explosion to $\sim$0.5\,mag $\sim$3\,d after explosion.
-We observe a steady $U - V$ color evolution from the red to the blue for \abc, however, with $U - V \approx 0.6 \, \mathrm{mag}$ $\sim$2\,d after $t_0$ and $U - V \approx 0 \, \mathrm{mag}$ $\sim$8\,d after $t_0$.
-As such we conclude that \abc\ is not the result of a sub-Chandrasekhar double detonation.
-\citet{2017MNRAS.472.2787N} note that their one-dimensional models may not capture the predicted asphericity for sub-Chandrasekhar double detonations, though moving away from the preferred viewing angle results in redder colors and a more gradual rise, which is not observed for \abc.
 
@@
   \caption{
-  \textbf{Comparison of the DD and PDD models of \citet{2014MNRAS.441..532D}
-  to the \abc\ $g$-band light curve (\textit{top}) and the $(B-V)_0$ color curve (\textit{bottom}). The
-  light curve has been corrected for the distance modulus to \abc\
-  (\S\ref{sec:host}), while both the light curve and color curve have been
-  corrected for reddening. Each light curve is translated to match the LCO
-  observations $\sim$1.7\,d after $t_0$ given the uncertain time of explosion.
-  Translational offsets are listed in the bottom panel legend, which shows the
-  models in order of decreasing $M_\mathrm{Ni}$ from top to bottom. DD models
+  \textbf{Same as Figure~\ref{fig:noebauer}, featuring the DD and PDD models
+  from \citet{2014MNRAS.441..532D}. The bottom panel legend lists the models
+  in order of decreasing $M_\mathrm{Ni}$ from top to bottom. DD models
   (labeled as DDC to match the nomenclature of \citealt{2014MNRAS.441..532D})
@@
   \caption{  
-  \textbf{Same as Figure~\ref{fig:dessart}, featuring models from
+  \textbf{Same as Figure~\ref{fig:noebauer}, featuring models from
   \citet{2016ApJ...826...96P}. The amount of $^{56}$Ni mixing in the SN ejecta

### 2017-11-15 doc/ms.tex
Include updates to the introduction

@@
 Although Type Ia supernovae (SNe Ia) have been extensively used as
-standardizable candles, their progenitor systems and explosion
-physics are still debated (see a recent review by
-\citealt{2014ARA&A..52..107M}). Extremely detailed
-observations in the hours to days after explosion provide a promising avenue to further constrain this problem.
-
-While the shock breakout of a SN Ia occurs on a sub-second timescale,
-the subsequent quasi-adiabatic expansion and cooling of the unbound
-ejecta produces thermal emission that can be used to infer the
-radius of the exploding star
-\citep{2010ApJ...708..598P,2011ApJ...728...63R}. Comparing models of this cooling emission to the earliest-phase data of SN~2011fe,
-\citet{2012ApJ...744L..17B} concluded that the explosion came from a star with $R_\ast \lesssim 0.02\;\sr$, where $\sr$ is the solar
-radius. Combining the radius constraint with the measured ejecta 
-mass, \citeauthor{2012ApJ...744L..17B} derive the mean density of the progenitor star, confirming that at least some Type Ia SNe come from compact and degenerate stars.
-
-Early phase observations of SNe Ia from a white dwarf (WD)$+$non-degenerate binary
-may detect excess emission, relative to most Type Ia SNe, due to the 
+standardizable candles, their progenitor systems and explosion physics are
+still debated (see a recent review by \citealt{2014ARA&A..52..107M}).
+Extremely detailed observations in the hours to days after explosion provide a
+promising avenue to further constrain this problem.
+
+While the shock breakout of a SN Ia occurs on a sub-second timescale, the
+subsequent quasi-adiabatic expansion and cooling of the unbound ejecta
+produces thermal emission that can be used to infer the radius of the
+exploding star \citep{2010ApJ...708..598P,2011ApJ...728...63R}. Comparing
+models of this cooling emission to the earliest-phase data of SN~2011fe,
+\citet{2012ApJ...744L..17B} concluded that the explosion came from a star with
+$R_\ast \lesssim 0.02\;\sr$, where $\sr$ is the solar radius. Combining the
+radius constraint with the measured ejecta mass,
+\citeauthor{2012ApJ...744L..17B} derive the mean density of the progenitor
+star, confirming that at least some Type Ia SNe come from compact and
+degenerate stars.
+
+Early phase observations of SNe Ia from a white dwarf (WD)$+$non-degenerate
+binary may detect excess emission, relative to most Type Ia SNe, due to the
 collision of the SN ejecta with the non-degenerate companion
-\citep{1973ApJ...186.1007W,2010ApJ...708.1025K}. This excess 
-emission was first detected in iPTF\,14atg  \citep{2015Natur.521..328C}, a low-velocity SN Ia with a significant and declining ultraviolet (UV) pulse detected within a
-few days of the SN explosion. This UV pulse is best interpreted as a SN ejecta-companion collision (but see also \citealt{2016MNRAS.459.4428K,2017MNRAS.472.2787N}). While such emission requires a 
-favorable geometric alignment and is only expected in $\lesssim$10\% of SNe Ia \citep{2010ApJ...708.1025K}, many studies have 
-searched for signatures of an ejecta-companion interaction, 
-typically resulting in non-detections 
-(e.g., \citealt{2010ApJ...722.1691H,2011ApJ...741...20B,2012ApJ...744...38F,
+\citep{1973ApJ...186.1007W,2010ApJ...708.1025K}. This excess emission was
+first detected in iPTF\,14atg \citep{2015Natur.521..328C}, a low-velocity SN
+Ia with a significant and declining ultraviolet (UV) pulse detected within a
+few days of the SN explosion. This UV pulse is best interpreted as a SN
+ejecta-companion collision (but see also
+\citealt{2016MNRAS.459.4428K,2017MNRAS.472.2787N}). While such emission
+requires a favorable geometric alignment and is only expected in
+$\lesssim$10\% of SNe Ia \citep{2010ApJ...708.1025K}, many studies have
+searched for signatures of an ejecta-companion interaction, typically
+resulting in non-detections (e.g.,
+\citealt{2010ApJ...722.1691H,2011ApJ...741...20B,2012ApJ...744...38F,
 2012ApJ...744L..17B,2015Natur.521..332O,
 2013ApJ...778L..15Z,2015ApJ...799..106G,2016ApJ...826..144S,
-  2015ApJS..221...22I}). Possible exceptions include SN\,2012cg, 
-which exhibited excess blue emission in its early-phase light curve 
-(\citealt{2016ApJ...820...92M}; though see 
-\citealt{2016arXiv161007601S} for an interpretation that does not 
-invoke ejecta-companion interaction), and SN\,2017cbv, which shows a clearly resolved ``bump'' in the early $UBg$ light curves \citep{2017ApJ...845L..11H}. 
+2015ApJS..221...22I}). Possible exceptions include SN\,2012cg, which exhibited
+excess blue emission in its early-phase light curve
+(\citealt{2016ApJ...820...92M}; though see \citealt{2016arXiv161007601S} for
+an interpretation that does not invoke ejecta-companion interaction), and
+SN\,2017cbv, which shows a clearly resolved ``bump'' in the early $UBg$ light
+curves \citep{2017ApJ...845L..11H}.
 % With only $\sim 10\%$ of single-degenerate progenitors occupying the preferred binary geometry for us to see the collision
@@
 
-Interaction is not limited to systems with a non-degenerate companion, however, as WDs enshrouded in diffuse material following a binary merger (e.g., \citealt{2015MNRAS.447.2803L}) or expanded due to a pre-explosion pulsation can give rise to ejecta-interaction signatures (e.g., \citealt{2014MNRAS.441..532D}).
-Models of this scenario naturally produce \ion{C}{2} absorption that is comparable in strength to \ion{Si}{2} in the days after explosion \citep{2014MNRAS.441..532D}, as was observed in SN\,2013dy \citep{2013ApJ...778L..15Z} and SN\,2017cbv \citep{2017ApJ...845L..11H}.
-
-The vast majority of SNe Ia are observed 
-to be powered purely by the radioactive decay of $^{56}$Ni. 
-While the detection of SN shock cooling or ejecta interaction is rare, the level of $^{56}$Ni mixing in the SN ejecta can fundamentally alter the appearance of the SN shortly after explosion.
-SNe Ia experience a dark phase after
-the SN shock breakout but before radioactive energy  
-diffuses into the photosphere \citep{2014ApJ...784...85P}. The 
-duration of this dark phase is set by how the newly synthesized 
-$^{56}$Ni is mixed and deposited into different layers of the ejecta. In the case of strong mixing, the dark phase is short, or 
-non-existent, as $\gamma$-rays from the radioactive $^{56}$Ni diffuse to the photosphere rapidly.
-This also leads to blue optical colors and a rapid initial rise in the observed light curve.
-If the mixing is weak and the $^{56}$Ni is confined to the innermost layers of the ejecta, the dark phase can last for several days.
-The early evolution of such SNe results in redder colors and a more moderate rise in luminosity \citep{2016ApJ...826...96P}.
-Thus, the early light curves of even non-exotic Type Ia SNe convey information about their progenitor systems by constraining the distribution of synthesized $^{56}$Ni, which in turn constrains the explosion mechanism.\footnote{\citet{2015A&A...574A..60T} found that a significant dark phase is not prevalent for a sample of Type Ib/c SNe.}
+Interaction is not limited to systems with a non-degenerate companion,
+however, as WDs enshrouded in diffuse material following a binary merger
+(e.g., \citealt{2015MNRAS.447.2803L}) or expanded due to a pre-explosion
+pulsation can give rise to ejecta-interaction signatures (e.g.,
+\citealt{2014MNRAS.441..532D}). Models of this scenario naturally produce
+\ion{C}{2} absorption that is comparable in strength to \ion{Si}{2} in the
+days after explosion \citep{2014MNRAS.441..532D}, as was observed in
+SN\,2013dy \citep{2013ApJ...778L..15Z} and SN\,2017cbv
+\citep{2017ApJ...845L..11H}.
+
+The vast majority of SNe Ia are observed to be powered purely by the
+radioactive decay of $^{56}$Ni. While the detection of SN shock cooling or
+ejecta interaction is rare, the level of $^{56}$Ni mixing in the SN ejecta can
+fundamentally alter the appearance of the SN shortly after explosion
+\textbf{(e.g.,
+\citealt{2014MNRAS.441..532D,2016ApJ...826...96P,2017MNRAS.466.3784S,2017MNRAS.472.2787N})}.
+
+SNe Ia experience a dark phase after the SN shock breakout but before
+radioactive energy diffuses into the photosphere \citep{2014ApJ...784...85P}.
+The duration of this dark phase is set by how the newly synthesized $^{56}$Ni
+is mixed and deposited into different layers of the ejecta. In the case of
+strong mixing, the dark phase is short, or non-existent, as $\gamma$-rays from
+the radioactive $^{56}$Ni diffuse to the photosphere rapidly. This also leads
+to blue optical colors and a rapid initial rise in the observed light curve.
+\textbf{Even with vigorous mixing it is difficult at very early times, $<
+1$\,d after explosion, to explain very large luminosities or blue colors,
+because the $^{56}$Ni has not had sufficient time to radioactively decay to
+$^{56}$Co.} If the mixing is weak and the $^{56}$Ni is confined to the
+innermost layers of the ejecta, the dark phase can last for several days. The
+early evolution of such SNe results in redder colors and a more moderate rise
+in luminosity \citep{2014MNRAS.441..532D,2016ApJ...826...96P}. Thus, the early
+light curves of even non-exotic Type Ia SNe convey information about their
+progenitor systems by constraining the distribution of synthesized $^{56}$Ni,
+which in turn constrains the explosion mechanism.
+
+% \footnote{\citet{2015A&A...574A..60T} found that a significant dark
+% phase is not prevalent for a sample of Type Ib/c SNe.}
 
 \citet{2017MNRAS.472.2787N} demonstrate that disambiguating between these different scenarios via optical photometry alone is challenging.
-\citeauthor{2017MNRAS.472.2787N} further show that estimates of the time of explosion, which are critical for comparing models with observations, are often incorrect by as many as $\sim$2\,d using common methods in the literature.
+\citeauthor{2017MNRAS.472.2787N} further show that estimates of the time of explosion, which are critical for comparing models with observations, are often incorrect by as \textbf{much} as $\sim$2\,d using common methods in the literature.
 While analytical models suggest that early spectra can be used to infer the time of explosion (e.g., \citealt{2014ApJ...784...85P}), more detailed simulations show that the photospheric evolution is not so simple \citep{2016ApJ...826...96P}.
@@
 We fit the measured velocities of \ion{Si}{2}\,$\lambda$6355 to the
-$v\propto(t-t_\mathrm{exp})^{-0.22}$ model by minimizing the $\chi^2$ value and find the best-fit explosion time relative to $T_{B,\mathrm{max}}$ in the SN rest frame to be $t_\mathrm{exp} = -17.45 \pm ^{0.14}_{0.16}\,\textrm{d}$, where the uncertainties represent the 95\% confidence interval (Figure \ref{fig:velocity_t_exp}).
-Following the analysis in \citet{2014ApJ...784...85P}, we additionally alter the power-law index to $-0.20$ and $-0.24$ to examine the sensitivity of the result on the assumed power-law index.
-We find that this variation in the power-law index results in a change of $t_\mathrm{exp}$ of $\approx\pm$0.5\,d (Figure \ref{fig:velocity_t_exp}).
-Given the analytical approximation that $v \propto t^{-0.22}$, we adopt $t_\mathrm{exp} = -17.5 \pm 0.5 \; \mathrm{d}$, where the uncertainty reflects possible variations in the power-lax index (see \citealt{2014ApJ...784...85P}).
-
-Comparing our estimates for $t_\mathrm{exp}$ and $t_0$ (left panel of 
-Figure \ref{fig:velocity_t_exp}), we find that 
-$t_0\lesssim t_\mathrm{exp}$.
-Since physical causality requires $t_\mathrm{exp} \le t_0$, we draw the qualitative
-conclusion that $t_0\simeq t_\mathrm{exp}$, which is consistent to within the uncertainties.
-Again, we caution that this derivation of $t_\mathrm{exp}$ relies on the assumption $v \propto t^{-0.22}$, which may not be valid for all SNe Ia.
+$v\propto(t-t_\mathrm{exp})^{-0.22}$ model by minimizing the $\chi^2$ value
+and find the best-fit explosion time relative to $T_{B,\mathrm{max}}$ in the
+SN rest frame to be $t_\mathrm{exp} = -17.45 \pm ^{0.14}_{0.16}\,\textrm{d}$,
+where the uncertainties represent the 95\% confidence interval (Figure
+\ref{fig:velocity_t_exp}). Following the analysis in
+\citet{2014ApJ...784...85P}, we additionally alter the power-law index to
+$-0.20$ and $-0.24$ to examine the sensitivity of the result on the assumed
+power-law index. We find that this variation in the power-law index results in
+a change of $t_\mathrm{exp}$ of $\approx\pm$0.5\,d (Figure
+\ref{fig:velocity_t_exp}). Given the analytical approximation that $v \propto
+t^{-0.22}$, we adopt $t_\mathrm{exp} = -17.5 \pm 0.5 \; \mathrm{d}$, where the
+uncertainty reflects possible variations in the power-lax index (see
+\citealt{2014ApJ...784...85P}).
+
+Comparing our estimates for $t_\mathrm{exp}$ and $t_0$ (left panel of Figure
+\ref{fig:velocity_t_exp}), we find that $t_0\lesssim t_\mathrm{exp}$. Since
+physical causality requires $t_\mathrm{exp} \le t_0$, we draw the qualitative
+conclusion that $t_0\simeq t_\mathrm{exp}$, which is consistent to within the
+uncertainties. Again, we caution that this derivation of $t_\mathrm{exp}$
+relies on the assumption $v \propto t^{-0.22}$, which may not be valid for all
+SNe Ia.
 
@@
 
-The early spectra of \abc\ exhibit unusually strong absorption due 
-to \ion{C}{2} $\lambda\lambda$6580, 7234. We highlight the evolution 
-of these spectral features in Figure~\ref{fig:carbon}. From these 
-spectra we see that \ion{C}{2}\,$\lambda$6580 is as strong as 
-\ion{Si}{2}\,$\lambda$6355 at $t \approx -15 \; \mathrm{d}$. The 
-strength of the \ion{C}{2} lines declines with time, and by $t \approx -10 \; \mathrm{d}$ \ion{C}{2} is no longer detectable.
+The early spectra of \abc\ exhibit unusually strong absorption due to
+\ion{C}{2} $\lambda\lambda$6580, 7234. We highlight the evolution of these
+spectral features in Figure~\ref{fig:carbon}. From these spectra we see that
+\ion{C}{2}\,$\lambda$6580 is as strong as \ion{Si}{2}\,$\lambda$6355 at $t
+\approx -15 \; \mathrm{d}$. The strength of the \ion{C}{2} lines declines with
+time, and by $t \approx -10 \; \mathrm{d}$ \ion{C}{2} is no longer detectable.
 
@@
   \includegraphics[width=0.49\textwidth]{CarbonFeature.pdf}
-  \caption{Evolution of the \ion{C}{2} features observed in the 
-  early spectra of \abc. The raw spectra are shown in orange, while 
-  the solid blue lines show the best-fit models including Gaussian 
-  components for each line and a linear component for the continuum 
-  (see text for further details). The dark grey vertical lines show 
-  the measured line centers, indicating the decline in the 
+  \caption{
+  Evolution of the \ion{C}{2} features observed in the early spectra of \abc.
+  The raw spectra are shown in orange, while the solid blue lines show the
+  best-fit models including Gaussian components for each line and a linear
+  component for the continuum (see text for further details). The dark grey
+  vertical lines show the measured line centers, indicating the decline in the
   photosphere velocity in the $\sim$7~d after explosion (note that
-  \ion{C}{2}\,$\lambda$7234 is not detected in the $-10.9$\,d 
-  spectrum). The phase of each spectrum relative to 
-  $T_{B,\mathrm{max}}$ is labeled.
+  \ion{C}{2}\,$\lambda$7234 is not detected in the $-10.9$\,d spectrum). The
+  phase of each spectrum relative to $T_{B,\mathrm{max}}$ is labeled.
   }
@@
 
-Similar to our analysis of the \ion{Si}{2}\,$\lambda$6355 line, we 
-can measure velocities and pEWs of 
-\ion{C}{2}\,$\lambda\lambda$6580, 7234. We compare the velocity 
-evolution of the \ion{C}{2} lines to \ion{Si}{2} in the right panel 
-of Figure \ref{fig:velocity_t_exp}, which also shows the pEW evolution of these lines.
-These measurements confirm the qualitative analysis from Figure~\ref{fig:carbon}: namely, the pEW of \ion{C}{2}\,$\lambda$6580 is comparable to that
-of \ion{Si}{2}\,$\lambda$6355 at $t \approx -16 \; \mathrm{d}$ and 
-the pEW of \ion{C}{2} 
-decreases until the feature is no longer detectable 
-around $t = -10$ d.
+Similar to our analysis of the \ion{Si}{2}\,$\lambda$6355 line, we can measure
+velocities and pEWs of \ion{C}{2}\,$\lambda\lambda$6580, 7234. We compare the
+velocity evolution of the \ion{C}{2} lines to \ion{Si}{2} in the right panel
+of Figure \ref{fig:velocity_t_exp}, which also shows the pEW evolution of
+these lines. These measurements confirm the qualitative analysis from
+Figure~\ref{fig:carbon}: namely, the pEW of \ion{C}{2}\,$\lambda$6580 is
+comparable to that of \ion{Si}{2}\,$\lambda$6355 at $t \approx -16 \;
+\mathrm{d}$ and the pEW of \ion{C}{2} decreases until the feature is no longer
+detectable around $t = -10$ d.
 
@@
 
-Roughly 16\,d prior to $B$-band maximum, the $(B - V)_0$ color of \abc\ is $\sim$0.5 mag bluer than SN\,2011fe.
-Like \abc, SN\,2012cg \citep{2016ApJ...820...92M} and SN\,2017cbv \citep{2017ApJ...845L..11H} exhibit $(B - V)_0$ colors that are significantly bluer than SN\,2011fe at very early epochs.
-While there are many factors that contribute to the early optical colors of SNe Ia (see \S\ref{sec:lc_energy} below), early blue colors are often interpreted as a hallmark of interaction between the SN ejecta and a binary companion.
-Nevertheless, it is interesting to note that despite the blue optical colors, the $\mathrm{UV} - \mathrm{optical}$ colors of \abc, SN\,2012cg, and SN\,2017cbv are significantly redder at these early epochs than the $\mathrm{UV} - \mathrm{optical}$ colors of iPTF\,14atg \citep{2015Natur.521..328C}, the most likely candidate for SN ejecta-companion interaction.
-
-\section{Discussion: \textbf{Modeling the Early Evolution of \abc}}
-\label{sec:lc_energy}
-
-Relative to the nearby, normal SN\,2011fe, we have identified several distinct characteristics of the early evolution of \abc, including: (i) a near-linear photometric rise, (ii) a qualitatively short, or possibly absent, dark phase, assuming $v_\mathrm{ph} \propto t^{-0.22}$, (iii) the presence of strong \ion{C}{2} absorption, and (iv) blue and non-evolving $(B - V)_0$ color in the week after explosion.
-While most SNe Ia are powered purely by radioactive decay, the observed radiation shortly after explosion can also include contributions
-from SN shock cooling or the collision of the SN ejecta with a non-degenerate companion or \textbf{nearby, unbound} material.
-Here we consider those scenarios as a possible explanation for the early behavior of \abc.
+Roughly 16\,d prior to $B$-band maximum, the $(B - V)_0$ color of \abc\ is
+$\sim$0.5 mag bluer than SN\,2011fe. Like \abc, SN\,2012cg
+\citep{2016ApJ...820...92M} and SN\,2017cbv \citep{2017ApJ...845L..11H}
+exhibit $(B - V)_0$ colors that are significantly bluer than SN\,2011fe at
+very early epochs. While there are many factors that contribute to the early
+optical colors of SNe Ia (see \S\ref{sec:lc_energy} below), early blue colors
+are often interpreted as a hallmark of interaction between the SN ejecta and a
+binary companion. Nevertheless, it is interesting to note that despite the
+blue optical colors, the $\mathrm{UV} - \mathrm{optical}$ colors of \abc,
+SN\,2012cg, and SN\,2017cbv are significantly redder at these early epochs
+than the $\mathrm{UV} - \mathrm{optical}$ colors of iPTF\,14atg
+\citep{2015Natur.521..328C}, the most likely candidate for SN ejecta-companion
+interaction.
+
+\section{\textbf{Modeling the Early Evolution of \abc}} \label{sec:lc_energy}
+
+Relative to the nearby, normal SN\,2011fe, we have identified several distinct
+characteristics of the early evolution of \abc, including: (i) a near-linear
+photometric rise, (ii) a qualitatively short, or possibly absent, dark phase,
+assuming $v_\mathrm{ph} \propto t^{-0.22}$, (iii) the presence of strong
+\ion{C}{2} absorption, and (iv) blue and non-evolving $(B - V)_0$ color in the
+week after explosion. While most SNe Ia are powered purely by radioactive
+decay, the observed radiation shortly after explosion can also include
+contributions from SN shock cooling or the collision of the SN ejecta with a
+non-degenerate companion or \textbf{nearby, unbound} material. Here we
+consider those scenarios as a possible explanation for the early behavior of
+\abc.
 
@@
 \textbf{In Figure~\ref{fig:noebauer} we compare photometric observations of
-\abc\ to the models presented in
-\citet{2017MNRAS.472.2787N}.
-Interestingly, the sub-Chandrasekhar double detonation model (subChDoubleDet) replicates the early wiggle in the $V$-band light curve.
-However, this match requires an explosion \textit{after} our initial detection of \abc, \textit{and} extreme color evolution.
-Thus, the subChDoubleDet model is incompatible with the observations.
-The sub-Chandrasekhar detonation (subChDet) provides a better match to the observations, though this model is not favored as a particularly realistic scenario (see above).
-Of the sub-Chandrasekhar models the violent merger model (Merger) provides the best match to the observations including the early rise and color evolution.
-In detail, however, this model does not match the early wiggles in the light curve, has consistently redder colors than \abc, and requires $t_\mathrm{exp} \approx 2.3$\,d prior to $t_0$.
-As such, we postulate that \abc\ is not the result of a violent WD-WD merger.}
-
-\textbf{For clarity, of the two pure deflagration models only N5def is shown, however, the evolution of N1600Cdef is very similar.
-While the pure deflagration models produce the bluest colors at early times, they are underluminous at times $> t_0 + 4\,\mathrm{d}$ and already rapidly evolving towards the red at $\sim$$t_0 + 7$ (\abc\ exhibits a nearly constant $(B-V)_0$ color for $\sim$19\,d after $t_0$).
-Thus, we conclude that \abc\ is not compatible with pure deflagrations.}
-
-\textbf{Of the $M_\textrm{Ch}$ models, the W7 model better matches the observations as the N100 model features a faster rise and higher luminosity than what is observed.
-We explore delayed detonation models in further detail below.
-}
+\abc\ to the models presented in \citet{2017MNRAS.472.2787N}. Interestingly,
+the sub-Chandrasekhar double detonation model (subChDoubleDet) replicates the
+early wiggle in the $V$-band light curve. However, this match requires an
+explosion \textit{after} our initial detection of \abc, \textit{and} extreme
+color evolution. Thus, the subChDoubleDet model is incompatible with the
+observations. The sub-Chandrasekhar detonation (subChDet) provides a better
+match to the observations, though this model is not favored as a particularly
+realistic scenario (see above). Of the sub-Chandrasekhar models the violent
+merger model (Merger) provides the best match to the observations including
+the early rise and color evolution. In detail, however, this model does not
+match the early wiggles in the light curve, has consistently redder colors
+than \abc, and requires $t_\mathrm{exp} \approx 2.3$\,d prior to $t_0$. As
+such, we postulate that \abc\ is not the result of a violent WD-WD merger.}
+
+\textbf{For clarity, of the two pure deflagration models only N5def is shown,
+however, the evolution of N1600Cdef is very similar. While the pure
+deflagration models produce the bluest colors at early times, they are
+underluminous at times $> t_0 + 4\,\mathrm{d}$ and already rapidly evolving
+towards the red at $\sim$$t_0 + 7$ (\abc\ exhibits a nearly constant $(B-V)_0$
+color for $\sim$19\,d after $t_0$). Thus, we conclude that \abc\ is not
+compatible with pure deflagrations.}
+
+\textbf{Of the $M_\textrm{Ch}$ models, the W7 model better matches the
+observations as the N100 model features a faster rise and higher luminosity
+than what is observed. We explore delayed detonation models in further detail
+below.}
 

### 2017-11-16 doc/ms.tex
acknowledge the referee

@@
            At early times, core-normal and broad-line SNe have significantly
-           faster \ion{Si}{2} than \abc, while the declining trend of coolSNe
+           faster \ion{Si}{2} than \abc, while the declining trend of cool SNe
            does not match \abc.}
@@
 
-We are deeply grateful to R.~C.~Thomas for indulging a slew of questions regarding \ion{C}{2} in SNe.
-Similarly, it is our pleasure to buy a beer for R.~Amanullah and U.~Feindt for discussions regarding SALT2.
+\textbf{This study has benefited from the suggestions of an anonymous
+referee.} We are deeply grateful to R.~C.~Thomas for indulging a slew of
+questions regarding \ion{C}{2} in SNe. Similarly, it is our pleasure to buy a
+beer for R.~Amanullah and U.~Feindt for discussions regarding SALT2.
 

### 2017-11-16 doc/ms.tex
update title and abstract to emphasize interaction over mixing

@@
 
-\title{Early Observations of \abc:\\
-\textbf{a Type Ia Supernova Featuring Either} Strong Ejecta Mixing and/or Interaction with Diffuse Material}
+\title{Early Observations of the Type Ia Supernova \abc:\\
+\textbf{a Case of Interaction with Nearby, Unbound Material and/or} Strong Ejecta Mixing}
 
@@
 including: (i) the rapid, near-linear rise, (ii) the non-evolving blue colors,
-and (iii) the strong absorption from ionized carbon, are the result of either
-vigorous mixing of radioactive $^{56}$Ni in the SN ejecta, or ejecta
-interaction with diffuse material, or a combination of the two. In the next
-few years, dozens of very young \textit{normal} SNe Ia will be discovered, and
-observations similar to those presented here will constrain the white dwarf    
-explosion mechanism.
+and (iii) the strong \textbf{\ion{C}{2}} absorption, are the result of either
+\textbf{ejecta interaction with nearby, unbound material or vigorous mixing of
+radioactive $^{56}$Ni in the SN ejecta,} or a combination of the two. In the
+next few years, dozens of very young \textit{normal} SNe Ia will be
+discovered, and observations similar to those presented here will constrain
+the white dwarf explosion mechanism.
 

### 2017-11-16 doc/ms.tex
include revisions to the intro in the manuscript

@@
 %% keywords and the rules for their use.
-\keywords{methods: observational --- surveys --- supernovae: general --- supernovae: individual (\abc)}
+\keywords{methods: observational --- surveys --- supernovae: general --- supernovae: individual (\abc, SN\,2011fe)}
 
@@
 \textbf{(e.g.,
-\citealt{2014MNRAS.441..532D,2016ApJ...826...96P,2017MNRAS.466.3784S,2017MNRAS.472.2787N})}.
+\citealt{2014MNRAS.441..532D,2016ApJ...826...96P,2017MNRAS.472.2787N})}.
 
@@
 The duration of this dark phase is set by how the newly synthesized $^{56}$Ni
-is mixed and deposited into different layers of the ejecta. In the case of
-strong mixing, the dark phase is short, or non-existent, as $\gamma$-rays from
-the radioactive $^{56}$Ni diffuse to the photosphere rapidly. This also leads
-to blue optical colors and a rapid initial rise in the observed light curve.
+is mixed and deposited into different layers of the ejecta. \textbf{Strong
+mixing leads to a short, or non-existent, dark phase, because the radioactive
+$\gamma$-rays rapidly diffuse to the photosphere.} This also leads to
+\textbf{larger luminosities and bluer optical colors at early times}.
 \textbf{Even with vigorous mixing it is difficult at very early times, $<
@@
 $^{56}$Co.} If the mixing is weak and the $^{56}$Ni is confined to the
-innermost layers of the ejecta, the dark phase can last for several days. The
-early evolution of such SNe results in redder colors and a more moderate rise
-in luminosity \citep{2014MNRAS.441..532D,2016ApJ...826...96P}. Thus, the early
+innermost layers of the ejecta, the dark phase can last for several days.
+\textbf{Weak mixing} results in redder colors and a more moderate rise in
+luminosity \citep{2014MNRAS.441..532D,2016ApJ...826...96P}. Thus, the early
 light curves of even non-exotic Type Ia SNe convey information about their
-progenitor systems by constraining the distribution of synthesized $^{56}$Ni,
-which in turn constrains the explosion mechanism.
-
+progenitor systems and explosion mechanisms by constraining the distribution
+of $^{56}$Ni.
 % \footnote{\citet{2015A&A...574A..60T} found that a significant dark
@@
 
-\citet{2017MNRAS.472.2787N} demonstrate that disambiguating between these different scenarios via optical photometry alone is challenging.
-\citeauthor{2017MNRAS.472.2787N} further show that estimates of the time of explosion, which are critical for comparing models with observations, are often incorrect by as \textbf{much} as $\sim$2\,d using common methods in the literature.
-While analytical models suggest that early spectra can be used to infer the time of explosion (e.g., \citealt{2014ApJ...784...85P}), more detailed simulations show that the photospheric evolution is not so simple \citep{2016ApJ...826...96P}.
-Reconciling these issues requires both a larger sample of early SNe Ia observations and more detailed models that produce synthetic light curves and spectra.
-
-In this paper, we report observations of an extraordinarily young SN Ia, \abc, which was discovered by the intermediate Palomar Transient Factory (iPTF) on 2016 April $3.36$ UTC at $\textrm{R.A.}=13^h34^m45.49^s$, $\textrm{Dec.}=+13\degr51\arcmin14\farcs3$ (J2000) with a $g_\mathrm{PTF}$-band magnitude of $21.31\pm0.27$ \citep{2016ATel.8907....1M}.
-The transient is spatially coincident with a tidal tail of the galaxy NGC\,5221, which lies at a distance of $\sim$100\,Mpc.
-\abc\ is not detected to a limit of $g=22.1$\,mag on April $2.42$, less than 1\,d prior to discovery, and rose by $\sim$2 mag in the 24 hr following its initial detection.
-Our spectroscopic follow-up
-campaign classified \abc\ as a normal SN Ia
-\citep{2016ATel.8909....1C}.
-Our observations and analysis show that the early evolution of \abc\ exhibited several distinct properties relative to SN\,2011fe.
-We interpret those differences as arising from either strong $^{56}$Ni mixing or ejecta interaction with diffuse material, or a combination of the two.
-Alongside this paper, we have released our open source analysis and all of the data utilized in this study.
-These are available online at \texttt{GitHub} \url{https://github.com/adamamiller/iPTF16abc}.
+\citet{2017MNRAS.472.2787N} demonstrate that disambiguating between these
+different scenarios via optical photometry alone is challenging.
+\citeauthor{2017MNRAS.472.2787N} further show that estimates of the time of
+explosion, which are critical for comparing models with observations, are
+often incorrect by as \textbf{much} as $\sim$2\,d using common methods in the
+literature. While analytical models suggest that early spectra can be used to
+infer the time of explosion (e.g., \citealt{2014ApJ...784...85P}), more
+detailed simulations show that the photospheric evolution is not so simple
+\citep{2016ApJ...826...96P}. Reconciling these issues requires both a larger
+sample of early SNe Ia observations and more detailed models that produce
+synthetic light curves and spectra.
+
+In this paper, we report observations of an extraordinarily young SN Ia, \abc,
+which was discovered by the intermediate Palomar Transient Factory (iPTF) on
+2016 April $3.36$ UTC at $\textrm{R.A.}=13^h34^m45.49^s$,
+$\textrm{Dec.}=+13\degr51\arcmin14\farcs3$ (J2000) with a
+$g_\mathrm{PTF}$-band magnitude of $21.31\pm0.27$ \citep{2016ATel.8907....1M}.
+The transient is spatially coincident with a tidal tail of the galaxy
+NGC\,5221, which lies at a distance of $\sim$100\,Mpc. \abc\ is not detected
+to a limit of $g_\mathrm{PTF}=22.1$\,mag on April $2.42$, less than 1\,d prior
+to discovery, and rose by $\sim$2\,mag in the 24\,hr following its initial
+detection. Our spectroscopic follow-up campaign classified \abc\ as a normal
+SN Ia \citep{2016ATel.8909....1C}. Our observations and analysis show that the
+early evolution of \abc\ exhibited several distinct properties relative to
+SN\,2011fe. We interpret those differences as arising from either strong
+$^{56}$Ni mixing or ejecta interaction with \textbf{nearby, unbound} material,
+or a combination of the two. Alongside this paper, we have released our open
+source analysis and all of the data utilized in this study. These are
+available online at \texttt{GitHub}
+\url{https://github.com/adamamiller/iPTF16abc}.
 
@@
 This paper utilizes the LCO infrastructure for rapid and regular monitoring of SNe, and we thank S.~Valenti and I.~Arcavi for their development efforts.
+\textbf{Figure~\ref{fig:branch_vel} would not have been possible without S.~Blondin generously sharing the data from \citet{2012AJ....143..126B}.}
 

### 2017-11-16 doc/ms.tex
update text in observations section

@@
 
-During the spring of 2016, the iPTF survey observed the field of \abc\ every night during dark time in either the $g_\mathrm{PTF}$ or 
-$R_\mathrm{PTF}$ band.\footnote{P48 observations of \abc\ are reported in the $g_\mathrm{PTF}$ and $R_\mathrm{PTF}$ filters throughout, which are similar to the SDSS $g'$ and Mould-$R$ filters, respectively (see \citealt{2012PASP..124..854O} for details on PTF calibration).
-The correction from the $g_\mathrm{PTF}$ and $R_\mathrm{PTF}$ filters to SDSS $g'$ and $r'$ requires knowledge of the intrinsic source color (see Eqns.~1 and 2 in \citealt{2012PASP..124..854O}).
-The spectral diversity of SNe Ia in the days after explosion is poorly constrained, and as a result the color terms for \abc\ at these epochs are unknown.
-We proceed by assuming the $g_\mathrm{PTF}$ and $R_\mathrm{PTF}$ calibration is on the AB system, which strictly speaking is incorrect, but this does not fundamentally alter any of our conclusions.}
-Survey observations were conducted with the
-CFH12K camera \citep{2008SPIE.7014E..4YR} on the Palomar Observatory 
-48-inch telescope (P48; \citealt{2009PASP..121.1395L}). Images were processed by the IPAC image
-subtraction and discovery pipeline which subtracts off the background
-galaxy light with stacked pre-SN images and performs forced
+During the spring of 2016, the iPTF survey observed the field of \abc\ every
+night during dark time in either the $g_\mathrm{PTF}$ or $R_\mathrm{PTF}$
+band.\footnote{P48 observations of \abc\ are reported in the $g_\mathrm{PTF}$
+and $R_\mathrm{PTF}$ filters throughout, which are similar to the SDSS $g'$
+and Mould-$R$ filters, respectively (see \citealt{2012PASP..124..854O} for
+details on PTF calibration). The correction from the $g_\mathrm{PTF}$ and
+$R_\mathrm{PTF}$ filters to SDSS $g'$ and $r'$ requires knowledge of the
+intrinsic source color (see Eqns.~1 and 2 in \citealt{2012PASP..124..854O}).
+The spectral diversity of SNe Ia in the days after explosion is poorly
+constrained, and as a result the color terms for \abc\ at these epochs are
+unknown. We proceed by assuming the $g_\mathrm{PTF}$ and $R_\mathrm{PTF}$
+calibration is on the AB system, which strictly speaking is incorrect, but
+this does not fundamentally alter any of our conclusions.} Survey observations
+were conducted with the CFH12K camera \citep{2008SPIE.7014E..4YR} on the
+Palomar Observatory 48-inch telescope (P48; \citealt{2009PASP..121.1395L}).
+Images were processed by the IPAC image-subtraction pipeline, which subtracts
+background galaxy light \textbf{using deep} pre-SN images, and performs forced
 point-spread-function (PSF) photometry at the location of the SN
-\citep{2017PASP..129a4002M}. The
-photometry is then calibrated to the PTF photometric catalog
-\citep{2012PASP..124..854O}.
+\citep{2017PASP..129a4002M}. The photometry is then calibrated to the PTF
+photometric catalog \citep{2012PASP..124..854O}.
 
@@
     \includegraphics[width=0.48\textwidth]{logLC_with_colors.pdf} 
-  \caption{The $g$-band
-  light curve of \abc. Observations from different 
-  telescopes are shown with different symbols. Time is measured in 
-  rest-frame days relative to the time of first light, $t_0$ (see 
-  \S\ref{sec:lc_fit}). Note that the horizontal axis is shown with 
-  a linear scale for $-2 \; \mathrm{d} \le t - t_0 \le 3 \; 
+    \caption{
+    The $g$-band light curve of \abc. Observations from different telescopes
+    are shown with different symbols. Time is measured in rest-frame days
+    relative to $t_0$ (see \S\ref{sec:lc_fit}). Note that the horizontal axis
+    is shown with a linear scale for $-2 \; \mathrm{d} \le t - t_0 \le 3 \;
     \mathrm{d}$ and a $\log$ scale for $t - t_0 > 3 \; \mathrm{d}$.
-  The black ticks near the
-  bottom of the panel show epochs of spectroscopic observations.
-  }
+    \textbf{Vertical} black ticks show epochs of spectroscopic observations. }
     \label{fig:lightcurve} 
@@
 
-After discovery, photometric observations in the $g'$, $r'$ and $i'$
-filters were obtained with the SED Machine 
-(SEDm; Blagorodnova et al.\ 2017, in prep.) mounted on the Palomar Observatory 
-60-inch telescope (P60).
-We utilized the Fremling Automated Pipeline (\texttt{FPipe}; \citealt{2016A&A...593A..68F}) to subtract galaxy light from the SEDm images using archival Sloan Digital Sky Survey (SDSS) images as a reference.
-This pipeline then performed forced-PSF photometry at the location of \abc, which is calibrated to the SDSS catalog \citep{2014ApJS..211...17A}.
-
-Photometric observations in the $BVg'r'i'$ filters were conducted by the Las Cumbres Observatory (LCO) 1-m
-telescope network.  PSF photometry was measured on these images using
-the \texttt{lcogtsnpipe} pipeline \citep{2016MNRAS.459.3939V}. The
-\textit{BV} magnitudes are calibrated to the Fourth USNO CCD
-Astrograph Catalog \citep{2013AJ....145...44Z}, and the \textit{g'r'i'}
-magnitudes are calibrated to SDSS Data Release 6
-\citep{2008ApJS..175..297A}.
-
-The Reionization and Transients InfraRed (RATIR) camera on the autonomous 1.5\,m Harold L.
-Johnson Telescope at the Observatorio Astron\'{o}mico Nacional \citep{2012SPIE.8446E..10B,2012SPIE.8444E..5LW} was used to observe \abc\ in the $r'i'ZYJH$ filters.
-By design, RATIR lacks a cold shutter, which means IR dark frames are not available.
-Laboratory testing, however, confirms that the dark current is negligible in both IR detectors \citep{2012SPIE.8453E..1OF}.
-
-The RATIR data were reduced, coadded, and analyzed using standard CCD and IR processing techniques in \texttt{IDL}, \texttt{Python}, \texttt{SExtractor} \citep{1996A&AS..117..393B}, and \texttt{SWarp}.
-Aperture photometry is obtained following the methods described in \citet{2014AJ....148....2L}.
-The $r'i'Z$ filters are calibrated to SDSS \citep{2014ApJS..211...17A}, while the $JH$ filters are calibrated to the Two Micron All Sky Survey \citep{2006AJ....131.1163S}.
-For the $Y$-band calibration, we used an empirical relation in terms of the $J$ and $H$ magnitudes derived from the United Kingdom Infrared Telescope (UKIRT; \citealt{2007A&A...467..777C}) Wide Field Camera observations \citep{2009MNRAS.394..675H}.
+After discovery, $g'$, $r'$ and $i'$-band \textbf{photometry was} obtained
+with the SED Machine (SEDm; \citealt{2017arXiv171002917B}) mounted on the
+Palomar Observatory 60-inch telescope (P60). We utilized the Fremling
+Automated Pipeline (\texttt{FPipe}; \citealt{2016A&A...593A..68F}) to subtract
+galaxy light from the SEDm images using archival Sloan Digital Sky Survey
+(SDSS) images as a reference. This pipeline then performed forced-PSF
+photometry at the location of \abc, which is calibrated to the SDSS catalog
+\citep{2014ApJS..211...17A}.
+
+\textbf{The Las Cumbres Observatory (LCO) 1-m telescope network obtained
+$BVg'r'i'$ photometry.} PSF photometry was measured on these images using the
+\texttt{lcogtsnpipe} pipeline \citep{2016MNRAS.459.3939V}. The \textit{BV}
+magnitudes are calibrated to the Fourth USNO CCD Astrograph Catalog
+\citep{2013AJ....145...44Z}, and the \textit{g'r'i'} magnitudes are calibrated
+to SDSS Data Release 6 \citep{2008ApJS..175..297A}.
+
+The Reionization and Transients InfraRed (RATIR) camera on the autonomous
+1.5\,m Harold L. Johnson Telescope
+\citep{2012SPIE.8446E..10B,2012SPIE.8444E..5LW} was used to observe \abc\ in
+the $r'i'ZYJH$ filters. By design, RATIR lacks a cold shutter, which means IR
+dark frames are not available. Laboratory testing, however, confirms that the
+dark current is negligible in both IR detectors \citep{2012SPIE.8453E..1OF}.
+
+The RATIR data were reduced, coadded, and analyzed using standard CCD and IR
+processing techniques in \texttt{IDL}, \texttt{Python}, \texttt{SExtractor}
+\citep{1996A&AS..117..393B}, and \texttt{SWarp}. Aperture photometry is
+obtained following the methods described in \citet{2014AJ....148....2L}. The
+$r'i'Z$ filters are calibrated to SDSS \citep{2014ApJS..211...17A}, while the
+$JH$ filters are calibrated to the Two Micron All Sky Survey
+\citep{2006AJ....131.1163S}. For the $Y$-band calibration, we used an
+empirical relation in terms of the $J$ and $H$ magnitudes derived from the
+United Kingdom Infrared Telescope (UKIRT; \citealt{2007A&A...467..777C}) Wide
+Field Camera observations \citep{2009MNRAS.394..675H}.
 
 The \textit{Swift} satellite observed \abc\ on 14 epochs, beginning
-$\sim$15\,d pre-maximum light through $\sim$22\,d post maximum. The SN 
-flux is measured via aperture photometry on Ultraviolet-Optical
-Telescope (UVOT) images via the usual procedures in 
-\texttt{HEASoft}, including corrections for coincidence loss and 
-aperture loss. The image counts
-are converted to physical fluxes using the latest calibration
-\citep{2011AIPC.1358..373B}. There are no pre-SN UVOT images at the 
-SN location in the \textit{Swift} archive.  Visual inspection of the
-UVOT images suggests negligible host-galaxy contamination in our 
-UVOT flux measurements. No X-ray emission is detected from \abc\ by the \textit{Swift} X-ray Telescope (XRT).
-
-The $g$-band discovery and follow-up data of \abc\ are 
-illustrated in Figure~\ref{fig:lightcurve}.
-The photometry is shown in the AB system.
-As previously noted the color terms necessary to convert $g_\mathrm{PTF}$ to the AB system are unknown and assumed to be zero.
-
-Spectroscopic observations of \abc\ were taken with a variety
-of telescopes and instruments over multiple epochs spanning from a
-couple of days after discovery to two months after $B$-band maximum. 
-An observing log is listed in Table \ref{tab:spec_obs_log}. The spectra were reduced using standard routines in \texttt{IDL}/\texttt{Python}/\texttt{Matlab}. The optical
-spectral evolution of \abc\ is illustrated in Figure
-\ref{fig:spec_seq}, which excludes high-resolution Very Large Telescope (VLT) spectra for clarity.
+$\sim$15\,d pre-maximum light through $\sim$22\,d post maximum. The SN flux is
+measured via aperture photometry on Ultraviolet-Optical Telescope (UVOT)
+images via the usual procedures in \texttt{HEASoft}, including corrections for
+coincidence loss and aperture loss. The image counts are converted to physical
+fluxes using the latest calibration \citep{2011AIPC.1358..373B}. There are no
+pre-SN UVOT images at the SN location in the \textit{Swift} archive. Visual
+inspection of the UVOT images suggests negligible host-galaxy contamination in
+our UVOT flux measurements. No X-ray emission is detected from \abc\ by the
+\textit{Swift} X-ray Telescope (XRT).
+
+The $g$-band discovery and follow-up data of \abc\ are illustrated in
+Figure~\ref{fig:lightcurve}. The photometry is shown in the AB system. As
+previously noted the color terms necessary to convert $g_\mathrm{PTF}$ to the
+AB system are unknown and assumed to be zero.
+
+Spectroscopic observations of \abc\ were taken with a variety of telescopes
+and instruments over multiple epochs \textbf{beginning $\sim$2\,d} after
+discovery \textbf{and ending $\sim$2} months after $B$-band maximum. An
+observing log is listed in Table \ref{tab:spec_obs_log}. The spectra were
+reduced using standard procedures in
+\texttt{IDL}/\texttt{Python}/\texttt{Matlab}. The optical spectral evolution
+of \abc\ is illustrated in Figure \ref{fig:spec_seq}, which excludes
+high-resolution Very Large Telescope (VLT) spectra for clarity.
 
@@
   \includegraphics[width=0.69\textwidth]{spectra.pdf}
-  \caption{Observed spectral sequence of \abc. The spectra are 
-  normalized by their median flux between 6,000 and 
-  7,000$\,\textrm{\AA}$.  The phase of each spectrum 
-  relative to \textbf{the time of $B$-band maximum} is shown. Telluric absorption
-  bands are grayed out. Line identifications are provided for 
-  the spectral features discussed in the text. 
-  For clarity, high-resolution spectra obtained with the VLT have been omitted (see Ferretti et al.\ 2017, submitted, for a detailed discussion of these spectra).}
+  \caption{
+  Observed spectral sequence of \abc. The spectra are normalized by their
+  median flux between 6000 and 7000$\,\textrm{\AA}$. The phase of each
+  spectrum relative to \textbf{the time of $B$-band maximum} is shown.
+  Telluric absorption bands are grayed out. Line identifications are provided
+  for the spectral features discussed in the text. For clarity,
+  high-resolution spectra obtained with the VLT have been omitted (see
+  \citealt{2017A&A...606A.111F} for a detailed discussion of these spectra).}
   \label{fig:spec_seq}
@@
 A detailed study of the reddening towards \abc\ is presented in a 
-companion paper (Ferretti et al.\ 2017, submitted). Briefly, the 
+companion paper \citep{2017A&A...606A.111F}. Briefly, the 
 foreground Galactic extinction toward \abc\
 is $E(B-V) = 0.0279 \, \mathrm{mag}$ \citep{2011ApJ...737..103S}.
-The high-resolution spectra presented in Ferretti et al.\ (2017) show multiple absorption components for both the \ion{Ca}{2}\,H$+$K and \ion{Na}{1}\,D doublets.
-While the equivalent width (EW) of these lines is quite large, implying significant extinction (e.g., \citealt{2012MNRAS.426.1465P}), Ferretti et al.\ compare the evolution of \abc\ to the well-observed normal Type Ia SN\,2011fe and only find evidence for a small amount of extinction.
+The high-resolution spectra presented in \citet{2017A&A...606A.111F} show multiple absorption components for both the \ion{Ca}{2}\,H$+$K and \ion{Na}{1}\,D doublets.
+While the equivalent width (EW) of these lines is quite large, implying significant extinction (e.g., \citealt{2012MNRAS.426.1465P}), \citeauthor{2017A&A...606A.111F} compare the evolution of \abc\ to the well-observed normal Type Ia SN\,2011fe and only find evidence for a small amount of extinction.
 The empirical relation between the EW of \ion{Na}{1}\,D and extinction is known to have a large scatter, and \citet{2013ApJ...779...38P} have shown that \ion{Na}{1}\,D absorption is a poor tracer of reddening in Type Ia SNe.
-Thus, we adopt $E(B-V) = 0.05 \, \mathrm{mag}$ as the local extinction for \abc\ (Ferretti et al.\ 2017).
+Thus, we adopt $E(B-V) = 0.05 \, \mathrm{mag}$ as the local extinction for \abc\ \citep{2017A&A...606A.111F}.
 For the remainder of our analysis we assume a total, Galactic $+$ host galaxy, line-of-sight extinction of $E(B-V) = 0.08 \, \mathrm{mag}$.

### 2017-11-16 doc/ms.tex
update text in the classification section

@@
 
-The location of \abc\ is spatially coincident with a tidal tail of
-galaxy NGC\,5221. \citet{2007A&A...465...71T} derived a distance
-modulus of $35.0\pm0.4\,\textrm{mag}$ to NGC\,5221 from the 
-Tully-Fisher relation, which is consistent with what we later derive from the SN light curve (see \S\ref{sec:classification}).
-
-Separately, \citet{2015MNRAS.447.1531C} observe the 21-cm line in
-NGC\,5221 and measure a redshift of $0.0234$, which we adopt for the remaining analysis in this paper.
+\abc\ is spatially coincident with a tidal tail of galaxy NGC\,5221.
+\citet{2007A&A...465...71T} derived a distance modulus of
+$35.0\pm0.4\,\textrm{mag}$ to NGC\,5221 from the Tully-Fisher relation,
+consistent with \textbf{our derivation} from the SN light curve (see
+\S\ref{sec:classification}).
+
+Separately, \citet{2015MNRAS.447.1531C} observe the 21-cm line in NGC\,5221
+and measure a redshift of $0.0234$, which we adopt for the remaining analysis
+in this paper.
 
@@
 
-A detailed study of the reddening towards \abc\ is presented in a 
-companion paper \citep{2017A&A...606A.111F}. Briefly, the 
-foreground Galactic extinction toward \abc\
-is $E(B-V) = 0.0279 \, \mathrm{mag}$ \citep{2011ApJ...737..103S}.
-The high-resolution spectra presented in \citet{2017A&A...606A.111F} show multiple absorption components for both the \ion{Ca}{2}\,H$+$K and \ion{Na}{1}\,D doublets.
-While the equivalent width (EW) of these lines is quite large, implying significant extinction (e.g., \citealt{2012MNRAS.426.1465P}), \citeauthor{2017A&A...606A.111F} compare the evolution of \abc\ to the well-observed normal Type Ia SN\,2011fe and only find evidence for a small amount of extinction.
-The empirical relation between the EW of \ion{Na}{1}\,D and extinction is known to have a large scatter, and \citet{2013ApJ...779...38P} have shown that \ion{Na}{1}\,D absorption is a poor tracer of reddening in Type Ia SNe.
-Thus, we adopt $E(B-V) = 0.05 \, \mathrm{mag}$ as the local extinction for \abc\ \citep{2017A&A...606A.111F}.
-For the remainder of our analysis we assume a total, Galactic $+$ host galaxy, line-of-sight extinction of $E(B-V) = 0.08 \, \mathrm{mag}$.
+A detailed study of the reddening towards \abc\ is presented in a companion
+paper \citep{2017A&A...606A.111F}. Briefly, the foreground Galactic extinction
+toward \abc\ is $E(B-V) = 0.0279$\,mag \citep{2011ApJ...737..103S}.
+High-resolution spectra of \abc\ show multiple absorption components for both
+the \ion{Ca}{2}\,H$+$K and \ion{Na}{1}\,D doublets. \textbf{Despite large
+equivalent widths (EWs) for these lines, implying significant extinction
+(e.g., \citealt{2012MNRAS.426.1465P}), \citeauthor{2017A&A...606A.111F}~find
+evidence for only a small amount of extintion.} The empirical relation between
+the EW of \ion{Na}{1}\,D and extinction has a large scatter, and
+\citet{2013ApJ...779...38P} have shown that \ion{Na}{1}\,D absorption is a
+poor tracer of reddening in Type Ia SNe. Thus, we adopt $E(B-V) = 0.05 \,
+\mathrm{mag}$ as the local extinction for \abc\ \citep{2017A&A...606A.111F}.
+For the remainder of our analysis we assume a total, Galactic $+$ host galaxy,
+line-of-sight extinction of $E(B-V) = 0.08 \, \mathrm{mag}$.
 
@@
 \abc\ at $+18.8$\,d is best matched by normal SNe Ia. Several characteristic
-features of a SN Ia, such as \ion{Si}{2}, \ion{S}{2}, can be easily identified
-in the spectra of \abc\ (Figure \ref{fig:spec_seq}). From the $+3.7 \,
-\mathrm{d}$ LCO spectrum, we measure the pseudo-equivalent widths (pEWs) of
-the absorption features near 5750 and 6100 \AA, which are respectively
-attributed to \ion{Si}{2}\,$\lambda\lambda$6580, 7234, to be $-12 \pm 2$\,\AA\
-and $-55 \pm 5$\,\AA, respectively. According to the classification scheme
-presented in \citet{2006PASP..118..560B}, these pEW measurements indicate that
-\abc\ is a shallow silicon SN, similar to the SN\,1999aa-likes
-\citep{2009PASP..121..238B}. \textbf{In Figure~\ref{fig:branch_vel}, the
-velocity evolution of \ion{Si}{2}$\,\lambda6355$ in \abc\ is compared to the
-median evolution of the four spectroscopic subclasses defined in
+features of a SN Ia, such as \ion{Si}{2} and \ion{S}{2}, can be easily
+identified in \abc\ (Figure \ref{fig:spec_seq}). From the $+3.7 \, \mathrm{d}$
+LCO spectrum, we measure the pseudo-equivalent widths (pEWs) of $-12 \pm
+2$\,\AA\ and $-55 \pm 5$\,\AA\ for the absorption features near 5750 and 6100
+\AA, attributed to \ion{Si}{2}\,$\lambda\lambda$5972, 6355, respectively.
+According to the \citet{2006PASP..118..560B} classification scheme, \abc\ is a
+shallow silicon SN, similar to 1999aa-like SNe \citep{2009PASP..121..238B}.
+\textbf{In Figure~\ref{fig:branch_vel}, the velocity evolution of the \abc\
+\ion{Si}{2}$\,\lambda6355$ absorption minimum is compared to the median
+evolution of the four spectroscopic subclasses from
 \citet{2006PASP..118..560B}. The median evolution is defined using the sample
@@
 \ion{Si}{2} velocity, $v_{\mathrm{Si\,II}\,\lambda6355}$, to a fixed grid at
-1\,d intervals. We then take the median $v_{\mathrm{Si\,II}\,\lambda6355}$ for
-each point on the grid, and only retain those points with at least 3 SNe (to
-prevent the early and late evolution to be defined by a single SN). The
-evolution of \ion{Si}{2} is most reminicent of the shallow-silicon subclass
-defined in \citet{2006PASP..118..560B}. }
+1\,d intervals. The curves are defined by the median
+$v_{\mathrm{Si\,II}\,\lambda6355}$ at each point on the grid with at least 3
+SNe (this prevents just 1 or 2 SNe from defining the evolution of the entire
+subclass). The velocity evolution of \abc\ is most reminicent of the
+shallow-silicon subclass.}
 
@@
   \includegraphics[width=0.48\textwidth]{Branch_vel_evol.pdf}
-  \caption{\textbf{Velocity evolution of \ion{Si}{2},   
-           $v_{\mathrm{Is\,II}\,\lambda6355}$, for \abc\ compared to the median
+  \caption{
+
+  \textbf{Velocity evolution of \ion{Si}{2},
+  $v_{\mathrm{Si\,II}\,\lambda6355}$, for \abc\ compared to the median
   evolution of the four spectroscopic subclasses defined in
-           \citet{2006PASP..118..560B}, using data from
-           \citet{2012AJ....143..126B}. Typical uncertainties for \abc\ are
-           $\sim$1000\,km\,s$^{-1}$ before $T_{B,\mathrm{max}}$, when the
-           \ion{Si}{2}$\,\lambda6355$ profile is shallow and the minimum of
-           absorption is difficult to determine, and $\sim$300\,km\,s$^{-1}$
-           after $T_{B,\mathrm{max}}$. For the median curves, the typical
-           scatter, determined via the interquartile range of the sample, is
-           $\sim$700\,km\,s$^{-1}$, around $T_{B,\mathrm{max}}$.
-           At early times, core-normal and broad-line SNe have significantly
-           faster \ion{Si}{2} than \abc, while the declining trend of cool SNe
-           does not match \abc.}
-  }
+  \citet{2006PASP..118..560B}, using data from \citet{2012AJ....143..126B}.
+  Typical uncertainties for \abc\ are $\sim$1000\,km\,s$^{-1}$ before
+  $T_{B,\mathrm{max}}$, when the \ion{Si}{2}$\,\lambda6355$ profile is shallow
+  and the minimum of absorption is difficult to determine, and
+  $\sim$300\,km\,s$^{-1}$ after $T_{B,\mathrm{max}}$. For the median curves,
+  the typical scatter, determined via the interquartile range of the sample,
+  is $\sim$700\,km\,s$^{-1}$, around $T_{B,\mathrm{max}}$. At early times,
+  core-normal and broad-line SNe have significantly faster \ion{Si}{2} than
+  \abc, while the declining trend of cool SNe does not match \abc.} }
+
   \label{fig:branch_vel}
@@
 
-To determine the brightness and time of $B$-band maximum for 
-\abc, we fit the P60 light curves with the \texttt{sncosmo} software package.\footnote{\texttt{sncosmo} is available at
-  \url{https://sncosmo.readthedocs.io}.} This fit includes a \texttt{SALT2} template \citep{2007A&A...466...11G} that has been corrected for extinction using the \citet{1999PASP..111...63F} reddening law, $R_V=3.1$, and $E(B-V) = 0.08 \; \mathrm{mag}$.
+To determine the brightness and time of $B$-band maximum for \abc, we fit the
+P60 light curves with the \texttt{sncosmo} software
+package.\footnote{\texttt{sncosmo} is available at
+\url{https://sncosmo.readthedocs.io}.} This fit includes a \texttt{SALT2}
+template \citep{2007A&A...466...11G} that has been corrected for extinction
+using the \citet{1999PASP..111...63F} reddening law, $R_V=3.1$, and $E(B-V) =
+0.08 \, \mathrm{mag}$.
 
@@
 $m^*_{B}=15.80 \pm 0.04 \,\textrm{mag}$ in the SN rest frame. In the following
-sections, we define the best-fit value $\textrm{MJD}_\mathrm{max}=57499.54$ as
-the time of $B$-band maximum, $T_{B_\mathrm{max}}$, which we also define as
-phase $t=0$.
+sections, we adopt $\textrm{MJD}_\mathrm{max}=57499.54$ as the time of
+$B$-band maximum, $T_{B_\mathrm{max}}$, and phase $t=0$.
 
@@
 are interpolated so that $L_{UVOIR}$ is evaluated at common epochs in each
-filter. From this integration, we determine that \abc\ reaches a maximum
-luminosity $L_\mathrm{max} = 1.2 \pm 0.1 \times 10^{43} \; \mathrm{erg \;
-s}^{-1}$. This value is consistent with the normal SNe Ia studied in
-\citet{2016A&A...588A..84D}, a sample which excludes low-luminosity SNe.
-\textbf{Following Arnett's rule \citet{1982ApJ...253..785A,
-1985Natur.314..337A}, it is possible to derive the mass of $^{56}$Ni
-synthesized in the explosion from $L_\mathrm{max}$. Assuming a rise time of
-$19 \pm 3$\,d (see \citealt{2006A&A...450..241S}) we find $M_\mathrm{Ni} = 0.6
-\pm 0.1 M_\odot$.\footnote{Assuming a rise time of 17.9\,d, see
-\S\ref{sec:lc_fit} results in a consistent estimate of $M_\mathrm{Ni}$.}}
+filter. From this integration, we measure a maximum luminosity $L_\mathrm{max}
+= 1.2 \pm 0.1 \times 10^{43} \; \mathrm{erg \; s}^{-1}$ for \abc. This value
+is consistent with the normal SNe Ia studied in \citet{2016A&A...588A..84D}.
+\textbf{Following Arnett's rule \citep{1982ApJ...253..785A,
+1985Natur.314..337A}, the mass of $^{56}$Ni synthesized in the explosion can
+be derived from $L_\mathrm{max}$. Assuming a rise time of $19 \pm 3$\,d (see
+\citealt{2006A&A...450..241S}) we find $M_\mathrm{Ni} = 0.6 \pm 0.1
+M_\odot$.\footnote{A 17.9\,d rise time (\S\ref{sec:lc_fit}),
+yields a consistent estimate of $M_\mathrm{Ni}$.}}
 
@@
 \citet{1982ApJ...253..785A} derives that $f \propto t^2$, where $f$ is the SN
-flux and $t$ is the time since explosion. Despite the basic assumption of a
-constant temperature at early times, multiple studies have found that the
+flux and $t$ is the time since explosion. Despite \textbf{these simplified assumptions}, multiple studies have found that the
 early emission from Type Ia SNe can be described as a power law in time, with

### 2017-11-16 doc/ms.tex
update text in the fitting section

@@
   \caption{
-
   \textbf{Velocity evolution of \ion{Si}{2},
@@
   \abc, while the declining trend of cool SNe does not match \abc.} }
-
   \label{fig:branch_vel}
@@
 sections, we adopt $\textrm{MJD}_\mathrm{max}=57499.54$ as the time of
-$B$-band maximum, $T_{B_\mathrm{max}}$, and phase $t=0$.
+$B$-band maximum, $T_{B,_\mathrm{max}}$, and phase $t=0$.
 
@@
 \citealt{2006AJ....132.1707C, 2010ApJ...712..350H,
-2011MNRAS.416.2607G}).\footnote{Many of the studies that find $f \propto t^2$
-sample SNe Ia light curves at a phase that is closer to $T_{B,\mathrm{max}}$
-than the initial observations of \abc\ discussed here.}
-
-As our observations include especially early observations of \abc, there are
-upper limits $\sim$1 d prior to the discovery epoch, we model the early flux
-from \abc\ as a power law, but allow the power-law index to vary:
+2011MNRAS.416.2607G}).\footnote{Many of these studies
+sample SNe Ia light curves at phases closer to $T_{B,\mathrm{max}}$
+than our initial observations of \abc.}
+
+As our observations include especially early observations of \abc, the SN is
+not detected $\sim$1\,d prior to discovery, we model the early flux from \abc\
+as a power law:
 
@@
 \end{equation}
+% 
 where $t_0$ is the time of first light, $\alpha$ is the power-law index, and
 $t$ is measured in the SN rest-frame. \textbf{We allow $\alpha$ to vary to
-find the best match to the data, and later show that models with $\alpha = 2$
-do not explain the data.} To determine $t_0$ and $\alpha$ we fit the earliest
-observations of \abc. Due to slight variations in the passbands, we fit the
-model only to the relative flux measured in the $g_\mathrm{PTF}$-band, which
+find the best match to the data, and later show that $\alpha = 2$ is not
+compatible with the observations.} To determine $t_0$ and $\alpha$ we fit the
+earliest observations of \abc. Due to slight variations in the passbands, the
+model is fit only to the relative $g_\mathrm{PTF}$-band flux. $g_\mathrm{PTF}$
 is the only filter with observations prior to first light, a necessity for
@@
 modeling results show that the SN flux rises approximately linearly between
-$t=-18\,\textrm{d}$ and $t=-15\,\textrm{d}$. Figure \ref{fig:early_lc_fit}
+$t=-18\,\mathrm{d}$ and $t=-15\,\mathrm{d}$. Figure \ref{fig:early_lc_fit}
 shows the best-fit result and the joint marginal distribution of $t_0$ and
@@
 marginalized 95\% confidence intervals. Our first detection of \abc\ occurred
-$\sim$${0.15}\,\textrm{d}$ after the SN first light. In the analysis that
+$\sim$${0.15}\,\textrm{d}$ after $t_0$. In the analysis that
 follows, the precise values of the best-fit parameters are not important. The
@@
 we find $t_\mathrm{rise} = 17.91\pm _{0.07}^{0.15}$ d based on our fit for
-$t_0$. We caution that this measurement may be underestimated due to the
-uncertain time of explosion.
+$t_0$. We caution, \textbf{however, that $t_0$ corresponds to the time when \abc\ was first detectable by P48 and not the time of explosion.}
 
@@
   \includegraphics[width=0.48\textwidth]{early_lc.pdf}
-  \caption{Best-fit power-law model to describe the early flux 
-  from \abc\ in the $g_\mathrm{PTF}$ band. \textit{Top}: The 
-  relative flux, 
-  $f_{g_\mathrm{PTF}}$, shown as green circles, is measured via 
-  forced-PSF photometry at the SN location. The model flux, 
-  adopting best-fit parameters $\alpha=0.98$ and 
-  $t_0=-17.94\,\textrm{d}$, is shown as a dashed black line. Also 
-  shown is the best-fit model after fixing 
-  $\alpha=2$ (thin, dash-dot line). 
-  The joint distribution of $t_0$ and $\alpha$ for the best-fit 
-  power-law model is illustrated in the inset. 
-  The solid contours represent the $68\%$ and $99.7\%$ confidence 
-  levels.
-  \textit{Bottom}: 
-  The observations and models following 
-  subtraction of the best-fit power-law model, $f_{\alpha = 0.98}$.
-  The $t^{0.98}$ model provides a much better fit to the 
-  observations than the $t^2$ model. 
-  }
+  \caption{
+  Best-fit $f \propto t^\alpha$ model to describe the early flux from \abc\ in
+  the $g_\mathrm{PTF}$ band. \textit{Top}: The relative flux,
+  $f_{g_\mathrm{PTF}}$, shown as green circles, is measured via forced-PSF
+  photometry. The model flux, adopting best-fit parameters $\alpha=0.98$ and
+  $t_0=-17.91\,\textrm{d}$, is shown as a thick, dashed line. Also shown is
+  the best-fit model after fixing $\alpha=2$ (thin, dash-dot line). The inset
+  shows the joint distribution of $t_0$ and $\alpha$ for the best-fit
+  power-law model. The solid contours represent the $68\%$ and $99.7\%$
+  confidence levels. \textit{Bottom}: The observations and models following
+  subtraction of the best-fit power-law model, $f_{\alpha = 0.98}$. The
+  $t^{0.98}$ model provides a much better fit to the observations than the
+  $t^2$ model.}
   \label{fig:early_lc_fit}
@@
 
-Simulations presented in \citet{2017MNRAS.472.2787N} show that the flux from
-SNe Ia explosion models does not evolve as a power law in time. Despite this
-non-power-law evolution, \citet{2017MNRAS.472.2787N} show that $f \propto
-t^\alpha$ models produce good formal fits to simulated observations. The $f
-\propto t^\alpha$ fits to the \citeauthor{2017MNRAS.472.2787N}\ models result
-in glaring errors to the estimated explosion times. Despite the caution
-advised in \citet{2017MNRAS.472.2787N}, we proceed with the power-law fits
-from above for several reasons. (1) Our primary aim with the fit is to
-characterize $\alpha$ for \abc\ compared to SN\,2011fe (see below). (2) The
-errors in the estimated explosion times from \citeauthor{2017MNRAS.472.2787N}
-increase the later the first observation of the SN is obtained.
-\citeauthor{2017MNRAS.472.2787N} only present fits to observations that start
-$>$2\,d after explosion, whereas the discovery epoch for \abc\ is likely much
-earlier than that (see \S\ref{sec:early_vel}). (3) We do not use the fits to
-estimate the time of explosion, $t_0$ instead is an estimate of the time of
-first light. \textbf{Finally,} (4) Pre-discovery upper limits, which are not
-included in \citeauthor{2017MNRAS.472.2787N}, provide additional strong
-constraints on the time of first light.
-
 Unlike \abc, the early emission from SN\,2011fe is well fit by a $f \propto
-t^2$ model \citep{2011Natur.480..344N}. Thus, the near-linear rise in flux
-over the first few days after first light for \abc\ is distinct compared to
-SN\,2011fe. To our knowledge this behavior has only been observed in 2 other
-SNe (2013dy, 2014J;
+t^2$ model \citep{2011Natur.480..344N}. Thus, the near-linear flux evolution
+observed in \abc\ is distinct compared to SN\,2011fe. To our knowledge this
+behavior has only been observed in 2 other SNe (2013dy, 2014J;
 \citealt{2013ApJ...778L..15Z,2014ApJ...783L..24Z,2015ApJ...799..106G}). Any
@@
 
+As a brief aside, we note that simulations presented in
+\citet{2017MNRAS.472.2787N} show that SNe Ia explosion models do not evolve as
+a power law in time. \textbf{\citeauthor{2017MNRAS.472.2787N}\ demonstrate
+that $f \propto t^\alpha$ fits to simulated light curves result in glaring
+errors to the estimated explosion times. While caution is advised in
+\citet{2017MNRAS.472.2787N}, we note that our primary aim with the power-law
+fit is to characterize $\alpha$ for \abc\ compared to SN\,2011fe.}
+
 \subsection{Time of Explosion from the Photospheric Velocity}
@@
 
-The potential dark phase following shock breakout, where SNe Ia are not luminous because the energy deposition from radioactive decay has not had sufficient time to diffuse to the photosphere, means that the explosion time $t_\mathrm{exp} \ne t_0$ in some cases.
-\citet{2014ApJ...784...85P} suggest that measurements of the photospheric velocity be used to determine $t_\mathrm{exp}$ given that the ejecta begin expanding from the moment of explosion.
-Assuming a constant opacity in the ejecta, \citeauthor{2014ApJ...784...85P}
-find that the photospheric velocity evolves as
-$v_\mathrm{ph}\propto(t-t_\mathrm{exp})^{-0.22}$.
-Numerical experiments by \citet{2016ApJ...826...96P} find that the constant-opacity assumption strongly depends on the amount of $^{56}$Ni mixing in the SN ejecta (for a more detailed discussion of $^{56}$Ni mixing see \S\ref{sec:Ni_mixing}).
-As a result, the adoption of a $t^{-0.22}$ power-law model may not be valid for all SNe Ia.
-Nevertheless, we proceed on the assumption that \abc\ experienced strong $^{56}$Ni mixing, corresponding to the models that are best approximated as a $t^{-0.22}$ power law.
-We do this in part to compare with previous studies, though we caution that the inferred value of $t_{exp}$ is subject to uncertainties related to ejecta mixing.
-
-While the photospheric velocity
-is not easy to measure, line velocities of \ion{Si}{2} or \ion{Ca}{2}
-can be used as a proxy
-\citep{2014ApJ...784...85P,2016ApJ...826..144S}. In the case of \abc, the \ion{Ca}{2} IR triplet is very weak, 
-likely due to high temperatures in the ejecta. Thus, we
-determine the photospheric velocity from the 
-\ion{Si}{2}\,$\lambda$6355 line. Visual inspection shows no 
-sign of multi-velocity components of \ion{Si}{2}, and that 
-the \ion{C}{2}\,$\lambda$6580 line overlaps the red
-wing of the \ion{Si}{2} line (see Figures~\ref{fig:spec_seq} and \ref{fig:carbon}). Consequently, we model the observed 
-spectra between 5900 and 6500\,\AA\ (rest-frame) as the 
-combination of two Gaussian kernels plus a linear baseline, which
-accounts for \ion{Si}{2}, \ion{C}{2} and the
-continuum, respectively. The expansion
-velocity of \ion{Si}{2} is measured by the central wavelength
-of the \ion{Si}{2} Gaussian kernel.
+\textbf{Given that the time of explosion $t_\mathrm{exp}$ is not constrained
+by $t_0$ (see above),} \citet{2014ApJ...784...85P} suggest that measurements
+of the photospheric velocity can determine $t_\mathrm{exp}$ given that the
+ejecta begin expanding from the moment of explosion. Assuming a constant
+opacity in the ejecta, \citeauthor{2014ApJ...784...85P} find that the
+photospheric velocity evolves as
+$v_\mathrm{ph}\propto(t-t_\mathrm{exp})^{-0.22}$. Numerical experiments by
+\citet{2016ApJ...826...96P} find that the constant-opacity assumption strongly
+depends on the amount of $^{56}$Ni mixing in the SN ejecta. As a result, the
+adoption of a $t^{-0.22}$ power-law model may not be valid for all SNe Ia.
+Nevertheless, we proceed on the assumption that \abc\ experienced strong
+$^{56}$Ni mixing \textbf{(see \S\ref{sec:Ni_mixing})}, corresponding to the
+models that are best approximated as a $t^{-0.22}$ power law. We do this in
+part to compare with previous studies, though we caution that the inferred
+value of $t_{exp}$ is subject to uncertainties related to ejecta mixing.
+
+While the photospheric velocity is not easy to measure, line velocities of
+\ion{Si}{2} or \ion{Ca}{2} can be used as a proxy
+\citep{2014ApJ...784...85P,2016ApJ...826..144S}. In the case of \abc, the
+\ion{Ca}{2} IR triplet is very weak, likely due to high temperatures in the
+ejecta. Thus, we determine the photospheric velocity from the
+\ion{Si}{2}\,$\lambda$6355 line. Visual inspection shows no sign of
+multi-velocity components of \ion{Si}{2}, and that the
+\ion{C}{2}\,$\lambda$6580 line overlaps the red wing of the \ion{Si}{2} line
+(see Figures~\ref{fig:spec_seq} and \ref{fig:carbon}). Consequently, we model
+the observed spectra between 5900 and 6500\,\AA\ (rest-frame) as the
+combination of two Gaussian kernels plus a linear baseline, which accounts for
+\ion{Si}{2}, \ion{C}{2} and the continuum, respectively. The expansion
+velocity of \ion{Si}{2} is measured by the central wavelength of the
+\ion{Si}{2} Gaussian kernel.
 
@@
   \includegraphics[width=0.48\textwidth]{VelocityPlot.pdf}
-  \caption{Constraints on $t_\mathrm{exp}$ from fitting the velocity
-    evolution of \ion{Si}{2}.
-    \textit{Left panel:} the dashed, solid and dash-dotted curves 
-    show $\chi^2$ for fitting power laws with
-    indices $-0.20$, $-0.22$ and $-0.24$, respectively. The blue
-    vertical line and the orange shaded region indicate $t_0$ and 
-    its 95\% confidence interval from Section
-    \ref{sec:lc_fit}, respectively.
-    \textit{Right panel:} Observed \ion{Si}{2}\,$\lambda$6355
-    velocities (blue circles) and the best-fit power-law model
-     with an index of $-0.22$ (dashed line). Additionally, the 
-     measured velocities of \ion{C}{2}\,$\lambda\lambda$6580, 7234 
-     are shown. Typical uncertainties are smaller than the size of 
-     the points. \textit{Right inset}: Evolution of the 
-     pseudo-equivalent width of \ion{Si}{2}\,$\lambda$6355, and 
-     \ion{C}{2}\,$\lambda\lambda$6580, 7234 in the $\sim$7~d    
-     following explosion.}
+  \caption{
+  Constraints on $t_\mathrm{exp}$ from the velocity evolution of \ion{Si}{2}.
+  \textit{Left panel:} the dashed, solid and dash-dotted curves show $\chi^2$
+  for fitting power laws with indices $-0.20$, $-0.22$ and $-0.24$,
+  respectively. The blue vertical line and the orange shaded region indicate
+  $t_0$ and its 95\% confidence interval from Section \ref{sec:lc_fit},
+  respectively. \textit{Right panel:} Observed \ion{Si}{2}\,$\lambda$6355
+  velocities (blue circles) and the best-fit power-law model with an index of
+  $-0.22$ (dashed line). \textbf{For comparison}, the measured velocities of
+  \ion{C}{2}\,$\lambda\lambda$6580, 7234 are also shown. Typical uncertainties
+  are smaller than the size of the points. \textit{Right inset}: Evolution of
+  the pseudo-equivalent width of \ion{Si}{2}\,$\lambda$6355, and
+  \ion{C}{2}\,$\lambda\lambda$6580, 7234 in the $\sim$7\,d following 
+  explosion.}
   \label{fig:velocity_t_exp}
@@
 We fit the measured velocities of \ion{Si}{2}\,$\lambda$6355 to the
-$v\propto(t-t_\mathrm{exp})^{-0.22}$ model by minimizing the $\chi^2$ value
-and find the best-fit explosion time relative to $T_{B,\mathrm{max}}$ in the
-SN rest frame to be $t_\mathrm{exp} = -17.45 \pm ^{0.14}_{0.16}\,\textrm{d}$,
-where the uncertainties represent the 95\% confidence interval (Figure
-\ref{fig:velocity_t_exp}). Following the analysis in
-\citet{2014ApJ...784...85P}, we additionally alter the power-law index to
+$v_\mathrm{ph}\propto(t-t_\mathrm{exp})^{-0.22}$ model by minimizing the
+$\chi^2$ value and find the best-fit explosion time relative to
+$T_{B,\mathrm{max}}$ in the SN rest frame to be $t_\mathrm{exp} = -17.45 \pm
+^{0.14}_{0.16}\,\textrm{d}$, where the uncertainties represent the 95\%
+confidence interval (Figure \ref{fig:velocity_t_exp}). Following the analysis
+in \citet{2014ApJ...784...85P}, we additionally alter the power-law index to
 $-0.20$ and $-0.24$ to examine the sensitivity of the result on the assumed
-power-law index. We find that this variation in the power-law index results in
-a change of $t_\mathrm{exp}$ of $\approx\pm$0.5\,d (Figure
-\ref{fig:velocity_t_exp}). Given the analytical approximation that $v \propto
-t^{-0.22}$, we adopt $t_\mathrm{exp} = -17.5 \pm 0.5 \; \mathrm{d}$, where the
-uncertainty reflects possible variations in the power-lax index (see
-\citealt{2014ApJ...784...85P}).
-
-Comparing our estimates for $t_\mathrm{exp}$ and $t_0$ (left panel of Figure
-\ref{fig:velocity_t_exp}), we find that $t_0\lesssim t_\mathrm{exp}$. Since
-physical causality requires $t_\mathrm{exp} \le t_0$, we draw the qualitative
-conclusion that $t_0\simeq t_\mathrm{exp}$, which is consistent to within the
-uncertainties. Again, we caution that this derivation of $t_\mathrm{exp}$
-relies on the assumption $v \propto t^{-0.22}$, which may not be valid for all
+value of $-0.22$. We find that this variation in the power-law index results
+in a change of $t_\mathrm{exp}$ of $\approx\pm$0.5\,d (Figure
+\ref{fig:velocity_t_exp}). Given the analytical approximation that
+$v_\mathrm{ph} \propto t^{-0.22}$, we adopt $t_\mathrm{exp} = -17.5 \pm 0.5 \;
+\mathrm{d}$, where the uncertainty reflects possible variations in the
+power-lax index (see \citealt{2014ApJ...784...85P}).
+
+Comparing our estimates for $t_\mathrm{exp}$ and $t_0$
+(Figure~\ref{fig:velocity_t_exp}), we find that $t_0\lesssim t_\mathrm{exp}$.
+Since physical causality requires $t_\mathrm{exp} \le t_0$, we draw the
+qualitative conclusion that $t_0\simeq t_\mathrm{exp}$, which is consistent to
+within the uncertainties. This derivation of $t_\mathrm{exp}$ relies on the
+assumption $v_\mathrm{ph} \propto t^{-0.22}$, which may not be valid for all
 SNe Ia.
-
-% From $t_{exp}$, we estimate the actual rise time of \abc\ from the
-% time of explosion to \textit{B}-band maximum to be $17.95$ d.  In
-% comparison, SN2011fe has $t_0=-17.7$\,d \citep{2013A&A...554A..27P}
-% with a preceding dark phase of $\sim 1$ day
-% \citep{2014ApJ...784...85P}. ASASSN-14lp has $t_0=-16.94$ days with a
-% preceding dark phase of about acouple of days
-% \citep{2016ApJ...826..144S}. This comparison suggests that the actual
-% rise time of a SN Ia between the SN explosion and the \textit{B}-band
-% maximum is roughly a constant, which largely depends on the total mass
-% of synthesized $^{56}$Ni.\ycao{I am not convinced by this last sentence}
 
@@
 
-The early spectra of \abc\ exhibit unusually strong absorption due to
-\ion{C}{2} $\lambda\lambda$6580, 7234. We highlight the evolution of these
-spectral features in Figure~\ref{fig:carbon}. From these spectra we see that
+The early spectra of \abc\ exhibit unusually strong \ion{C}{2} $\lambda\lambda$6580, 7234 absorption. The evolution of these
+spectral features is highlighted in Figure~\ref{fig:carbon}, which shows that
 \ion{C}{2}\,$\lambda$6580 is as strong as \ion{Si}{2}\,$\lambda$6355 at $t
-\approx -15 \; \mathrm{d}$. The strength of the \ion{C}{2} lines declines with
-time, and by $t \approx -10 \; \mathrm{d}$ \ion{C}{2} is no longer detectable.
+\approx -15 \, \mathrm{d}$. The strength of the \ion{C}{2} lines declines with
+time, and by $t \approx -10 \, \mathrm{d}$ \ion{C}{2} is no longer detectable.
 
@@
   The raw spectra are shown in orange, while the solid blue lines show the
-  best-fit models including Gaussian components for each line and a linear
-  component for the continuum (see text for further details). The dark grey
-  vertical lines show the measured line centers, indicating the decline in the
-  photosphere velocity in the $\sim$7~d after explosion (note that
+  best-fit models (see text for further details). The dark grey vertical lines
+  show the measured line centers, \textbf{and clearly show} the decline in the
+  photosphere velocity in the $\sim$7~d after explosion (
   \ion{C}{2}\,$\lambda$7234 is not detected in the $-10.9$\,d spectrum). The
@@
 velocities and pEWs of \ion{C}{2}\,$\lambda\lambda$6580, 7234. We compare the
-velocity evolution of the \ion{C}{2} lines to \ion{Si}{2} in the right panel
-of Figure \ref{fig:velocity_t_exp}, which also shows the pEW evolution of
-these lines. These measurements confirm the qualitative analysis from
-Figure~\ref{fig:carbon}: namely, the pEW of \ion{C}{2}\,$\lambda$6580 is
-comparable to that of \ion{Si}{2}\,$\lambda$6355 at $t \approx -16 \;
-\mathrm{d}$ and the pEW of \ion{C}{2} decreases until the feature is no longer
-detectable around $t = -10$ d.
-
-The detection of \ion{C}{2} in SN Ia spectra is relatively rare
-as it requires both unburned carbon, which is likely only present in the outermost layers of the ejecta, and non-local thermal equilibrium effects in order to excite the ionized carbon (e.g., \citealt{2007ApJ...654L..53T}).
-Spectra obtained around or after $T_{B_\mathrm{max}}$ rarely show \ion{C}{2} as the photosphere has receded from the outermost ejecta, while pre-max spectra show evidence for \ion{C}{2} in $\sim$1/4 of all normal SNe Ia (e.g., \citealt{2011ApJ...732...30P,2012MNRAS.425.1917S,2011ApJ...743...27T}), but the signatures are typically weak.
-While we caution that the sample of SNe Ia with spectra taken within a few days of explosion is small, SNe\,2013dy and 2017cbv are the only other objects known to have strong \ion{C}{2} features like \abc\ \citep{2013ApJ...778L..15Z,2017ApJ...845L..11H}.
-As a counterexample, SN\,2011fe only exhibited weak \ion{C}{2} features in its first spectra
-\citep{2012ApJ...752L..26P}. Thus, models of \abc\ must explain the strong \ion{C}{2} absorption observed shortly after explosion.
+velocity evolution of \ion{C}{2} to \ion{Si}{2} in the right panel of Figure
+\ref{fig:velocity_t_exp}, which also shows the pEWs of these lines. These
+measurements confirm the qualitative analysis from Figure~\ref{fig:carbon}:
+namely, the \textbf{strength} of \ion{C}{2}\,$\lambda$6580 is \textbf{similar
+to} \ion{Si}{2}\,$\lambda$6355 at $t \approx -16 \, \mathrm{d}$ before
+decreasing and eventually disappearing around $t = -10$ d.
+
+The detection of \ion{C}{2} in SN Ia spectra is relatively rare as it requires
+both unburned carbon, which is likely only present in the outermost layers of
+the ejecta, and non-local thermal equilibrium effects in order to excite the
+ionized carbon (e.g., \citealt{2007ApJ...654L..53T}). Spectra obtained around
+or after $T_{B,_\mathrm{max}}$ rarely show \ion{C}{2} as the photosphere has
+receded from the outermost ejecta, while pre-max spectra show evidence for
+weak \ion{C}{2} absorption in $\sim$1/4 of all normal SNe Ia (e.g.,
+\citealt{2011ApJ...732...30P,2011ApJ...743...27T,2012MNRAS.425.1917S}). While
+the sample of SNe Ia with spectra taken within a few days of explosion is
+small, SNe\,2013dy and 2017cbv are the only other objects known to have strong
+\ion{C}{2} features like \abc\
+\citep{2013ApJ...778L..15Z,2017ApJ...845L..11H}. As a counterexample,
+SN\,2011fe only exhibited weak \ion{C}{2} features in its first spectra
+\citep{2012ApJ...752L..26P}. Thus, models of \abc\ must explain the strong
+\ion{C}{2} absorption observed shortly after explosion.
 
@@
 
-Multiband observations of \abc\ began $\sim$1.5 d after discovery, which allows us to trace its color evolution starting $\sim$1.7 d after $t_0$.
-In Figure~\ref{fig:B-Vcolors} we compare the $(B - V)_0$ color evolution of \abc\ and SN\,2011fe, where the observations of SN\,2011fe are taken from \citet{2016ApJ...820...67Z}.
-For both SNe the colors have been corrected for the total inferred reddening along the line of sight.
-Interestingly, \abc\ has a nearly flat color evolution up to 10\,d before $T_{B,\mathrm{max}}$, while SN\,2011fe exhibits red colors initially before evolving to the blue.
+Multiband observations of \abc\ began $\sim$1.5\,d after discovery, which
+allows us to trace its color evolution starting $\sim$1.7\,d after $t_0$. In
+Figure~\ref{fig:B-Vcolors} we compare the $(B - V)_0$ color evolution of \abc\
+to observations of SN\,2011fe \citep{2016ApJ...820...67Z}. For both SNe the
+colors have been corrected for the total inferred reddening along the line of
+sight. Interestingly, \abc\ has a nearly flat color evolution up to $t \approx
+-10$\,d, while SN\,2011fe initially exhibits red colors before evolving to the
+blue.
 
@@
   \includegraphics[width=0.48\textwidth]{16abc_11fe_colors.pdf}
-  \caption{$(B - V)_0$ color evolution of \abc\ (shown as squares) 
-    compared to SN\,2011fe (shown as stars). The $B$ and $V$ 
-    photometry are calibrated on the Vega system, and have been 
-    corrected for extinction. The data for 
+  \caption{$(B - V)_0$ color evolution of \abc\ (squares) 
+    compared to SN\,2011fe (stars). The $B$ and $V$ photometry are calibrated
+    on the Vega system, and have been corrected for extinction. The data for
     SN\,2011fe are from \citet{2016ApJ...820...67Z}.}
@@
 
-Roughly 16\,d prior to $B$-band maximum, the $(B - V)_0$ color of \abc\ is
-$\sim$0.5 mag bluer than SN\,2011fe. Like \abc, SN\,2012cg
+Roughly 16\,d prior to $T_{B,_\mathrm{max}}$, the $(B - V)_0$ color of \abc\ is
+$\sim$0.5\,mag bluer than SN\,2011fe. Like \abc, SN\,2012cg
 \citep{2016ApJ...820...92M} and SN\,2017cbv \citep{2017ApJ...845L..11H}

### 2017-11-16 doc/ms.tex
update text in the discussion section

@@
 assuming $v_\mathrm{ph} \propto t^{-0.22}$, (iii) the presence of strong
-\ion{C}{2} absorption, and (iv) blue and non-evolving $(B - V)_0$ color in the
-week after explosion. While most SNe Ia are powered purely by radioactive
-decay, the observed radiation shortly after explosion can also include
-contributions from SN shock cooling or the collision of the SN ejecta with a
-non-degenerate companion or \textbf{nearby, unbound} material. Here we
-consider those scenarios as a possible explanation for the early behavior of
+\ion{C}{2} absorption, and (iv) blue and \textbf{nearly constant} $(B - V)_0$
+color in the week after explosion. While most SNe Ia are powered purely by
+radioactive decay, the observed radiation shortly after explosion can also
+include contributions from SN shock cooling or the collision of the SN ejecta
+with a non-degenerate companion or \textbf{nearby, unbound} material. Here we
+consider these scenarios as possible explanations for the early behavior of
 \abc.
@@
 
-The shock breakout of a SN Ia lasts for a fraction of a second due to
-compact size of the exploding star. Emission from the subsequent 
-cooling phase may last for several days, however (e.g., 
-\citealt{2010ApJ...708..598P}). Following the analysis of \citet{2012ApJ...744L..17B} for SN\,2011fe, we
-compare the early-phase $g_\mathrm{PTF}$ light curve of \abc\ with
-two shock cooling models \citep{2011ApJ...728...63R, 
-2010ApJ...708..598P}. From this analysis, we constrain the \abc\ 
-progenitor radius to be $<1\,\sr$. Our observations of \abc\ cannot 
-place tight constraints on the size of SN Ia progenitors. Indeed, 
-for a typical WD radius, such as that inferred for SN\,2011fe 
-($\lesssim 0.02$--$0.04\,\sr$; \citealt{2012ApJ...744L..17B, 
+The shock breakout of a SN Ia lasts for a fraction of a second due to compact
+size of the exploding star. Emission from the subsequent cooling phase may
+last for several days, however (e.g., \citealt{2010ApJ...708..598P}).
+Following the analysis of \citet{2012ApJ...744L..17B} for SN\,2011fe, we
+compare the early-phase $g_\mathrm{PTF}$ light curve of \abc\ with two shock
+cooling models \citep{2011ApJ...728...63R, 2010ApJ...708..598P}. From this
+analysis, we constrain the \abc\ progenitor radius to be $<1\,\sr$. Our
+observations of \abc\ cannot place tight constraints on the size of its
+progenitor. Indeed, for a typical WD radius, such as that inferred for
+SN\,2011fe ($\lesssim 0.02$--$0.04\,\sr$; \citealt{2012ApJ...744L..17B,
 2014ApJ...784...85P}), the expected emission from shock cooling is
-$\sim$2 mag fainter than the P48 $g_\mathrm{PTF}$ detection limit at this distance. 
-Thus, we conclude that shock cooling does not contribute to the 
-early emission from \abc.
+$\sim$2\,mag fainter than the P48 $g_\mathrm{PTF}$ detection limit at this
+distance. Thus, we conclude that shock cooling does not contribute to the
+early emission \textbf{detected} from \abc.
 
@@
 
-The detection of emission from the collision of the SN ejecta 
-with a non-degenerate companion requires a favorable orbital 
-alignment relative to the line of sight. Thus, from geometric 
-considerations alone the probability of detecting ejecta-companion 
-interaction is low, $\sim$10\%. \citet{2010ApJ...708.1025K} 
-calculates that the collision of SN ejecta with a companion  
-generates thermal emission with a spectrum that peaks in the 
-UV. The resulting \textit{g}-band emission is expected to be weak.
-
-To examine the possibility of a SN-companion signature in the early
-light curve of \abc, we employ the \citet{2010ApJ...708.1025K}
-model and assume canonical values for the ejecta mass, $1.4\,\sm$, expansion velocity, $10^{4}\,\textrm{km}\,\textrm{s}^{-1}$, and a constant opacity, $0.2\,\textrm{cm}^2\,\textrm{g}^{-1}$.
-We calculate the expected $g_\mathrm{PTF}$ brightness of an ejecta-companion collision at the distance of \abc\ behind a total reddening of $E(B-V) = 0.08 \, \mathrm{mag}$ using the parameterized equations in \citet{2012ApJ...749...18B}.
-If we assume the binary is aligned with the optimal orientation relative to the line of sight, a binary separation of $a \approx 3 \times 10^{11}\, \mathrm{cm}$ is needed to explain the initial detection of \abc, as shown in Figure~\ref{fig:SN-companion}.
-The minimum binary separation capable of explaining the observed brightness at the epoch of discovery is $a \approx 10^{11} \, \mathrm{cm}$.
-Figure~\ref{fig:SN-companion} shows that such models peak at $g_\mathrm{PTF} \approx 21.5 \, \mathrm{mag}$, provided that $t_\mathrm{exp} \approx t_0 - 0.3 \, \mathrm{d}$.
-These models do not, however, match the $g_\mathrm{PTF}$ evolution for $t > t_0 + 0.5 \, \mathrm{d}$ (though it is possible that the SN photosphere dominates the companion-interaction signature at this phase).
-While they are otherwise compatible with the observations, we do not favor the above models as the explanation for the early flux from \abc\ because they do not explain the 2 mag rise in the $\sim$24 hr after discovery.
+The detection of emission from the collision of the SN ejecta with a
+non-degenerate companion requires a favorable orbital alignment relative to
+the line of sight. Thus, from geometric considerations alone the probability
+of detecting ejecta-companion interaction is low, $\sim$10\%.
+\citet{2010ApJ...708.1025K} calculates that the collision of SN ejecta with a
+companion generates thermal emission with a spectrum that peaks in the UV. The
+resulting \textit{g}-band emission is expected to be weak.
+
+To examine the possibility of a SN-companion signature in the early light
+curve of \abc, we employ the \citet{2010ApJ...708.1025K} model and assume
+canonical values for the ejecta mass, $1.4\,\sm$, expansion velocity,
+$10^{4}\,\textrm{km}\,\textrm{s}^{-1}$, and a constant opacity,
+$0.2\,\textrm{cm}^2\,\textrm{g}^{-1}$. We calculate the expected
+$g_\mathrm{PTF}$ brightness of an ejecta-companion collision at the distance
+of \abc\ behind a total reddening of $E(B-V) = 0.08 \, \mathrm{mag}$ using the
+parameterized equations in \citet{2012ApJ...749...18B}. If we assume the
+binary is aligned with the optimal orientation relative to the line of sight,
+a binary separation of $a \approx 3 \times 10^{11}\, \mathrm{cm}$ is needed to
+explain the initial detection of \abc, as shown in
+Figure~\ref{fig:SN-companion}. The minimum binary separation capable of
+explaining the observed brightness at the epoch of discovery is $a \approx
+10^{11} \, \mathrm{cm}$. Figure~\ref{fig:SN-companion} shows that such models
+peak at $g_\mathrm{PTF} \approx 21.5 \, \mathrm{mag}$, provided that
+$t_\mathrm{exp} \approx t_0 - 0.3 \, \mathrm{d}$. These models do not,
+however, match the $g_\mathrm{PTF}$ evolution for $t > t_0 + 0.5 \,
+\mathrm{d}$ (though it is possible that the SN photosphere dominates the
+companion-interaction signature at this phase). While they are otherwise
+compatible with the observations, we do not favor the above models as the
+explanation for the early flux from \abc\ because they do not explain the
+2\,mag rise in the $\sim$24 hr after discovery.
 
@@
 
-Figure~\ref{fig:SN-companion} additionally shows that a companion at $a \approx 18 \times 10^{11} \, \mathrm{cm}$ provides a good match to the initial optical rise, if $t_\mathrm{exp} \approx t_0 + 0.1 \; \mathrm{d}$.
-Models with $a \gtrsim 10^{12} \, \mathrm{cm}$, which can explain the initial $g_\mathrm{PTF}$ rise, significantly overpredict the observed UV flux, however.
-There is no choice of $a$ capable of replicating the early rise of \abc\ without also overpredicting the observed UV flux.
-
-The challenges associated with each of the previously considered models lead us to conclude that the early evolution of \abc\ cannot be explained via the interaction of the SN ejecta with a companion.
-We cannot, however, exclude the presence of a red-giant, or other non-degenerate, companion as our calculations have assumed that the binary is aligned with the optimal geometry relative to the line of sight.
-If the geometry is not favorable, then it is possible that signatures from interaction with a companion are not visible.
+Figure~\ref{fig:SN-companion} additionally shows that a companion at $a
+\approx 18 \times 10^{11} \, \mathrm{cm}$ provides a good match to the initial
+optical rise, if $t_\mathrm{exp} \approx t_0 + 0.1 \; \mathrm{d}$. Models with
+$a \gtrsim 10^{12} \, \mathrm{cm}$, which can explain the initial
+$g_\mathrm{PTF}$ rise, significantly overpredict the observed UV flux,
+however. There is no choice of $a$ capable of replicating the early rise of
+\abc\ without also overpredicting the observed UV flux.
+
+The challenges associated with each of the previously considered models lead
+us to conclude that the early evolution of \abc\ cannot be explained via
+ejecta-companion interaction. We cannot, however, exclude the presence of a
+red-giant, or other non-degenerate, companion as our calculations have assumed
+that the binary is aligned with the optimal geometry relative to the line of
+sight. If the geometry is not favorable, then it is possible that signatures
+from interaction with a companion are not visible.
 
@@
 examine two Chandrasekhar-mass ($M_\mathrm{Ch}$) explosions and compare their
-evolution to sub-Chandrasekhar explosions and pure deflagrations. The
+evolution to sub-Chandrasekhar detonations and pure deflagrations. The
 $M_\mathrm{Ch}$ explosions include the ``W7'' carbon-deflagration model of
@@
 detonation explosion, in which a He-surface-layer detonation triggers a carbon
-detonation in the core. \citet{2017MNRAS.472.2787N} note that, of these
-last two sub-Chandrasehkar models, the later provides the more realistic
-scenario. Finally, \citet{2017MNRAS.472.2787N} also examine the ``N5def'' and
-``N1600Cdef'' pure deflagration explosions from \citet{2014MNRAS.438.1762F}.}
+detonation in the core. \citet{2017MNRAS.472.2787N} note that, of these last
+two sub-Chandrasehkar models, the later provides the more realistic scenario.
+Finally, \citeauthor{2017MNRAS.472.2787N} also examine the ``N5def'' and
+``N1600Cdef'' pure deflagration explosions from \citet{2014MNRAS.438.1762F}.
+The ``N5def'' model is particularly unique in that it does not fully unbind
+the WD and therefore leaves a remnant.}
 
@@
   modulus to \abc\ (\S\ref{sec:host}), while both the light curve and color
-  curve have been corrected for reddening. To guide the eye early
-  $g_\mathrm{PTF}$ observations are shown as open circles, though we caution
+  curve have been corrected for reddening. To guide the eye,
+  $g_\mathrm{PTF}$ observations are shown, though we caution
   that \abc\ may exhibit significant color evolution at this phase in which
@@
   the top panel shows the residuals relative to the W7 model.} }
+  %
   \label{fig:noebauer} 
@@
 \textbf{In Figure~\ref{fig:noebauer} we compare photometric observations of
-\abc\ to the models presented in \citet{2017MNRAS.472.2787N}. Interestingly,
-the sub-Chandrasekhar double detonation model (subChDoubleDet) replicates the
-early wiggle in the $V$-band light curve. However, this match requires an
-explosion \textit{after} our initial detection of \abc, \textit{and} extreme
-color evolution. Thus, the subChDoubleDet model is incompatible with the
+\abc\ to the models presented in
+\citet{2017MNRAS.472.2787N}.\footnote{Available here:
+\url{https://hesma.h-its.org/}.} Interestingly, the sub-Chandrasekhar double
+detonation model (subChDoubleDet) replicates the early wiggle in the $V$-band
+light curve. However, this match requires an explosion \textit{after} our
+initial detection of \abc, and predicts extreme color evolution that is not
+observed. Thus, the subChDoubleDet model is incompatible with the
 observations. The sub-Chandrasekhar detonation (subChDet) provides a better
@@
 
-\textbf{Of the $M_\textrm{Ch}$ models, the W7 model better matches the
+\textbf{Of the $M_\mathrm{Ch}$ models, the W7 model better matches the
 observations as the N100 model features a faster rise and higher luminosity
@@
 
-To model SN\,2011fe, \citet{2014MNRAS.441..532D} recently examined
+To model SN\,2011fe, \citet{2014MNRAS.441..532D} examined
 pulsational delayed-detonation (PDD) models as an explanation for some SNe
@@
   \caption{
-  \textbf{Same as Figure~\ref{fig:noebauer}, featuring the DD and PDD models
-  from \citet{2014MNRAS.441..532D}. The bottom panel legend lists the models
-  in order of decreasing $M_\mathrm{Ni}$ from top to bottom. DD models
-  (labeled as DDC to match the nomenclature of \citealt{2014MNRAS.441..532D})
-  are shown as dash-dot lines, while PDD models (labeled as PDDEL) are shown
-  as dashed lines. The inset in the top panel shows the residuals relative to
-  the PDDEL7n model. The PDD models provide a better match to the
-  observations.} 
-  } \label{fig:dessart} 
+  %
+  \textbf{Same as Figure~\ref{fig:noebauer}, featuring the $g$-band light
+  curve and the DD and PDD models from \citet{2014MNRAS.441..532D}. The bottom
+  panel legend lists the models in order of decreasing $M_\mathrm{Ni}$ from
+  top to bottom. DD models (labeled as DDC to match the nomenclature of
+  \citealt{2014MNRAS.441..532D}) are shown as dash-dot lines, while PDD models
+  (labeled as PDDEL) are shown as dashed lines. The inset in the top panel
+  shows the residuals relative to the PDDEL7n model. The PDD models provide a
+  better match to the observations.} }
+  %
+  \label{fig:dessart} 
 \end{figure}
@@
 \textbf{In Figure~\ref{fig:dessart} we compare photometric observations of
-\abc\ to the large-$^{56}$Ni yield DD and PDD models presented in
-\citet{2014MNRAS.441..532D}. DD and PDD models with $M_\mathrm{Ni}/M_\odot \la
-0.7$ and 0.5, respectively, fail to match the early luminosity and blue colors
-of \abc. The PDD models provide a better match to the observations than the DD
-models. The PDD models evolve more rapidly towards blue colors and provide a
-better match to the $g$-band flux in the days after explosion. Furthermore,
-unlike the DD models, the PDD models exhibit strong \ion{C}{2} lines that
-gradually disappear in the $\sim$week after explosion
-\citet{2014MNRAS.441..532D}. In detail, the early wiggles in the \abc\ light
-curve are not matched by the PDD models, which exhibit more smooth variations.
-Furthermore, while the focus of this study is the early evolution of \abc, the
-PDD models evolve more rapidly to the red post-peak than the observations.
-Nevertheless, the PDD models presented in \citet{2014MNRAS.441..532D} provide
-several attractive explanations for the unusual features in the early behavior
-of \abc, and small adjustments to the model (e.g., additional mixing of the
-radioactive material, which \citeauthor{2014MNRAS.441..532D} only explore for
-the DD model) may better match \abc.}
+\abc\ to the high-$^{56}$Ni yield DD and PDD models presented in
+\citet{2014MNRAS.441..532D}.\footnote{Available here:
+\url{https://www-n.oca.eu/supernova/snia/snia_ddc_pddel.html}.} DD and PDD
+models with $M_\mathrm{Ni}/M_\odot \la 0.7$ and 0.5, respectively, fail to
+match the early luminosity and blue colors of \abc. The PDD models provide a
+better match to the observations than the DD models. The PDD models evolve
+more rapidly towards blue colors and provide a better match to the $g$-band
+flux in the days after explosion. Furthermore, unlike the DD models, the PDD
+models exhibit strong \ion{C}{2} lines that gradually disappear in the
+$\sim$week after explosion \citep{2014MNRAS.441..532D}. In detail, the early
+wiggles in the \abc\ light curve are not matched by the PDD models, which
+exhibit more smooth variations. Furthermore, while the focus of this study is
+the early evolution of \abc, the PDD models evolve more rapidly to the red
+post-peak than the observations. Nevertheless, the PDD models presented in
+\citet{2014MNRAS.441..532D} provide several attractive explanations for the
+unusual features in the early behavior of \abc. Small adjustments to the PDD
+models (e.g., additional $^{56}$Ni mixing, which
+\citeauthor{2014MNRAS.441..532D} only explore for DD models) may better match
+\abc.}
 
@@
   \caption{
-  \textbf{Same as Figure~\ref{fig:noebauer}, featuring models from
-  \citet{2016ApJ...826...96P}. The amount of $^{56}$Ni mixing in the SN ejecta
-  increases from the short-dash, light lines to the long-dash, dark lines.
-  Unlike Figure~\ref{fig:dessart}, each model features the same
-  $M_\mathrm{Ni}$, while the model names reflect the boxcar widths used to
-  approximate the effects of mixing in the ejecta (see
-  \citealt{2016ApJ...826...96P}). The top panel inset shows the
-  residuals relative to the $0.25\,M_\odot$ model. The observations are best
-  matched by the $0.25\,M_\odot$ model, i.e. the model with the most
-  significant mixing.}
-  }
+  %
+  \textbf{Same as Figure~\ref{fig:noebauer}, featuring the $g$-band light
+  curve and models from \citet{2016ApJ...826...96P}. The amount of $^{56}$Ni
+  mixing in the SN ejecta increases from the short-dash, light lines to the
+  long-dash, dark lines. Unlike Figure~\ref{fig:dessart}, each model features
+  the same $M_\mathrm{Ni}$, while the model names reflect the boxcar widths
+  used to approximate the effects of mixing in the ejecta (see
+  \citealt{2016ApJ...826...96P}). The top panel inset shows the residuals
+  relative to the $0.25\,M_\odot$ model. The observations are best matched by
+  the $0.25\,M_\odot$ model, i.e. the model with the most significant mixing.}}
+  %
   \label{fig:piro}
@@
 optical photometric evolution of \abc, they consistently overpredict the flux
-in the UV. \textbf{They} also overpredict the
-photospheric velocity of \abc\ by $\sim$2--3,000$\; \mathrm{km \; s}^{-1}$.
-Future modeling efforts may improve the match between the simulations and
-observations for \abc.
+in the UV. \textbf{They} also overpredict the photospheric velocity of \abc\
+by $\sim$2--3,000$\; \mathrm{km \; s}^{-1}$. \textbf{Furthermore, the simple
+grey opacities in SNEC likely produce a faster rise and bluer colors than the
+more detailed treatments employed in \citet{2014MNRAS.441..532D} and
+\citet{2017MNRAS.472.2787N}.}
 

### 2017-11-17 doc/ms.tex
update text in the SN comp section

@@
 
-\section{\textbf{Discussion: The Emerging Sample of Young \sneia}}
-
-The proliferation of high-cadence, time-domain surveys has led to several SNe Ia being discovered within $\lesssim$2\,d of first light in the past $\sim$decade.
-Observations probing the early evolution of these SNe allows us to place unique constraints on their progenitor systems and the corresponding explosion physics.
-This has revealed diversity in the earliest epochs after explosion and that commonly used SNe Ia templates do not match observations (e.g., \citealt{2012ApJ...744...38F}).
-
-In \S\ref{sec:first_light} we compared our early observations of \abc\ to SN\,2011fe, which has the most comprehensive observations of the young SN Ia sample.
-Given its normal spectroscopic and photometric evolution, SN\,2011fe has been adopted as a standard for the early evolution of SNe Ia in many studies.
-While a detailed quantitative analysis is beyond the scope of this study, a qualitative examination of very young SNe Ia that otherwise exhibit normal spectra and evolution at and post-peak\footnote{This definition excludes iPTF\,14atg, which was shown to be subluminous with SN\,2002es-like spectra \citep{2015Natur.521..328C}.} reveals considerable diversity.
-In other words, at early times SN\,2011fe may not be the norm.
-
-For SN\,2011fe the initial rise is well described by a $t^2$ power law, the $(B - V)_0$ colors evolve from the red to the blue in the $\sim$week after explosion, and the \ion{C}{2} present in the initial spectra is weak \citep{2011Natur.480..344N,2016ApJ...820...67Z,2012ApJ...752L..26P}.
-In contrast, \abc\ exhibits a near linear rise in flux, the $(B - V)_0$ colors are blue and roughly constant, and the \ion{C}{2} absorption is strong.
-Examining just these 3 qualitative features, SN\,2009ig is well matched to SN\,2011fe \citep{2012ApJ...744...38F}, while SN\,2013dy \citep{2013ApJ...778L..15Z}, SN\,2017cbv \citep{2017ApJ...845L..11H}, and \abc\ all bear a striking resemblance.
-SN\,2012cg, on the other hand, is intermediate to these two groups with weak C II and a relatively shallow early rise, like SN\,2011fe, but blue $(B - V)_0$ colors, like \abc\ \citep{2012ApJ...756L...7S,2016ApJ...820...92M}.
-SN\,2014J is intermediate in the other direction in that it exhibits a near linear rise \citep{2014ApJ...783L..24Z,2015ApJ...799..106G}, but the color evolution is very similar to SN\,2011fe \citep{2014ApJ...788L..21A}.\footnote{\ion{C}{2} is not detected in the spectra of SN\,2014J \citep{2014ApJ...784L..12G,2014ApJ...783L..24Z}, though the earliest spectra of SN\,2014J were obtained at a much later phase than the other SNe discussed here.
-\citet{2015ApJ...798...39M} find evidence for \ion{C}{1} in the NIR spectra of SN\,2014J, but this detection cannot constrain the relative strength of \ion{C}{2} and \ion{Si}{2} shortly after explosion.} That these early observations cannot be easily separated into two distinct groups suggests that it is unlikely that a single physical mechanism drives the diversity of SNe Ia at early times.
-
-In the case of SN\,2012cg and SN\,2017cbv it has been argued that the early blue optical colors are indicative of interaction between the SN ejecta and a binary companion \citep{2016ApJ...820...92M,2017ApJ...845L..11H}.
-SN\,2017cbv is particularly remarkable in that the observations presented in \citet{2017ApJ...845L..11H} show a clearly resolved bump in the $U$, $B$, and $g'$ bands in the $\sim$5\,d after explosion.
-In \citeauthor{2017ApJ...845L..11H} it is found that the bump can be explained via the combination of ejecta-companion interaction and the normal evolution of a SN Ia.
-A challenge for this model, similar to \abc\ (see \S\ref{sec:companion}), is that it significantly overpredicts the UV brightness of the SN compared to what is observed.
-Indeed, in the case of SNe\,2012cg, 2017cbv, and \abc\ the $\mathrm{UV} - \mathrm{optical}$ colors are significantly redder than those observed in iPTF\,14atg.
-It is argued in \citet{2017ApJ...845L..11H} that several model assumptions, including: (i) ideal blackbody emission, (ii) a constant opacity, (iii) a simple power-law density profile for the ejecta, and (iv) spherical symmetry, may be incorrect, which could reconcile the discrepancy with the UV observations.
-Above, we argued for circumstellar interaction and strong $^{56}$Ni mixing as a possible explanation for \abc, and indeed \citet{2017ApJ...845L..11H} consider these possibilities for SN\,2017cbv as well.
-Separately, several arguments against companion interaction for SN\,2012cg are presented in \citet{2016arXiv161007601S}.
-
-Ultimately, there are arguments in favor of and against each of the possibilities to explain the early emission from SNe Ia.
-Moving forward, more detailed models and simulations are needed to properly explain the observed diversity.
-No matter the correct explanation for the early behavior of SNe\,2013dy, 2017cbv, and \abc, the strong similarities between these events suggests that they may reflect a common physical origin.
+\section{\textbf{The Emerging Sample of Young \sneia}}
+
+The proliferation of high-cadence, time-domain surveys has led to several SNe
+Ia being discovered within $\sim$2\,d of first light in the past $\sim$decade.
+Observations probing the early evolution of these SNe allows us to place
+unique constraints on their progenitor systems and the corresponding explosion
+physics. This has revealed diversity in the earliest epochs after explosion,
+and that commonly used SNe Ia templates do not match observations at these
+phases (e.g., \citealt{2012ApJ...744...38F}).
+
+In \S\ref{sec:first_light} we compared our early observations of \abc\ to
+SN\,2011fe, which has the most comprehensive observations of the young SN Ia
+sample. Given its normal spectroscopic and photometric evolution, SN\,2011fe
+has been adopted as a standard for the early evolution of SNe Ia in many
+studies. While a detailed quantitative analysis is beyond the scope of this
+study, a qualitative examination of very young SNe Ia that otherwise exhibit
+normal spectra and evolution at and post peak\footnote{This definition
+excludes iPTF\,14atg, which was shown to be subluminous with SN\,2002es-like
+spectra \citep{2015Natur.521..328C}.} reveals considerable diversity. In other
+words, at early times SN\,2011fe may not be the norm.
+
+For SN\,2011fe the initial rise is well described by a $t^2$ power law, the
+$(B - V)_0$ colors evolve from the red to the blue in the $\sim$week after
+explosion, and the \ion{C}{2} present in the initial spectra is weak
+\citep{2011Natur.480..344N,2016ApJ...820...67Z,2012ApJ...752L..26P}. In
+contrast, \abc\ exhibits a near linear rise in flux, the $(B - V)_0$ colors
+are blue and roughly constant, and the \ion{C}{2} absorption is strong.
+Examining just these 3 qualitative features, SN\,2009ig is well matched to
+SN\,2011fe \citep{2012ApJ...744...38F}, while SN\,2013dy
+\citep{2013ApJ...778L..15Z}, SN\,2017cbv \citep{2017ApJ...845L..11H}, and
+\abc\ all bear a striking resemblance. SN\,2012cg, on the other hand, is
+intermediate to these two groups with weak C II and a relatively shallow early
+rise, like SN\,2011fe, but blue $(B - V)_0$ colors, like \abc\
+\citep{2012ApJ...756L...7S,2016ApJ...820...92M}. SN\,2014J is intermediate in
+the other direction in that it exhibits a near linear rise
+\citep{2014ApJ...783L..24Z,2015ApJ...799..106G}, but the color evolution is
+very similar to SN\,2011fe \citep{2014ApJ...788L..21A}.\footnote{\ion{C}{2} is
+not detected in the spectra of SN\,2014J
+\citep{2014ApJ...784L..12G,2014ApJ...783L..24Z}, though the earliest spectra
+of SN\,2014J were obtained at a much later phase than the other SNe discussed
+here. \citet{2015ApJ...798...39M} find evidence for \ion{C}{1} in the NIR
+spectra of SN\,2014J, but this detection cannot constrain the relative
+strength of \ion{C}{2} and \ion{Si}{2} shortly after explosion.} That these
+early observations cannot be easily separated into two distinct groups
+suggests that it is unlikely that a single physical mechanism drives the
+diversity of SNe Ia at early times.
+
+In the case of SN\,2012cg and SN\,2017cbv it has been argued that the early
+blue optical colors are indicative of interaction between the SN ejecta and a
+binary companion \citep{2016ApJ...820...92M,2017ApJ...845L..11H}. SN\,2017cbv
+is particularly remarkable in that the observations presented in
+\citet{2017ApJ...845L..11H} show a clearly resolved bump in the $U$, $B$, and
+$g'$ bands in the $\sim$5\,d after explosion. In
+\citeauthor{2017ApJ...845L..11H} it is found that the bump can be explained
+via the combination of ejecta-companion interaction and the normal evolution
+of a SN Ia. A challenge for this model, similar to \abc\ (see
+\S\ref{sec:companion}), is that it significantly overpredicts the UV
+brightness of the SN compared to what is observed. Indeed, in the case of
+SNe\,2012cg, 2017cbv, and \abc\ the $\mathrm{UV} - \mathrm{optical}$ colors
+are significantly redder than those observed in iPTF\,14atg. It is argued in
+\citet{2017ApJ...845L..11H} that several model assumptions, including: (i)
+ideal blackbody emission, (ii) a constant opacity, (iii) a simple power-law
+density profile for the ejecta, and (iv) spherical symmetry, may be incorrect,
+which could reconcile the discrepancy with the UV observations. Above, we
+argued for interaction \textbf{with diffuse, unbound material} and strong
+$^{56}$Ni mixing as a possible explanation for \abc, and indeed
+\citet{2017ApJ...845L..11H} consider these possibilities for SN\,2017cbv as
+well. Separately, several arguments against companion interaction for
+SN\,2012cg are presented in \citet{2016arXiv161007601S}.
+
+Ultimately, there are arguments in favor of and against each of the
+possibilities to \textbf{model} the early emission from SNe Ia. Moving
+forward, more detailed models and simulations are needed to properly explain
+the observed diversity. No matter the correct explanation for the early
+behavior of SNe\,2013dy, 2017cbv, and \abc, the strong similarities between
+these events suggests that they may reflect a common physical origin.
 

### 2017-11-17 doc/ms.tex
update text in the conclusions

@@
 \begin{itemize}
-    \item Extrapolation of the early light curve shows that the initial detection of \abc\ occurred only $0.15\pm_{0.07}^{0.15}$~d after the time of first light, $t_0$.
-
-    \item We find no evidence for detectable signatures of SN shock cooling or the collision of the SN ejecta with a non-degnerate binary companion.
-
-    \item Assuming that $v_\mathrm{ph} \propto t^{-0.22}$, then $t_\mathrm{exp} \approx t_0$.
-A short dark phase, as this implies, is likely the result of either strong $^{56}$Ni mixing or interaction of the SN ejecta with diffuse material.
-
-    \item The strong and short-lived carbon features seen in the 
-earliest spectra of \abc\ can only be explained if there is incomplete burning.
-The pulsational delayed detonation models presented in \citet{2014MNRAS.441..532D} produce \ion{C}{2} absorption that is as strong as \ion{Si}{2} at very early phases.
-
-    \item In contrast to SN\,2011fe, $(B - V)_0$ is $\sim$0.5 mag bluer for \abc\ $\sim$2\,d after $t_0$.
-Furthermore, the $(B - V)_0$ colors of \abc\ show no evolution over the first $\sim$7\,d  of observations.
-
-    \item Finally, we show that the early light curve evolution and colors of \abc\ are well matched by the theoretical models of \citet{2016ApJ...826...96P} that include significant mixing of $^{56}$Ni into the outer layers of the SN ejecta.
+
+    \item Extrapolation of the early light curve shows that the initial
+    detection of \abc\ occurred only $0.15\pm_{0.07}^{0.15}$~d after the time
+    of first light, $t_0$.
+
+    \item We find no evidence for detectable signatures of SN shock cooling or
+    the collision of the SN ejecta with a non-degnerate binary companion.
+
+    \item Assuming that $v_\mathrm{ph} \propto t^{-0.22}$, then
+    $t_\mathrm{exp} \approx t_0$. A short dark phase, as this implies, is
+    likely the result of either strong $^{56}$Ni mixing or interaction of the
+    SN ejecta with \textbf{nearby, unbound} material.
+
+    \item The strong and short-lived carbon features seen in the earliest
+    spectra of \abc\ can only be explained if there is incomplete burning. The
+    pulsational delayed detonation models presented in
+    \citet{2014MNRAS.441..532D} produce \ion{C}{2} absorption that is as
+    strong as \ion{Si}{2} at very early phases.
+
+    \item In contrast to SN\,2011fe, $(B - V)_0$ is $\sim$0.5 mag bluer for
+    \abc\ at $t \approx -16$\,d. Furthermore, the $(B - V)_0$ colors of \abc\
+    show no evolution over the first $\sim$7\,d of observations.
+
+    \item Finally, we show that the early light curve evolution and colors of
+    \abc\ are best \textbf{matched by the pulsational delayed detonation
+    models of \citet{2014MNRAS.441..532D}} and the ejecta-mixing models of
+    \citet{2016ApJ...826...96P}.
 
@@
 %
-Taken together, these observations all indicate that the nucleosynthetic products from the explosion are well mixed throughout the SN ejecta.
-There are elements of the PDD models from \citet{2014MNRAS.441..532D} that are attractive for explaining \abc, in particular, the strong \ion{C}{2} absorption seen at early times.
-In the future, it would be useful to investigate more detailed PDD models that incorporate strong $^{56}$Ni mixing to see if they better replicate the observations of \abc\ as it is otherwise difficult to distinguish between these two scenarios \citep{2017MNRAS.472.2787N}.\footnote{Both \citet{2014MNRAS.441..532D} and \citet{2016ApJ...826...96P} consider models with strong mixing \textit{and} interaction, but those studies do not replicate each of the salient features of \abc.}
+Taken together, these observations \textbf{suggest that the early emission
+from \abc\ is due to either the collision of the SN with nearby, unbound
+material and/or that there is significant mixing of $^{56}$Ni in the SN
+ejecta.} The PDD models from \citet{2014MNRAS.441..532D} are particularly
+attractive for explaining \abc, \textbf{because they produce} strong
+\ion{C}{2} absorption at early times. In the future, it would be useful to
+investigate more detailed PDD models that incorporate strong $^{56}$Ni mixing
+to see if they better replicate the observations of \abc\ as it is otherwise
+difficult to distinguish between these two scenarios.
 
@@
 Furthermore, only $\sim$10\% of single-degenerate progenitors are expected to give rise to detectable emission following the collision of the SN ejecta with the binary companion \citep{2010ApJ...708.1025K}.
-Despite these limitations, this study of \abc\ shows that the early detection of SNe Ia can probe explosion physics by measuring the amount of mixing in the SN ejecta.
+Despite these limitations, this study of \abc\ shows that the early detection of SNe Ia \textbf{may} probe explosion physics by measuring the amount of mixing in the SN ejecta.
 Moving forward, a large sample of such objects will enable strict constraints on the proposed explosion mechanisms for Type Ia SNe.
@@
 Without the early recognition of the youth of this SN, and the associated follow-up, much of the analysis presented herein would not have been possible.
-The ability to trigger such observations is essential to improve our understanding of the physics of SNe Ia.
+The ability to trigger such observations is essential to improve our \textbf{physical} understanding of Type Ia SNe.
 
@@
 
-This paper utilizes the LCO infrastructure for rapid and regular monitoring of SNe, and we thank S.~Valenti and I.~Arcavi for their development efforts.
-\textbf{Figure~\ref{fig:branch_vel} would not have been possible without S.~Blondin generously sharing the data from \citet{2012AJ....143..126B}.}
-
-Much of the analysis presented herein would not have been possible without the help of several observers.
-We thank M.~West for taking the first spectrum of \abc\ as a ToO on the DCT.
-We also thank P.~GuhaThakurta, E.~C.~Cunningham, K.~A.~Plant, H.~Jang, and J.~Torres for executing a Keck ToO as part of the UC/Caltech partnership, and also the Gemini service observers for executing our ToO observations.
-Additionally, J.~Cohen, N.~Suzuki, V.~Ravi, R.~Walters, A.~Ho, H.~Vedanthamand, K.~De, and L.~Yan helped obtain data for this paper.
-
-AAM is funded by the Large Synoptic Survey Telescope Corporation in support of the Data Science Fellowship Program.
-YC thanks support from a postdoc fellowship in the eScience institute, University of Washington.
+This paper utilizes the LCO infrastructure for rapid and regular monitoring of
+SNe, and we thank S.~Valenti and I.~Arcavi for their development efforts.
+\textbf{Figure~\ref{fig:branch_vel} would not have been possible without
+S.~Blondin generously sharing the data from \citet{2012AJ....143..126B}.}
+
+Much of the analysis presented herein would not have been possible without the
+help of several observers. We thank M.~West for taking the first spectrum of
+\abc\ as a ToO on the DCT. We also thank P.~GuhaThakurta, E.~C.~Cunningham,
+K.~A.~Plant, H.~Jang, and J.~Torres for executing a Keck ToO as part of the
+UC/Caltech partnership, and also the Gemini service observers for executing
+our ToO observations. Additionally, J.~Cohen, N.~Suzuki, V.~Ravi, R.~Walters,
+A.~Ho, H.~Vedanthamand, K.~De, and L.~Yan helped obtain data for this paper.
+
+AAM is funded by the Large Synoptic Survey Telescope Corporation in support of
+the Data Science Fellowship Program. YC thanks support from a postdocal
+fellowship at the eScience Institute, University of Washington.
 
@@
 The upgrade of the DeVeny optical spectrograph has been funded by a generous grant from John and Ginger Giovale.
-Based on observations made with the Nordic Optical Telescope, operated by the Nordic Optical Telescope Scientific Association at the Observatorio del Roque de los Muchachos, La Palma, Spain, of the Instituto de Astrofisica de Canarias.
+Based on observations made with the Nordic Optical Telescope, operated by the Nordic Optical Telescope Scientific Association at the Observatorio del Roque de los Muchachos, La Palma, Spain, of the Instituto de Astrof\'isica de Canarias.
 
@@
   \includegraphics[width=0.48\textwidth]{lightcurve.pdf}
-  \caption{UV, optical, and NIR light curves for \abc. 
-  \textit{Top}: $BVgri$ light curves from the P48, P60, and LCO-1m 
-  telescopes. The solid lines represent the best-fit model from 
-  SALT2 (see \ref{sec:classification}).
-  \textit{Bottom}: UV and NIR light curves from the \textit{Swift} 
-  and SPM-1.5m telescopes, respectively.
-  For both panels each light curve is represented with a different 
-  color, while the different symbols correspond to different 
-  instruments, as detailed in the legends. The legends also list 
-  offsets applied to each light curve. Photometry is shown in the 
-  AB mag system, with the exception of the $BV$ bands, which are 
-  shown in the Vega system. The photometry shown has not been 
-  corrected for line-of-sight extinction.
-  }
+  \caption{
+  %
+  UV, optical, and NIR light curves for \abc. \textit{Top}: $BVgri$ light
+  curves from the P48, P60, LCO-1m, and \textit{Swift} telescopes. The solid
+  lines represent the best-fit model from SALT2 (see
+  \S\ref{sec:classification}). \textit{Bottom}: UV and NIR light curves from
+  the \textit{Swift} and SPM-1.5m telescopes, respectively. For both panels
+  each light curve is represented with a different color, while the different
+  symbols correspond to different instruments, as detailed in the legends. The
+  legends also list offsets applied to each light curve. Photometry is shown
+  in the AB mag system, with the exception of the $BV$ bands, which are shown
+  in the Vega system. These \textbf{light curves have} not been corrected for
+  line-of-sight extinction.}
+  %
   \label{fig:ugly_LC}

### 2017-11-20 doc/ms.tex
Update figure widths to inches

@@
 $\textrm{Dec.}=+13\degr51\arcmin14\farcs3$ (J2000) with a
-$g_\mathrm{PTF}$-band magnitude of $21.31\pm0.27$ \citep{2016ATel.8907....1M}.
+$g_\mathrm{PTF}$-band magnitude of $21.44\pm0.25$ \citep{2016ATel.8907....1M}.
 The transient is spatially coincident with a tidal tail of the galaxy
 NGC\,5221, which lies at a distance of $\sim$100\,Mpc. \abc\ is not detected
-to a limit of $g_\mathrm{PTF}=22.1$\,mag on April $2.42$, less than 1\,d prior
-to discovery, and rose by $\sim$2\,mag in the 24\,hr following its initial
-detection. Our spectroscopic follow-up campaign classified \abc\ as a normal
-SN Ia \citep{2016ATel.8909....1C}. Our observations and analysis show that the
-early evolution of \abc\ exhibited several distinct properties relative to
-SN\,2011fe. We interpret those differences as arising from either strong
-$^{56}$Ni mixing or ejecta interaction with \textbf{nearby, unbound} material,
-or a combination of the two. Alongside this paper, we have released our open
-source analysis and all of the data utilized in this study. These are
+to a 5-$\sigma$ limit of $g_\mathrm{PTF}=21.9$\,mag on April $2.42$, less than
+1\,d prior to discovery, and rose by $\sim$2\,mag in the 24\,hr following its
+initial detection. Our spectroscopic follow-up campaign classified \abc\ as a
+normal SN Ia \citep{2016ATel.8909....1C}. Our observations and analysis show
+that the early evolution of \abc\ exhibited several distinct properties
+relative to SN\,2011fe. We interpret those differences as arising from either
+strong $^{56}$Ni mixing or ejecta interaction with \textbf{nearby, unbound}
+material, or a combination of the two. Alongside this paper, we have released
+our open source analysis and all of the data utilized in this study. These are
 available online at \texttt{GitHub}
@@
     \centering
-    \includegraphics[width=0.48\textwidth]{logLC_with_colors.pdf} 
+    \includegraphics[width=3.35in]{logLC_with_colors.pdf} 
     \caption{
-    The $g$-band light curve of \abc. Observations from different telescopes
-    are shown with different symbols. Time is measured in rest-frame days
-    relative to $t_0$ (see \S\ref{sec:lc_fit}). Note that the horizontal axis
-    is shown with a linear scale for $-2 \; \mathrm{d} \le t - t_0 \le 3 \;
-    \mathrm{d}$ and a $\log$ scale for $t - t_0 > 3 \; \mathrm{d}$.
-    \textbf{Vertical} black ticks show epochs of spectroscopic observations. }
+    %
+    The $g$-band light curve of \abc, with 5-$\sigma$ upper limits shown as
+    downward arrows. Observations from different telescopes are shown with
+    different symbols. The lower axis shows time measured in rest-frame days
+    relative to $t_0$ (see \S\ref{sec:lc_fit}), while the upper axis shows
+    time relative to $B$-band maximum. Note that the horizontal axis is shown
+    with a linear scale for $-2 \; \mathrm{d} \le t - t_0 \le 3 \; \mathrm{d}$
+    and a $\log$ scale for $t - t_0 > 3 \; \mathrm{d}$. \textbf{Vertical}
+    black ticks show epochs of spectroscopic observations. }
+% 
     \label{fig:lightcurve} 
@@
   \centering
-  \includegraphics[width=0.69\textwidth]{spectra.pdf}
+  \includegraphics[width=5.5in]{spectra.pdf}
   \caption{
@@
   \centering
-  \includegraphics[width=0.48\textwidth]{Branch_vel_evol.pdf}
+  \includegraphics[width=3.35in]{Branch_vel_evol.pdf}
   \caption{
@@
   \centering
-  \includegraphics[width=0.48\textwidth]{early_lc.pdf}
+  \includegraphics[width=3.35in]{early_lc.pdf}
   \caption{
@@
   \centering
-  \includegraphics[width=0.48\textwidth]{Chi2.pdf}
-  \includegraphics[width=0.48\textwidth]{VelocityPlot.pdf}
+  \includegraphics[width=3.35in]{Chi2.pdf}
+  \includegraphics[width=3.35in]{VelocityPlot.pdf}
   \caption{
@@
   \centering
-  \includegraphics[width=0.49\textwidth]{CarbonFeature.pdf}
+  \includegraphics[width=3.35in]{CarbonFeature.pdf}
   \caption{
@@
   \centering
-  \includegraphics[width=0.48\textwidth]{16abc_11fe_colors.pdf}
+  \includegraphics[width=3.35in]{16abc_11fe_colors.pdf}
   \caption{$(B - V)_0$ color evolution of \abc\ (squares) 
@@
   \centering
-  \includegraphics[width=0.48\textwidth]{companion_lc.pdf}
+  \includegraphics[width=3.35in]{companion_lc.pdf}
   \caption{Comparison of SN ejecta-companion interaction models 
@@
   \centering
-  \includegraphics[width=0.48\textwidth]{compare_Noebauer.pdf}
+  \includegraphics[width=3.35in]{compare_Noebauer.pdf}
   \caption{
@@
   \centering
-  \includegraphics[width=0.48\textwidth]{compare_Dessart.pdf}
+  \includegraphics[width=3.35in]{compare_Dessart.pdf}
   \caption{
@@
   \centering
-  \includegraphics[width=0.48\textwidth]{compare_Piro.pdf}
+  \includegraphics[width=3.35in]{compare_Piro.pdf}
   \caption{
@@
   \centering
-  \includegraphics[width=0.48\textwidth]{lightcurve.pdf}
+  \includegraphics[width=3.35in]{lightcurve.pdf}
   \caption{

### 2017-11-20 doc/ms.tex
minor figure caption clean up

@@
 NGC\,5221, which lies at a distance of $\sim$100\,Mpc. \abc\ is not detected
-to a 5-$\sigma$ limit of $g_\mathrm{PTF}=21.9$\,mag on April $2.42$, less than
-1\,d prior to discovery, and rose by $\sim$2\,mag in the 24\,hr following its
-initial detection. Our spectroscopic follow-up campaign classified \abc\ as a
-normal SN Ia \citep{2016ATel.8909....1C}. Our observations and analysis show
-that the early evolution of \abc\ exhibited several distinct properties
-relative to SN\,2011fe. We interpret those differences as arising from either
-strong $^{56}$Ni mixing or ejecta interaction with \textbf{nearby, unbound}
-material, or a combination of the two. Alongside this paper, we have released
-our open source analysis and all of the data utilized in this study. These are
-available online at \texttt{GitHub}
-\url{https://github.com/adamamiller/iPTF16abc}.
+\textbf{to a 5-$\sigma$ limit of} $g_\mathrm{PTF}=21.9$\,mag on April $2.42$,
+less than 1\,d prior to discovery, and rose by $\sim$2\,mag in the 24\,hr
+following its initial detection. Our spectroscopic follow-up campaign
+classified \abc\ as a normal SN Ia \citep{2016ATel.8909....1C}. Our
+observations and analysis show that the early evolution of \abc\ exhibited
+several distinct properties relative to SN\,2011fe. We interpret those
+differences as arising from either strong $^{56}$Ni mixing or ejecta
+interaction with \textbf{nearby, unbound} material, or a combination of the
+two. Alongside this paper, we have released our open source analysis and all
+of the data utilized in this study. These are available online at
+\texttt{GitHub} \url{https://github.com/adamamiller/iPTF16abc}.
 
@@
     downward arrows. Observations from different telescopes are shown with
-    different symbols. The lower axis shows time measured in rest-frame days
-    relative to $t_0$ (see \S\ref{sec:lc_fit}), while the upper axis shows
-    time relative to $B$-band maximum. Note that the horizontal axis is shown
-    with a linear scale for $-2 \; \mathrm{d} \le t - t_0 \le 3 \; \mathrm{d}$
-    and a $\log$ scale for $t - t_0 > 3 \; \mathrm{d}$. \textbf{Vertical}
-    black ticks show epochs of spectroscopic observations. }
+    different symbols. \textbf{The lower axis shows time} measured in
+    rest-frame days relative to $t_0$ (see \S\ref{sec:lc_fit}), \textbf{while
+    the upper axis shows time relative to $B$-band maximum.} Note that the
+    horizontal axis is shown with a linear scale for $-2 \; \mathrm{d} \le t -
+    t_0 \le 3 \; \mathrm{d}$ and a $\log$ scale for $t - t_0 > 3 \;
+    \mathrm{d}$. \textbf{Vertical} black ticks show epochs of spectroscopic
+    observations. }
 % 
@@
   \centering
-  \includegraphics[width=3.35in]{lightcurve.pdf}
+  \includegraphics[width=7in]{lightcurve2.pdf}
   \caption{
   %
-  UV, optical, and NIR light curves for \abc. \textit{Top}: $BVgri$ light
-  curves from the P48, P60, LCO-1m, and \textit{Swift} telescopes. The solid
-  lines represent the best-fit model from SALT2 (see
-  \S\ref{sec:classification}). \textit{Bottom}: UV and NIR light curves from
+  UV, optical, and NIR light curves for \abc. \textit{Left}: $BVgri$ light
+  curves from the P48, P60, LCO-1m, \textit{Swift}, and SPM-1.5m telescopes.
+  The solid lines represent the best-fit model from SALT2 (see
+  \S\ref{sec:classification}). \textit{Right}: UV and NIR light curves from
   the \textit{Swift} and SPM-1.5m telescopes, respectively. For both panels

### 2017-11-23 doc/ms.tex
Update following minor comments from Jesper

@@
 \textbf{larger luminosities and bluer optical colors at early times}.
-\textbf{Even with vigorous mixing it is difficult at very early times, $<
+\textbf{Even with vigorous mixing it is difficult at very early times, $\ll
 1$\,d after explosion, to explain very large luminosities or blue colors,
@@
 
-\textbf{Given that the time of explosion $t_\mathrm{exp}$ is not constrained
-by $t_0$ (see above),} \citet{2014ApJ...784...85P} suggest that measurements
-of the photospheric velocity can determine $t_\mathrm{exp}$ given that the
-ejecta begin expanding from the moment of explosion. Assuming a constant
-opacity in the ejecta, \citeauthor{2014ApJ...784...85P} find that the
-photospheric velocity evolves as
-$v_\mathrm{ph}\propto(t-t_\mathrm{exp})^{-0.22}$. Numerical experiments by
-\citet{2016ApJ...826...96P} find that the constant-opacity assumption strongly
-depends on the amount of $^{56}$Ni mixing in the SN ejecta. As a result, the
-adoption of a $t^{-0.22}$ power-law model may not be valid for all SNe Ia.
-Nevertheless, we proceed on the assumption that \abc\ experienced strong
-$^{56}$Ni mixing \textbf{(see \S\ref{sec:Ni_mixing})}, corresponding to the
-models that are best approximated as a $t^{-0.22}$ power law. We do this in
-part to compare with previous studies, though we caution that the inferred
-value of $t_{exp}$ is subject to uncertainties related to ejecta mixing.
+\textbf{The time of explosion $t_\mathrm{exp}$ is not equal to $t_0$ (see
+above), thus,} \citet{2014ApJ...784...85P} suggest that measurements of the
+photospheric velocity can determine $t_\mathrm{exp}$ given that the ejecta
+begin expanding from the moment of explosion. Assuming a constant opacity in
+the ejecta, \citeauthor{2014ApJ...784...85P} find that the photospheric
+velocity evolves as $v_\mathrm{ph}\propto(t-t_\mathrm{exp})^{-0.22}$.
+Numerical experiments by \citet{2016ApJ...826...96P} find that the
+constant-opacity assumption strongly depends on the amount of $^{56}$Ni mixing
+in the SN ejecta. As a result, the adoption of a $t^{-0.22}$ power-law model
+may not be valid for all SNe Ia. Nevertheless, we proceed on the assumption
+that \abc\ experienced strong $^{56}$Ni mixing \textbf{(see
+\S\ref{sec:Ni_mixing})}, corresponding to the models that are best
+approximated as a $t^{-0.22}$ power law. We do this in part to compare with
+previous studies, though we caution that the inferred value of $t_{exp}$ is
+subject to uncertainties related to ejecta mixing.
 
@@
 ``N1600Cdef'' pure deflagration explosions from \citet{2014MNRAS.438.1762F}.
-The ``N5def'' model is particularly unique in that it does not fully unbind
-the WD and therefore leaves a remnant.}
+The ``N5def'' model is particularly unique in that the explosion does not
+fully unbind the WD, meaning, unlike typical Type Ia SNe, a remnant remains.}
 
@@
 
-\facility{DCT, Gemini:Gillett, Hale, Keck:I, Keck:II, LCOGT, PO:1.2\,m, PO:1.5\,m, VLT, Swift, OANSPM:HJT}
+\facility{DCT, Gemini:Gillett, Hale, Keck:I, Keck:II, LCOGT, PO:1.2\,m, PO:1.5\,m, NOT, VLT, Swift, OANSPM:HJT}
 

### 2017-11-23 doc/ms.tex
Update abstract slightly

@@
 \abc. By fitting a power law to our early light curve, we infer that first
-light for the SN, \textbf{that is when the SN produces appreciable optical
-radiation following shock breakout}, \textbf{occurred only}
-$0.15\pm_{0.07}^{0.15}$\,d before our first detection. In the $\sim$24\,hr
-after discovery, \abc\ rose by $\sim$2\,mag, \textbf{featuring} a near-linear
-rise in flux for $\gtrsim$3 d. \textbf{Early spectra show strong \ion{C}{2}
-absorption, which disappears after $\sim$7\,d.} Unlike the
-extensively-observed Type Ia SN\,2011fe, the $(B-V)_0$ colors of \abc\ are
-blue and nearly constant in the days after explosion. We show that our early
-observations of \abc\ cannot be explained by either SN shock breakout and the
-associated, subsequent cooling, or the SN ejecta colliding with a stellar
-companion. Instead, we argue that the early characteristics of \abc,
-including: (i) the rapid, near-linear rise, (ii) the non-evolving blue colors,
-and (iii) the strong \textbf{\ion{C}{2}} absorption, are the result of either
-\textbf{ejecta interaction with nearby, unbound material or vigorous mixing of
-radioactive $^{56}$Ni in the SN ejecta,} or a combination of the two. In the
-next few years, dozens of very young \textit{normal} SNe Ia will be
-discovered, and observations similar to those presented here will constrain
-the white dwarf explosion mechanism.
+light for the SN, \textbf{that is when the SN could have first been detected
+by our survey}, \textbf{occurred only} $0.15\pm_{0.07}^{0.15}$\,d before our
+first detection. In the $\sim$24\,hr after discovery, \abc\ rose by
+$\sim$2\,mag, \textbf{featuring} a near-linear rise in flux for $\gtrsim$3 d.
+\textbf{Early spectra show strong \ion{C}{2} absorption, which disappears
+after $\sim$7\,d.} Unlike the extensively-observed Type Ia SN\,2011fe, the
+$(B-V)_0$ colors of \abc\ are blue and nearly constant in the days after
+explosion. We show that our early observations of \abc\ cannot be explained by
+either SN shock breakout and the associated, subsequent cooling, or the SN
+ejecta colliding with a stellar companion. Instead, we argue that the early
+characteristics of \abc, including: (i) the rapid, near-linear rise, (ii) the
+non-evolving blue colors, and (iii) the strong \textbf{\ion{C}{2}} absorption,
+are the result of either \textbf{ejecta interaction with nearby, unbound
+material or vigorous mixing of radioactive $^{56}$Ni in the SN ejecta,} or a
+combination of the two. In the next few years, dozens of very young
+\textit{normal} SNe Ia will be discovered, and observations similar to those
+presented here will constrain the white dwarf explosion mechanism.
 

### 2017-11-23 doc/ms.tex
Correct a minor typo

@@
 $^{56}$Co.} If the mixing is weak and the $^{56}$Ni is confined to the
-innermost layers of the ejecta, the dark phase can last for several days.
+innermost layers of the ejecta, the dark phase can last several days.
 \textbf{Weak mixing} results in redder colors and a more moderate rise in
